### 2023-10-16 lqg-strings.tex
Started main latex file, added Luigi's notes

\RequirePackage{snapshot}
\RequirePackage[final]{graphicx}
\documentclass[twocolumn,final,aps,nofootinbib,nobibnotes]{revtex4-2}

% revtex4 imports the natbib package which conflicts with biblatex. To remedy the resulting name conflicts the following recipe is taken from https://tex.stackexchange.com/a/37077
% Start of 'ignore natbib' hack
%\let\bibhang\relax
%\let\citename\relax
%\let\bibfont\relax
%\let\Citeauthor\relax
%\let\textcite\relax
%\makeatletter
%\DeclareRobustCommand{\MakeUppercase}[1]{{%
%      \def\i{I}\def\j{J}%
%      \def\reserved@a##1##2{\let##1##2\reserved@a}%
%      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
%      \protected@edef\reserved@a{\uppercase{#1}}%
%      \reserved@a
%   }}
%\DeclareRobustCommand{\MakeLowercase}[1]{{%
%      \def\reserved@a##1##2{\let##2##1\reserved@a}%
%      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
%      \protected@edef\reserved@a{\lowercase{#1}}%
%      \reserved@a
%   }}
%\makeatother
%\expandafter\let\csname ver@natbib.sty\endcsname\relax
% End of 'ignore natbib' hack

%\usepackage{graphicx}

\usepackage{amsmath,amssymb,amsfonts,amsthm}
%\usepackage[sort&compress,numbers]{natbib}
%\usepackage[english]{babel}

\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[colorinlistoftodos, shadow, textsize=small, obeyDraft]{todonotes}

\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,final]{hyperref}
%\usepackage{hyperref}

%\usepackage{hypernat}

\usepackage{comment}

% Biblatex setup
% The default is the 'numerical' style.
%\usepackage[backend=biber,url=true,eprint=true,doi=true,sorting=none,backref=true,style=phys]{biblatex}
% We use the following bibliography databases:
%\usepackage{bibtex}
%\addbibresource{../bib_library.bib}
% End biblatex

%%% BEGIN Custom commands %%%
\newcommand{\bite}{\begin{itemize}}
	\newcommand{\eat}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
	\newcommand{\eeq}{\end{equation}}
\newcommand{\rarrow}{\rightarrow}
\newcommand{\beqa}{\begin{align}}
	\newcommand{\eeqa}{\end{align}}
\newcommand{\barr}{\begin{array}}
	\newcommand{\earr}{\end{array}}
\newcommand{\del}{\partial}
\newcommand{\de}{\mathrm{d}}
%\newcommand{\mu\nu}{{\mu\nu}}
\renewcommand{\th}{\mathrm{th}}
\newcommand{\com}[1]{\begin{itemize}\color{RED}{{#1}}\end{itemize}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\btw}[1]{\color{PURPLE}{{#1}}\color{BLACK}}
\newcommand{\cut}[1]{\color{RED}{{#1}}\color{BLACK}}

%text
\newcommand{\ie}{\textit{i.e.}~}
\newcommand{\eg}{\textit{e.g.}~}
\newcommand{\wrt}{\textit{w.r.t.}~}
\newcommand{\etc}{\textit{etc.}~}

\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
% \newcommand{\H}{\mathcal{H}}

\newcommand{\bz}{\mathbf{z}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mf}[1]{\mathfrak{#1}}

\newcommand{\unit}[1]{\mathbf{\hat{#1}}}

%% Package bbold for bold identity symbol
\usepackage{bbold}

\newcommand{\id}{\mathbb{1}}

\newcommand{\utilde}[1]{\underaccent{\tilde}{#1}}

\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\bvec}[1]{\boldsymbol{\vec #1}}
\newcommand{\expect}[1]{\langle #1\rangle}
\newcommand{\innerp}[2]{\langle #1 \vert #2 \rangle}
\newcommand{\expectop}[3]{\langle #1 \vert #2 \vert #3 \rangle}
\newcommand{\bra}[1]{\langle #1 \vert}
\newcommand{\ket}[1]{\vert #1 \rangle}
\newcommand{\supersc}[1]{$^{\textrm{#1}}$}
\newcommand{\subsc}[1]{$_{\textrm{#1}}$}
\newcommand{\sltwoc}{\mathfrak{sl}(2,\mathbb{C})}

\newcommand{\norm}[1]{\lVert #1 \rVert}

\newcommand{\rket}[1]{\vert #1 ]}
\newcommand{\rbra}[1]{[ #1 \vert}

\newcommand{\rinnerp}[2]{[ #1 \vert #2 ]}

\newcommand{\bket}[1]{\vert #1 )}
\newcommand{\bbra}[1]{( #1 \vert}

\newcommand{\binnerp}[2]{( #1 \vert #2 )}

\newcommand{\innerpA}[2]{\langle #1 \vert #2 ]}
\newcommand{\innerpB}[2]{[ #1 \vert #2 \rangle}

\newcommand{\onehalf}{\frac{1}{2}}

\newcommand{\Tr}{\mathrm{Tr}}

\newcommand{\Cyl}{\mathrm{Cyl}}
%%% END Custom commands %%%

\graphicspath{{figures/}}

%opening
\begin{document}

\preprint{This line only printed with preprint option}

\title{Quantizing the Bosonic String on a Loop Quantum Gravity Background}

\author{Deepak Vaid}
\email{dvaid79@gmail.com}
\affiliation{National Institute of Technology, Karnataka, India}
\author{Luigi Teixeira de Sousa}
\email{luigits@estudante.ufscar.br}
\affiliation{Universidade Federal de São Carlos, Brasil}

\date{\today}

\begin{abstract}
	We write down an action for a bosonic string propagating in a bulk background whose geometry is specified in terms of connection and tetrad (or ``vierbein'') variables
\end{abstract}

\maketitle

\tableofcontents

\listoftodos

\end{document}

### 2023-10-23 lqg-strings.tex
Renamed Luigi's notes, added his personal email
Added useful pdf files, started writing intro

@@
 \author{Luigi Teixeira de Sousa}
-\email{luigits@estudante.ufscar.br}
+\email{luigi.tiraque@gmail.com}
 \affiliation{Universidade Federal de São Carlos, Brasil}
@@
 
+\section{Introduction}
+
+``Quantum gravity'' refers to the broad enterprise dedicated to finding a complete, consistent theory in which quantum mechanics coexists peacefully with general relativity.
+There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.
+The first is string theory, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
+However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.
+
+One of the primary criticisms of string theory is its apparent lack of ``background independence''.
+This is more general than the principle of \emph{general covariance} which states that physics should be independent of the choice of co-ordinates.
+Background independence is the statement that any \emph{quantum} theory of gravity - which, presumably, should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry - should provide a description of physics which is independent, not only of the choice of co-ordinates, but also of the choice of background manifold on which those co-ordinates live.
+On the face of it string theory, at least in its conventional form, does not satisfy this principle.
+
+There is an argument to be made that string theory is, in fact, background independent since the equations of motion which arise when
+
+\section{Modified Polyakov Action}
+
+\section{Equations of Motion}
+
+\section{Physical Implications}
+
+\section{Discussion}
+
+\begin{acknowledgments}
+
+\end{acknowledgments}
+
+\appendix
+
+\section{}
+
+\bibliographystyle{JHEP3}
+
+\bibliography{lqg-strings.bib}
+
 \end{document}

### 2023-10-23 lqg-strings.tex
Added to introduction, described problem of background independence in string theory. Started discussion of Hamiltonian vs Lagrangian quantization in preparation of discussion of LQG.

@@
 There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.
-The first is string theory, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
+The first of these is String Theory\footnote{In this work we will capitalize the words ``string theory'' since the second approach in question, loop quantum gravity is usually abbreviated as LQG.}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
 However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.
 
-One of the primary criticisms of string theory is its apparent lack of ``background independence''.
+One of the primary criticisms of String Theory is its apparent lack of ``background independence''.
 This is more general than the principle of \emph{general covariance} which states that physics should be independent of the choice of co-ordinates.
 Background independence is the statement that any \emph{quantum} theory of gravity - which, presumably, should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry - should provide a description of physics which is independent, not only of the choice of co-ordinates, but also of the choice of background manifold on which those co-ordinates live.
-On the face of it string theory, at least in its conventional form, does not satisfy this principle.
+On the face of it String Theory, at least in its conventional form, does not satisfy this principle.
 
-There is an argument to be made that string theory is, in fact, background independent since the equations of motion which arise when
+It is sometimes argued that String Theory is, in fact, background independent since the equations of motion which arise when the (Bosnic) string is coupled to the metric of the ``worldvolume'' (the background manifold in which the string is propagating) turn out to include Einstein's field equations for gravity.
+In  other words, Weyl invariance - one of the fundamental symmetries of the string worldsheet, \emph{requires} \todo{insert refs} that the background geometry must satisfy Einstein's equations.
+While technically correct, it begs the question, if general relativity ``emerges'' from String Theory then why is it not possible to quantize the string on an arbitrary background to begin with?
+As anybody who has studied the basics of String Theory knows, the standard quantization procedure \emph{assumes} that the worldvolume has a flat metric.
+It is, thus far, not technically feasible to do away with this assumption.
+
+There is another sense in which String Theory falls short of being a theory of quantum gravity.
+This, however, rests upon a philosophical perspective, about the nature of quantum gravity, which one may or may not choose to subscribe to.
+This is the viewpoint that in any quantum theory of gravity, geometry itself must be quantized.
+Again, one might say that gravitons - the quantum perturbations of the metric - are ``quanta of geometry''.
+However, gravitons \emph{live} upon some background manifold.
+Moreover, as mentioned, they are \emph{perturbative} by construction.
+Gravitons cannot provide a quantum description of geometry, anymore than quantizing water waves can provide a picture of the molecular structure of water\footnote{This viewpoint has been most clearly articulated by Jacobson \todo{insert ref}}.
+These considerations bring us to the second major\footnote{the characterization of LQG as a ``major'' approach is the our choice and not necessarily reflective of the consensus in the broader quantum gravity community.} approach towards a quantum theory of gravity, known as Loop Quantum Gravity or LQG for short.
+
+LQG arose almost by accident, something it has in common with String Theory.
+Traditionally, there are two ways in which a classical theory can be quantized.
+These are the Hamiltonian and Lagrangian approaches.
+The Lagrangian or path integral approach follows the prescription first suggested by Dirac and then made concrete by Feynman.
+There one views the classical action associated to a given evolution as corresponding to a \emph{phase angle} which determines the complex weight of the associated evolution.
+
+Prior to the advent of String Theory a great deal of effort was put into attempting to quantize gravity in exactly the same way as theories such as electrodynamics and the weak interaction had been successfuly quantized previously, leading to the triumphant prediction of the existence of the positron by Dirac
 

### 2023-10-24 lqg-strings.tex
Added pdf on deriving GR from string theory and completed LQG portion of intro.

@@
 There one views the classical action associated to a given evolution as corresponding to a \emph{phase angle} which determines the complex weight of the associated evolution.
+This approach respects spacetime covariance since here the central object is the action which is invariant under spacetime transformations by construction.
+The Hamiltonian approach, on the other hand, involves making a choice of a spacelike surface $\Sigma_t$ and a corresponding timelike vector $t^\mu$, normal to $\Sigma_t$ (here $t$ is a continuous parameter which labels the family of surfaces).
+This approach, therefore, necessarily does not respect spacetime covariance since it involves making a specific choice of the foliation of the background into spacelike surfaces.
 
-Prior to the advent of String Theory a great deal of effort was put into attempting to quantize gravity in exactly the same way as theories such as electrodynamics and the weak interaction had been successfuly quantized previously, leading to the triumphant prediction of the existence of the positron by Dirac
+In the decades prior to the advent of String Theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches.
+The Hamiltonian approach involves, as stated earlier, a choice of the foliation of the background geometry into a collection of spacelike surfaces $\Sigma_t$.
+Central to this approach was the ADM (Arnowitt-Deser-Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein-Hilbert action $S_{EH}$.
+The resulting phase is co-ordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of a the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following.
+Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}.
+The gravity Hamiltonian turns out to be a sum of two constraints known as the diffeomorphism (or ``momentum'') constraint $H_{diff}$ and the Hamiltonian constraint $H_{ham}$:
+
+\begin{equation}
+	H_{GR} = H_{diff} + H_{ham},
+\end{equation}
+
+and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$.
+The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$ , must be annihilated by these constraints:
+
+\begin{equation}
+	H_{GR} \ket{\Psi_{phys}} \equiv 0
+\end{equation}
+
+While this procedure is straightforward in principle, in practice is was impossible to implement in the quantum theory due to highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
+This unfortunate state of affairs persisted until the 1980s when Abhay Ashtekar recast general relativity as a theory of a Minkowski tetrad $E^I_\mu$ and a self-dual $\sltwoc$ connection $A_\mu^{IJ}$.
+Ashtekar realised that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables.
+It was quickly realised by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states.
+
+Following this, work by Rovelli and Smolin \todo{insert ref} and by Ashtekar, Rovelli and Smolin demonstrated the most remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two dimensional surfaces and volumes of three dimensional regions.
+Moreover, these operators could be diagonlized exactly in the spin-network basis and a lower bound on the smallest possible quantum of area and quantum of volume could be derived.
+This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression.
 

### 2023-10-29 lqg-strings.tex
Added Polyakov action, argument for "emergent gravity" in string theory and reference to Friedan's thesis.

@@
 
-\section{Modified Polyakov Action}
+\section{Strings in Background Fields and Emergent Gravity}
+
+Let us begin by recalling the Polyakov action for the bosonic string.
+
+\begin{equation}\label{eqn:polyakov-flat}
+	S_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
+\end{equation}
+Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.
+
+Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
+Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
+
+The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$.
+Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background.
+It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds.
+The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
+
+\begin{equation}\label{eqn:polyakov-gravity}
+	S'_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
+\end{equation}
+
+where the bulk metric is now a function of the bulk co-ordinates $G_{\mu\nu}(X)$.
+Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$.
+However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string.
+One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.
+
+Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), that the garviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry.
+The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
+\begin{equation}\label{eqn:ricci-flat}
+	\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
+\end{equation}
+Therefore we find that conformal invariance of the string worldsheet \emph{implies} that the background geometry in which the string propagates satisfies the \emph{vacuum} Einstein equations.
+It is this result which is often cited as evidence for the claim that string theory is a \emph{background independent} theory of quantum gravity.
 

### 2023-10-30 lqg-strings.tex
Completed section on motivation for new approach, added more refs to bib file.

@@
 \RequirePackage[final]{graphicx}
-\documentclass[twocolumn,final,aps,nofootinbib,nobibnotes]{revtex4-2}
+\documentclass[twocolumn,draft,aps,nofootinbib,nobibnotes]{revtex4-2}
 
@@
 \usepackage{xcolor}
-\usepackage[colorinlistoftodos, shadow, textsize=small, obeyDraft]{todonotes}
+\usepackage[colorinlistoftodos, shadow, textsize=small, obeyDraft,loadshadowlibrary]{todonotes}
+
+\setlength{\emergencystretch}{2em}
 
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 
@@
 
-\section{Strings in Background Fields and Emergent Gravity}
+\section{Strings in Background Fields and Emergent Gravity}\label{sec:strings-gravity}
 
@@
 
-\section{Equations of Motion}
+In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent. Our reasons are the following:
+
+\begin{enumerate}[itemsep=0.5em]
+	\item While the conformal invariance of the string worldsheet implies that the background is Ricci flat, this, in itself, is not very surprising.
+After all conformal invariance of worldsheet is equivalent to the statement of diffeomorphism invariance of the worldsheet, and in order for this to be consistent with the bulk geometry, the bulk geometry should also have a description in terms of diffeomorphism invariant physics.
+The simplest form of this requirement is that the background should satisfy the vacuum Einstein equations \todo{Does this make sense?
+Check!}.
+	\item One can ask what is the quantum mechanical description of the bulk geometry?
+It is often suggested that the bulk geometry corresponds to a coherent state or a graviton condensate, where the graviton are themselves excitations of the fundamental string.
+However, there does not appear to be an actual mathematical realization of this statement in terms of non-perturbative physics.
+	\item Finally, as mentioned in the introduction, in any \emph{quantum} theory of gravity one would expect to be able to describe the ``atoms of geometry''.
+There is no sense in which this is realised in this picture of gravity emerging from stringy physics.
+Even though one can calculate higher order corrections to the graviton beta function and this provides us with the quantum corrected effective action for the bulk geometry, all the physical quantities are still defined in terms of continuous fields such as the metric.
+For \eg, to the best of our knowledge, there is no clear sense in which one construct a \emph{non-perturbative} state which corresponds to a superposition of geometries using the quantum theory of a bosonic string alone.
+\end{enumerate}
+
+Despite all the concerns string theory has emerged as the primary candidate for a theory of quantum gravity.
+There are good reasons for this.
+AdS/CFT - the most concrete version of a \emph{non-perturbative} theory of quantum gravity - arose out of string theory.
+AdS/CFT is also far from being a complete quantum theory of quantum gravity.
+Our universe, for instance, is described by a positive cosmological constant $\Lambda > 0$ rather than $\Lambda < 0$ as is implied by the ``Anti-deSitter'' part of the correspondence.
+However, the correspondence has passed numerous checks and is now considered part of the established canon.
+Moreoever, it has led to numerous theoretical insights.
+We have gained a deep understanding of the properties of real world systems referred to as ``strange metals'' \todo{insert refs} by studying their dual gravitational theories.
+The significance of quantum error correction and quantum information for a theory of quantum gravity was also first most clearly illuminated via AdS/CFT \todo{insert refs}.
+For these, are other reasons too numerous to mention here, most theorists still regard string theory as the primary (or even the sole) candidate for a theory of quantum gravity.
+
+On the other hand LQG is also built upon a rigorous mathematical framework which follows the well-established rules of quantization\footnote{Though there are those who disagree with this assertion \todo[inline]{insert refs}}.
+Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
+
+Thus, we are now at an impasse.
+We have two theories, both built upon rigorous mathematical foundations, but which do not appear to be concordant with each other.
+There are two possibilities.
+The first is that one of the two approaches is fundamentally flawed in some way and must be rejected.
+The second is that we are missing some crucial ingredient which would allow us to find a missing link between the two theories.
+We feel that it worthwhile to explore the second option in greater detail, if for no other reason then to rule out the possibility of such a link between these two theories.
+
+\section{Strings and Quantum Geometry}\label{sec:string-geometry}
+
+\section{Equations of Motion}\label{sec:eom}
 

### 2023-11-05 lqg-strings.tex
Started work on building new action for lqg string

@@
 There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.
-The first of these is String Theory\footnote{In this work we will capitalize the words ``string theory'' since the second approach in question, loop quantum gravity is usually abbreviated as LQG.}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
+The first of these is string theory, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
 However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.
 
-One of the primary criticisms of String Theory is its apparent lack of ``background independence''.
+One of the primary criticisms of string theory is its apparent lack of ``background independence''.
 This is more general than the principle of \emph{general covariance} which states that physics should be independent of the choice of co-ordinates.
 Background independence is the statement that any \emph{quantum} theory of gravity - which, presumably, should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry - should provide a description of physics which is independent, not only of the choice of co-ordinates, but also of the choice of background manifold on which those co-ordinates live.
-On the face of it String Theory, at least in its conventional form, does not satisfy this principle.
+On the face of it string theory, at least in its conventional form, does not satisfy this principle.
 
-It is sometimes argued that String Theory is, in fact, background independent since the equations of motion which arise when the (Bosnic) string is coupled to the metric of the ``worldvolume'' (the background manifold in which the string is propagating) turn out to include Einstein's field equations for gravity.
+It is sometimes argued that string theory is, in fact, background independent since the equations of motion which arise when the (Bosnic) string is coupled to the metric of the ``worldvolume'' (the background manifold in which the string is propagating) turn out to include Einstein's field equations for gravity.
 In  other words, Weyl invariance - one of the fundamental symmetries of the string worldsheet, \emph{requires} \todo{insert refs} that the background geometry must satisfy Einstein's equations.
-While technically correct, it begs the question, if general relativity ``emerges'' from String Theory then why is it not possible to quantize the string on an arbitrary background to begin with?
-As anybody who has studied the basics of String Theory knows, the standard quantization procedure \emph{assumes} that the worldvolume has a flat metric.
+While technically correct, it begs the question, if general relativity ``emerges'' from string theory then why is it not possible to quantize the string on an arbitrary background to begin with?
+As anybody who has studied the basics of string theory knows, the standard quantization procedure \emph{assumes} that the worldvolume has a flat metric.
 It is, thus far, not technically feasible to do away with this assumption.
 
-There is another sense in which String Theory falls short of being a theory of quantum gravity.
+There is another sense in which string theory falls short of being a theory of quantum gravity.
 This, however, rests upon a philosophical perspective, about the nature of quantum gravity, which one may or may not choose to subscribe to.
@@
 Moreover, as mentioned, they are \emph{perturbative} by construction.
-Gravitons cannot provide a quantum description of geometry, anymore than quantizing water waves can provide a picture of the molecular structure of water\footnote{This viewpoint has been most clearly articulated by Jacobson \todo{insert ref}}.
+Gravitons cannot provide a quantum description of geometry, anymore than quantizing water waves can provide a picture of the molecular structure of water\footnote{This viewpoint has been most clearly articulated by Jacobson \cite{Jacobson1995Thermodynamics}}.
 These considerations bring us to the second major\footnote{the characterization of LQG as a ``major'' approach is the our choice and not necessarily reflective of the consensus in the broader quantum gravity community.} approach towards a quantum theory of gravity, known as Loop Quantum Gravity or LQG for short.
 
-LQG arose almost by accident, something it has in common with String Theory.
+LQG arose almost by accident, something it has in common with string theory.
 Traditionally, there are two ways in which a classical theory can be quantized.
@@
 
-In the decades prior to the advent of String Theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches.
+In the decades prior to the advent of string theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches.
 The Hamiltonian approach involves, as stated earlier, a choice of the foliation of the background geometry into a collection of spacelike surfaces $\Sigma_t$.
@@
 This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression.
+
+\todo[inline]{Insert brief intro to spin nets}
 
@@
 
+Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vierbein fields $E_\mu^I$.
+Further we will require that the bulk connection and the bulk vierbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued one-form fields $X^\mu_I$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^\mu_I$ with $X^\mu_i$.
+\begin{equation}\label{eqn:lqg-string-action}
+	S_{PA} = -\frac{T}{2} \int d\tau \wedge d\sigma\,e\,e^a_i\,e^b_j \, D_a X^\mu_i D_b X^\nu_j E_\mu^I E_{\nu I},
+\end{equation}
+where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
+\begin{equation}\label{eqn:worldsheet-deriv}
+	D_a X^\mu_i = \partial_a X^\mu_i + \omega_{a\,i}{}^j X^\mu_j,
+\end{equation}
+where $\omega_{a\,i}{}^j$ is the pullback of the bulk connection to the worldsheet.
+
 \section{Equations of Motion}\label{sec:eom}

### 2023-11-05 lqg-strings.tex
AddedCommands
SwappedPositionOfInternalIndicesForXFields

@@
 \newcommand{\Cyl}{\mathrm{Cyl}}
+
+%Luigi's custom commands
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\diff}{\mathrm{d}}
+\newcommand{\inp}{\mathrm{i}}
+\newcommand{\e}{\mathrm{e}}
+\newcommand{\Lagr}{\mathscr{L}}
+\newcommand{\PS}{\mathcal{P}}
 %%% END Custom commands %%%
@@
 
-Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vierbein fields $E_\mu^I$.
-Further we will require that the bulk connection and the bulk vierbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued one-form fields $X^\mu_I$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^\mu_I$ with $X^\mu_i$.
+Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
+Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
 \begin{equation}\label{eqn:lqg-string-action}
-	S_{PA} = -\frac{T}{2} \int d\tau \wedge d\sigma\,e\,e^a_i\,e^b_j \, D_a X^\mu_i D_b X^\nu_j E_\mu^I E_{\nu I},
+	S_{PA} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma\,e\,e^a_i\,e^b_j \, D_a X^{\mu i} D_b X^{\nu j} E_\mu^I E_{\nu I},
 \end{equation}
@@
 \begin{equation}\label{eqn:worldsheet-deriv}
-	D_a X^\mu_i = \partial_a X^\mu_i + \omega_{a\,i}{}^j X^\mu_j,
+	D_a X^{\mu i} = \partial_a X^{\mu i} + \omega_{a\,j}^i X^{\mu j},
 \end{equation}
-where $\omega_{a\,i}{}^j$ is the pullback of the bulk connection to the worldsheet.
+where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
 

### 2023-11-07 lqg-strings.tex
Added wedge in flat-space Polyakov action and made d's non-curly (sorry I have this habit of differential d being straight)
Did same as before to curved-space Polyakov action
Made omega's in the text have  internal2 indices to match eq(7)

@@
 \begin{equation}\label{eqn:polyakov-flat}
-	S_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
+	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
 \end{equation}
@@
 \begin{equation}\label{eqn:polyakov-gravity}
-	S'_{P} = -\frac{T}{2} \int d\tau d\sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
+	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
 \end{equation}
@@
 Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
+In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
 \begin{equation}\label{eqn:lqg-string-action}

### 2023-11-07 lqg-strings.tex
Mentioned the new internal WS fields in the text

@@
 Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
+In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $X^{\mu} \equiv X^{\mu} _{i} v^{i}$.
 \begin{equation}\label{eqn:lqg-string-action}

### 2023-11-07 lqg-strings.tex
Rewritten modified Polyakov action and action of covariant derivative, also added in text e = det(e)

@@
 \begin{equation}\label{eqn:lqg-string-action}
-	S_{PA} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma\,e\,e^a_i\,e^b_j \, D_a X^{\mu i} D_b X^{\nu j} E_\mu^I E_{\nu I},
+	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} (X^{\mu} _{k} v^{k}) D_{b} (X^{\nu} _{l} v^{l}) E_{\mu} ^{I} E_{\nu I} ,
 \end{equation}
-where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
-\begin{equation}\label{eqn:worldsheet-deriv}
-	D_a X^{\mu i} = \partial_a X^{\mu i} + \omega_{a\,j}^i X^{\mu j},
-\end{equation}
+where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
+\begin{align}\label{eqn:worldsheet-deriv}
+	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} \ , \\
+	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} \ ,
+\end{align}
+
 where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

### 2023-11-07 lqg-strings.tex
Removed indent after eqs(7-8)
Added tilde notation to embedding fields, action did not fit in line in more explicit form

@@
 In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $X^{\mu} \equiv X^{\mu} _{i} v^{i}$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
 \begin{equation}\label{eqn:lqg-string-action}
-	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} (X^{\mu} _{k} v^{k}) D_{b} (X^{\nu} _{l} v^{l}) E_{\mu} ^{I} E_{\nu I} ,
+	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E_{\mu} ^{I} E_{\nu I} ,
 \end{equation}
@@
 \end{align}
-
 where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

### 2023-11-07 lqg-strings.tex
Removed some spaces I put by habit after equations
Started EoMs section, added the dyad EoM and it's implication for the form of the dyad

@@
 \begin{align}\label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} \ , \\
-	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} \ ,
+	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} , \\
+	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} ,
 \end{align}
@@
 \section{Equations of Motion}\label{sec:eom}
+
+\subsection{The Dyad Equation}\label{subsec:dyad-eom}
+
+Variation of the modified Polyakov action(\ref{eqn:lqg-string-action}) w.r.t the zweibein $e^{c} _{k}$ yields the vanishing of the Lie algebra-valued energy-momentum tensor, which can be contracted with the dyad to yield the regular stress-energy tensor:
+\begin{equation} \label{eqn:variation-wrt-e}
+	\frac{\delta S_{PA}}{\delta e^{c} _{k}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{equation} \label{eqn:vanishing-em-tensor}
+	T^{k} _{c} := E^{I} _{\mu} E_{\nu I} (e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} -
+\end{equation}
+\begin{equation*}
+	- e^{k} _{c} e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu}) = 0 .
+\end{equation*}
+Equation(\ref{eqn:vanishing-em-tensor}) can be used to obtain an expression for the dyads in terms of the string coordinates $\Tilde{X}^{\mu}$ as in
+\begin{equation} \label{eqn:dyad-string-coordinates}
+	e^{k} _{c} = F e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} ,
+\end{equation}
+where the function $F$ is given by
+\begin{equation} \label{eqn:F-function-dyad}
+	\frac{1}{F} = e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} .
+\end{equation}
 

### 2023-11-07 lqg-strings.tex
Corrected a single index omega in the text

@@
 Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
-Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
 In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.

### 2023-11-08 lqg-strings.tex
Undid tilde notation for derivatives to act just on X rather than Xv

@@
 However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
-\begin{equation}\label{eqn:lqg-string-action}
-	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E_{\mu} ^{I} E_{\nu I} ,
-\end{equation}
+\begin{multline}\label{eqn:lqg-string-action}
+	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
+	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
+\end{multline}
 where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
@@
 
-Variation of the modified Polyakov action(\ref{eqn:lqg-string-action}) w.r.t the zweibein $e^{c} _{k}$ yields the vanishing of the Lie algebra-valued energy-momentum tensor, which can be contracted with the dyad to yield the regular stress-energy tensor:
+Variation of the modified Polyakov action(\ref{eqn:lqg-string-action}) w.r.t the zweibein $e^{c} _{l}$ yields the vanishing of the Lie algebra-valued energy-momentum tensor, which can be contracted with the dyad to yield the regular stress-energy tensor:
 \begin{equation} \label{eqn:variation-wrt-e}
-	\frac{\delta S_{PA}}{\delta e^{c} _{k}} \overset{!}{=} 0
+	\frac{\delta S_{PA}}{\delta e^{c} _{l}} \overset{!}{=} 0
 \end{equation}
@@
 \end{equation*}
-\begin{equation} \label{eqn:vanishing-em-tensor}
-	T^{k} _{c} := E^{I} _{\mu} E_{\nu I} (e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} -
-\end{equation}
-\begin{equation*}
-	- e^{k} _{c} e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu}) = 0 .
-\end{equation*}
-Equation(\ref{eqn:vanishing-em-tensor}) can be used to obtain an expression for the dyads in terms of the string coordinates $\Tilde{X}^{\mu}$ as in
+\begin{multline} \label{eqn:vanishing-em-tensor}
+	T^{l} _{c} := E^{I} _{\mu} E_{\nu I} (e^{a l} D_{a} X^{\mu} _{j} v^{j} D_{c} X^{\nu} _{k} v^{k} - \\
+	- e^{l} _{c} e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k}) = 0 .
+\end{multline}
+Equation(\ref{eqn:vanishing-em-tensor}) can be used to obtain an expression for the dyads in terms of the embbeding fields $X^{\mu} _{i}$ as in
 \begin{equation} \label{eqn:dyad-string-coordinates}
-	e^{k} _{c} = F e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} ,
+	e^{l} _{c} = F e^{a l} D_{a} X^{\mu} _{j} v^{j} D_{c} X^{\nu} _{k} v^{k} E^{I} _{\mu} E_{\nu I} ,
 \end{equation}
@@
 \begin{equation} \label{eqn:F-function-dyad}
-	\frac{1}{F} = e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} .
+	\frac{1}{F} = e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k} E^{I} _{\mu} E_{\nu I} .
 \end{equation}

### 2023-11-08 lqg-strings.tex
Removed derivative acting on v on eq(7)

@@
 However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
-\begin{multline}\label{eqn:lqg-string-action}
+\begin{multline} \label{eqn:lqg-string-action}
 	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
@@
 where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
-\begin{align}\label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} , \\
-	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} ,
-\end{align}
+\begin{equation} \label{eqn:worldsheet-deriv}
+	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
+\end{equation}
 where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

### 2023-11-09 lqg-strings.tex
Added connection EoM section to main file
Added new field EoM section

@@
 
+\subsection{The Connection Equation} \label{sec:omega-eom}
+
+Varying our action w.r.t connection $\omega ^{m n} _{c}$ gives the vanishing of world-sheet torsion $\mathcal{T}^{i} _{a b}$ as
+\begin{equation} \label{eqn:variation-wrt-omega}
+	\frac{\delta S_{P A}}{\delta \omega ^{m n} _{c}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{equation} \label{eqn:vanishing-torsion}
+	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} G_{\mu \nu} = 0 .
+\end{equation}
+
+\subsection{The New Field Equation} \label{sec:v-eom}
+
+The equation of motion for the new field $v^{l}$ gives a constraint on said field and the embbeding fields $X^{\mu} _{i}$
+\begin{equation} \label{eqn:variation-wrt-v}
+	\frac{\delta S_{P A}}{\delta v^{l}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{equation} \label{eqn:v-and-X-constraint}
+	g^{a b} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} G_{\mu \nu} = 0 .
+\end{equation}
+
 \section{Physical Implications}

### 2023-11-17 lqg-strings.tex
Swapped metrics for vielbeins in eqs(13) and (15)
Sketched X EoM and added the section for said EoM in the main file
Started new branch, added section on corrected Nambu-Goto action.

@@
 
+Before proceeding let us state our ``central dogma''.
+We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators - such as those which measure the area and volume of a given region of space - exist, have discrete spectra and are gapped, \ie, the smallest eigenvalue is greater than zero.
+We now wish to understand how to construct a worldsheet action which will reflect this central dogma.
+
+\section{Modified Nambu Goto Action}\label{sec:modified-ng}
+
+In a very real sense string theory is a quantum theory of geometry. After all, the Nambu-Goto action:
+\begin{equation}\label{eqn:ng-action}
+	S_{NG} = -T \int d^2 x \sqrt{\det h}
+\end{equation}
+is nothing more than the \emph{area} of the string worldsheet.
+So when we are constructing the quantum theory of the string we are constructing a theory in which the fundamental excitations are geometric in nature.
+What we would like to do is to modify the string action in a way which incorporates the insight from LQG that at the Planck scale there is a minimum quantum of area.
+One simple way in which to do this is to modify the integrand in \eqref{eqn:ng-action} as follows:
+\begin{equation*}
+	\sqrt{h} \rightarrow \sqrt{h + g \Delta}.
+\end{equation*}
+Here, $g = l_{pl}/l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a constant which corresponds to the square of the minimal quantum of area.
+In the limit that $l_s \gg l_{pl}$, $g \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
+In this limit we can expand the integrand as follows:
+\begin{equation}
+	\sqrt{h + g \Delta} \sim \sqrt{h}\left(1 + \frac{1}{2} \frac{g \Delta}{h} + \mc{O}(g^2/h^2)\right).
+\end{equation}
+Presumably the limit $g \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\sqrt{h} \gg \Delta$.
+Thus in this limit $ g^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections.
+The final area corrected Nambu-Goto action becomes:
+\begin{equation}
+	S'_{NG} = -T \int d^2 x \left( \sqrt{h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{h}} \right).
+\end{equation}
+This action has, to the best of our knowledge, not been explored in the string theory literature.
+However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections.
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}
@@
 \begin{equation} \label{eqn:vanishing-torsion}
-	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} G_{\mu \nu} = 0 .
+	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} E^{I} _{\mu} E_{\nu I} = 0 .
 \end{equation}
@@
 \begin{equation} \label{eqn:v-and-X-constraint}
-	g^{a b} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} G_{\mu \nu} = 0 .
+	e^{a} _{i} e^{b i} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} E^{I} _{\mu} E_{\nu I} = 0 .
 \end{equation}
+
+\subsection{The Embbeding Field Equation}
+
+Finally, varying the action w.r.t the embbeding fields $X^{\lambda} _{l}$ yields a slightly modified version of the classical equation of motion for strings propagating in curved space-time:
+\begin{equation} \label{eqn:variation-wrt-X}
+	\frac{\delta S_{P A}}{\delta X^{\lambda} _{l}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{multline} \label{eqn:string-eom}
+	e^{a} _{i} e^{b i} D_{b} (e v^{l} D_{a} X^{\mu} _{j} v^{j} E^{I} _{\mu} E_{\lambda I}) = \\
+	= e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k} \frac{\partial E^{I} _{\mu}}{\partial X^{\lambda} _{l}} E_{\nu I} .
+\end{multline}
 

### 2023-11-17 lqg-strings.tex
Just added a bit of context text in the new section and compiled the PDF

@@
 This action has, to the best of our knowledge, not been explored in the string theory literature.
-However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections.
+However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.
 

### 2023-11-17 lqg-strings.tex
Sketched EoM and B.C. for inverse area corrected NG action
Added corrected NG EoM and B.C. to main file

@@
 \usepackage{xcolor}
+\usepackage{mathrsfs}
 \usepackage[colorinlistoftodos, shadow, textsize=small, obeyDraft,loadshadowlibrary]{todonotes}
@@
 \begin{equation}\label{eqn:ng-action}
-	S_{NG} = -T \int d^2 x \sqrt{\det h}
+	S_{NG} = -T \int \diff ^2 x \sqrt{\det h}
 \end{equation}
@@
 The final area corrected Nambu-Goto action becomes:
-\begin{equation}
-	S'_{NG} = -T \int d^2 x \left( \sqrt{h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{h}} \right).
+\begin{equation} \label{eqn:modified-NG-action}
+	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{h}} \right).
 \end{equation}
@@
 However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.
+
+This correction does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+\begin{equation} \label{eqn:modified-NG-eom}
+	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
+\end{equation}
+and
+\begin{equation} \label{eqn:modified-NG-bc}
+	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
+\end{equation}
+where
+\begin{multline} \label{eqn:modified-NG-tau-currents}
+	\PS ^{\tau} _{\mu} = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} = \\
+	= - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{h}} \left( 1 - \frac{g \Delta}{2 h} \right) = \\
+	= \PS ^{\tau} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 h} \right)
+\end{multline}
+\begin{multline} \label{eqn:modified-NG-sigma-currents}
+	\PS ^{\sigma} _{\mu} = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} = \\
+	= - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{h}} \left( 1 - \frac{g \Delta}{2 h} \right) = \\
+	= \PS ^{\sigma} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 h} \right)
+\end{multline}
+and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
 

### 2023-11-17 lqg-strings.tex
Just added the missing - sign in the determinants of h in sec 3
Fixing misplaced parenthesis
Typo fixing
Fixed formatting of multiline equations. Removed unneeded files from tracking.

--- 2023-11-17 lqg-strings.tex
@@
 \begin{equation}\label{eqn:ng-action}
-	S_{NG} = -T \int d^2 x \sqrt{\det h}
+	S_{NG} = -T \int \diff ^2 x \sqrt{- \det h}
 \end{equation}
@@
 \begin{equation*}
-	\sqrt{h} \rightarrow \sqrt{h + g \Delta}.
+	\sqrt{- h} \rightarrow \sqrt{- h + g \Delta}.
 \end{equation*}
@@
 \begin{equation}
-	\sqrt{h + g \Delta} \sim \sqrt{h}\left(1 + \frac{1}{2} \frac{g \Delta}{h} + \mc{O}(g^2/h^2)\right).
+	\sqrt{- h + g \Delta} \sim \sqrt{- h}\left(1 + \frac{1}{2} \frac{g \Delta}{(- h)} + \mc{O}(g^2/h^2)\right).
 \end{equation}
@@
 The final area corrected Nambu-Goto action becomes:
-\begin{equation}
-	S'_{NG} = -T \int d^2 x \left( \sqrt{h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{h}} \right).
+\begin{equation} \label{eqn:modified-NG-action}
+	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{- h}} \right).
 \end{equation}
@@
 However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.
+
+This correction does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+\begin{equation} \label{eqn:modified-NG-eom}
+	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
+\end{equation}
+and
+\begin{equation} \label{eqn:modified-NG-bc}
+	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
+\end{equation}
+where
+\begin{align} \label{eqn:modified-NG-tau-currents}
+	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber \\
+	& = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	& = \PS ^{\tau} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+\begin{align} \label{eqn:modified-NG-sigma-currents}
+	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber \\
+	& = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	& = \PS ^{\sigma} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
 

### 2023-11-18 lqg-strings.tex
Sketched and added to main document the new energy and wave equation in static+transverse gauge

@@
 
+Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+\begin{equation} \label{eqn:string-energy}
+	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \diff s ,
+\end{equation}
+and the form of the wave equation maintains it's shape as in
+\begin{equation} \label{eqn:corrected-NG-wave-equation}
+	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
+\end{equation}
+where the effective mass density and effective tension are given by
+\begin{align}
+	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
+	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
+\end{align}
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}

### 2023-11-18 lqg-strings.tex
Sketched and added to main file further simplifications to the wave equation and modification to wave speed

@@
 
+Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F = (1 - g \Delta / (2 (- h)))$)
+\begin{equation} \label{eqn:sigma-parameterization}
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{F^2} ,
+\end{equation}
+we find the wave equation
+\begin{equation} \label{eqn:simplified-modified-wave-eqn}
+	F^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
+\end{equation}
+from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
+\begin{equation} \label{eqn:wave-speed-corrected}
+	v = \frac{c}{|F|} .
+\end{equation}
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}

### 2023-11-18 lqg-strings.tex
Changed sign in modified NG such that correction factor is always >1

@@
 \begin{equation*}
-	\sqrt{- h} \rightarrow \sqrt{- h + g \Delta}.
+	\sqrt{- h} \rightarrow \sqrt{- (h + g \Delta)}.
 \end{equation*}
@@
 \begin{equation}
-	\sqrt{- h + g \Delta} \sim \sqrt{- h}\left(1 + \frac{1}{2} \frac{g \Delta}{(- h)} + \mc{O}(g^2/h^2)\right).
+	\sqrt{- (h + g \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{g \Delta}{(- h)} + \mc{O}(g^2/h^2)\right).
 \end{equation}
@@
 \begin{equation} \label{eqn:modified-NG-action}
-	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{- h}} \right).
+	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} \frac{g \Delta}{\sqrt{- h}} \right).
 \end{equation}
@@
 	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
-	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 (- h)} \right)
+	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
 \end{align}
@@
 	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
-	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 - \frac{g \Delta}{2 (- h)} \right)
+	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
 \end{align}
@@
 \begin{equation} \label{eqn:string-energy}
-	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \diff s ,
+	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
 \end{equation}
@@
 \begin{align}
-	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
-	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
+	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
+	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
 \end{align}
 
-Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F = (1 - g \Delta / (2 (- h)))$)
+Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F = (1 + g \Delta / (2 (- h)))$)
 \begin{equation} \label{eqn:sigma-parameterization}
@@
 \begin{equation} \label{eqn:wave-speed-corrected}
-	v = \frac{c}{|F|} .
+	v = \frac{c}{F} .
 \end{equation}

### 2023-11-19 lqg-strings.tex
Simplified sigma parameterization in main file
Added portion on duality properties of modified NG action; added files to .gitgnore

@@
 
+The action \eqref{eqn:modified-NG-action} has some interesting properties.
+First, on the face of it it does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
+Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
+However, if we look at that expression we see that it can be written as:
+\begin{equation} \label{eqn:modified-NG-action-v2}
+	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {g \Delta}{\sqrt{- (h^{-1})}} \right),
+\end{equation}
+where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$.
+So, while the second term is not diffeomorphism invariant \wrt the original metric $h_{ab}$ it is clearly diffeomorphism invariant \wrt the inverse metric $h^{ab}$.
+
+Second, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
+If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
+\begin{align} \label{eqn:modified-NG-action-v3}
+	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
+	& = -T' \int \diff ^2 x \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
+\end{align}
+which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} {g \Delta} T $ and $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
+
+\subsection{Modified Equations of Motion}\label{sec:modified-eom}
+
 This correction does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
@@
 \begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{F^2} ,
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{F^2} = \frac{E (q)}{T F^2} ,
 \end{equation}

### 2023-11-19 lqg-strings.tex
Fixed minor formatting errors
Added refs. Described relation to bimetric gravity. Wrote down NG and Polyakov actions for bimetric string. Deleted e.o.m portion for old connection based string action.

@@
 \RequirePackage[final]{graphicx}
-\documentclass[twocolumn,draft,aps,nofootinbib,nobibnotes]{revtex4-2}
+\documentclass[twocolumn,draft,aps,prd,10pt,nofootinbib,nobibnotes]{revtex4-2}
 
@@
 %\usepackage{hyperref}
+
+% Nov 20, 2023
+% Added package mciteplus to collapse multiple papers into one item in bibliography.
+\usepackage{mciteplus}
 
@@
 \newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\mf}[1]{\mathfrak{#1}}
 \newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mf}[1]{\mathfrak{#1}}
 
@@
 %Luigi's custom commands
-\newcommand{\R}{\mathbb{R}}
+% \R is already defined as the same above.
+% \newcommand{\R}{\mathbb{R}}
 \newcommand{\diff}{\mathrm{d}}
@@
 
+Now, one might object and say that having an action which is the sum of Nambu-Goto actions for two different metrics seems strange.
+However, such actions have been extensively studied under the heading of ``bimetric gravity'', with the earliest work dating as far back as 1940 in two papers \cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER').
+In 2010, bimetric gravity gained great popularity due to the seminal paper \cite{de-Rham2011Resummation} which showed that by introducing a second \emph{reference} metric into a model for massive gravity one can get rid of the Boulware-Deser ghost \cite{Boulware1972Can-Gravitation} which otherwise plagues theories with massive gravitons.
+The \emph{reference} metric introduced in the work \cite{de-Rham2011Resummation} was taken to be a flat metric.
+However later work \cite{Hassan2012Bimetric,Hassan2012Ghost-Free} showed that the second metric need not be flat and that an action of the following form:
+\begin{align}\label{eqn:hassan-bimetric}
+	S & = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)} \nonumber \\
+	& + 2 m^2 M^2_{eff} \int \diff^4 x \sqrt{-g}\sum_{n=0}^{4}\beta_n e_n (\sqrt{g^{-1} f}),
+\end{align}
+where $g_{\mu\nu}$ and $f_{\mu\nu}$ are \emph{arbitrary} metrics, $M_g^2, M_f^2$ are the Planck masses for the two sectors respectively.
+$R^{(g)}, R^{(f)}$ are the respective Ricci scalars for each sector.
+The third term is an interaction term which is responsible for making one of the graviton massive while the other remains massless.
+$M^2_{eff}$ is an \emph{effective} Planck mass given by:
+\begin{equation}\label{eqn:hassan-effective-mpl}
+	M^2_{eff} = \left( \frac{1}{M^2_g} + \frac{1}{M^2_f} \right)^{-1}
+\end{equation}
+
+\subsection{The Bimetric String}\label{sec:bimetric-nambu-goto}
+
+It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+We can see that this is indeed the case as follows.
+
+Consider a string propagating in a target space whose geometry is described by two bulk metrics.
+There are two ways that a string with two metrics might arise.
+One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
+As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
+However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
+One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
+\begin{equation}\label{eqn:ws-bimetric-interaction}
+	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
+\end{equation}
+Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
+The resulting action would be of the form:
+\begin{equation}\label{eqn:ws-bimetric-action-v1}
+	S_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
+\end{equation}
+Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
+
+The second possibility is the following.
+Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
+As a result we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
+\begin{subequations}\label{eqn:ws-induced-metrics}
+	\begin{align}
+		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu} \\
+		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
+	\end{align}
+\end{subequations}
+We can then write down the combined action for the string worldsheet as:
+\begin{equation}\label{eqn:ws-bimetric-action-v2}
+	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
+\end{equation}
+where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
+
+\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
+
+The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics, unless these are included in the interaction term $S'_{int}$.
+One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
+
+Following the general procedure, given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
+\begin{equation}\label{eqn:polyakov-curved}
+	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
+\end{equation}
+where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
+\begin{align}\label{eqn:polyakov-flat}
+	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber \\
+	& -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
+\end{align}
+
 \subsection{Modified Equations of Motion}\label{sec:modified-eom}
@@
 \begin{equation} \label{eqn:wave-speed-corrected}
-	v = \frac{c}{F} .
+	v = \frac{c}{F}.
 \end{equation}
@@
 \begin{equation} \label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
+	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
 \end{equation}
 where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
-
-\section{Equations of Motion}\label{sec:eom}
-
-\subsection{The Dyad Equation}\label{subsec:dyad-eom}
-
-Variation of the modified Polyakov action(\ref{eqn:lqg-string-action}) w.r.t the zweibein $e^{c} _{l}$ yields the vanishing of the Lie algebra-valued energy-momentum tensor, which can be contracted with the dyad to yield the regular stress-energy tensor:
-\begin{equation} \label{eqn:variation-wrt-e}
-	\frac{\delta S_{PA}}{\delta e^{c} _{l}} \overset{!}{=} 0
-\end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
-\begin{multline} \label{eqn:vanishing-em-tensor}
-	T^{l} _{c} := E^{I} _{\mu} E_{\nu I} (e^{a l} D_{a} X^{\mu} _{j} v^{j} D_{c} X^{\nu} _{k} v^{k} - \\
-	- e^{l} _{c} e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k}) = 0 .
-\end{multline}
-Equation(\ref{eqn:vanishing-em-tensor}) can be used to obtain an expression for the dyads in terms of the embbeding fields $X^{\mu} _{i}$ as in
-\begin{equation} \label{eqn:dyad-string-coordinates}
-	e^{l} _{c} = F e^{a l} D_{a} X^{\mu} _{j} v^{j} D_{c} X^{\nu} _{k} v^{k} E^{I} _{\mu} E_{\nu I} ,
-\end{equation}
-where the function $F$ is given by
-\begin{equation} \label{eqn:F-function-dyad}
-	\frac{1}{F} = e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k} E^{I} _{\mu} E_{\nu I} .
-\end{equation}
-
-\subsection{The Connection Equation} \label{sec:omega-eom}
-
-Varying our action w.r.t connection $\omega ^{m n} _{c}$ gives the vanishing of world-sheet torsion $\mathcal{T}^{i} _{a b}$ as
-\begin{equation} \label{eqn:variation-wrt-omega}
-	\frac{\delta S_{P A}}{\delta \omega ^{m n} _{c}} \overset{!}{=} 0
-\end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
-\begin{equation} \label{eqn:vanishing-torsion}
-	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} E^{I} _{\mu} E_{\nu I} = 0 .
-\end{equation}
-
-\subsection{The New Field Equation} \label{sec:v-eom}
-
-The equation of motion for the new field $v^{l}$ gives a constraint on said field and the embbeding fields $X^{\mu} _{i}$
-\begin{equation} \label{eqn:variation-wrt-v}
-	\frac{\delta S_{P A}}{\delta v^{l}} \overset{!}{=} 0
-\end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
-\begin{equation} \label{eqn:v-and-X-constraint}
-	e^{a} _{i} e^{b i} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} E^{I} _{\mu} E_{\nu I} = 0 .
-\end{equation}
-
-\subsection{The Embbeding Field Equation}
-
-Finally, varying the action w.r.t the embbeding fields $X^{\lambda} _{l}$ yields a slightly modified version of the classical equation of motion for strings propagating in curved space-time:
-\begin{equation} \label{eqn:variation-wrt-X}
-	\frac{\delta S_{P A}}{\delta X^{\lambda} _{l}} \overset{!}{=} 0
-\end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
-\begin{multline} \label{eqn:string-eom}
-	e^{a} _{i} e^{b i} D_{b} (e v^{l} D_{a} X^{\mu} _{j} v^{j} E^{I} _{\mu} E_{\lambda I}) = \\
-	= e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k} \frac{\partial E^{I} _{\mu}}{\partial X^{\lambda} _{l}} E_{\nu I} .
-\end{multline}
 

### 2023-11-20 lqg-strings.tex
Just changed some wording in the beggining of sec 3.C
Added citation in beggining of sec 3.C

@@
 
-This correction does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+Following the procedure done in $\cite{Zwiebach2009A-First}$, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
 \begin{equation} \label{eqn:modified-NG-eom}

### 2023-11-20 lqg-strings.tex
Reorganized the main file sections and swapped x for y in the integration variable in first term of eq (25)

@@
 
-\subsection{The Bimetric String}\label{sec:bimetric-nambu-goto}
-
-It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
-We can see that this is indeed the case as follows.
-
-Consider a string propagating in a target space whose geometry is described by two bulk metrics.
-There are two ways that a string with two metrics might arise.
-One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
-As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
-However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
-One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
-\begin{equation}\label{eqn:ws-bimetric-interaction}
-	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
-\end{equation}
-Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
-The resulting action would be of the form:
-\begin{equation}\label{eqn:ws-bimetric-action-v1}
-	S_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
-\end{equation}
-Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
-
-The second possibility is the following.
-Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
-As a result we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
-\begin{subequations}\label{eqn:ws-induced-metrics}
-	\begin{align}
-		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
-		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
-	\end{align}
-\end{subequations}
-We can then write down the combined action for the string worldsheet as:
-\begin{equation}\label{eqn:ws-bimetric-action-v2}
-	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
-\end{equation}
-where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
-
-\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
-
-The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics, unless these are included in the interaction term $S'_{int}$.
-One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
-
-Following the general procedure, given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
-\begin{equation}\label{eqn:polyakov-curved}
-	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
-\end{equation}
-where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{align}\label{eqn:polyakov-flat}
-	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber \\
-	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
-\end{align}
-
 \subsection{Modified Equations of Motion}\label{sec:modified-eom}
@@
 
+\section{The Bimetric String}\label{sec:bimetric-nambu-goto}
+
+It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+We can see that this is indeed the case as follows.
+
+Consider a string propagating in a target space whose geometry is described by two bulk metrics.
+There are two ways that a string with two metrics might arise.
+One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
+As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
+However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
+One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
+\begin{equation}\label{eqn:ws-bimetric-interaction}
+	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
+\end{equation}
+Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
+The resulting action would be of the form:
+\begin{equation}\label{eqn:ws-bimetric-action-v1}
+	S_{BNG} = -T \int \diff^2 y \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
+\end{equation}
+Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
+
+The second possibility is the following.
+Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
+As a result we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
+\begin{subequations}\label{eqn:ws-induced-metrics}
+	\begin{align}
+		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
+		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
+	\end{align}
+\end{subequations}
+We can then write down the combined action for the string worldsheet as:
+\begin{equation}\label{eqn:ws-bimetric-action-v2}
+	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
+\end{equation}
+where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
+
+\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
+
+The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics, unless these are included in the interaction term $S'_{int}$.
+One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
+
+Following the general procedure, given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
+\begin{equation}\label{eqn:polyakov-curved}
+	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
+\end{equation}
+where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
+\begin{align}\label{eqn:polyakov-flat}
+	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber \\
+	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
+\end{align}
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}

### 2023-11-20 lqg-strings.tex
Swapped y back for x in eq(25)
Added bimetric Polyakov EoMs to main file

@@
 $R^{(g)}, R^{(f)}$ are the respective Ricci scalars for each sector.
-The third term is an interaction term which is responsible for making one of the graviton massive while the other remains massless.
+The third term is an interaction term which is responsible for making one of the gravitons massive while the other remains massless.
 $M^2_{eff}$ is an \emph{effective} Planck mass given by:
@@
 \end{equation}
-and the form of the wave equation maintains it's shape as in
+and the form of the wave equation maintains its shape as in
 \begin{equation} \label{eqn:corrected-NG-wave-equation}
@@
 One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
-As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
-However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
+As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
+However, in this case, we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
 One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
@@
 \begin{equation}\label{eqn:ws-bimetric-action-v1}
-	S_{BNG} = -T \int \diff^2 y \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
+	S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
 \end{equation}
@@
 Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
-As a result we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
+As a result, we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
 \begin{subequations}\label{eqn:ws-induced-metrics}
@@
 
-The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics, unless these are included in the interaction term $S'_{int}$.
+The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
 One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
@@
 
+\subsection{The Bimetric Polyakov Equations} \label{sec:bimetric-polyakov-eoms}
+
+Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
+\begin{equation} \label{eqn:variation-wrt-g}
+	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{multline} \label{eqn:g-em-tensor}
+	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
+\end{multline}
+\begin{equation*}
+	\Downarrow
+\end{equation*}
+\begin{equation} \label{eqn:g-expression}
+	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+\end{equation}
+where the function $f^{(G)}$ is given by
+\begin{equation} \label{eqn:g's-f-function}
+	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
+\end{equation}
+and completely analogously for the $H_{\mu \nu}$ metric,
+\begin{equation} \label{variation-wrt-h}
+	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{multline} \label{h-em-tensor}
+	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
+\end{multline}
+\begin{equation*}
+	\Downarrow
+\end{equation*}
+\begin{equation} \label{h-expression}
+	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
+\end{equation}
+with
+\begin{equation} \label{h's-f-function}
+	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
+\end{equation}
+
+As for the embbeding fields equation, we get a wave equation for the combined metric
+\begin{equation} \label{eqn:variation-wrt-X}
+	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{equation} \label{eqn:bimetric-wave-equation}
+	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
+\end{equation}
+where
+\begin{equation} \label{eqn:coupled-ws-metric}
+	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
+\end{equation}
+\begin{equation} \label{eqn:combined-bulk-metric}
+	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
+\end{equation}
+in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$.
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}
@@
 Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
-Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
 In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.

### 2023-11-20 lqg-strings.tex
Used conformal symmetry to simplify eq(40) and eq(39), reducing to eq(22)

@@
 and completely analogously for the $H_{\mu \nu}$ metric,
-\begin{equation} \label{variation-wrt-h}
+\begin{equation} \label{eqn:variation-wrt-h}
 	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
@@
 \end{equation*}
-\begin{multline} \label{h-em-tensor}
+\begin{multline} \label{eqn:h-em-tensor}
 	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
@@
 \end{equation*}
-\begin{equation} \label{h-expression}
+\begin{equation} \label{eqn:h-expression}
 	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
@@
 with
-\begin{equation} \label{h's-f-function}
+\begin{equation} \label{eqn:h's-f-function}
 	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
@@
 
-As for the embbeding fields equation, we get a wave equation for the combined metric
+As for the embbeding fields equation, we get a wave equation for the coupled metric
 \begin{equation} \label{eqn:variation-wrt-X}
@@
 in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$.
+Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
+\begin{equation} \label{eqn:conformal-coupled-metric}
+	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
+\end{equation}
+and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.
 

### 2023-11-20 lqg-strings.tex
Corrected end of sec 4.B

@@
 \end{equation}
-and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.
+and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$ and the background geometry being fixed i.e $\partial _{\lambda} F_{\mu \nu}$, we see that eq(\ref{eqn:bimetric-wave-equation}) almost reduces to eq(\ref{eqn:simplified-modified-wave-eqn}), the only difference being that the correction factor loses the dependence on the determinant $h$.
 

### 2023-11-20 lqg-strings.tex
Forgot a 0 at the end of sec 4.B

--- 2023-11-20 lqg-strings.tex
@@
 \end{equation}
-and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.
+and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$ and the background geometry being fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$, we see that eq(\ref{eqn:bimetric-wave-equation}) almost reduces to eq(\ref{eqn:simplified-modified-wave-eqn}), the only difference being that the correction factor loses the dependence on the determinant $h$.
 

### 2023-11-21 lqg-strings.tex
Reduced the EoM into a Klein-Gordon equation and added a section relating it to sec(3)

--- 2023-11-20 lqg-strings.tex
@@
 \begin{equation} \label{eqn:conformal-coupled-metric}
-	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
+	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} .
 \end{equation}
-and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.
+In the special case where the second metric comes from the quantum geometry correction in the form of inverse area, where $T' = T k \Delta / 2$, eq(\ref{eqn:bimetric-wave-equation}) thus reduces to
+\begin{equation} \label{eqn:reduced-Polyakov-equation}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\kappa} = \frac{1}{2} \eta ^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} F^{\kappa \lambda} \partial _{\lambda} F_{\mu \nu} ,
+\end{equation}
+where if the R.H.S is set to be proportional to the embbeding fields, we thus get a Klein-Gordon equation
+\begin{equation} \label{eqn:Polyakov-Klein-Gordon-equation}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} - \kappa X^{\mu} = 0 .
+\end{equation}
+
+\subsection{Relation With The Nambu-Goto Equation}
+
+At first glance, our recent analysis seems to conflict with the one done in sec(\ref{sec:modified-eom}), but as pointed out in \cite{}, the variable-speed wave equation can be turned into a Klein-Gordon equation as long as the speed function satisfies certain constraints [need to show], while it is known from the GR literature that variable-speed waves are equivalent to waves in curved space, which is precisely what we found, since for eq(\ref{eqn:bimetric-wave-equation}) to reduce into the Klein-Gordon equation(\ref{eqn:Polyakov-Klein-Gordon-equation}) we needed for the background geometry to be dynamical.
 

### 2023-11-21 lqg-strings.tex
Just changed wording after eq(42)
added new calculations to main file

--- 2023-11-20 lqg-strings.tex
@@
 
-Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
+Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
 \begin{equation} \label{eqn:variation-wrt-g}
@@
 
-As for the embbeding fields equation, we get a wave equation for the coupled metric
+As for the embbeding fields equation, we get a non-homogeneous wave equation for the coupled metric
 \begin{equation} \label{eqn:variation-wrt-X}
@@
 \begin{equation} \label{eqn:bimetric-wave-equation}
-	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
+	\partial _{a} \left( f^{\prime a b} \partial _{b} X^{\mu} \right) F_{\mu \lambda} = 0 ,
 \end{equation}
-where
+with the coupled metric $f^{\prime a b}$ and the combined bulk metric $F_{\mu \nu}$ given by
 \begin{equation} \label{eqn:coupled-ws-metric}
-	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
+	f^{\prime a b} = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
 \end{equation}
 \begin{equation} \label{eqn:combined-bulk-metric}
-	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
+	F_{\mu \nu} = G_{\mu \nu} + H_{\mu \nu},
 \end{equation}
-in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$.
-Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
-\begin{equation} \label{eqn:conformal-coupled-metric}
-	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
-\end{equation}
-and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$ and the background geometry being fixed i.e $\partial _{\lambda} F_{\mu \nu}$, we see that eq(\ref{eqn:bimetric-wave-equation}) almost reduces to eq(\ref{eqn:simplified-modified-wave-eqn}), the only difference being that the correction factor loses the dependence on the determinant $h$.
+where the coupled metric $f^{\prime a b}$ has a prime since it is not quite the metric induced by the combined metric $F_{\mu \nu}$.
+In the special case where $h = g^{-1}$ and $T' = T k \Delta / 2$, we get
+\begin{multline} \label{eqn:h-equal-g-inverse-f'}
+	f^{\prime a b} = T \bigg( \sqrt{- g} g^{a b} + \\
+	+ \frac{k \Delta}{2} \sqrt{- g^{-1}} U^{a} _{\ a'} (g^{-1})^{a' b'} U^{\ b} _{b'} \bigg) ,
+\end{multline}
+where we have a new $\mathrm{SO}(1,1)$ symmetry in the second metric since forcing the determinant to be the inverse of the first doesn't mean the second matrix will be just the inverse, but rather any matrix that differs by an orthogonal transformation $U$.
+Given the metric itself is a function of world-sheet coordinates, we require this to be a local symmetry $U(x)$, thus eq(\ref{eqn:bimetric-wave-equation}) becomes
+\begin{multline} \label{eqn:gauge-wave-eqn}
+	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} + T \Big( \partial _{a} (\sqrt{- g} g^{a b}) + \\
+	+ \frac{k \Delta}{2} \Big( U^{a} _{\ a'} \partial _{a} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) U^{\ b} _{b'} + \\
+	+ \partial _{a} U^{a} _{\ a'} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) U^{\ b} _{b'} + \\
+	+ U^{a} _{\ a'} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) \partial _{a} U^{\ b} _{b'} \Big) \Big) \partial _{b} X^{\mu} = 0 ,
+\end{multline}
+and after applying the conformal symmetry of 2D metrics in the form $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ the above equation reduces to
+\begin{multline}
+	\left( 1 + \frac{k \Delta}{2} \right) \eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \\
+	+ \frac{k \Delta}{2} \Big( \partial _{a} U^{a} _{\ a'} \eta ^{a' b'} U^{\ b} _{b'} + \\
+	+ U^{a} _{\ a'} \eta ^{a' b'} \partial _{a} U^{\ b} _{b'} \Big) \partial _{b} X^{\mu} = 0 .
+\end{multline}
 

### 2023-12-07 lqg-strings.tex
Added recent inverse metric Polyakov analysis to main file

--- 2023-11-20 lqg-strings.tex
@@
 In this limit we can expand the integrand as follows:
-\begin{equation}
+\begin{equation} \label{eqn:inverse-metric-correction}
 	\sqrt{- (h + g \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{g \Delta}{(- h)} + \mc{O}(g^2/h^2)\right).
@@
 
-Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F = (1 + g \Delta / (2 (- h)))$)
+Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
 \begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{F^2} = \frac{E (q)}{T F^2} ,
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} = \frac{E (q)}{T (F^+)^2} ,
 \end{equation}
@@
 \begin{equation} \label{eqn:simplified-modified-wave-eqn}
-	F^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
+	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
 \end{equation}
@@
 \begin{equation} \label{eqn:wave-speed-corrected}
-	v = \frac{c}{F}.
+	v = \frac{c}{F^+}.
 \end{equation}
+
+\section{Inverse Metric Polyakov} \label{sec:inverse-metric-Polyakov}
+
+In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string.
+we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+\begin{multline} \label{eqn:inverse-metric-Polyakov}
+	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
+\end{multline}
+The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
+\begin{equation} \label{eqn:vary-wrt-g}
+	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{multline}
+	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
+\end{multline}
+from which we can extract the metric $g_{c d}$ as
+\begin{equation} \label{eqn:ws-metric}
+	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+\end{equation}
+where the function $f$ is given by
+\begin{equation} \label{eqn:inverse-area-f}
+	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
+\end{equation}
+
+As for variation w.r.t the embbeding fields $X^{\lambda}$, we have
+\begin{equation} \label{eqn:vary-wrt-X}
+	\frac{\delta S_{I A P}}{\delta X^{\lambda}} \overset{!}{=} 0
+\end{equation}
+\begin{equation*}
+	\downarrow
+\end{equation*}
+\begin{multline} \label{eqn:X-eom-inverse-area}
+	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
+\end{multline}
+where $F^{-} = 1 - k \Delta / 2 (- g)$.
+Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+\begin{equation} \label{eqn:X-eom-simplified}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \partial _{a} \ln (F^{-}) \partial _{b} X^{\mu} = 0 .
+\end{equation}
+
+\subsection{Solving The Equations of Motion} \label{sec:solving-eoms-inverse-area}
+
+Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal function $\phi (x)$ appearing in $F^{-}$.
+By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
+\begin{equation}
+	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
+\end{equation}
+from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+\begin{equation} \label{eqn:derivatives-F-minus}
+	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
+\end{equation}
+thus we have
+\begin{equation} \label{eqn:ln-F}
+	\ln (F^{-}) = i (E \tau + p \sigma) + a
+\end{equation}
+\begin{equation*}
+	\Downarrow
+\end{equation*}
+\begin{equation} \label{eqn:F-minus-exp}
+	F^{-} = A \e ^{i (E \tau + p \sigma)}
+\end{equation}
+\begin{equation*}
+	\Downarrow
+\end{equation*}
+\begin{equation} \label{eqn:phi}
+	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} ,
+\end{equation}
+where $A = \e ^{a}$ and $a$ is some constant.
+At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$.
+With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
+\begin{equation} \label{eqn:X-Klein-Gordon-eqn}
+	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - m^2 X^{\mu} = 0 .
+\end{equation}
+
+\subsection{Relation With The Nambu-Goto Analysis} \label{sec:relation-with-NG-case}
+
+At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string.
+However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found), as long as the speed function $c(x)$ satisfy certain criteria.[need to show]
 
@@
 \end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
-\begin{equation} \label{eqn:bimetric-wave-equation}
-	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
-\end{equation}
-where
-\begin{equation} \label{eqn:coupled-ws-metric}
-	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
-\end{equation}
-\begin{equation} \label{eqn:combined-bulk-metric}
-	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
-\end{equation}
-in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$.
-Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
-\begin{equation} \label{eqn:conformal-coupled-metric}
-	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
-\end{equation}
-and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$ and the background geometry being fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$, we see that eq(\ref{eqn:bimetric-wave-equation}) almost reduces to eq(\ref{eqn:simplified-modified-wave-eqn}), the only difference being that the correction factor loses the dependence on the determinant $h$.
 

### 2023-12-12 lqg-strings.tex
Sketched another possibility for inverse area corrected Polyakov action

@@
 
-\subsection{Solving The Equations of Motion} \label{sec:solving-eoms-inverse-area}
+\subsection{Simplifying The Equations of Motion} \label{sec:solving-eoms-inverse-area}
 
@@
 \begin{equation} \label{eqn:ln-F}
-	\ln (F^{-}) = i (E \tau + p \sigma) + a
+	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
 \end{equation}
@@
 \begin{equation} \label{eqn:F-minus-exp}
-	F^{-} = A \e ^{i (E \tau + p \sigma)}
+	F^{-} = A \e ^{i (E \tau + p \sigma + \varphi)} , \ A > 0
 \end{equation}
@@
 \begin{equation} \label{eqn:phi}
-	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} ,
+	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma + \varphi)} \right)}} .
 \end{equation}
-where $A = \e ^{a}$ and $a$ is some constant.
 At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$.

### 2023-12-28 lqg-strings.tex
Removed all the down arrows :)
Added transition from NG to Polyakov analysis into main file

@@
 \end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
+from which we obtain the stress-energy tensor for the worldsheet:
 \begin{multline}
@@
 \end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
+
 \begin{multline} \label{eqn:X-eom-inverse-area}
@@
 \end{equation}
-\begin{equation*}
-	\Downarrow
-\end{equation*}
+
 \begin{equation} \label{eqn:F-minus-exp}
@@
 \end{equation}
-\begin{equation*}
-	\Downarrow
-\end{equation*}
 \begin{equation} \label{eqn:phi}
@@
 At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string.
-However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found), as long as the speed function $c(x)$ satisfy certain criteria.[need to show]
+However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
+While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.
+
+Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq(\ref{eqn:simplified-modified-wave-eqn}) obtained in sec(\ref{sec:modified-eom}), renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t , x) \rightarrow (\tau (t , x) , \sigma (t , x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
+\begin{multline} \label{eqn:new-coordinates-constraints-quadratic}
+	\ \ \ \ \ \ \ \ \ \ (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \\
+	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma , \ \ \ \ \ \ \ \ \ \ \ \
+\end{multline}
+or more compactly,
+\begin{multline} \label{eqn:new-coordinates-constraints-compact}
+	\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \partial _{t} \tau = v \partial _{x} \sigma \\
+	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ,
+\end{multline}
+which is equivalent to
+\begin{multline} \label{eqn:new-coordinates-constraints-second-order}
+	\ \ \ \ \ \ \ \ \ \ \ \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau = \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \\
+	\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . \ \ \ \ \ \ \
+\end{multline}
+This turns eq(\ref{eqn:simplified-modified-wave-eqn}) into
+\begin{multline} \label{eqn:modified-wave-eqn-new}
+	\partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \\
+	+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \\
+	+ \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
+\end{multline}
+Next, we introduce $X^{\mu} = \kappa (\tau , \sigma) W^{\mu} (\tau , \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
+This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$.
+With this, eq(\ref{eqn:modified-wave-eqn-new}) turns into a Klein-Gordon equation
+\begin{equation}
+	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + m^2 W^{\mu} = 0 ,
+\end{equation}
+with \textquotedblleft mass" squared given by
+\begin{equation}
+	m^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
+\end{equation}
+and $\tau (t , x)$ satisfying constraints(\ref{eqn:new-coordinates-constraints-compact}).
+This shows that our action(\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the inverse area corrected Nambu-Goto action(\ref{eqn:modified-NG-action}).
 
@@
 \end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
 \begin{multline} \label{eqn:g-em-tensor}
@@
 \end{multline}
-\begin{equation*}
-	\Downarrow
-\end{equation*}
+
 \begin{equation} \label{eqn:g-expression}
@@
 \end{equation}
-\begin{equation*}
-	\downarrow
-\end{equation*}
 \begin{multline} \label{eqn:h-em-tensor}
@@
 \end{multline}
-\begin{equation*}
-	\Downarrow
-\end{equation*}
 \begin{equation} \label{eqn:h-expression}

### 2023-12-31 lqg-strings.tex
Added solution of EoM to main file

@@
 from which we obtain the stress-energy tensor for the worldsheet:
-\begin{multline}
+\begin{multline} \label{eqn:inverse-area-em-tensor}
 	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
@@
 \begin{equation} \label{eqn:X-Klein-Gordon-eqn}
-	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - m^2 X^{\mu} = 0 .
+	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
 \end{equation}
@@
 \begin{equation}
-	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + m^2 W^{\mu} = 0 ,
+	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0 ,
 \end{equation}
@@
 \begin{equation}
-	m^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
+	\mu ^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
 \end{equation}
@@
 This shows that our action(\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the inverse area corrected Nambu-Goto action(\ref{eqn:modified-NG-action}).
+
+\subsection{Solving The String Klein-Gordon Equation}
+
+From our analysis of the inverse-area corrected Polyakov action, we got $D$ Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}.
+The constraints are nothing new, they're precisely the same as the ones of regular String Theory.
+What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
+\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( a^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ b^{\mu} _{n} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
+\end{multline}
+with $E_{p} = \sqrt{p^2 + \mu ^2}$. Reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
+\begin{equation} \label{eqn:reality-consequence}
+	b^{\mu} _{n} = (a^{\mu} _{- n})^{*} .
+\end{equation}
+
+When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get $\tau$-dependent \textquotedblleft Virasoro modes"
+\begin{align}
+	L_{n} (\tau)              & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} a^{\mu} _{p} a^{\nu} _{n - p} \eta _{\mu \nu} \e ^{- i (E_{n} + E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-1}         \\
+	\widetilde{L} _{n} (\tau) & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} a^{\mu} _{p} (a^{\nu} _{p - n})^{*} \eta _{\mu \nu} \e ^{- i (E_{n} - E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-2} .
+\end{align}
+
+Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
+\begin{equation} \label{eqn:X-sol-0-term}
+	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( a^{\mu} _{0} \e ^{- i \mu \tau} + (a^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
+\end{equation}
+which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(a^{\mu} _{0}) = 0$.
+Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
+\begin{equation} \label{eqn:a-p-relation}
+	a^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
+\end{equation}
+Since our Virasoro-like \textquotedblleft modes" have a $n - p$ factor, we see that the 0-th term of $L_{0} (\tau)$ is vanishes, thus the string rest mass $M^2$ is given only in terms of the 0-th oscilator mode
+\begin{equation} \label{eqn:string-rest-mass}
+	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} a^{\mu} _{0} a^{\nu} _{0} \eta _{\mu \nu} .
+\end{equation}
+
+Collecting our results, we have that the solution for our string is given by
+\begin{multline} \label{eqn:KG-Polyakov-solution-final}
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 \E_{p}} \Big( a^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (a^{\mu} _{- n})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
+\end{multline}
+subject to the infinite family of constraints
+\begin{equation}
+	L_{n} (\tau) = \widetilde{L}_{n} (\tau) = 0
+\end{equation} \label{eqn:"Virasoro"-constraints}
+and 0-th oscillation mode related to center of mass momentum
+\begin{equation*}
+	a^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
+\end{equation*}
 

### 2023-12-31 lqg-strings.tex
Changed notation in main text to be more in line with literature

@@
 
-From our analysis of the inverse-area corrected Polyakov action, we got $D$ Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}.
+From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}.
 The constraints are nothing new, they're precisely the same as the ones of regular String Theory.
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( a^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ b^{\mu} _{n} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ \beta ^{\mu} _{n} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
 \end{multline}
@@
 \begin{equation} \label{eqn:reality-consequence}
-	b^{\mu} _{n} = (a^{\mu} _{- n})^{*} .
+	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
 \end{equation}
@@
 \begin{align}
-	L_{n} (\tau)              & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} a^{\mu} _{p} a^{\nu} _{n - p} \eta _{\mu \nu} \e ^{- i (E_{n} + E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-1}         \\
-	\widetilde{L} _{n} (\tau) & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} a^{\mu} _{p} (a^{\nu} _{p - n})^{*} \eta _{\mu \nu} \e ^{- i (E_{n} - E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-2} .
+	L_{n} (\tau)              & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} \e ^{- i (E_{n} + E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-1}         \\
+	\widetilde{L} _{n} (\tau) & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} \e ^{- i (E_{n} - E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-2} .
 \end{align}
@@
 \begin{equation} \label{eqn:X-sol-0-term}
-	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( a^{\mu} _{0} \e ^{- i \mu \tau} + (a^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
+	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
 \end{equation}
-which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(a^{\mu} _{0}) = 0$.
+which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$.
 Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
 \begin{equation} \label{eqn:a-p-relation}
-	a^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
+	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
 \end{equation}
@@
 \begin{equation} \label{eqn:string-rest-mass}
-	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} a^{\mu} _{0} a^{\nu} _{0} \eta _{\mu \nu} .
+	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
 \end{equation}
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-final}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 \E_{p}} \Big( a^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (a^{\mu} _{- n})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 \E_{p}} \Big( \alpha ^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (\alpha ^{\mu} _{- n})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
 \end{multline}
@@
 \begin{equation*}
-	a^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
+	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
 \end{equation*}

### 2023-12-31 lqg-strings.tex
Barely started quantization and corrected some typos in main file

@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ \beta ^{\mu} _{n} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
 \end{multline}
@@
 
-When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get $\tau$-dependent \textquotedblleft Virasoro modes"
+When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
 \begin{align}
-	L_{n} (\tau)              & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} \e ^{- i (E_{n} + E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-1}         \\
-	\widetilde{L} _{n} (\tau) & := \frac{1}{2} \sum _{p \in \mathbb{Z}} \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} \e ^{- i (E_{n} - E_{n - p}) \tau} \label{eqn:"Virasoro"-modes-2} .
+	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
+	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
 \end{align}
@@
 \end{equation}
-Since our Virasoro-like \textquotedblleft modes" have a $n - p$ factor, we see that the 0-th term of $L_{0} (\tau)$ is vanishes, thus the string rest mass $M^2$ is given only in terms of the 0-th oscilator mode
+Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
 \begin{equation} \label{eqn:string-rest-mass}
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-final}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 \E_{p}} \Big( \alpha ^{\mu} _{n} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (\alpha ^{\mu} _{- n})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
 \end{multline}
@@
 \begin{equation}
-	L_{n} (\tau) = \widetilde{L}_{n} (\tau) = 0
+	L_{n , p} = \widetilde{L}_{n , p} = 0
 \end{equation} \label{eqn:"Virasoro"-constraints}

### 2024-01-03 lqg-strings.tex
Some more progress in the quantization
Started adding quantization into main file, made more progress on the sketch, and added Witten's book to .bib

@@
 \end{multline}
-with $E_{p} = \sqrt{p^2 + \mu ^2}$. Reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
+with $E_{p} = \sqrt{p^2 + \mu ^2}$.
+From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
 \begin{equation} \label{eqn:reality-consequence}
@@
 \end{equation*}
+
+\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
+
+In this paper, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}
 

### 2024-01-03 lqg-strings.tex
Stuff

@@
 
-In this paper, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}
+In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}.
+To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
+\begin{multline} \label{eqn:canonical-momentum}
+	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \left( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \right) \eta _{\nu \mu} ,
+\end{multline}
+and then we proceed to turn the equal-time Poisson bracket relations
+\begin{equation} \label{eqn:Poisson-brackets-1}
+	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
+\begin{equation} \label{eqn:Poisson-brackets-2}
+	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
+\end{equation}
+into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
+\begin{equation}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
 

### 2024-01-03 lqg-strings.tex
Added the recent quantization progress to main file

@@
 where $F^{-} = 1 - k \Delta / 2 (- g)$.
-Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+Using conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 
-Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal function $\phi (x)$ appearing in $F^{-}$.
+Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\phi (x)$ appearing in $F^{-}$.
 By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
@@
 \end{equation}
-from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal function to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
-While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.
+While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.
 
@@
 into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
-\begin{equation}
+\begin{equation} \label{eqn:canonical-commutator-1}
 	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
 \end{equation}
+\begin{equation} \label{eqn:canonical-commutator-2}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
+\end{equation}
+From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
+\begin{equation} \label{eqn:non-vanishing-commutator}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
+\end{equation}
+\begin{equation} \label{eqn:vanishing-commutators}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
+\end{equation}
+which are just harmonic oscillator relations with
+\begin{align}
+	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
+	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
+\end{align}
+For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
+\begin{equation} \label{eqn:annihilation-vacuum}
+	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
+\end{equation}
+and for $p = 0$
+\begin{equation} \label{eqn:momentum-vacuum}
+	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
+\end{equation}
+Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
+\begin{multline} \label{eqn:general-state}
+	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
+	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
+\end{multline}
+
+As usual, by the appearance of the Minkowski metric in the non-zero commutator
+\begin{equation} \label{eqn:ghosts}
+	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
+\end{equation}
+we have ghosts in the theory which must be dealt with.
+When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
+\begin{equation} \label{eqn:L-constraint-quantum-1}
+	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
+\end{equation}
+\begin{equation} \label{eqn:L-constraint-quantum-2}
+	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
+\end{equation}
+$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
+\begin{equation} \label{eqn:L-normal-ordering}
+	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
+\end{equation}
+with the annihilation operator to the right, which manifests in the imposition of the constraint as
+\begin{equation} \label{eqn:shifted-L-constraint}
+	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
+\end{equation}
+for some sequence $c_{p}$.
+The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
+Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
+\begin{equation} \label{eqn:alternative-classical-rest-mass}
+	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
+\end{equation}
+from where we can now see that the string mass spectrum will get shifted by
+\begin{equation} \label{eqn:shifted-mass-spectrum}
+	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
+\end{equation}
+Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
+\begin{equation} \label{eqn:cp-limit}
+	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
+\end{equation}
+like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
+
+The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
+\begin{equation} \label{eqn:L-commutators-1}
+	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
+\end{equation}
+\begin{multline} \label{eqn:L-commutators-2}
+	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
+	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
+\end{multline}
+\begin{multline} \label{eqn:L-commutators-3}
+	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
+	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
+	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg)
+\end{multline}
 

### 2024-01-03 lqg-strings.tex
Fixed a typo in sec 4

@@
 In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string.
-we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
-	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg)
+	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
 \end{multline}

### 2024-01-03 lqg-strings.tex
Typo

@@
 \begin{equation} \label{eqn:alternative-classical-rest-mass}
-	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
+	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{p \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
 \end{equation}

### 2024-01-13 lqg-strings.tex
Figured out how to introduce gauge field on worldsheet

--- 2024-01-03 lqg-strings.tex
@@
 where $F^{-} = 1 - k \Delta / 2 (- g)$.
-Using conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 
-Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\phi (x)$ appearing in $F^{-}$.
+Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal function $\phi (x)$ appearing in $F^{-}$.
 By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
@@
 \end{equation}
-from which we can use the freedom in the conformal function to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
-While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.
+While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.
 
@@
 \end{equation*}
-
-\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
-
-In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}.
-To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
-\begin{multline} \label{eqn:canonical-momentum}
-	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \left( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \right) \eta _{\nu \mu} ,
-\end{multline}
-and then we proceed to turn the equal-time Poisson bracket relations
-\begin{equation} \label{eqn:Poisson-brackets-1}
-	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:Poisson-brackets-2}
-	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
-\end{equation}
-into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
-\begin{equation} \label{eqn:canonical-commutator-1}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:canonical-commutator-2}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
-\end{equation}
-From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
-\begin{equation} \label{eqn:non-vanishing-commutator}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
-\end{equation}
-\begin{equation} \label{eqn:vanishing-commutators}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
-\end{equation}
-which are just harmonic oscillator relations with
-\begin{align}
-	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
-	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
-\end{align}
-For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
-\begin{equation} \label{eqn:annihilation-vacuum}
-	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
-\end{equation}
-and for $p = 0$
-\begin{equation} \label{eqn:momentum-vacuum}
-	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
-\end{equation}
-Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
-\begin{multline} \label{eqn:general-state}
-	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
-	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
-\end{multline}
-
-As usual, by the appearance of the Minkowski metric in the non-zero commutator
-\begin{equation} \label{eqn:ghosts}
-	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
-\end{equation}
-we have ghosts in the theory which must be dealt with.
-When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
-\begin{equation} \label{eqn:L-constraint-quantum-1}
-	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
-\end{equation}
-\begin{equation} \label{eqn:L-constraint-quantum-2}
-	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
-\end{equation}
-$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
-\begin{equation} \label{eqn:L-normal-ordering}
-	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
-\end{equation}
-with the annihilation operator to the right, which manifests in the imposition of the constraint as
-\begin{equation} \label{eqn:shifted-L-constraint}
-	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
-\end{equation}
-for some sequence $c_{p}$.
-The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
-Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
-\begin{equation} \label{eqn:alternative-classical-rest-mass}
-	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
-\end{equation}
-from where we can now see that the string mass spectrum will get shifted by
-\begin{equation} \label{eqn:shifted-mass-spectrum}
-	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
-\end{equation}
-Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
-\begin{equation} \label{eqn:cp-limit}
-	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
-\end{equation}
-like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
-
-The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
-\begin{equation} \label{eqn:L-commutators-1}
-	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
-\end{equation}
-\begin{multline} \label{eqn:L-commutators-2}
-	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
-	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
-\end{multline}
-\begin{multline} \label{eqn:L-commutators-3}
-	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
-	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
-	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg)
-\end{multline}
 
@@
 
+$X^\mu(\sigma, \tau)$ are the space-time coordinates of a point $(\sigma, \tau)$ on the worldsheet.
+Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $D+1$ scalar fields living on a $1+1$ worldsheet.
+But these are not scalars, they are components of a $D+1$ dim vector because they transform as elements of $SO(D,1)$ under global Lorentz transformations on the ambient space-time.
+
+The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}.
+If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $SO(D,1)$ just takes one point in Minkowski to another point in Minkowski.
+The overall geometry is invariant under SO(D,1).
+Now, consider the case when the background geometry is not flat.
+Immediately you can see that the $X$'s can no longer be treated as elements of a $SO(D,1)$ vector under \emph{global} Lorentz transformations.
+
+But now instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p(M)$ of the background manifold $M$.
+And what happens when you go from point $p$ to point $p'$ in $M$, the local Lorentz frames at the two points are related by an element of $g(p,p') \in SO(D,1)$.
+This group element can be thought of arising from taking the holonomy of a $\mf{so}(D,1)$ Lie algebra valued connection living on $M$, along a path connecting $p$ and $p'$.
+
+Now, let's remind ourselves what we're trying to do here.
+We want a gauge field, which lives on the background geometry and which encodes the background geometry, should appear in an action of a Bosonic string.
+The end result is that we now have with a gauge field $\mc{A}_a^J(\sigma, \tau)$ living on the worldsheet $\Sigma$.
+Here the lower index $a$ is the worldsheet index and $J$ labels generators of the Lie algebra $\mf{so}(D,1)$.
+Remember this is a gauge field which is now living on the worldsheet.
+The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:
+
+\begin{equation}
+	\mc{D}_a X^I(\sigma,\tau) = \partial_a X^I + g \mc{A}_a X^I,
+\end{equation}
+where $\mc{A}_a$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(D,1)$.
+
 Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
@@
 
-\section{}
+\section{Worldsheet Action in Terms of Transverse Velocity}
 

### 2024-01-15 lqg-strings.tex
Expanded abstract, added paper outline to intro, moved bimetric string section to appendix, edited and expanded portion on gauged bosonic action

@@
 \begin{abstract}
-	We write down an action for a bosonic string propagating in a bulk background whose geometry is specified in terms of connection and tetrad (or ``vierbein'') variables
+	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a Bosonic string.
+We consider two types of modifications.
+The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geoemtry and are bounded from below.
+The second is an action in which the background geometry is described in terms of a vielbein $E^\mu_I$ and a connection field $A_\mu^{IJ}$, in the spirit of LQG.
+The modified Nambu-Goto action is constructed by pulling back the background connection onto the worldsheet and replacing ordinary partial derivatives by covariant derivatives with respect to the pulled back conection $\mc{A}_a^{IJ}$.
 \end{abstract}
@@
 \todo[inline]{Insert brief intro to spin nets}
+
+The following is the outline of the paper.
+In \autoref{sec:intro} we recall the Nambu-Goto action and its symmetries.
+We explain how the bulk (embedding manifold) geometry is coupled to the worldsheet geometry and the conventional argument for the statement that string theory describes not only the object but also its background (the geometry it is propagating) in and is therefore a complete theory of quantum gravity.
+We critique this claim and explain in what way LQG might provide a resolution of some of the puzzles of string theory.
+In \autoref{sec:modified-ng} we present a phenomenological modification of the Nambu-Goto action based on the observation from LQG that there exists a non-zero, positive, eigenvalue of the area operator.
+We show that this action can be expanded in terms of a small coupling constant $g = l_{pl}/l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $g \ll 1$.
+We point out that the lowest order correction to the NG action can be viewed as a bimetric action for the string.
+We derive the classical equations of motion for this area-corrected NG action.
+In \autoref{sec:inverse-metric-Polyakov} we construct the Polyakov version of the modified NG action, show that the equations of motion it yields are the same as those coming from the modified NG action.
+Further we solve the string equations of motion to find the fundamental modes and perform the quantization of the Bosonic string in the usual manner.
+In \autoref{sec:string-geometry} we describe how to construct an action for the Bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
+We discuss possible avenues for quantizing this action and further studying its implications for the relationship between string theory and LQG.
+
+In \autoref{app:bimetric-string} we discuss further the bimetric extension of the string action in both the Nambu-Goto and Polyakov version.
 
@@
 
-\section{The Bimetric String}\label{sec:bimetric-nambu-goto}
+\section{Strings and Quantum Geometry}\label{sec:string-geometry}
+
+Uptil now we have studied a phenomenological modification of the string action.
+However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system.
+Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that to the Bosonic string.
+In this section we present a possible action in which the bulk geometry is encoded in the string action in terms of a connection living on the worldsheet.
+
+Let us begin by writing down the action of a string propagating in a background geometry.
+The background geometry is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
+Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+$X^\mu(\sigma, \tau)$ are the space-time coordinates of a point $(\sigma, \tau)$ on the worldsheet.
+Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $D+1$ scalar fields living on a $1+1$ worldsheet.
+But these fields are not scalars.
+They are components of a $D+1$ dim vector because they transform as elements of $SO(D,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.
+
+The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}.
+If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $SO(D,1)$ just takes one point in Minkowski to another point in Minkowski.
+The overall geometry is invariant under SO(D,1).
+Now, consider the case when the background geometry is not flat.
+Immediately you can see that the $X$'s can no longer be treated as elements of a $SO(D,1)$ vector under \textbf{global} Lorentz transformations.
+
+Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p(M)$ at a given point $p$ of the background manifold $M$.
+When we travel along some path $\mc{C} \in M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in SO(D,1)$.
+This group element arises from taking the holonomy of a $\mf{so}(D,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.
+
+Let us remind ourselves what we're trying to do here.
+We want a gauge field, which lives on the background geometry and which encodes the background geometry, to somehow make an appearance in the action of a Bosonic string.
+There is an obvious connection $\mc{A}_a^{IJ}$ living on the worldsheet which is the pullback from $M$ to $\Sigma$ of the connection $A_{\mu}^{IJ}$.
+
+The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\sigma, \tau)$ living on the worldsheet $\Sigma$.
+Here the lower index $a$ is the worldsheet index and $J$ labels generators of the Lie algebra $\mf{so}(D,1)$.
+Remember this is a gauge field which is now living on the worldsheet.
+The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:
+
+\begin{equation}
+	\mc{D}_a X^I(\sigma,\tau) = \partial_a X^I + g \mc{A}_a X^I,
+\end{equation}
+where $\mc{A}_a$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(D,1)$.
+We should therefore think of the embedding fields as $(D+1)$ dimensional vectors living in the fundamental representation of $SO(D,1)$.
+
+This viewpoint on the embedding fields, as elements of the tangent space $T_p(M)$, might appear to be at odds with their prescribed usage as co-ordinate functions on $M$.
+However, some reflection shows that this is not the case.
+For instance, one can take the embedding manifold to be a two-dimensional sphere $S^2$.
+Then the co-ordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$.
+The action for this system would be:
+\begin{equation}\label{eqn:s2-string}
+	S_{S^2} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a \theta^\mu \partial_b \theta^\nu G_{\mu\nu},
+\end{equation}
+where $\theta^\mu(\sigma,\tau) \in \{\theta, \phi\}$ are the embedding fields, and $G_{\mu\nu}$ is \emph{a} metric living on $S^2$.
+
+\hline
+
+ In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
+However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
+\begin{multline} \label{eqn:lqg-string-action}
+	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
+	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
+\end{multline}
+where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
+\begin{equation} \label{eqn:worldsheet-deriv}
+	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
+\end{equation}
+where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
+
+\section{Physical Implications}
+
+\section{Discussion}
+
+\begin{acknowledgments}
+
+\end{acknowledgments}
+
+\appendix
+
+\section{Worldsheet Action in Terms of Transverse Velocity}\label{app:transverse-action}
+
+\section{The Bimetric String}\label{app:bimetric-string}
 
@@
 
-\section{Strings and Quantum Geometry}\label{sec:string-geometry}
-
-$X^\mu(\sigma, \tau)$ are the space-time coordinates of a point $(\sigma, \tau)$ on the worldsheet.
-Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $D+1$ scalar fields living on a $1+1$ worldsheet.
-But these are not scalars, they are components of a $D+1$ dim vector because they transform as elements of $SO(D,1)$ under global Lorentz transformations on the ambient space-time.
-
-The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}.
-If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $SO(D,1)$ just takes one point in Minkowski to another point in Minkowski.
-The overall geometry is invariant under SO(D,1).
-Now, consider the case when the background geometry is not flat.
-Immediately you can see that the $X$'s can no longer be treated as elements of a $SO(D,1)$ vector under \emph{global} Lorentz transformations.
-
-But now instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p(M)$ of the background manifold $M$.
-And what happens when you go from point $p$ to point $p'$ in $M$, the local Lorentz frames at the two points are related by an element of $g(p,p') \in SO(D,1)$.
-This group element can be thought of arising from taking the holonomy of a $\mf{so}(D,1)$ Lie algebra valued connection living on $M$, along a path connecting $p$ and $p'$.
-
-Now, let's remind ourselves what we're trying to do here.
-We want a gauge field, which lives on the background geometry and which encodes the background geometry, should appear in an action of a Bosonic string.
-The end result is that we now have with a gauge field $\mc{A}_a^J(\sigma, \tau)$ living on the worldsheet $\Sigma$.
-Here the lower index $a$ is the worldsheet index and $J$ labels generators of the Lie algebra $\mf{so}(D,1)$.
-Remember this is a gauge field which is now living on the worldsheet.
-The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:
-
-\begin{equation}
-	\mc{D}_a X^I(\sigma,\tau) = \partial_a X^I + g \mc{A}_a X^I,
-\end{equation}
-where $\mc{A}_a$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(D,1)$.
-
-Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
-Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
-\begin{multline} \label{eqn:lqg-string-action}
-	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
-	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
-\end{multline}
-where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
-\begin{equation} \label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
-\end{equation}
-where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
-
-\section{Physical Implications}
-
-\section{Discussion}
-
-\begin{acknowledgments}
-
-\end{acknowledgments}
-
-\appendix
-
-\section{Worldsheet Action in Terms of Transverse Velocity}
-
 \bibliographystyle{JHEP3}

### 2024-01-15 lqg-strings.tex
Reverted accidental deletion (by me) of Luigi's section on quantization of string action.

--- 2024-01-03 lqg-strings.tex
@@
 In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string.
-We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 \begin{equation} \label{eqn:alternative-classical-rest-mass}
-	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{p \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
+	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
 \end{equation}
@@
 
-\section{The Bimetric String}\label{sec:bimetric-nambu-goto}
+\section{The Bimetric String}\label{app:bimetric-string}
 
@@
 
-\section{Strings and Quantum Geometry}\label{sec:string-geometry}
-
-Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
-Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
-\begin{multline} \label{eqn:lqg-string-action}
-	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
-	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
-\end{multline}
-where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
-\begin{equation} \label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
-\end{equation}
-where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
-
-\section{Physical Implications}
-
-\section{Discussion}
-
-\begin{acknowledgments}
-
-\end{acknowledgments}
-
-\appendix
-
-\section{}
-
 \bibliographystyle{JHEP3}

### 2024-01-15 lqg-strings.tex
Moved bimetric section to appendix, recovered my section on lqg strings, some compilation errors remaining

--- 2024-01-15 lqg-strings.tex
@@
 
-\begin{equation}\label{eqn:polyakov-flat}
+\begin{equation}
 	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
@@
 
-Following the procedure done in $\cite{Zwiebach2009A-First}$, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
 \begin{equation} \label{eqn:modified-NG-eom}
@@
 
+\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
+
+In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
+To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
+\begin{multline} \label{eqn:canonical-momentum}
+	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
+\end{multline}
+and then we proceed to turn the equal-time Poisson bracket relations
+\begin{equation} \label{eqn:Poisson-brackets-1}
+	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
+\begin{equation} \label{eqn:Poisson-brackets-2}
+	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
+\end{equation}
+into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
+\begin{equation} \label{eqn:canonical-commutator-1}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
+\begin{equation} \label{eqn:canonical-commutator-2}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
+\end{equation}
+From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
+\begin{equation} \label{eqn:non-vanishing-commutator}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
+\end{equation}
+\begin{equation} \label{eqn:vanishing-commutators}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
+\end{equation}
+which are just harmonic oscillator relations with
+\begin{align}
+	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
+	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
+\end{align}
+For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
+\begin{equation} \label{eqn:annihilation-vacuum}
+	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
+\end{equation}
+and for $p = 0$
+\begin{equation} \label{eqn:momentum-vacuum}
+	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
+\end{equation}
+Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
+\begin{multline} \label{eqn:general-state}
+	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
+	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
+\end{multline}
+
+As usual, by the appearance of the Minkowski metric in the non-zero commutator
+\begin{equation} \label{eqn:ghosts}
+	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
+\end{equation}
+we have ghosts in the theory which must be dealt with.
+When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
+\begin{equation} \label{eqn:L-constraint-quantum-1}
+	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
+\end{equation}
+\begin{equation} \label{eqn:L-constraint-quantum-2}
+	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
+\end{equation}
+$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
+\begin{equation} \label{eqn:L-normal-ordering}
+	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
+\end{equation}
+with the annihilation operator to the right, which manifests in the imposition of the constraint as
+\begin{equation} \label{eqn:shifted-L-constraint}
+	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
+\end{equation}
+for some sequence $c_{p}$.
+The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
+Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
+\begin{equation} \label{eqn:alternative-classical-rest-mass}
+	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
+\end{equation}
+from where we can now see that the string mass spectrum will get shifted by
+\begin{equation} \label{eqn:shifted-mass-spectrum}
+	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
+\end{equation}
+Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
+\begin{equation} \label{eqn:cp-limit}
+	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
+\end{equation}
+like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
+
+The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
+\begin{equation} \label{eqn:L-commutators-1}
+	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
+\end{equation}
+\begin{multline} \label{eqn:L-commutators-2}
+	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
+	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
+\end{multline}
+\begin{multline} \label{eqn:L-commutators-3}
+	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
+	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
+	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
+\end{multline}
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}
@@
 
-\hline
+% \hline
 

### 2024-01-15 lqg-strings.tex
Just polished a bit your recent addition

@@
 Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
-$X^\mu(\sigma, \tau)$ are the space-time coordinates of a point $(\sigma, \tau)$ on the worldsheet.
-Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $D+1$ scalar fields living on a $1+1$ worldsheet.
-But these fields are not scalars.
-They are components of a $D+1$ dim vector because they transform as elements of $SO(D,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.
+$X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet.
+Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet.
+But these fields are not really scalars.
+They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.
 
 The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}.
-If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $SO(D,1)$ just takes one point in Minkowski to another point in Minkowski.
-The overall geometry is invariant under SO(D,1).
+If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $\mathrm{SO}(d,1)$ just takes one point in Minkowski to another point in Minkowski.
+The overall geometry is invariant under $\mathrm{SO}(d,1)$.
 Now, consider the case when the background geometry is not flat.
-Immediately you can see that the $X$'s can no longer be treated as elements of a $SO(D,1)$ vector under \textbf{global} Lorentz transformations.
+Immediately you can see that the $X$'s can no longer be treated as elements of a $\mathrm{SO}(d,1)$ vector under \textbf{global} Lorentz transformations.
 
-Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p(M)$ at a given point $p$ of the background manifold $M$.
-When we travel along some path $\mc{C} \in M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in SO(D,1)$.
-This group element arises from taking the holonomy of a $\mf{so}(D,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.
+Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
+When we travel along some path $\mc{C} \subset M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in \mathrm{SO}(d,1)$.
+This group element arises from taking the holonomy of a $\mf{so}(d,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.
 
@@
 
-The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\sigma, \tau)$ living on the worldsheet $\Sigma$.
-Here the lower index $a$ is the worldsheet index and $J$ labels generators of the Lie algebra $\mf{so}(D,1)$.
+The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\tau , \sigma)$ living on the worldsheet $\Sigma$.
+Here the lower index $a$ is the worldsheet index and $I , J$ labels the generators of the Lie algebra $\mf{so}(d,1)$.
 Remember this is a gauge field which is now living on the worldsheet.
@@
 \begin{equation}
-	\mc{D}_a X^I(\sigma,\tau) = \partial_a X^I + g \mc{A}_a X^I,
+	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
 \end{equation}
-where $\mc{A}_a$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(D,1)$.
-We should therefore think of the embedding fields as $(D+1)$ dimensional vectors living in the fundamental representation of $SO(D,1)$.
+where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$.
+We should therefore think of the embedding fields as $d+1$ dimensional vectors living in the fundamental representation of $\mathrm{SO}(d,1)$.
 

### 2024-01-15 lqg-strings.tex
Pushing the confirmation that there is no anomalous term in the algebra to main file

@@
 \end{multline}
+The commutator (\ref{eqn:L-commutators-2}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutators-3}) seem like it would have ordering ambiguities for $k - p = 0$ and $n - m = 0$.
+However it has a $(m - n)(k - p)$ factor multiplying the whole expression, so the commutator is $0$, which can also be seen by setting $n = m$ or $k = p$ on the L.H.S, in which case we get $\Hat{\widetilde{L}}_{n , n}$, which is identically equal to $0$ by the $n - m$ factor in front, thus we would be commuting something with $0$, which has to yield 0 on the R.H.S.
+As a result, our \textquotedblleft Virasoro-Klein-Gordon" algebra has no anomalous terms.
 

### 2024-03-10 lqg-strings.tex
Updated abstract, started work on explaining gauged Polyakov action

@@
 \begin{abstract}
-	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a Bosonic string.
+
+	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a bosonic string.
 We consider two types of modifications.
-The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geoemtry and are bounded from below.
-The second is an action in which the background geometry is described in terms of a vielbein $E^\mu_I$ and a connection field $A_\mu^{IJ}$, in the spirit of LQG.
-The modified Nambu-Goto action is constructed by pulling back the background connection onto the worldsheet and replacing ordinary partial derivatives by covariant derivatives with respect to the pulled back conection $\mc{A}_a^{IJ}$.
+The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geometry and are bounded from below.
+This leads us to a string action which is similar to that of bimetric gravity.
+We provide formulations of the bimetric string for both the Nambu-Goto (second order) and Polyakov (first order) formulations.
+We explore the classical solutions of this action and its quantization and relate it to the conventional string solutions.
+
+	The second is an action in which the background geometry is described in terms of the pullback of the connection which describes the bulk geometry to the worldsheet.
+The resulting action is in the form of a gauged sigma model, where the spacetime co-ordinates are now SO(D,1) vectors.
+We find that for the particular case of a constant background connection the action reduces to the bimetric action discussed above.
+We discuss classical solutions and quantization strategies for this action and its implications for the broader program of unifying string theory and loop quantum gravity.
 \end{abstract}
@@
 
-\begin{equation}
+\begin{equation}\label{eqn:polyakov-action}
 	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
 \end{equation}
+
 Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.
@@
 
+First let us recall the form of the Polyakov action for the bosonic string \eqref{eqn:polyakov-action}:
+
+\begin{equation*}
+	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
+\end{equation*}
+
+If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$.
+The resulting action would now have the form:
+
+\begin{equation}\label{eqn:polyakov-gauged}
+	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu},
+\end{equation}
+
+where the covariant derivative $\mc{D}_a$ is of the form:
+\begin{equation}\label{eqn:covariant-deriv}
+	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
+\end{equation}
+where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling.
+A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming
+
 Let us begin by writing down the action of a string propagating in a background geometry.

### 2024-03-27 lqg-strings.tex
Started section on relation between X derivatives and vielbein

@@
 %\usepackage{hyperref}
+
+% Mar 25, 2023
+% Added parskip package for spacing between paragraphs.
+\usepackage{parskip}
+\setlength{\parindent}{15pt}
 
@@
 
+\subsection{Gauging Lorentz Transformations}\label{sec:gauging-lt}
+
 Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
@@
 
-% \hline
+\subsection{Two Expressions for Area}\label{eqn:area-formulae}
 
-In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$.
-However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
-\begin{multline} \label{eqn:lqg-string-action}
-	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
-	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
-\end{multline}
-where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
-\begin{equation} \label{eqn:worldsheet-deriv}
-	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
+There is another explanation for why it makes sense to promote the $X$'s to local fields.
+This can be found in terms of the expression for the area of a 2-surface.
+We have a manifold $\mc M$, within which is embedded a two dimensional submanifold $\mc N$.
+Let $(\tau,\sigma)$ be the location of a point on the worldsheet and $X^\mu(\tau, \sigma)$ be the location of that same point in terms of co-ordinates on $\mc M$.
+Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of the embedding fields and their derivatives:
+
+\begin{equation}\label{eqn:ws-metric}
+	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} g_{\mu\nu},
 \end{equation}
-where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
+where $g_{\mu\nu}$ is the metric in the ambient space $\mc M$.
+Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{\det(h)}$ and integrating over that patch:
+\begin{equation}\label{eqn:patch-area-v1}
+	A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{\det(h)}.
+\end{equation}
+This is, of course, the expression for the Nambu-Goto action - modulo some constants - which we all know and love.
+In LQG we don't have a notion of embedding fields.
+Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding co-ordinates of the curves and surface turn to not be needed.
+When promoting classical observables into quantum operators acting on lines and surfaces the embedding co-ordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.
+
+How then does one define the area of a surface in LQG?
+It is defined as the magnitude of the area two form.
+Recall that given a tetradic basis $e_\mu^I$ for a local Lorentz frame whose metric is given by $g_{\mu\nu}$, we can write the metric in terms of the tetrad in the usual manner:
+\begin{equation}\label{eqn:metric-from-tetrad}
+	g_{\mu\nu} = e_\mu^I e_\nu^J \eta_{IJ},
+\end{equation}
+where $\eta_{IJ}$ is the flat Minkowski metric on the ``internal'' flat space.
+If we consider any two dimensional surface in the local Lorentz frame, then its area can be written in terms of the vielbein as:
+\begin{equation}
+	A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e_\mu \wedge e_\nu) dx^\mu \wedge dx^\nu,
+\end{equation}
+the trace is taken over the ``internal'' Lorentz indices.
+
+Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x_a$ of the embedding co-ordinates and the vielbein $e_\mu^I$.
+This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.
 

### 2024-04-02 lqg-strings.tex

@@
 where the covariant derivative $\mc{D}_a$ is of the form:
-\begin{equation}\label{eqn:covariant-deriv}
+\begin{equation}\label{eqn:covariant-deriv-v1}
 	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
@@
 
-\begin{equation}
+\begin{equation}\label{eqn:covariant-deriv-v2}
 	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
@@
 This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.
+
+\textbf{From Embedding Fields:}
+
+We take the bulk metric $g_{\mu\nu}$ to be flat.
+Let $\{\tau,\sigma\} := \{x^0, x^1\}$ be the spacetime co-ordinates on the worldsheet.
+Derivatives of the $X$'s in terms of these co-ordinates can be written as:
+\begin{equation}
+	\dot X := \left\{\frac{\partial X^\mu}{\partial \tau}\right\}; \quad X' := \left\{\frac{\partial X^\mu}{\partial \sigma}\right\}
+\end{equation}
+ we obtain the following form for the determinant of the worldsheet metric (\eqref{eqn:patch-area-v1}) in terms of the embedding fields:
+\begin{align}\label{eqn:area-embedding}
+	\det h & = \begin{vmatrix}
+		h_{00} && h_{01} \\
+		h_{10} && h_{11} 
+	\end{vmatrix} = \begin{vmatrix}
+		\dot X^2 && \dot X \cdot X' \\
+		\dot X \cdot X' && X'^2
+	\end{vmatrix} \nonumber \\
+	& = \dot X^2 X'^2 - (\dot X \cdot X')^2
+\end{align}
+
+\textbf{From Vielbein:}
+
+We can proceed to obtain the area of a 2-surface from the bulk vielbein as follows.
+Starting with the bulk vielbein $e_\mu^I$, we perform a local Lorentz transformation such that two ``legs'' of the vielbein are tangent to the worldsheet surface.
+We then project down the vielbein $e_\mu^I$ to a dyad $e_a^i$ living in the tangent space of the worldsheet, in terms of which the worldsheet metric can be written as:
+\begin{equation}
+	h_{ab} = e_a^i e_b^j \eta_{ij},
+\end{equation}
+where $\eta_{ij}$ is the flat $(1+1)$ Minkowski metric. The determinant then becomes:
+\begin{align}\label{eqn:area-vielbein}
+	\det h & = \begin{vmatrix}
+		h_{00} && h_{01} \\
+		h_{10} && h_{11} 
+	\end{vmatrix} = \begin{vmatrix}
+		e_x{}^i e_x{}^j & e_x{}^i e_y{}^j \\
+		e_y{}^i e_x{}^j & e_y{}^i e_y{}^j
+	\end{vmatrix} \eta_{ij} \nonumber \\
+	& = \vec e_x{}^2 \vec e_y{}^2 - (\vec e_x \cdot \vec e_y)^2,
+\end{align}
+where $\vec e_x \cdot \vec e_y = e_x{}^i e_y{}^j \eta_{ij}$.
+It is clear by comparing the two expressions \eqref{eqn:area-embedding} and \eqref{eqn:area-vielbein} that we have the following correspondence between the vielbein the $X$ derivatives:
+\begin{equation}
+	\vec e_\tau \equiv \frac{\partial \vec X}{\partial \tau}; \quad \vec e_\sigma \equiv \frac{\partial \vec X}{\partial \sigma}.
+\end{equation}
+In other words we can identify the vielbein with the derivatives of the embedding fields.
+Of course, this is not altogether surprising.
+If we consider any manifold on which we have some set of fields $\{X^I(x^\mu)\}$, where $I$ is valued in the Lie algebra ${\mc g}$ of some group $\mc G$, as a function of some  ``fiducial'' co-ordinates $\{x^\mu\}$, then we can always define a set of ${\mc g}$ valued vector fields:
+$$
+	e^I_\mu := \frac{\partial X^I}{\partial x^\mu}.
+$$
+In the usual formulation of the string action the embedding fields are \emph{not} Lie-algebra valued but are co-ordinate fields on what is generally taken to be a flat background.
+In order for this correspondence between vielbein and $X$ derivatives to work we have to view the $X$ fields as taking values in a Lie algebra.
+But these same $X$ fields \emph{also} serve as local co-ordinates for the bulk.
+In order for the co-ordinates to change from point to point in the bulk geometry, we must therefore have that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely!
+If $\mc A$ vanishes then that will imply that the fields $X$ don't change from one point to the next.
+Thus the amplitude $|\mc A|$ can be arbitrarily small but it can never be zero.
 

### 2024-04-15 lqg-strings.tex
sketched some stuff and started correcting the main file

@@
 \end{multline}
-The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
+The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}$.
+The equations of motion for the auxiliary metric are completely unchanged by this correction, so they are
 \begin{equation} \label{eqn:vary-wrt-g}
-	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
+	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
 \end{equation}
@@
 \begin{equation} \label{eqn:vary-wrt-X}
-	\frac{\delta S_{I A P}}{\delta X^{\lambda}} \overset{!}{=} 0
+	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
 \end{equation}
@@
 where $F^{-} = 1 - k \Delta / 2 (- g)$.
-Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+In conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 \end{equation}
-from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 \end{equation}
-At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$.
+At first glance it seems problematic that we have a complex conformal factor $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it will also pick the respective component of $\phi$.
 With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
@@
 However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
-While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.
+While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence.
 
@@
 	\det h & = \begin{vmatrix}
-		h_{00} && h_{01} \\
-		h_{10} && h_{11} 
+		           h_{00} &  & h_{01} \\
+		           h_{10} &  & h_{11}
 	           \end{vmatrix} = \begin{vmatrix}
-		\dot X^2 && \dot X \cdot X' \\
-		\dot X \cdot X' && X'^2
+		                           \dot X^2        &  & \dot X \cdot X' \\
+		                           \dot X \cdot X' &  & X'^2
 	                           \end{vmatrix} \nonumber \\
@@
 	\det h & = \begin{vmatrix}
-		h_{00} && h_{01} \\
-		h_{10} && h_{11} 
+		           h_{00} &  & h_{01} \\
+		           h_{10} &  & h_{11}
 	           \end{vmatrix} = \begin{vmatrix}

### 2024-04-16 lqg-strings.tex
working on the main file

@@
 \end{multline}
-with $E_{p} = \sqrt{p^2 + \mu ^2}$.
-From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
+with $E_{p} = \sqrt{p^2 + \mu ^2}$ for the closed string.
+From here on, we shall deal only with closed strings, unless otherwise stated.
+Following an analogous procedure to the one found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
 \begin{equation} \label{eqn:reality-consequence}
@@
 \begin{align}
-	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
-	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
+	L_{n , p}              & := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu} = 0 , \ \forall \ n , p \in \mathbb{Z} \label{eqn:"Virasoro"-modes-1} \\
+	\widetilde{L} _{n , p} & := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{- p})^{*} \eta _{\mu \nu} = 0 , \ n \neq - p \label{eqn:"Virasoro"-modes-2}
 \end{align}
-
-Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
+\begin{equation} \label{eqn:"Virasoro"-modes-sum}
+	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
+\end{equation}
+
+Before proceeding, we have one more remark: the 0-th term of the solution reads
 \begin{equation} \label{eqn:X-sol-0-term}
@@
 \end{equation}
-which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$.
+which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$.
 Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
 \begin{equation} \label{eqn:a-p-relation}
-	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation}
-Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
-\begin{equation} \label{eqn:string-rest-mass}
-	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
-\end{equation}
-
-Collecting our results, we have that the solution for our string is given by
+	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
+\end{equation}
+
+After analysing closer the $n = - p$ constraint(\ref{eqn:"Virasoro"-modes-sum}), we get the string mass in terms of vibrational modes and center of mass position
+\begin{multline} \label{eqn:string-rest-mass}
+	M^2 = - p^{\mu} p_{\mu} = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' m)^{2} x^{\mu} x_{\mu} - \\
+	- \sum _{n \neq 0} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) a^{\mu} _{n} (a^{\nu} _{n})^{*} \eta _{\mu \nu} \right) \Bigg) .
+\end{multline}
+
+Collecting our results, we have that the solution for our closed string is given by
 \begin{multline} \label{eqn:KG-Polyakov-solution-final}
@@
 \end{multline}
-subject to the infinite family of constraints
+subject to the family of constraints
+\begin{equation} \label{eqn:"Virasoro"-constraints}
+	L_{n , p} = \widetilde{L}_{n , p} = 0
+\end{equation}
+\begin{equation*}
+	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
+\end{equation*}
+and 0-th oscillator mode related to center of mass position and momentum
+\begin{equation*}
+	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
+\end{equation*}
+One thing to note is that the constraint(\ref{eqn:"Virasoro"-modes-2}) implies we only have $D$ non-zero modes in the solution, since all modes must be mutually orthogonal.
+
+\subsection{The Modes and Constraints Algebra} \label{sec:modes-constraint-algebra}
+
+We start by calculating the momentum canonical to $X^{\mu}$, $\Pi _{\lambda}$:
+\begin{multline} \label{eqn:canonical-momentum}
+	\Pi _{\lambda} = \frac{\partial \Lagr}{\partial (\partial _{\tau} X^{\lambda})} = \\
+	= F^{-} \frac{i}{4 \pi \alpha '} \sum _{n \in \mathbb{Z}} \bigg( - \alpha ^{\nu} _{n} \e ^{i (- E_{n} \tau + n \sigma)} + \\
+	+ (\alpha ^{\nu} _{- n})^{*} \e ^{i (E_{n} \tau + n \sigma)} \bigg) \eta _{\nu \lambda}
+\end{multline}
+and proceed by using the canonical equal-time Poisson bracket between $X^{\mu}$ and $\Pi ^{\nu}$
 \begin{equation}
-	L_{n , p} = \widetilde{L}_{n , p} = 0
-\end{equation} \label{eqn:"Virasoro"-constraints}
-and 0-th oscillation mode related to center of mass momentum
-\begin{equation*}
-	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation*}
+	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
 
@@
 In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
-To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
-\begin{multline} \label{eqn:canonical-momentum}
-	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
-\end{multline}
-and then we proceed to turn the equal-time Poisson bracket relations
-\begin{equation} \label{eqn:Poisson-brackets-1}
-	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:Poisson-brackets-2}
-	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
-\end{equation}
-into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
+
+We turn the equal-time Poisson bracket relations into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
 \begin{equation} \label{eqn:canonical-commutator-1}

### 2024-04-16 lqg-strings.tex
working on main file

@@
 and proceed by using the canonical equal-time Poisson bracket between $X^{\mu}$ and $\Pi ^{\nu}$
-\begin{equation}
+\begin{equation} \label{eqn:equal-time-Poisson-bracket}
 	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
 \end{equation}
+which, under the assumption of constant conformal factor $\phi$, leads to
+\begin{equation} \label{eqn:modes-bracket-0}
+	\left\{ \alpha ^{\mu} _{k} , \alpha ^{\nu} _{- m} \right\} = \left\{ (\alpha ^{\mu} _{- k})^{*} , (\alpha ^{\nu} _{m})^{*} \right\} = 0
+\end{equation}
+\begin{multline} \label{eqn:modes-bracket-oscillator}
+	\left\{ \alpha ^{\mu} _{k} , (\alpha ^{\nu} _{m})^{*} \right\} = - \left\{ (\alpha ^{\mu} _{- k})^{*} , \alpha ^{\nu} _{- m} \right\} = \\
+	- i \frac{4 \pi (\alpha ')^{2}}{F^{-}} E_{k} \eta ^{\mu \nu} \delta _{k , m} .
+\end{multline}
+This are just rescaled harmonic oscillator Poisson bracket relations, so we define the oscillator modes
+\begin{align}
+	a^{\mu} _{k}       & : = \frac{1}{2 \alpha '} \sqrt{\frac{F^{-}}{\pi}} \frac{1}{\sqrt{E_{k}}} \alpha ^{\mu} _{k} \label{eqn:annihilation-mode}      \\
+	(a^{\mu} _{k})^{*} & : =  \frac{1}{2 \alpha '} \sqrt{\frac{F^{-}}{\pi}} \frac{1}{\sqrt{E_{k}}} (\alpha ^{\mu} _{k})^{*} \label{eqn:creation-mode} ,
+\end{align}
+such that the bracket relations become proper harmonic oscillator bracket relations
+\begin{align}
+	\left\{ a^{\mu} _{k} , (a^{\nu} _{p})^{*} \right\} & = - i \eta ^{\mu \nu} \delta _{k , p} \label{eqn:oscillator-bracket}                   \\
+	\left\{ a^{\mu} _{k} , a^{\nu} _{p} \right\}       & = \left\{ (a^{\mu} _{k})^{*} , (a^{\nu} _{p})^{*} \right\} = 0 \label{eqn:0-bracket} .
+\end{align}
+By analysing the $k = p = 0$ case, we also get the relation for $x^{\mu}$ and $p^{\nu}$
+\begin{align}
+	\left\{ x^{\mu} , x^{\nu} \right\} & = \left\{ p^{\mu} , p^{\nu} \right\} = 0 \label{eqn:x-x-p-p-bracket}       \\
+	\left\{ x^{\mu} , p^{\nu} \right\} & = \frac{1}{4 \pi \alpha ' F^{-}} \eta ^{\mu \nu} \label{eqn:x-p-bracket} ,
+\end{align}
+where by choosing
+\begin{equation} \label{eqn:constant-conformal-factor}
+	\phi = \sqrt{\frac{k \Delta}{2 \left( 1 - \dfrac{1}{4 \pi \alpha '} \right)}}
+\end{equation}
+we can simplify the bracket(\ref{eqn:x-p-bracket}) to the expected
+\begin{equation} \label{eqn:x-p-bracket-normalized}
+	\left\{ x^{\mu} , p^{\nu} \right\} = \eta ^{\mu \nu} .
+\end{equation}
+
+Having the bracket algebra between the expansion modes and redefining the constraints $L_{n , m}$ and $\widetilde{L}_{k , p}$ to be between the normalized modes $a^{\mu} _{n}$ instead of the $\alpha ^{\mu} _{n}$ (we can do this since $E_{n} = \sqrt{n^2 + \mu ^2} \neq 0$), we get the \textquotedblleft Klein-Gordon-Virasoro algebra"
+\begin{align}
+	\left\{ L_{n , m} , L_{k , p} \right\}                         & = 0 \label{eqn:L-bracket-0}                                                                                                      \\
+	\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\}             & = - i \left( L_{m, k} \delta _{n , - p} + L_{n , k} \delta _{m , - p} \right) \label{eqn:L-bracket-1}                            \\
+	\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} & = - i \left( \widetilde{L}_{k , m} \delta _{n , - p} - \widetilde{L}_{n , p} \delta _{- m , k} \right) . \label{eqn:L-bracket-2}
+\end{align}
 
@@
 In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
-
-We turn the equal-time Poisson bracket relations into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
-\begin{equation} \label{eqn:canonical-commutator-1}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:canonical-commutator-2}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
-\end{equation}
-From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
-\begin{equation} \label{eqn:non-vanishing-commutator}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
-\end{equation}
-\begin{equation} \label{eqn:vanishing-commutators}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
-\end{equation}
-which are just harmonic oscillator relations with
+We turn the Poisson bracket relations into commutation relations between the now operator variables, $\{ , \} \mapsto i [ , ]$, yielding
 \begin{align}
-	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
-	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
-\end{align}
-For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
+	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:commutator-X-Pi}                                      \\
+	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] = 0 \label{eqn:commutator-X-X-Pi-Pi}                         \\
+	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{m} \right]                           & = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{m})^{\dagger} \right] = 0 \label{eqn:commutator-a-a} \\
+	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{m})^{\dagger} \right]               & = \eta ^{\mu \nu} \delta _{n , m} \label{eqn:commutator-a-a*}                                                   \\
+	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] = 0 \label{eqn:commutator-x-x-p-p}                               \\
+	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} . \label{eqn:commutator-x-p}
+\end{align}
+
+We define a vacuum state for the string to obey
 \begin{equation} \label{eqn:annihilation-vacuum}
-	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
-\end{equation}
-and for $p = 0$
-\begin{equation} \label{eqn:momentum-vacuum}
-	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
-\end{equation}
-Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
+	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
+\end{equation}
+Since $\Hat{a}^{\mu} _{0}$ contains $\Hat{x}^{\mu}$ and $\Hat{p}^{\mu}$, the vacuum also has extra structure from those
+\begin{align}
+	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-x-rep}                               \\
+	\Hat{p}_{\mu} \ket{0 ; x} & = - i \frac{\partial}{\partial x^{\mu}} \ket{0 ; x} \label{eqn:p-x-rep}
+\end{align}
+in position representation and
+\begin{align}
+	\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\partial}{\partial p_{\mu}} \ket{0 ; p} \label{eqn:x-p-rep} \\
+	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-p-rep}
+\end{align}
+in momentum representation. Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
 \begin{multline} \label{eqn:general-state}
-	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
-	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
+	\ket{\psi} = ((\Hat{a}^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((\Hat{a}^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
+	\times ((\Hat{a}^{\nu _1} _{- 1})^{\dagger})^{n_{\nu _1}} ((\Hat{a}^{\mu _2} _{- 2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
 \end{multline}
@@
 \end{equation}
-$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
-\begin{equation} \label{eqn:L-normal-ordering}
-	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
-\end{equation}
-with the annihilation operator to the right, which manifests in the imposition of the constraint as
-\begin{equation} \label{eqn:shifted-L-constraint}
-	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
-\end{equation}
-for some sequence $c_{p}$.
-The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
-Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
-\begin{equation} \label{eqn:alternative-classical-rest-mass}
-	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
-\end{equation}
-from where we can now see that the string mass spectrum will get shifted by
-\begin{equation} \label{eqn:shifted-mass-spectrum}
-	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
-\end{equation}
-Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
-\begin{equation} \label{eqn:cp-limit}
-	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
-\end{equation}
-like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
-
-The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
-\begin{equation} \label{eqn:L-commutators-1}
-	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
-\end{equation}
-\begin{multline} \label{eqn:L-commutators-2}
-	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
-	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
-\end{multline}
-\begin{multline} \label{eqn:L-commutators-3}
-	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
-	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
-	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
-\end{multline}
-The commutator (\ref{eqn:L-commutators-2}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutators-3}) seem like it would have ordering ambiguities for $k - p = 0$ and $n - m = 0$.
-However it has a $(m - n)(k - p)$ factor multiplying the whole expression, so the commutator is $0$, which can also be seen by setting $n = m$ or $k = p$ on the L.H.S, in which case we get $\Hat{\widetilde{L}}_{n , n}$, which is identically equal to $0$ by the $n - m$ factor in front, thus we would be commuting something with $0$, which has to yield 0 on the R.H.S.
-As a result, our \textquotedblleft Virasoro-Klein-Gordon" algebra has no anomalous terms.
 

### 2024-04-23 lqg-strings.tex
just changed a minor thing
pushed the quantisation work to the main file

@@
 \end{equation}
+This is in fact an expected result for a effective theory emerging from a discretised background geometry, see\cite{Bodendorfer-LQG}.
 
@@
 The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}$.
+Also as we shall see, this action yields the exact same equation of motion as a more rigorous bimetric analysis, see appendix(\ref{app:bimetric-string}).
 The equations of motion for the auxiliary metric are completely unchanged by this correction, so they are
@@
 \end{equation}
+The modification to the dispersion relation via the mass term is also an expected effect of a discrete background geometry as mentioned in\cite{Bodendorfer-LQG}.
 
@@
 In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
-We turn the Poisson bracket relations into commutation relations between the now operator variables, $\{ , \} \mapsto i [ , ]$, yielding
+We turn the Poisson bracket relations into commutation relations between the now operator variables, $[ , ] = i \{ , \}$, yielding
 \begin{align}
@@
 \end{equation}
-we have ghosts in the theory which must be dealt with.
+we have ghosts in the theory which must be dealt with(\cite{Tong2009Lectures},\cite{Green2012Superstring}).
 When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
@@
 \end{equation}
-
-\section{Strings and Quantum Geometry}\label{sec:string-geometry}
+\begin{equation} \label{eqn:L-constranit-quantum-sum}
+	\bra{\phi} \sum _{p} \left( \left( \frac{p}{E_{p}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{p , - p} \ket{\psi} = 0 .
+\end{equation}
+
+When translating the constraints as quantum operators, for $\Hat{L}_{p , k}$ we have no ambiguities since it's composed only of annihilation operators.
+As for $\Hat{\widetilde{L}}_{p , k}$, there is an ambiguity when $p = - k$, which manifests in the imposition of this constraint as
+\begin{equation}
+	\bra{\phi} \sum _{p} \left( \left( \left( \frac{p}{E_{p}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{p , - p} \right) - a \ket{\psi} = 0 ,
+\end{equation}
+for some constant $a$\cite{Green2012Superstring}. This constant appears in the mass spectrum of the quantum string as in
+\begin{multline}
+	\Hat{M}^2 = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' \mu)^{2} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
+	- \left( \sum _{n \neq 0} \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} - a \right) \Bigg) .
+\end{multline}
+The commutation algebra of constraints is inherited by the constraint algebra(\ref{eqn:L-bracket-0},\ref{eqn:L-bracket-1},\ref{eqn:L-bracket-2}), namely
+\begin{equation} \label{eqn:L-commutator-0}
+	\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right] = 0
+\end{equation}
+\begin{equation} \label{eqn:L-commutator-1}
+	\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{L}_{m , k} \delta _{n , - p} + \Hat{L}_{n , k} \delta _{m , - p}
+\end{equation}
+\begin{equation} \label{eqn:L-commutator-2}
+	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{n , - p} - \Hat{\widetilde{L}}_{n , p} \delta _{- m , k} .
+\end{equation}
+The only commutator with ordering ambiguities is(\ref{eqn:L-commutator-2}) when $m = - k$ and $p = -n$, thus we include anomalous terms\cite{Green2012Superstring}
+\begin{multline} \label{eqn:L-commutator-anomalous}
+	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{n , - p} - \Hat{\widetilde{L}}_{n , p} \delta _{- m , k} + \\
+	+ C_{n} \delta _{n , -p} + D_{k} \delta _{- m , k} .
+\end{multline}
+By noting that $C_{- n} = - C_{n}$ and $D_{- n} = - D_{n}$ and using the Jacobi identity of the commutator, we conclude that $C_{n} = - D_{n} = C_{1} n$, where we can find the value of $C_{1}$ by calculating the vacuum expectation value of the commutator $[\Hat{\widetilde{L}}_{1 , k} , \Hat{\widetilde{L}}_{k , - 1}]$, which yields that $C_{1} = 0$, thus {\it the quantum algebra of our constraints has no anomalies}.
+This is a very important result, since it doesn't constrain the dimension of the background manifold to any particular value, so our model works just as well for $D = 4$ as for any other value {\it a priori}.
+
+After analysing the mass-shell condition for the $n$-th excited state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger} \ket{0 ; p}$\cite{Green2012Superstring}, under the assumption that the momentum wave-function is given by [justification needed]
+\begin{equation} \label{eqn:p-wave-func}
+	\psi (p) = \frac{\alpha '}{\mu} p^{2} ,
+\end{equation}
+we find that $\zeta _{\mu} p^{\mu} = 0$ and the momentum of this state is given by
+\begin{equation} \label{eqn:nth-vector-mode-momentum}
+	2 (4 \pi (\alpha ')^2)^2 p^2 = \frac{n^2}{n^2 + \mu ^2} - 1 - a .
+\end{equation}
+From this, for the absence of ghosts we then require that
+\begin{equation} \label{eqn:a-condition-no-ghosts}
+	a \geq \frac{d^2}{d^2 + \mu ^2} - 1 .
+\end{equation}
+In the boundary case, the $d$-th ($d = D - 1$) vector state is massless, while the other spin-1 states are massive and the ground state is a tachyon.
+Doing a similar analysis for the $d$-th spin-2 state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ with $\zeta _{\mu \nu} = \zeta _{\nu \mu}$ and $\zeta _{\ \mu} ^{\mu} = 0$ yields $\zeta _{\mu \nu} p^{\mu} = \zeta _{\mu \nu} p^{\nu} = 0$ and
+\begin{equation} \label{eqn:a-conition-massless-spin-2}
+	a = 2 \left( \frac{d^{2}}{d^{2} + \mu ^{2}} - 1 \right)
+\end{equation}
+for it to be massless.
+However, the quantity in parenthesis is negative, so doubling it makes it less than the minimum condition for the absense of ghosts(\ref{eqn:a-condition-no-ghosts}), thus we can't get massless spin-2 states.
+This is not really a problem because as pointed out in\cite{Bodendorfer-LQG}, a discrete background geometry modifies the dispersion relation at the effective level, so even tho at the fundamental level gravity would travel at $c$, in the effective limit it would appear \textquotedblleft massive", however with a very small mass.
+Thus, since we need $a$ to be at least as big as in(\ref{eqn:a-condition-no-ghosts}), we can choose $a > 0$ to also get rid of the ground state tachyon without the need to introduce supersymmetry or other unverified hypothesis.
+
+The most natural value for $a$ is $a = 1$, which comes from the analysis of physical and spurious states\cite{Green2012Superstring} of the form
+\begin{equation} \label{eqn:phys-spurious-state}
+	\ket{\psi _{- 2 , n}} = \sum _{m} \Hat{\widetilde{L}}_{n , m} \ket{\widetilde{\chi}_{- 2 , m}} ,
+\end{equation}
+where $\ket{\widetilde{\chi}_{- 2 , m}}$ satisfies the constraints(\ref{eqn:L-constraint-quantum-1},\ref{eqn:L-constraint-quantum-2}) and also
+\begin{multline} \label{eqn:spurious-basis-condition}
+	\Bigg( \sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{n , - n} \right) - \\
+	- a + 2 - m \Bigg) \ket{\widetilde{\chi}_{- 2 , m}} = 0 .
+\end{multline}
+States of the form(\ref{eqn:phys-spurious-state}) are annihilated by $\Hat{\widetilde{L}}_{p , k}$ for $p \neq - k$, and for these cases we have
+\begin{equation*}
+	\sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{- 1 , - n} \ket{\psi _{- 2 , n}} \right) =
+\end{equation*}
+\begin{multline*}
+	= \sum _{n} \Bigg( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{- 1 , - n} \times \\
+	\times \sum _{m} \Hat{\widetilde{L}}_{n , m} \ket{\widetilde{\chi}_{- 2 , m}} \Bigg)  =
+\end{multline*}
+\begin{equation} \label{eqn:spurious-annihilation}
+	= \sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{n , - n} \right) \ket{\widetilde{\chi}_{- 2 , 1}} ,
+\end{equation}
+which vanishes for $a = 1$.
+
+\section{Strings and Quantum Geometry} \label{sec:string-geometry}
 

### 2024-04-23 lqg-strings.tex
added comments on Poincaré invariance

@@
 
-The action \eqref{eqn:modified-NG-action} has some interesting properties.
-First, on the face of it it does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
-Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
-However, if we look at that expression we see that it can be written as:
-\begin{equation} \label{eqn:modified-NG-action-v2}
-	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {g \Delta}{\sqrt{- (h^{-1})}} \right),
-\end{equation}
-where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$.
-So, while the second term is not diffeomorphism invariant \wrt the original metric $h_{ab}$ it is clearly diffeomorphism invariant \wrt the inverse metric $h^{ab}$.
-
-Second, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
+Although the action\eqref{eqn:modified-NG-action} is clearly not reparameterisation invariant anymore since the second term has a inverse metric determinant, thus under reparameterisation would pick up a squared Jacobian, it is still manifestly Poincaré invariant, since it only contains derivatives of $X^{\mu}$, thus it's variations vanish under global Lorentz transformations and translations.
+At face value, this action does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
+This stems from the fact that we are assuming the existence of a minimum quantum of area, so it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
+
+In the expression\eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
 If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
@@
 Also as we shall see, this action yields the exact same equation of motion as a more rigorous bimetric analysis, see appendix(\ref{app:bimetric-string}).
+This action has the same properties as\eqref{eqn:modified-NG-action}: it is not reparameterisation invariant but is evidently Poincaré-invariant.
+
 The equations of motion for the auxiliary metric are completely unchanged by this correction, so they are
@@
 
-It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+It would be natural to suspect that the action\eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
 We can see that this is indeed the case as follows.
 
-Consider a string propagating in a target space whose geometry is described by two bulk metrics.
 There are two ways that a string with two metrics might arise.

### 2024-04-24 lqg-strings.tex
showed Poincaré invariance of corrected NG and Polyakov action in the main file

@@
 
-Although the action\eqref{eqn:modified-NG-action} is clearly not reparameterisation invariant anymore since the second term has a inverse metric determinant, thus under reparameterisation would pick up a squared Jacobian, it is still manifestly Poincaré invariant, since it only contains derivatives of $X^{\mu}$, thus it's variations vanish under global Lorentz transformations and translations.
+The action\eqref{eqn:modified-NG-action} is still manifestly Poincaré invariant, since it only contains derivatives of $X^{\mu}$, thus it's variations vanish under global translations as in
+\begin{equation} \label{eqn:global-inf-transl-NG}
+	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu} ,
+\end{equation}
+thus $\delta (\partial _{a} X^{\mu}) = \partial _{a} (\delta X^{\mu}) = \partial _{a} \epsilon ^{\mu} \equiv 0$. As for Lorentz transformations, we have that
+\begin{equation} \label{eqn:global-inf-LT-NG}
+	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu \nu} X_{\nu} ,
+\end{equation}
+and since every term in the action is of the form
+\begin{equation} \label{eqn:NG-general-term-form}
+	\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+with $\epsilon ^{\mu \nu} = - \epsilon ^{\nu \mu}$, we see immediately that the transformation leaves the action unchanged:
+\begin{equation*}
+	\delta (\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}) =
+\end{equation*}
+\begin{equation*}
+	= (\partial _{a} (\delta X^{\mu}) \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} (\delta X^{\nu})) \eta _{\mu \nu} =
+\end{equation*}
+\begin{equation*}
+	= (\epsilon ^{\mu \rho} \partial _{a} X_{\rho} \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} X_{\rho} \epsilon ^{\nu \rho}) \eta _{\mu \nu} =
+\end{equation*}
+\begin{equation*}
+	= \epsilon _{\nu \mu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} + \epsilon _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} =
+\end{equation*}
+\begin{equation} \label{eqn:vanishing-inf-LT-NG}
+	= (\epsilon _{\mu \nu} + \epsilon _{\nu \mu}) \partial _{a} X^{\mu} \partial _{b} X^{\nu} \equiv 0
+\end{equation}
+by the anti-symmetry of $\epsilon _{\mu \nu}$.
 At face value, this action does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
@@
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
-	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
-\end{multline}
-The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}$.
-Also as we shall see, this action yields the exact same equation of motion as a more rigorous bimetric analysis, see appendix(\ref{app:bimetric-string}).
-This action has the same properties as\eqref{eqn:modified-NG-action}: it is not reparameterisation invariant but is evidently Poincaré-invariant.
+	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
+\end{multline}
+The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}$.
+This action has the same properties as\eqref{eqn:modified-NG-action}: it is not reparameterisation invariant but is evidently Poincaré-invariant by the same arguments as before.
 
@@
 \begin{multline} \label{eqn:inverse-area-em-tensor}
-	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
+	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} = 0 ,
 \end{multline}
@@
 \begin{equation} \label{eqn:ws-metric}
-	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} ,
 \end{equation}
@@
 \begin{equation} \label{eqn:inverse-area-f}
-	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
+	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
 \end{equation}
@@
 \begin{multline} \label{eqn:X-eom-inverse-area}
-	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
-\end{multline}
-where $F^{-} = 1 - k \Delta / 2 (- g)$.
-In conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} \eta _{\lambda \nu} + \\
+	+ \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} \eta _{\lambda \nu} = 0 ,
+\end{multline}
+where $F^{-} = 1 - k \Delta / 2 (- g)$. In conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-final}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
 	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)

### 2024-04-24 lqg-strings.tex
justified choice of parameterisation of NG corrected string below eq(19)

@@
 
-Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$.
+The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen because this parameterisation implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation.
+From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
 \begin{equation} \label{eqn:string-energy}

### 2024-04-24 lqg-strings.tex
minro wording change to justification below eqn(19)

@@
 In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$.
-The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen because this parameterisation implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation.
+The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen such that the $\sigma$ parameter is parallel to the parameter $s$, which is the length along the string parameter and this implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation.
 From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor

### 2024-04-25 lqg-strings.tex
added a paragraph justifying the use of conformal gauge below eqn(34)
added citation for every 2d metric is conformally flat theorem
minor wording change in paragraph below eqn(34)
minor wording changes and addition of bimetric analysis to main file

@@
 \begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} = \frac{E (q)}{T (F^+)^2} ,
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
 \end{equation}
@@
 \end{equation}
+The reason we can still use conformal gauge even tho our action no longer has Weyl symmetry is because of a theorem stating that {\it every 2d metric is conformally flat}(theorem 7.2 in\cite{Schottenloher}).
 
@@
 \end{equation}
-from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal factor to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{align}\label{eqn:polyakov-flat}
-	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber \\
-	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
-\end{align}
+\begin{multline} \label{eqn:bimetric-Polyakov}
+	S_{BP} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} - \\
+	-\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \\
+	+ \int \diff ^2 x \Phi (g , h) \Psi (X) \Theta (G , H) ,
+\end{multline}
+where the last term defines an interaction term $S_{int}$.
 
@@
 \begin{equation} \label{eqn:variation-wrt-g}
-	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
+	\frac{\delta S_{B P}}{\delta g^{c d}} = 0
 \end{equation}
@@
 	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}}
 \end{multline}
@@
 \begin{equation} \label{eqn:g-expression}
-	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+	g_{c d} = 2 f^{(G)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \frac{2}{T \sqrt{- g}} \frac{\delta S_{int}}{\delta g^{c d}} \right) ,
 \end{equation}
@@
 \begin{equation} \label{eqn:variation-wrt-h}
-	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
+	\frac{\delta S_{B P}}{\delta h^{c d}} = 0
 \end{equation}
@@
 	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
-	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}}
 \end{multline}
 \begin{equation} \label{eqn:h-expression}
-	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
+	h_{c d} = 2 f^{(H)} \left( \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} - \frac{2}{T' \sqrt{- h}} \frac{\delta S_{int}}{\delta h^{c d}} \right) ,
 \end{equation}
@@
 \end{equation}
+If $S_{int} = 0$ and the auxiliary metrics $g_{a b}$ and $h_{a b}$ coincide with the induced metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, then the action\eqref{eqn:bimetric-Polyakov} reduces to
+\begin{equation} \label{eqn:reduced-bimetric-action}
+	S' _{B P} = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
+\end{equation}
+which, if $T' = - T k \Delta / 2$ and $h = g^{-1}$ becomes precisely the Nambu-Goto area corrected action\eqref{eqn:modified-NG-action}. The condition $h = g^{-1}$ can be achieved by
+\begin{equation} \label{eqn:h=SgS}
+	h_{a b} = S_{a c} g^{c d} S_{d b} ,
+\end{equation}
+where $S \in \mathrm{SL}(2 , \mathbb{C})$.
+The fact that we require $S = S^{\dagger}$ for $h$ to be real and symmetric restricts $S$ to be a boost.
+By requiring that the induced metric by $H_{\mu \nu}$ be equal to\eqref{eqn:h=SgS}, we get
+\begin{equation} \label{eqn:H-from-SgS}
+	\partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} = S_{a c} g^{c d} S_{d b}
+\end{equation}
+from which follows
+\begin{equation}
+	H_{\mu \nu} = \frac{1}{8 (- g)} (\Tr (S \varepsilon))^2 G_{\mu \nu} ,
+\end{equation}
+constraining $S$ to necessarily being not symmetric otherwise the trace $\Tr (S \varepsilon)$ vanishes and we would get $H _{\mu \nu} = 0$.
+In fact, to recover the modified Nambu-Goto action\eqref{eqn:modified-NG-action}, we require $(\Tr (S \varepsilon))^2 = 8$, thus $H_{\mu \nu} = G_{\mu \nu} / (- g)$.
 
@@
 \begin{equation} \label{eqn:variation-wrt-X}
-	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
-\end{equation}
+	\frac{\delta S_{P B}}{\delta X^{\lambda}} = 0
+\end{equation}
+\begin{equation} \label{eqn:bimetric-X-eom}
+	\partial _{a} \left( F^{a b} _{\mu \lambda} \partial _{b} X^{\mu} \right) = \frac{1}{2} \partial _{\lambda} F^{a b} _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} ,
+\end{equation}
+where the coupled double-metric $F^{a b} _{\mu \nu}$ is given by
+\begin{equation} \label{eqn:coupled-double-metric}
+	F^{a b} _{\mu \nu} = T \sqrt{- g} g^{a b} G_{\mu \nu} + T' \sqrt{- h} h^{a b} H_{\mu \nu} .
+\end{equation}
+If the conditions for $h = g^{-1}$ are satisfied and $G_{\mu \nu} = \eta _{\mu \nu}$, eq\eqref{eqn:bimetric-X-eom} reduces to
+\begin{multline} \label{eqn:bimetric-X-simplified-1}
+	\partial _{a} \big( \big( \sqrt{- g} g^{a b} - \\
+	- \frac{k \Delta}{2 (- g)} \sqrt{- g}^{-1} (S^{-1})^{a c} g_{c d} (S^{-1})^{d b} \big) \partial _{b} X^{\mu} \big) = 0 ,
+\end{multline}
+which in conformal gauge $g_{a b} = \phi (x) \eta _{a b}$ and with
+\begin{equation} \label{eqn:S-simplification-condition}
+	(S^{-1})^{a c} \eta _{c d} (S^{-1})^{d b} = \eta ^{a b}
+\end{equation}
+simplifies further to
+\begin{equation} \label{eqn:bimetric-eom-simplified}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \partial _{a} \ln (F^{-}) \partial _{b} X^{\mu} = 0 .
+\end{equation}
+This is the exact form derived earlier in\eqref{eqn:X-eom-simplified}, thus leading to the same Klein-Gordon equation.
 

### 2024-04-25 lqg-strings.tex
minor wording changes in bimetric section of main file and sketching

@@
 
-Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
+Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the auxiliary metrics $g_{c d}$ and $h_{c d}$:
 \begin{equation} \label{eqn:variation-wrt-g}
@@
 where $S \in \mathrm{SL}(2 , \mathbb{C})$.
-The fact that we require $S = S^{\dagger}$ for $h$ to be real and symmetric restricts $S$ to be a boost.
+The fact that we require $S = S^{\dagger}$ for $h$ to be real and symmetric restricts $S$ to be in the boosts sector of $\mathrm{SL}(2 , \mathbb{C})$.
 By requiring that the induced metric by $H_{\mu \nu}$ be equal to\eqref{eqn:h=SgS}, we get

### 2024-04-28 lqg-strings.tex
Started section on Einstein-Cartan string

--- 2024-04-24 lqg-strings.tex
@@
 
-The action\eqref{eqn:modified-NG-action} is still manifestly Poincaré invariant, since it only contains derivatives of $X^{\mu}$, thus it's variations vanish under global translations as in
-\begin{equation} \label{eqn:global-inf-transl-NG}
-	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu} ,
-\end{equation}
-thus $\delta (\partial _{a} X^{\mu}) = \partial _{a} (\delta X^{\mu}) = \partial _{a} \epsilon ^{\mu} \equiv 0$. As for Lorentz transformations, we have that
-\begin{equation} \label{eqn:global-inf-LT-NG}
-	X^{\mu} \mapsto X^{\mu} + \epsilon ^{\mu \nu} X_{\nu} ,
-\end{equation}
-and since every term in the action is of the form
-\begin{equation} \label{eqn:NG-general-term-form}
-	\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} ,
-\end{equation}
-with $\epsilon ^{\mu \nu} = - \epsilon ^{\nu \mu}$, we see immediately that the transformation leaves the action unchanged:
-\begin{equation*}
-	\delta (\partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}) =
-\end{equation*}
-\begin{equation*}
-	= (\partial _{a} (\delta X^{\mu}) \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} (\delta X^{\nu})) \eta _{\mu \nu} =
-\end{equation*}
-\begin{equation*}
-	= (\epsilon ^{\mu \rho} \partial _{a} X_{\rho} \partial _{b} X^{\nu} + \partial _{a} X^{\mu} \partial _{b} X_{\rho} \epsilon ^{\nu \rho}) \eta _{\mu \nu} =
-\end{equation*}
-\begin{equation*}
-	= \epsilon _{\nu \mu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} + \epsilon _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} =
-\end{equation*}
-\begin{equation} \label{eqn:vanishing-inf-LT-NG}
-	= (\epsilon _{\mu \nu} + \epsilon _{\nu \mu}) \partial _{a} X^{\mu} \partial _{b} X^{\nu} \equiv 0
-\end{equation}
-by the anti-symmetry of $\epsilon _{\mu \nu}$.
-At face value, this action does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
-This stems from the fact that we are assuming the existence of a minimum quantum of area, so it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
-
-In the expression\eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
+The action \eqref{eqn:modified-NG-action} has some interesting properties.
+First, on the face of it it does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
+Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
+However, if we look at that expression we see that it can be written as:
+\begin{equation} \label{eqn:modified-NG-action-v2}
+	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {g \Delta}{\sqrt{- (h^{-1})}} \right),
+\end{equation}
+where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$.
+So, while the second term is not diffeomorphism invariant \wrt the original metric $h_{ab}$ it is clearly diffeomorphism invariant \wrt the inverse metric $h^{ab}$.
+
+Second, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
 If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
@@
 
-In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$.
-The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen such that the $\sigma$ parameter is parallel to the parameter $s$, which is the length along the string parameter and this implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation.
-From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
 \begin{equation} \label{eqn:string-energy}
@@
 \end{equation}
-This is in fact an expected result for a effective theory emerging from a discretised background geometry, see\cite{Bodendorfer-LQG}.
 
@@
 In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string.
-We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
-	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
-\end{multline}
-The reason for considering this form and not one in which the inverse metric $g^{a b}$ also gets a correction term is that this form of a Polyakov inverse area-corrected action reduces nicely to the Nambu-Goto corrected action(\ref{eqn:modified-NG-action}) when the auxiliary metric $g_{a b}$ coincides with the induced metric $h_{a b} = \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu}$.
-This action has the same properties as\eqref{eqn:modified-NG-action}: it is not reparameterisation invariant but is evidently Poincaré-invariant by the same arguments as before.
-
-The equations of motion for the auxiliary metric are completely unchanged by this correction, so they are
+	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
+\end{multline}
+The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
 \begin{equation} \label{eqn:vary-wrt-g}
-	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
+	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
 \end{equation}
@@
 \begin{multline} \label{eqn:inverse-area-em-tensor}
-	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} = 0 ,
+	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
 \end{multline}
@@
 \begin{equation} \label{eqn:ws-metric}
-	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} \eta _{\mu \nu} ,
+	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
 \end{equation}
@@
 \begin{equation} \label{eqn:inverse-area-f}
-	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \eta _{\mu \nu} .
+	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
 \end{equation}
@@
 \begin{equation} \label{eqn:vary-wrt-X}
-	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
+	\frac{\delta S_{I A P}}{\delta X^{\lambda}} \overset{!}{=} 0
 \end{equation}
@@
 \begin{multline} \label{eqn:X-eom-inverse-area}
-	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} \eta _{\lambda \nu} + \\
-	+ \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} \eta _{\lambda \nu} = 0 ,
-\end{multline}
-where $F^{-} = 1 - k \Delta / 2 (- g)$. In conformal gauge $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
+\end{multline}
+where $F^{-} = 1 - k \Delta / 2 (- g)$.
+Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 \end{equation}
-from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 \end{equation}
-At first glance it seems problematic that we have a complex conformal factor $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it will also pick the respective component of $\phi$.
+At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$.
 With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
@@
 \end{equation}
-The modification to the dispersion relation via the mass term is also an expected effect of a discrete background geometry as mentioned in\cite{Bodendorfer-LQG}.
 
@@
 However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
-While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence.
+While they're work deals only with space-varying wave speed, it is straight forward to generalise the procedure to also include time dependence, but ironically enough the calculations lead to the conclusion that the wave speed $v = 1 / F^{+}$ is actually time independent.
 
@@
 \end{multline}
-with $E_{p} = \sqrt{p^2 + \mu ^2}$ for the closed string.
-From here on, we shall deal only with closed strings, unless otherwise stated.
-Following an analogous procedure to the one found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
+with $E_{p} = \sqrt{p^2 + \mu ^2}$.
+From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
 \begin{equation} \label{eqn:reality-consequence}
@@
 \begin{align}
-	L_{n , p}              & := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu} = 0 , \ \forall \ n , p \in \mathbb{Z} \label{eqn:"Virasoro"-modes-1} \\
-	\widetilde{L} _{n , p} & := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{- p})^{*} \eta _{\mu \nu} = 0 , \ n \neq - p \label{eqn:"Virasoro"-modes-2}
+	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
+	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
 \end{align}
-\begin{equation} \label{eqn:"Virasoro"-modes-sum}
-	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
-\end{equation}
-
-Before proceeding, we have one more remark: the 0-th term of the solution reads
+
+Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
 \begin{equation} \label{eqn:X-sol-0-term}
@@
 \end{equation}
-which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$.
+which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$.
 Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
 \begin{equation} \label{eqn:a-p-relation}
-	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation}
-
-After analysing closer the $n = - p$ constraint(\ref{eqn:"Virasoro"-modes-sum}), we get the string mass in terms of vibrational modes and center of mass position
-\begin{multline} \label{eqn:string-rest-mass}
-	M^2 = - p^{\mu} p_{\mu} = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' m)^{2} x^{\mu} x_{\mu} - \\
-	- \sum _{n \neq 0} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) a^{\mu} _{n} (a^{\nu} _{n})^{*} \eta _{\mu \nu} \right) \Bigg) .
-\end{multline}
-
-Collecting our results, we have that the solution for our closed string is given by
+	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
+\end{equation}
+Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
+\begin{equation} \label{eqn:string-rest-mass}
+	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
+\end{equation}
+
+Collecting our results, we have that the solution for our string is given by
 \begin{multline} \label{eqn:KG-Polyakov-solution-final}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
 	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
 \end{multline}
-subject to the family of constraints
-\begin{equation} \label{eqn:"Virasoro"-constraints}
+subject to the infinite family of constraints
+\begin{equation}
 	L_{n , p} = \widetilde{L}_{n , p} = 0
-\end{equation}
+\end{equation} \label{eqn:"Virasoro"-constraints}
+and 0-th oscillation mode related to center of mass momentum
 \begin{equation*}
-	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
+	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
 \end{equation*}
-and 0-th oscillator mode related to center of mass position and momentum
-\begin{equation*}
-	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation*}
-One thing to note is that the constraint(\ref{eqn:"Virasoro"-modes-2}) implies we only have $D$ non-zero modes in the solution, since all modes must be mutually orthogonal.
-
-\subsection{The Modes and Constraints Algebra} \label{sec:modes-constraint-algebra}
-
-We start by calculating the momentum canonical to $X^{\mu}$, $\Pi _{\lambda}$:
+
+\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
+
+In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
+To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
 \begin{multline} \label{eqn:canonical-momentum}
-	\Pi _{\lambda} = \frac{\partial \Lagr}{\partial (\partial _{\tau} X^{\lambda})} = \\
-	= F^{-} \frac{i}{4 \pi \alpha '} \sum _{n \in \mathbb{Z}} \bigg( - \alpha ^{\nu} _{n} \e ^{i (- E_{n} \tau + n \sigma)} + \\
-	+ (\alpha ^{\nu} _{- n})^{*} \e ^{i (E_{n} \tau + n \sigma)} \bigg) \eta _{\nu \lambda}
-\end{multline}
-and proceed by using the canonical equal-time Poisson bracket between $X^{\mu}$ and $\Pi ^{\nu}$
-\begin{equation} \label{eqn:equal-time-Poisson-bracket}
+	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
+	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
+\end{multline}
+and then we proceed to turn the equal-time Poisson bracket relations
+\begin{equation} \label{eqn:Poisson-brackets-1}
 	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
 \end{equation}
-which, under the assumption of constant conformal factor $\phi$, leads to
-\begin{equation} \label{eqn:modes-bracket-0}
-	\left\{ \alpha ^{\mu} _{k} , \alpha ^{\nu} _{- m} \right\} = \left\{ (\alpha ^{\mu} _{- k})^{*} , (\alpha ^{\nu} _{m})^{*} \right\} = 0
-\end{equation}
-\begin{multline} \label{eqn:modes-bracket-oscillator}
-	\left\{ \alpha ^{\mu} _{k} , (\alpha ^{\nu} _{m})^{*} \right\} = - \left\{ (\alpha ^{\mu} _{- k})^{*} , \alpha ^{\nu} _{- m} \right\} = \\
-	- i \frac{4 \pi (\alpha ')^{2}}{F^{-}} E_{k} \eta ^{\mu \nu} \delta _{k , m} .
-\end{multline}
-This are just rescaled harmonic oscillator Poisson bracket relations, so we define the oscillator modes
+\begin{equation} \label{eqn:Poisson-brackets-2}
+	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
+\end{equation}
+into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
+\begin{equation} \label{eqn:canonical-commutator-1}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
+\begin{equation} \label{eqn:canonical-commutator-2}
+	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
+\end{equation}
+From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
+\begin{equation} \label{eqn:non-vanishing-commutator}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
+\end{equation}
+\begin{equation} \label{eqn:vanishing-commutators}
+	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
+\end{equation}
+which are just harmonic oscillator relations with
 \begin{align}
-	a^{\mu} _{k}       & : = \frac{1}{2 \alpha '} \sqrt{\frac{F^{-}}{\pi}} \frac{1}{\sqrt{E_{k}}} \alpha ^{\mu} _{k} \label{eqn:annihilation-mode}      \\
-	(a^{\mu} _{k})^{*} & : =  \frac{1}{2 \alpha '} \sqrt{\frac{F^{-}}{\pi}} \frac{1}{\sqrt{E_{k}}} (\alpha ^{\mu} _{k})^{*} \label{eqn:creation-mode} ,
+	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
+	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
 \end{align}
-such that the bracket relations become proper harmonic oscillator bracket relations
-\begin{align}
-	\left\{ a^{\mu} _{k} , (a^{\nu} _{p})^{*} \right\} & = - i \eta ^{\mu \nu} \delta _{k , p} \label{eqn:oscillator-bracket}                   \\
-	\left\{ a^{\mu} _{k} , a^{\nu} _{p} \right\}       & = \left\{ (a^{\mu} _{k})^{*} , (a^{\nu} _{p})^{*} \right\} = 0 \label{eqn:0-bracket} .
-\end{align}
-By analysing the $k = p = 0$ case, we also get the relation for $x^{\mu}$ and $p^{\nu}$
-\begin{align}
-	\left\{ x^{\mu} , x^{\nu} \right\} & = \left\{ p^{\mu} , p^{\nu} \right\} = 0 \label{eqn:x-x-p-p-bracket}       \\
-	\left\{ x^{\mu} , p^{\nu} \right\} & = \frac{1}{4 \pi \alpha ' F^{-}} \eta ^{\mu \nu} \label{eqn:x-p-bracket} ,
-\end{align}
-where by choosing
-\begin{equation} \label{eqn:constant-conformal-factor}
-	\phi = \sqrt{\frac{k \Delta}{2 \left( 1 - \dfrac{1}{4 \pi \alpha '} \right)}}
-\end{equation}
-we can simplify the bracket(\ref{eqn:x-p-bracket}) to the expected
-\begin{equation} \label{eqn:x-p-bracket-normalized}
-	\left\{ x^{\mu} , p^{\nu} \right\} = \eta ^{\mu \nu} .
-\end{equation}
-
-Having the bracket algebra between the expansion modes and redefining the constraints $L_{n , m}$ and $\widetilde{L}_{k , p}$ to be between the normalized modes $a^{\mu} _{n}$ instead of the $\alpha ^{\mu} _{n}$ (we can do this since $E_{n} = \sqrt{n^2 + \mu ^2} \neq 0$), we get the \textquotedblleft Klein-Gordon-Virasoro algebra"
-\begin{align}
-	\left\{ L_{n , m} , L_{k , p} \right\}                         & = 0 \label{eqn:L-bracket-0}                                                                                                      \\
-	\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\}             & = - i \left( L_{m, k} \delta _{n , - p} + L_{n , k} \delta _{m , - p} \right) \label{eqn:L-bracket-1}                            \\
-	\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} & = - i \left( \widetilde{L}_{k , m} \delta _{n , - p} - \widetilde{L}_{n , p} \delta _{- m , k} \right) . \label{eqn:L-bracket-2}
-\end{align}
-
-\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
-
-In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
-We turn the Poisson bracket relations into commutation relations between the now operator variables, $[ , ] = i \{ , \}$, yielding
-\begin{align}
-	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:commutator-X-Pi}                                      \\
-	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] = 0 \label{eqn:commutator-X-X-Pi-Pi}                         \\
-	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{m} \right]                           & = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{m})^{\dagger} \right] = 0 \label{eqn:commutator-a-a} \\
-	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{m})^{\dagger} \right]               & = \eta ^{\mu \nu} \delta _{n , m} \label{eqn:commutator-a-a*}                                                   \\
-	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] = 0 \label{eqn:commutator-x-x-p-p}                               \\
-	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} . \label{eqn:commutator-x-p}
-\end{align}
-
-We define a vacuum state for the string to obey
+For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
 \begin{equation} \label{eqn:annihilation-vacuum}
-	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
-\end{equation}
-Since $\Hat{a}^{\mu} _{0}$ contains $\Hat{x}^{\mu}$ and $\Hat{p}^{\mu}$, the vacuum also has extra structure from those
-\begin{align}
-	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-x-rep}                               \\
-	\Hat{p}_{\mu} \ket{0 ; x} & = - i \frac{\partial}{\partial x^{\mu}} \ket{0 ; x} \label{eqn:p-x-rep}
-\end{align}
-in position representation and
-\begin{align}
-	\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\partial}{\partial p_{\mu}} \ket{0 ; p} \label{eqn:x-p-rep} \\
-	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-p-rep}
-\end{align}
-in momentum representation. Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
+	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
+\end{equation}
+and for $p = 0$
+\begin{equation} \label{eqn:momentum-vacuum}
+	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
+\end{equation}
+Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
 \begin{multline} \label{eqn:general-state}
-	\ket{\psi} = ((\Hat{a}^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((\Hat{a}^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
-	\times ((\Hat{a}^{\nu _1} _{- 1})^{\dagger})^{n_{\nu _1}} ((\Hat{a}^{\mu _2} _{- 2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
+	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
+	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
 \end{multline}
@@
 \end{equation}
-we have ghosts in the theory which must be dealt with(\cite{Tong2009Lectures},\cite{Green2012Superstring}).
+we have ghosts in the theory which must be dealt with.
 When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
@@
 \end{equation}
-\begin{equation} \label{eqn:L-constranit-quantum-sum}
-	\bra{\phi} \sum _{p} \left( \left( \frac{p}{E_{p}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{p , - p} \ket{\psi} = 0 .
-\end{equation}
-
-When translating the constraints as quantum operators, for $\Hat{L}_{p , k}$ we have no ambiguities since it's composed only of annihilation operators.
-As for $\Hat{\widetilde{L}}_{p , k}$, there is an ambiguity when $p = - k$, which manifests in the imposition of this constraint as
-\begin{equation}
-	\bra{\phi} \sum _{p} \left( \left( \left( \frac{p}{E_{p}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{p , - p} \right) - a \ket{\psi} = 0 ,
-\end{equation}
-for some constant $a$\cite{Green2012Superstring}. This constant appears in the mass spectrum of the quantum string as in
-\begin{multline}
-	\Hat{M}^2 = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' \mu)^{2} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
-	- \left( \sum _{n \neq 0} \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} - a \right) \Bigg) .
-\end{multline}
-The commutation algebra of constraints is inherited by the constraint algebra(\ref{eqn:L-bracket-0},\ref{eqn:L-bracket-1},\ref{eqn:L-bracket-2}), namely
-\begin{equation} \label{eqn:L-commutator-0}
-	\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right] = 0
-\end{equation}
-\begin{equation} \label{eqn:L-commutator-1}
-	\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{L}_{m , k} \delta _{n , - p} + \Hat{L}_{n , k} \delta _{m , - p}
-\end{equation}
-\begin{equation} \label{eqn:L-commutator-2}
-	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{n , - p} - \Hat{\widetilde{L}}_{n , p} \delta _{- m , k} .
-\end{equation}
-The only commutator with ordering ambiguities is(\ref{eqn:L-commutator-2}) when $m = - k$ and $p = -n$, thus we include anomalous terms\cite{Green2012Superstring}
-\begin{multline} \label{eqn:L-commutator-anomalous}
-	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{n , - p} - \Hat{\widetilde{L}}_{n , p} \delta _{- m , k} + \\
-	+ C_{n} \delta _{n , -p} + D_{k} \delta _{- m , k} .
-\end{multline}
-By noting that $C_{- n} = - C_{n}$ and $D_{- n} = - D_{n}$ and using the Jacobi identity of the commutator, we conclude that $C_{n} = - D_{n} = C_{1} n$, where we can find the value of $C_{1}$ by calculating the vacuum expectation value of the commutator $[\Hat{\widetilde{L}}_{1 , k} , \Hat{\widetilde{L}}_{k , - 1}]$, which yields that $C_{1} = 0$, thus {\it the quantum algebra of our constraints has no anomalies}.
-This is a very important result, since it doesn't constrain the dimension of the background manifold to any particular value, so our model works just as well for $D = 4$ as for any other value {\it a priori}.
-
-After analysing the mass-shell condition for the $n$-th excited state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger} \ket{0 ; p}$\cite{Green2012Superstring}, under the assumption that the momentum wave-function is given by [justification needed]
-\begin{equation} \label{eqn:p-wave-func}
-	\psi (p) = \frac{\alpha '}{\mu} p^{2} ,
-\end{equation}
-we find that $\zeta _{\mu} p^{\mu} = 0$ and the momentum of this state is given by
-\begin{equation} \label{eqn:nth-vector-mode-momentum}
-	2 (4 \pi (\alpha ')^2)^2 p^2 = \frac{n^2}{n^2 + \mu ^2} - 1 - a .
-\end{equation}
-From this, for the absence of ghosts we then require that
-\begin{equation} \label{eqn:a-condition-no-ghosts}
-	a \geq \frac{d^2}{d^2 + \mu ^2} - 1 .
-\end{equation}
-In the boundary case, the $d$-th ($d = D - 1$) vector state is massless, while the other spin-1 states are massive and the ground state is a tachyon.
-Doing a similar analysis for the $d$-th spin-2 state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ with $\zeta _{\mu \nu} = \zeta _{\nu \mu}$ and $\zeta _{\ \mu} ^{\mu} = 0$ yields $\zeta _{\mu \nu} p^{\mu} = \zeta _{\mu \nu} p^{\nu} = 0$ and
-\begin{equation} \label{eqn:a-conition-massless-spin-2}
-	a = 2 \left( \frac{d^{2}}{d^{2} + \mu ^{2}} - 1 \right)
-\end{equation}
-for it to be massless.
-However, the quantity in parenthesis is negative, so doubling it makes it less than the minimum condition for the absense of ghosts(\ref{eqn:a-condition-no-ghosts}), thus we can't get massless spin-2 states.
-This is not really a problem because as pointed out in\cite{Bodendorfer-LQG}, a discrete background geometry modifies the dispersion relation at the effective level, so even tho at the fundamental level gravity would travel at $c$, in the effective limit it would appear \textquotedblleft massive", however with a very small mass.
-Thus, since we need $a$ to be at least as big as in(\ref{eqn:a-condition-no-ghosts}), we can choose $a > 0$ to also get rid of the ground state tachyon without the need to introduce supersymmetry or other unverified hypothesis.
-
-The most natural value for $a$ is $a = 1$, which comes from the analysis of physical and spurious states\cite{Green2012Superstring} of the form
-\begin{equation} \label{eqn:phys-spurious-state}
-	\ket{\psi _{- 2 , n}} = \sum _{m} \Hat{\widetilde{L}}_{n , m} \ket{\widetilde{\chi}_{- 2 , m}} ,
-\end{equation}
-where $\ket{\widetilde{\chi}_{- 2 , m}}$ satisfies the constraints(\ref{eqn:L-constraint-quantum-1},\ref{eqn:L-constraint-quantum-2}) and also
-\begin{multline} \label{eqn:spurious-basis-condition}
-	\Bigg( \sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{n , - n} \right) - \\
-	- a + 2 - m \Bigg) \ket{\widetilde{\chi}_{- 2 , m}} = 0 .
-\end{multline}
-States of the form(\ref{eqn:phys-spurious-state}) are annihilated by $\Hat{\widetilde{L}}_{p , k}$ for $p \neq - k$, and for these cases we have
-\begin{equation*}
-	\sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{- 1 , - n} \ket{\psi _{- 2 , n}} \right) =
-\end{equation*}
-\begin{multline*}
-	= \sum _{n} \Bigg( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{- 1 , - n} \times \\
-	\times \sum _{m} \Hat{\widetilde{L}}_{n , m} \ket{\widetilde{\chi}_{- 2 , m}} \Bigg)  =
-\end{multline*}
-\begin{equation} \label{eqn:spurious-annihilation}
-	= \sum _{n} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) \Hat{\widetilde{L}}_{n , - n} \right) \ket{\widetilde{\chi}_{- 2 , 1}} ,
-\end{equation}
-which vanishes for $a = 1$.
-
-\section{Strings and Quantum Geometry} \label{sec:string-geometry}
+$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
+\begin{equation} \label{eqn:L-normal-ordering}
+	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
+\end{equation}
+with the annihilation operator to the right, which manifests in the imposition of the constraint as
+\begin{equation} \label{eqn:shifted-L-constraint}
+	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
+\end{equation}
+for some sequence $c_{p}$.
+The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
+Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
+\begin{equation} \label{eqn:alternative-classical-rest-mass}
+	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
+\end{equation}
+from where we can now see that the string mass spectrum will get shifted by
+\begin{equation} \label{eqn:shifted-mass-spectrum}
+	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
+\end{equation}
+Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
+\begin{equation} \label{eqn:cp-limit}
+	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
+\end{equation}
+like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
+
+The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
+\begin{equation} \label{eqn:L-commutators-1}
+	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
+\end{equation}
+\begin{multline} \label{eqn:L-commutators-2}
+	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
+	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
+\end{multline}
+\begin{multline} \label{eqn:L-commutators-3}
+	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
+	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
+	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
+\end{multline}
+The commutator (\ref{eqn:L-commutators-2}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutators-3}) seem like it would have ordering ambiguities for $k - p = 0$ and $n - m = 0$.
+However it has a $(m - n)(k - p)$ factor multiplying the whole expression, so the commutator is $0$, which can also be seen by setting $n = m$ or $k = p$ on the L.H.S, in which case we get $\Hat{\widetilde{L}}_{n , n}$, which is identically equal to $0$ by the $n - m$ factor in front, thus we would be commuting something with $0$, which has to yield 0 on the R.H.S.
+As a result, our \textquotedblleft Virasoro-Klein-Gordon" algebra has no anomalous terms.
+
+\section{Strings and Quantum Geometry}\label{sec:string-geometry}
 
@@
 
+\subsection{The Einstein-Cartan String}\label{sec:cartan-string}
+
+The careful reader will have noticed that there is a serious difficulty in the above argument.
+The bulk geometry is $d+1$ dimensional, therefore there are $d+1$ embedding fields.
+We have taken these fields $X^\mu$ and cast them as
+components of a $SO(d,1)$ vector.
+Let us pick an arbitrary point $P_0$ on the bulk manifold and call it the ``origin''.
+At $P_0$ the co-ordinates are all zero $\vec X_0 = (0,0,\ldots,0)$.
+If we start acting with infinitesimal $SO(d,1)$ transformations on $\vec X_0$, the resulting surface will correspond to a ``constant energy'' hyperboloid in the bulk.
+This is because $SO(d,1)$ contains only boosts and rotations.
+We also need translations to generate the entirety of the bulk starting from a single base point.
+
+This is where we run into a problem.
+There is no way to express translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$.
+In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold.
+Now we have $d+2$ embedding fields which we can write as:
+\begin{equation}
+	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
+\end{equation}
+where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate.
+
+treating the $X$'s as co-ordinates for the bulk background and also as
+
 \subsection{Two Expressions for Area}\label{eqn:area-formulae}
@@
 	\det h & = \begin{vmatrix}
-		           h_{00} &  & h_{01} \\
-		           h_{10} &  & h_{11}
+		h_{00} && h_{01} \\
+		h_{10} && h_{11} 
 	\end{vmatrix} = \begin{vmatrix}
-		                           \dot X^2        &  & \dot X \cdot X' \\
-		                           \dot X \cdot X' &  & X'^2
+		\dot X^2 && \dot X \cdot X' \\
+		\dot X \cdot X' && X'^2
 	\end{vmatrix} \nonumber \\
@@
 	\det h & = \begin{vmatrix}
-		           h_{00} &  & h_{01} \\
-		           h_{10} &  & h_{11}
+		h_{00} && h_{01} \\
+		h_{10} && h_{11} 
 	\end{vmatrix} = \begin{vmatrix}
@@
 But these same $X$ fields \emph{also} serve as local co-ordinates for the bulk.
-In order for the co-ordinates to change from point to point in the bulk geometry, we must therefore have that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely!
-If $\mc A$ vanishes then that will imply that the fields $X$ don't change from one point to the next.
+In order for the co-ordinates to change from point to point in the bulk geometry, we must therefore require that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely!
+If $\mc A$ vanishes then that will imply that the fields $X$ don't change from one point to the next and cannot therefore be viewed as co-ordinate functions.
 Thus the amplitude $|\mc A|$ can be arbitrarily small but it can never be zero.
 
+\subsection{}\label{sec:}
+
 \section{Physical Implications}
@@
 
+We have presented in this work a possible way to formulate string theory in background independent manner.
+
 \begin{acknowledgments}
@@
 
-It would be natural to suspect that the action\eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
 We can see that this is indeed the case as follows.
 
+Consider a string propagating in a target space whose geometry is described by two bulk metrics.
 There are two ways that a string with two metrics might arise.

### 2024-06-01 lqg-strings.tex
sketch changes and started to transcribe to main file

@@
 
-The action \eqref{eqn:modified-NG-action} has some interesting properties.
-First, on the face of it it does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
+The action eq \eqref{eqn:modified-NG-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action, all its terms are derivatives of $X^{\mu}$ with all indices contracted, thus are Lorentz scalars.
+It also does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
 Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
-However, if we look at that expression we see that it can be written as:
+Moreover, if we look at that expression we see that it can be written as:
 \begin{equation} \label{eqn:modified-NG-action-v2}
@@
 where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$.
-So, while the second term is not diffeomorphism invariant \wrt the original metric $h_{ab}$ it is clearly diffeomorphism invariant \wrt the inverse metric $h^{ab}$.
-
-Second, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
+As such, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
 If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
@@
 
-Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+In the following, we parametrize the WS using $\tau = t$ and
+\begin{equation} \label{eqn:transverse-'gauge'}
+	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
+\end{equation}
+where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string given that longitudinal motion does not happen.
+We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
 \begin{equation} \label{eqn:string-energy}
@@
 \begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} = \frac{E (q)}{T (F^+)^2} ,
-\end{equation}
-we find the wave equation
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
+\end{equation}
+we find the variable-speed wave equation
 \begin{equation} \label{eqn:simplified-modified-wave-eqn}
@@
 
-In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string.
-we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov action.
+We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 \end{multline}
-The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
+One might think this action is incomplete since we only applied the correction to the determinant and didn't change the inverse metric $g^{a b}$, but there are good reasons for that: the first is that the action in this form, as we shall see, reduces neatly to the area-corrected Nambu-Goto action \eqref{eqn:modified-NG-action}, and the second comes from a more rigorous bimetric Polyakov string analysis which will be done in appendix \ref{app:bimetric-string}, where we show that starting from a bimetric Polyakov string one can derive the action \eqref{eqn:inverse-metric-Polyakov}.
+
+This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables.
+This time, however, not only is WS diffeomorphism invariance destroyed, but so is WS Weyl symmetry, since the second term has inverse determinant multiplied by inverse metric.
+
+The equations of motion for the world-sheet metric are completely unchanged by this correction,
 \begin{equation} \label{eqn:vary-wrt-g}
-	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
-\end{equation}
-from which we obtain the stress-energy tensor for the worldsheet:
+	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
+\end{equation}
+which leads to the stress-energy tensor for the worldsheet:
 \begin{multline} \label{eqn:inverse-area-em-tensor}
@@
 \begin{equation} \label{eqn:vary-wrt-X}
-	\frac{\delta S_{I A P}}{\delta X^{\lambda}} \overset{!}{=} 0
-\end{equation}
-
+	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
+\end{equation}
 \begin{multline} \label{eqn:X-eom-inverse-area}
@@
 \end{multline}
-where $F^{-} = 1 - k \Delta / 2 (- g)$.
-Using conformal symmetry $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ and assuming flat background $G_{\mu \nu} = \eta _{\mu \nu}$, eq(\ref{eqn:X-eom-inverse-area}) simplify to
+where
+\begin{equation} \label{eqn:F-minus-def}
+	F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
+\end{equation}
+Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g^{a b} = \e ^{- \phi (x)} \eta ^{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
 \begin{equation} \label{eqn:X-eom-simplified}
-	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \partial _{a} \ln (F^{-}) \partial _{b} X^{\mu} = 0 .
-\end{equation}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
+\end{equation}
+By expanding the definition of $F^{-}$ we get
+\begin{equation} \label{eqn:coupling-X-phi}
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + 2 \eta ^{a b} \frac{\partial _{a} \phi (x)}{\dfrac{2 \e ^{2 \phi (x)}}{k \Delta} - 1} \partial _{b} X^{\mu} = 0 ,
+\end{equation}
+revealing a wave equation sourced by a coupling between the WS conformal factor and the embedding fields much akin to the dilaton field \cite{Tong2009Lectures}.
+We'll come back to this in \autoref{sec:discussion}.
 
@@
 
-Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal function $\phi (x)$ appearing in $F^{-}$.
+Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$.
 By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
@@
 \end{equation}
-from which we can use the freedom in the conformal function to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell, and this in turn implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 \begin{equation} \label{eqn:F-minus-exp}
-	F^{-} = A \e ^{i (E \tau + p \sigma + \varphi)} , \ A > 0
+	F^{-} = A \e ^{i (E \tau + p \sigma)} , \ A \in \C
 \end{equation}
 \begin{equation} \label{eqn:phi}
-	\phi (\tau , \sigma) = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma + \varphi)} \right)}} .
-\end{equation}
-At first glance it seems problematic that we have a complex conformal function $\phi (x)$, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\phi$.
+	\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
+\end{equation}
+At first glance, it seems problematic that we have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$.
 With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
@@
 \end{equation}
+The imposition that
+\begin{equation} \label{eqn:mu-constraint-1}
+	i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
+\end{equation}
+can be used to find the explicit dependence of $\mu ^2$ with the quantum geometry parameters $k \Delta$ as in
+\begin{equation} \label{eqn:mu-constraint-final}
+	\mu ^2 = \frac{2 i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} (p \partial _{\sigma} \phi - E \partial _{\tau} \phi) .
+\end{equation}
 
@@
 
+In the following, we focus on the analysis of the closed string unless otherwise stated.
+
 From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}.
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
+	X^{\mu} (\tau , \sigma) = \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \bigg( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \\
+	+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \bigg) ,
 \end{multline}
@@
 \begin{equation} \label{eqn:reality-consequence}
-	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
+	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{n})^{*} .
 \end{equation}
@@
 \begin{align}
-	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
-	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
-\end{align}
-
-Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
+	L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
+	\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
+	\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
+\end{align}
+Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution.
+This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.
+
+Before proceeding, we have one remark: the 0-th term of the solution reads
 \begin{equation} \label{eqn:X-sol-0-term}
-	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
-\end{equation}
-which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$.
+	\sqrt{\frac{\alpha '}{2}} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
+\end{equation}
+which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$.
 Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
 \begin{equation} \label{eqn:a-p-relation}
-	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation}
-Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
-\begin{equation} \label{eqn:string-rest-mass}
-	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
-\end{equation}
-
-Collecting our results, we have that the solution for our string is given by
-\begin{multline} \label{eqn:KG-Polyakov-solution-final}
-	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
-\end{multline}
-subject to the infinite family of constraints
-\begin{equation}
-	L_{n , p} = \widetilde{L}_{n , p} = 0
-\end{equation} \label{eqn:"Virasoro"-constraints}
-and 0-th oscillation mode related to center of mass momentum
-\begin{equation*}
-	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
-\end{equation*}
+	\alpha ^{\mu} _{0} = \sqrt{\frac{2}{\alpha '}} \mu x^{\mu} + i \frac{1}{2} \sqrt{\frac{\alpha '}{2}} p^{\mu} .
+\end{equation}
+This in actuality will differ from the normal ST literature by a factor of $1 / 2$ in the momentum term, but this is needed for the Poisson brackets to give the expected results.
+
+Looking closer at our Virasoro-like \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
+\begin{multline} \label{eqn:string-rest-mass-classical-1}
+	M^2 = - p^{\mu} p_{\mu} = - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
+	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) =
+\end{multline}
+\begin{multline} \label{eqn:string-rest-mass-classical-2}
+	= - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \\
+	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) .
+\end{multline}
+
+\subsection{The Expansion Modes Algebra}
+
+We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
+\begin{multline} \label{eqn:canonical-momentum-density}
+	\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \bigg( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \\
+	- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \bigg)
+\end{multline}
+where
+\begin{multline} \label{eqn:F-minus-full-sum}
+	F^{-} = 1 - \frac{k \Delta}{2 \e ^{\phi (x)}} = \\
+	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
+\end{multline}
+and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
+\begin{equation} \label{eqn:canonical-bracket-relation}
+	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+\end{equation}
+to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$.
+After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
+\begin{equation} \label{eqn:expansion-modes-bracket-0}
+	\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\} = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\}
+\end{equation}
+\begin{equation} \label{eqn:expansion-modes-bracket-1}
+	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{m} \delta _{|m| , |p|} \eta ^{\mu \nu} = - \left\{ (\alpha ^{\mu} _{n})^{*} , \alpha ^{\nu} _{p} \right\} ,
+\end{equation}
+from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
+\begin{align}
+	a^{\mu} _{n}       & := \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \label{eqn:normalized-oscillator-modes}         \\
+	(a^{\mu} _{n})^{*} & := \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \label{eqn:normalized-oscillator-modes-*}
+\end{align}
+\begin{equation} \label{eqn:harmonic-bracket-relations}
+	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
+\end{equation}
+The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
+\begin{align}
+	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
+	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
+\end{align}
+
+\subsection{The \textquotedblleft Virasoro-Klein-Gordon" Algebra}
+
+Having the bracket relations between the vibrational modes of the string, we can now calculate the constraint algebra, which we shall refer to as the Virasoro-Klein-Gordon Algebra.
+For simplicity, since $E_{n} = \sqrt{n^2 + \mu ^2} > 0$, we shall work with the normalized harmonic oscillator modes $a^{\mu} _{n}$ instead of the expansion modes $\alpha ^{\mu} _{n}$.
+The algebra is given by
+\begin{equation} \label{eqn:L-brackets-0}
+	\left\{ L_{n , m} , L_{k , p} \right\} = 0
+\end{equation}
+\begin{equation} \label{eqn:L-brackets-1}
+	\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( L_{m , k} \delta _{|n| , |p|} + L_{n , k} \delta _{|m| , |p|} \right)
+\end{equation}
+\begin{equation} \label{eqn:L-brackets-2}
+	\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( \widetilde{L}_{k , m} \delta _{|n| , |p|} - \widetilde{L}_{n , p} \delta _{|m| , |k|} \right) .
+\end{equation}
 
@@
 
-In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.
-To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
-\begin{multline} \label{eqn:canonical-momentum}
-	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
-	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
-\end{multline}
-and then we proceed to turn the equal-time Poisson bracket relations
-\begin{equation} \label{eqn:Poisson-brackets-1}
-	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:Poisson-brackets-2}
-	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
-\end{equation}
-into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
-\begin{equation} \label{eqn:canonical-commutator-1}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
-\end{equation}
-\begin{equation} \label{eqn:canonical-commutator-2}
-	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
-\end{equation}
-From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
-\begin{equation} \label{eqn:non-vanishing-commutator}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
-\end{equation}
-\begin{equation} \label{eqn:vanishing-commutators}
-	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
-\end{equation}
-which are just harmonic oscillator relations with
+We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}).
+The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ .
+, .
+\}$ being replaced by commutators $[ .
+, .
+] = i \hbar \{ .
+, .
+\}$:
 \begin{align}
-	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
-	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
-\end{align}
-For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
+	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
+	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
+	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
+	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
+	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
+	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
+\end{align}
+
+As usual, we define the vacuum state of the string to obey
 \begin{equation} \label{eqn:annihilation-vacuum}
-	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
-\end{equation}
-and for $p = 0$
-\begin{equation} \label{eqn:momentum-vacuum}
-	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
-\end{equation}
+	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
+\end{equation}
+For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
+\begin{align}
+	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
+	\Hat{p}_{\mu} \ket{0 ; 0} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
+\end{align}
+in position representation and
+\begin{align}
+	\Hat{x}^{\mu} \ket{0 ; p} & = i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
+	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
+\end{align}
+in momentum representation.
+
 Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
-\begin{multline} \label{eqn:general-state}
-	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
-	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
-\end{multline}
-
-As usual, by the appearance of the Minkowski metric in the non-zero commutator
+\begin{equation} \label{eqn:general-state}
+	\ket{\psi} = \prod _{i \neq 0} ((\Hat{a}^{\mu _{i}} _{i})^{\dagger})^{n_{i}} \ket{0} .
+\end{equation}
+
+As usual, the appearance of the Minkowski metric in the non-zero commutator
 \begin{equation} \label{eqn:ghosts}
-	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
-\end{equation}
-we have ghosts in the theory which must be dealt with.
+	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{|p| , |k|} ,
+\end{equation}
+brings ghosts into the theory which must be dealt with.
+
 When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
@@
 \end{equation}
-$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
+$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators.
+As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
 \begin{equation} \label{eqn:L-normal-ordering}
-	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
-\end{equation}
-with the annihilation operator to the right, which manifests in the imposition of the constraint as
+	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
+\end{equation}
+This ambiguity manifests in the imposition of the constraint as
 \begin{equation} \label{eqn:shifted-L-constraint}
-	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
-\end{equation}
-for some sequence $c_{p}$.
-The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important.
-Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
-\begin{equation} \label{eqn:alternative-classical-rest-mass}
-	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
-\end{equation}
-from where we can now see that the string mass spectrum will get shifted by
-\begin{equation} \label{eqn:shifted-mass-spectrum}
-	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
-\end{equation}
-Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
-\begin{equation} \label{eqn:cp-limit}
-	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
-\end{equation}
-like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
-
-The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
-\begin{equation} \label{eqn:L-commutators-1}
-	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
-\end{equation}
-\begin{multline} \label{eqn:L-commutators-2}
-	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
-	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
-\end{multline}
-\begin{multline} \label{eqn:L-commutators-3}
-	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
-	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
-	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
-\end{multline}
-The commutator (\ref{eqn:L-commutators-2}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutators-3}) seem like it would have ordering ambiguities for $k - p = 0$ and $n - m = 0$.
-However it has a $(m - n)(k - p)$ factor multiplying the whole expression, so the commutator is $0$, which can also be seen by setting $n = m$ or $k = p$ on the L.H.S, in which case we get $\Hat{\widetilde{L}}_{n , n}$, which is identically equal to $0$ by the $n - m$ factor in front, thus we would be commuting something with $0$, which has to yield 0 on the R.H.S.
-As a result, our \textquotedblleft Virasoro-Klein-Gordon" algebra has no anomalous terms.
+	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
+\end{equation}
+for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
+\begin{multline} \label{eqn:shifted-mass-spectrum}
+	\Hat{M}^2 = \frac{8}{\alpha '} \Bigg( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
+	- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Bigg) .
+\end{multline}
+This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
+\begin{equation}
+	a = D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} .
+\end{equation}
+
+The commutation relations between the constraints are inherited by the Poisson brackets
+\begin{align}
+	\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right]                         & = 0 \label{eqn:L-commutator-0}                                                                                                   \\
+	\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right]             & = \Hat{L}_{m , k} \delta _{|n| , |p|} + \Hat{L}_{n , k} \delta _{|m| , |p|} \label{eqn:L-commutator-1}                           \\
+	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] & = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} \label{eqn:L-commutator-2} .
+\end{align}
+The commutator (\ref{eqn:L-commutator-1}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutator-2}) have ordering ambiguities for $|m| = |k|$ and/or $|n| = |p|$, so we add the anomalous terms
+\begin{multline} \label{eqn:L-commutator-anomalous-initial}
+	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} + \\
+	+ C_{n} \delta _{|n| , |p|} + D_{k} \delta _{|m| , |k|} .
+\end{multline}
+Clearly, $C_{0} = D_{0} = 0$, since when all indices are $0$ we have only the position and momentum operators, and thus the commutator should vanish identically.
+Also, because of the symmetry in the indices we have that $C_{- n} = C_{n}$ and $D_{- k} = D_{k}$.
+Using the Jacobi identity
+\begin{multline} \label{eqn:L-Jacobi-identity}
+	\left[ \Hat{\widetilde{L}}_{n , m} , \left[ \Hat{\widetilde{L}}_{k , p} , \Hat{\widetilde{L}}_{r , s} \right] \right] + \\
+	+ \left[ \Hat{\widetilde{L}}_{r , s} , \left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] \right] + \\
+	+ \left[ \Hat{\widetilde{L}}_{k , p} , \left[ \Hat{\widetilde{L}}_{r , s} , \Hat{\widetilde{L}}_{n , m} \right] \right] = 0
+\end{multline}
+we get the difference equation
+\begin{equation} \label{eqn:F-difference-eqn}
+	F_{n + 1} + F_{n} + F_{1} = 0
+\end{equation}
+for the sum of both sequences $F_{n} = C_{n} + D_{n}$. This difference equation has solution
+\begin{equation} \label{eqn:F-sequence}
+	F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) ,
+\end{equation}
+and since both $C_{n}$ and $D_{n}$ need to satisfy the initial value of $0$, each of then is half of $F_{n}$,
+\begin{equation} \label{eqn:C-D-sequences}
+	C_{n} = D_{n} = \frac{F_{n}}{2} = \frac{F_{1}}{4} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) .
+\end{equation}
+Next, by calculating the vacuum expectation value (VEV) of the commutator \eqref{eqn:L-commutator-2} with $|m| \neq |k|$ and $n = p = 1$, we find that $F_{1} = 0$, thus both sequences $C_{n} = D_{n} = 0$ vanish and we conclude that the quantum version of our algebra \emph{has no anomalies}.
+This is a relevant result, since it could mean our model doesn't need a specific number of dimensions to work, which will be explored again later in section \ref{sec:discussion}.
+
+Let us denote the ground state with momentum $p^{\mu}$ by $\ket{0 ; p}$. Then, the mass-shell condition \eqref{eqn:shifted-mass-spectrum} implies that
+\begin{equation} \label{eqn:ground-state-mass-shell}
+	\frac{\alpha '}{8} p^2 = - \left( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 + a \right) .
+\end{equation}
+Next we look at the $n$-th excited state $\zeta _{\mu} (\Hat{a}^{\mu} _{d})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The mass-shell now reads
+\begin{multline} \label{eqn:nth-state-mass-shell}
+	\frac{\alpha '}{8} M^2 = - \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
+	- 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) + a \Bigg) ,
+\end{multline}
+while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ implies that
+\begin{equation} \label{eqn:zeta-p-psi}
+	\zeta _{\mu} p^{\mu} = - \frac{4 \mu}{\alpha '} \zeta _{\mu} \frac{\partial \psi (p)}{\partial p_{\mu}} .
+\end{equation}
+If the momentum wave-function is taken to be
+\begin{equation} \label{eqn:p-wave-function}
+	\psi (p) = - \frac{\alpha '}{8 \mu} p^{\mu} p_{\mu} ,
+\end{equation}
+eq \eqref{eqn:zeta-p-psi} reduces to $\zeta _{\mu} p^{\mu} = 0$. Putting this back in the mass-shell yields
+\begin{equation} \label{eqn:ground-state-mass-shell-simplified}
+	\frac{\alpha '}{4} p^2 = - a
+\end{equation}
+for the ground state and
+\begin{equation} \label{eqn:nth-mass-shell-simplified}
+	\frac{\alpha '}{4} p^2 = 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) - a
+\end{equation}
+for the $n$-th state.
+The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, so if we choose $p^{\mu}$ to lie on the $(0 , 1)$-plane, then the $D - 2$ spacelike polarizations normal to said plane have positive norm.
+If $a$ is chosen such that the $n = d , d = D - 1$ excited state is a tachyon with $p^2 > 0$, then $p^{\mu}$ can be taken to have no time component, leaving $\zeta _{\mu}$ timelike with negative norm.
+If the choice is made such that $p^2 < 0$, $p^{\mu}$ can be chosen to have only a time component, making $\zeta _{\mu}$ spacelike with positive norm again.
+At last, if we choose for $p^2 = 0$, then $\zeta _{\mu}$ is proportional to $p^{\mu}$ with 0 norm, so for the absence of ghosts we require that
+\begin{equation} \label{eqn:c-no-ghost-spin-1}
+	a \geq 4 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) .
+\end{equation}
+In the boundary case, the $d$-th excited vector state is massless and all other vector states (plus the ground state) are regular massive particles with $M^2 > 0$.
+This, however, is to get a massless vector state for the closed string.
+The actual massless particle we want from the closed string is a symmetric, traceless spin-2 particle, so let's now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor.
+The mass-shell reads
+\begin{equation} \label{eqn:dth-spin-2-mass-shell}
+	\frac{\alpha '}{4} p^2 = 8 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) - a
+\end{equation}
+and the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{d , 0} \zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ together with the momentum wave-function \eqref{eqn:p-wave-function} implies
+\begin{equation}
+	\zeta _{\mu \nu} p^{\mu} = 0 .
+\end{equation}
+We can decompose the polarization into a symmetric traceless part $G_{\mu \nu} = G_{\nu \mu} , \eta ^{\mu \nu} G_{\mu \nu} = 0$, a anti-symmetric part $B_{\mu \nu} = - B_{\nu \mu}$ and a trace part $\Phi \eta _{\mu \nu} , \Phi = \eta ^{\alpha \beta} \zeta _{\alpha \beta} / D$, $\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-knwon types of background fields: the graviton $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$.
 
@@
 
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
 

### 2024-06-03 lqg-strings.tex
finished quantization of area corrected string and bimetric appendix in main file

@@
 \begin{multline} \label{eqn:string-rest-mass-classical-1}
-	M^2 = - p^{\mu} p_{\mu} = - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
+	M^2 = - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
 	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) =
@@
 \begin{multline} \label{eqn:string-rest-mass-classical-2}
-	= - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \\
+	= \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \\
 	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) .
@@
 \begin{equation} \label{eqn:expansion-modes-bracket-1}
-	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{m} \delta _{|m| , |p|} \eta ^{\mu \nu} = - \left\{ (\alpha ^{\mu} _{n})^{*} , \alpha ^{\nu} _{p} \right\} ,
+	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} ,
 \end{equation}
@@
 \begin{align}
-	\Hat{x}^{\mu} \ket{0 ; p} & = i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
+	\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
 	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
@@
 This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
-\begin{equation}
-	a = D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} .
-\end{equation}
+\begin{multline}
+	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
+	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} .
+\end{multline}
 
@@
 \begin{equation} \label{eqn:ground-state-mass-shell}
-	\frac{\alpha '}{8} p^2 = - \left( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 + a \right) .
-\end{equation}
-Next we look at the $n$-th excited state $\zeta _{\mu} (\Hat{a}^{\mu} _{d})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The mass-shell now reads
+	\frac{\alpha '}{8} p^2 = \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 + a .
+\end{equation}
+Next we look at the $n$-th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector.
+The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have independent left and right sectors, thus permitting spin-1 states.
+We'll discuss these closed string single excitation states in section \ref{sec:discussion}.
+The mass-shell now reads
 \begin{multline} \label{eqn:nth-state-mass-shell}
-	\frac{\alpha '}{8} M^2 = - \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
-	- 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) + a \Bigg) ,
+	\frac{\alpha '}{8} M^2 = \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
+	- \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Bigg) ,
 \end{multline}
@@
 \begin{equation} \label{eqn:p-wave-function}
-	\psi (p) = - \frac{\alpha '}{8 \mu} p^{\mu} p_{\mu} ,
+	\psi (p) = - \frac{\alpha '}{8 \sqrt{2} \mu} p^{\mu} p_{\mu} ,
 \end{equation}
@@
 \begin{equation} \label{eqn:ground-state-mass-shell-simplified}
-	\frac{\alpha '}{4} p^2 = - a
+	\frac{\alpha '}{16} p^2 = a = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k}
 \end{equation}
 for the ground state and
-\begin{equation} \label{eqn:nth-mass-shell-simplified}
-	\frac{\alpha '}{4} p^2 = 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) - a
-\end{equation}
+\begin{multline} \label{eqn:nth-mass-shell-simplified}
+	\frac{\alpha '}{16} p^2 = a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} = \\
+	= - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n}
+\end{multline}
 for the $n$-th state.
-The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, so if we choose $p^{\mu}$ to lie on the $(0 , 1)$-plane, then the $D - 2$ spacelike polarizations normal to said plane have positive norm.
-If $a$ is chosen such that the $n = d , d = D - 1$ excited state is a tachyon with $p^2 > 0$, then $p^{\mu}$ can be taken to have no time component, leaving $\zeta _{\mu}$ timelike with negative norm.
-If the choice is made such that $p^2 < 0$, $p^{\mu}$ can be chosen to have only a time component, making $\zeta _{\mu}$ spacelike with positive norm again.
-At last, if we choose for $p^2 = 0$, then $\zeta _{\mu}$ is proportional to $p^{\mu}$ with 0 norm, so for the absence of ghosts we require that
-\begin{equation} \label{eqn:c-no-ghost-spin-1}
-	a \geq 4 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) .
-\end{equation}
-In the boundary case, the $d$-th excited vector state is massless and all other vector states (plus the ground state) are regular massive particles with $M^2 > 0$.
-This, however, is to get a massless vector state for the closed string.
-The actual massless particle we want from the closed string is a symmetric, traceless spin-2 particle, so let's now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor.
+The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, and since by eq \eqref{eqn:nth-mass-shell-simplified} we see that $p^2 < 0$, thus $\zeta ^2 > 0$ always holds and we have no ghosts in the closed string spin-1 spectrum.
+This analysis, however, is for vector states from the closed string.
+The actual particle we want from the closed string is a symmetric, traceless spin-2 particle, so let's now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor.
 The mass-shell reads
-\begin{equation} \label{eqn:dth-spin-2-mass-shell}
-	\frac{\alpha '}{4} p^2 = 8 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) - a
-\end{equation}
-and the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{d , 0} \zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ together with the momentum wave-function \eqref{eqn:p-wave-function} implies
-\begin{equation}
-	\zeta _{\mu \nu} p^{\mu} = 0 .
-\end{equation}
-We can decompose the polarization into a symmetric traceless part $G_{\mu \nu} = G_{\nu \mu} , \eta ^{\mu \nu} G_{\mu \nu} = 0$, a anti-symmetric part $B_{\mu \nu} = - B_{\nu \mu}$ and a trace part $\Phi \eta _{\mu \nu} , \Phi = \eta ^{\alpha \beta} \zeta _{\alpha \beta} / D$, $\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-knwon types of background fields: the graviton $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$.
+\begin{equation} \label{eqn:nth-spin-2-mass-shell}
+	\frac{\alpha '}{16} p^2 = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - 4 \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n} .
+\end{equation}
+The auxiliary $\bra{0 ; p} \xi _{\alpha} \Hat{a}^{\alpha} _{n} \Hat{\widetilde{L}}_{n , 0} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \zeta _{\mu \nu} \ket{0 ; p} = 0$ condition where $\xi _{\alpha}$ is a arbitrary polarization for the auxiliary vector excitation implies that
+\begin{equation} \label{eqn:spin-2-zeta-p=0}
+	(\zeta _{\mu \nu} + \zeta _{\nu \mu}) p^{\mu} = 0 .
+\end{equation}
+We can decompose the polarization into a symmetric traceless part $G_{\mu \nu}$, an anti-symmetric part $B_{\mu \nu}$ and a trace part $\Phi \eta _{\mu \nu}$ given by
+\begin{align}
+	G_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} + \zeta _{\nu \mu}) - \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \eta _{\mu \nu} \label{eqn:G-zeta} \\
+	B_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} - \zeta _{\nu \mu}) \label{eqn:B-zeta}                                                                          \\
+	\Phi        & = \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \label{eqn:Phi-zeta} ,
+\end{align}
+$\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-known types of background fields: the spacetime metric $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$, all of those having squared mass given by eq \eqref{eqn:nth-spin-2-mass-shell}.
+We thus see that the symmetric part $S_{\mu \nu} = G_{\mu \nu} + \Phi \eta _{\mu \nu}$ of $\zeta _{\mu \nu}$ is orthogonal to the momentum of the string, $S_{\mu \nu} p^{\mu} = 0$, and since $p^2 < 0$, we can choose a reference frame where $p^{\mu} = (p , 0 , ...
+, 0)$ only has a time component, leaving us with $S_{0 \nu} = 0$, implying that $\zeta _{0 \nu} = - \zeta _{\nu 0}$.
+This condition guarantees that the timelike components of $\zeta _{\mu \nu}$ have a positive contribution to its square $\zeta ^{\mu \nu} \zeta _{\mu \nu} = \zeta ^{i j} \zeta _{i j} + b , \ b = \zeta ^{0 i} \zeta _{0 i} > 0$, and the remaining part is spacelike thus must also have positive square, so we get that $\zeta ^{\mu \nu} \zeta _{\mu \nu} > 0$, so we are free of ghosts in the spin-2 spectrum.
+
+It seems we're in trouble since eq \eqref{eqn:nth-spin-2-mass-shell} tells us we have no massless 2 excitation states, but in fact, this is not a problem and is actually expected since quantum geometric effects are expected to violate Lorentz invariance near the Planck scale \cite{Bodendorfer-LQG}, making it so massless particles effectively travel slightly slower than $c$, with corrections on the order of $\sim E_{pl} ^{- 4}$.
+
+The fact that $G_{\mu \nu}$ is symmetric, traceless and satisfies $G_{\mu \nu} p^{\mu} = 0$ leaves it with
+\begin{equation} \label{eqn:G-polarizations}
+	\frac{1}{2} D (D - 1) - 1
+\end{equation}
+possible polarizations, which shows that indeed those polarizations fit nicely in a representation of $\mathrm{SO} (D - 1 , 1)$, \ie the traceless symmetric tensor representation, thus all our excited spin-2 states are consistent with Lorentz symmetry at the macroscopic scale even tho near the Planck scale they deviate a bit by having an effective mass.
 
@@
 
-Following the general procedure, given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
+Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
 \begin{equation}\label{eqn:polyakov-curved}
@@
 	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
-	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
+	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
+	         & + S_{int} [g , h , X].
 \end{align}
@@
 
-Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the auxiliary metrics $g_{c d}$ and $h_{c d}$:
+Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
 \begin{equation} \label{eqn:variation-wrt-g}
-	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
+	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
 \end{equation}
@@
 	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
-\end{multline}
-
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
+\end{multline}
+and completely analogous for the $H_{\mu \nu}$ metric,
+\begin{equation} \label{eqn:variation-wrt-h}
+	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
+\end{equation}
+\begin{multline} \label{eqn:h-em-tensor}
+	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
+\end{multline}
+If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
 \begin{equation} \label{eqn:g-expression}
@@
 \begin{equation} \label{eqn:g's-f-function}
-	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
-\end{equation}
-and completely analogously for the $H_{\mu \nu}$ metric,
-\begin{equation} \label{eqn:variation-wrt-h}
-	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
-\end{equation}
-\begin{multline} \label{eqn:h-em-tensor}
-	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
-	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
-\end{multline}
+	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
+\end{equation}
+and for $h_{c d}$
 \begin{equation} \label{eqn:h-expression}
@@
 \end{equation}
-with
+with $f^{(H)}$ given by
 \begin{equation} \label{eqn:h's-f-function}
@@
 \end{equation}
-
-As for the embbeding fields equation, we get a non-homogeneous wave equation for the coupled metric
+If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
+\begin{equation} \label{eqn:double-NG-action}
+	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
+\end{equation}
+and from here we note that if $T' = - T k \Delta / 2$ and $h = g^{-1}$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
+\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
+	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
+\end{equation}
+The condition $h = g^{-1}$ can be achieved by
+\begin{equation} \label{eqn:h=SgS}
+	h_{a b} = S_{a c} g^{c d} S_{d b}
+\end{equation}
+where $S \in \mathrm{SL} (2 , \C)$ with $S^{\dagger} = S$. This implies that
+\begin{multline} \label{eqn:SgS-implication}
+	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} S_{a c} \varepsilon ^{c c'} S_{d b} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
+	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
+\end{multline}
+which can be achieved by choosing
+\begin{equation} \label{eqn:S=sigma_y}
+	S_{a c} = i \varepsilon _{a c} = - \sigma _{y} ,
+\end{equation}
+thus leading us to
+\begin{equation} \label{eqn:H=1/(2g)G}
+	H_{\mu \nu} = \frac{1}{2 g} G_{\mu \nu} .
+\end{equation}
+
+As for the embedding fields equation, continuing to assume no interaction term we get a non-homogeneous wave equation for the coupled metric $F^{a b} _{\mu \nu} = T \sqrt{- g} g^{a b} G_{\mu \nu} + T' \sqrt{- h} h^{a b} H_{\mu \nu}$
 \begin{equation} \label{eqn:variation-wrt-X}
-	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
-\end{equation}
+	\frac{\delta S_{P B}}{\delta X^{\lambda}} = 0
+\end{equation}
+\begin{equation} \label{eqn:bimetric-X-eom}
+	\partial _{a} \left( F^{a b} _{\mu \lambda} \partial _{b} X^{\mu} \right) = \frac{1}{2} \partial _{\lambda} F^{a b} _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} ,
+\end{equation}
+whereby assuming the conditions for $h = g^{-1}$ \eqref{eqn:h=SgS} and \eqref{eqn:S=sigma_y} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
+\begin{equation} \label{eqn:bimetric-X-eom-simplified-1}
+	\del _{a} \left( \left( 1 - \frac{k \Delta}{2 (- g)} \right) \sqrt{- g} g^{a b} \del _{b} X^{\mu} \right) = 0 ,
+\end{equation}
+which in conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ simplifies further to eq \eqref{eqn:X-eom-simplified} derived in section \ref{sec:inverse-metric-Polyakov}.
+In fact, if we plug in the conditions \eqref{eqn:h=SgS} and \eqref{eqn:S=sigma_y} and $T' = - T k \Delta / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
 

### 2024-06-03 lqg-strings.tex
minor correction in appendix B
added emergent dimensions discussion in section VIII and talked about conformal factor being WS dilaton

@@
 
+\subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}
+
+The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a glaring disadvantage: they do not have WS diffeomorphism invariance, making it so it is not clear what WS parameterization should be used and neither if physical predictions can be extracted from them since it is not obvious that different parameterizations describe the same system.
+If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS diffeomorphism invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
+\begin{multline} \label{eqn:emergent-dimensions-action}
+	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
+\end{multline}
+where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
+\gg m_{d}$.
+This is Afshordi's model \cite{Afshordi-emergent}.
+Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
+\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
+	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
+\end{equation}
+so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
+\begin{equation} \label{eqn:X-masses-constraint}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
+\end{equation}
+where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
+
+Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
+
+By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
+\begin{equation} \label{eqn:emergent-dimensions-g}
+	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+with $f$ given by
+\begin{equation} \label{eqn:emergent-dimensions-f}
+	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier.
+By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.
+
+One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
+\begin{multline} \label{eqn:emergent-dimensions-curved}
+	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
+\end{multline}
+where the mass parameters will be constrained as in
+\begin{equation} \label{eqn:X-masses-constraint-2}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
+\end{equation}
+since those are the ones that show up in the $X^{\mu}$ equations of motion
+\begin{multline}
+	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
+	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
+\end{multline}
+
+In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
+We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
+\begin{equation} \label{eqn:mu0-phi-relation}
+	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
+\end{equation}
+where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
+
 \begin{acknowledgments}
@@
 \end{equation}
-where $S \in \mathrm{SL} (2 , \C)$ with $S^{\dagger} = S$. This implies that
+where $\det (S) = \pm 1$ and $S^{\dagger} = S$. This implies that
 \begin{multline} \label{eqn:SgS-implication}
@@
 \begin{equation} \label{eqn:S=sigma_y}
-	S_{a c} = i \varepsilon _{a c} = - \sigma _{y} ,
-\end{equation}
-thus leading us to
+	S_{a c} = i \varepsilon _{a c} = - (\sigma _{y})_{a c}
+\end{equation}
+and if the background metrics are related by
 \begin{equation} \label{eqn:H=1/(2g)G}

### 2024-06-04 lqg-strings.tex
added a paragraph in discussion section about what vector excitations of closed string could relate to

@@
 
+In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors.
+Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to?
+Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in Einstein-Cartan [ref] formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+\begin{equation} \label{eqn:connection-string-vector-excitation}
+	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
+\end{equation}
+Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
+\begin{equation} \label{eqn:AEF-string-vector-excitation}
+	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
+\end{equation}
+
 \subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}

### 2024-06-04 lqg-strings.tex
added missing reference in latest paragraph of discussion

@@
 Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to?
-Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in Einstein-Cartan [ref] formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
 \begin{equation} \label{eqn:connection-string-vector-excitation}

### 2024-06-07 lqg-strings.tex
promoted \Delta to a field in main file, plus minor additions in sec V

@@
 \end{equation*}
-Here, $g = l_{pl}/l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a constant which corresponds to the square of the minimal quantum of area.
+Here, $g = l_{pl}/l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of some worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the spin foam pierces the WS.
 In the limit that $l_s \gg l_{pl}$, $g \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
@@
 \end{equation}
-Presumably the limit $g \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\sqrt{h} \gg \Delta$.
+Presumably the limit $g \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
 Thus in this limit $ g^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections.
@@
 This action has, to the best of our knowledge, not been explored in the string theory literature.
-However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.
-
-The action eq \eqref{eqn:modified-NG-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action, all its terms are derivatives of $X^{\mu}$ with all indices contracted, thus are Lorentz scalars.
-It also does not appear to satisfy diffeomorphism invariance of the string worldsheet because of the second term.
-Given that we are assuming the existence of a minimum quantum of area, it is obvious that diffeomorphism invariance, at least in the classical sense, will no longer be an exact symmetry of the theory.
+However, such an inverse determinant term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.
+
+The action eq \eqref{eqn:modified-NG-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars.
+At first glance it might seem to not be WS reparameterization invariant because of the second term, however, this is corrected by the fact that $\Delta$ is a scalar \emph{density} of weight 2, thus counteracting the inverse metric determinant.
 Moreover, if we look at that expression we see that it can be written as:
@@
 \begin{align} \label{eqn:modified-NG-action-v3}
-	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
-	                 & = -T' \int \diff ^2 x \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
-\end{align}
-which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} {g \Delta} T $ and $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$
-This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
+	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
+	                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
+\end{align}
+which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} g T $, $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$ and $\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x$ (or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g' \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
 
@@
 
-In the following, we parametrize the WS using $\tau = t$ and
+In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
 \begin{equation} \label{eqn:transverse-'gauge'}
@@
 \end{equation}
-where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string given that longitudinal motion does not happen.
+where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string.
 We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
@@
 \end{multline}
-One might think this action is incomplete since we only applied the correction to the determinant and didn't change the inverse metric $g^{a b}$, but there are good reasons for that: the first is that the action in this form, as we shall see, reduces neatly to the area-corrected Nambu-Goto action \eqref{eqn:modified-NG-action}, and the second comes from a more rigorous bimetric Polyakov string analysis which will be done in appendix \ref{app:bimetric-string}, where we show that starting from a bimetric Polyakov string one can derive the action \eqref{eqn:inverse-metric-Polyakov}.
+One might think this action is incomplete since we only applied the correction to the determinant and didn't change the inverse metric $g^{a b}$, however the correction \ref{eqn:inverse-metric-correction} is a correction to the \emph{area} of the WS, not its metric.
+Moreover, there are other good reasons for this form of the Polyakov action: the first is that the action in this form, as we shall see, reduces neatly to the area-corrected Nambu-Goto action \eqref{eqn:modified-NG-action}, and the second comes from a more rigorous bimetric Polyakov string analysis which will be done in appendix \ref{app:bimetric-string}, where we show that starting from a bimetric Polyakov string one can derive the action \eqref{eqn:inverse-metric-Polyakov}.
 
 This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables.
-This time, however, not only is WS diffeomorphism invariance destroyed, but so is WS Weyl symmetry, since the second term has inverse determinant multiplied by inverse metric.
+This time, however, we lose WS Weyl symmetry, since the second term has inverse determinant multiplied by inverse metric.
 
@@
 \end{equation}
-Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g^{a b} = \e ^{- \phi (x)} \eta ^{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
+Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 \begin{equation} \label{eqn:coupling-X-phi}
-	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + 2 \eta ^{a b} \frac{\partial _{a} \phi (x)}{\dfrac{2 \e ^{2 \phi (x)}}{k \Delta} - 1} \partial _{b} X^{\mu} = 0 ,
-\end{equation}
-revealing a wave equation sourced by a coupling between the WS conformal factor and the embedding fields much akin to the dilaton field \cite{Tong2009Lectures}.
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0 ,
+\end{equation}
+revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \cite{Balthazar-t-backgrounds}.
 We'll come back to this in \autoref{sec:discussion}.
@@
 can be used to find the explicit dependence of $\mu ^2$ with the quantum geometry parameters $k \Delta$ as in
-\begin{equation} \label{eqn:mu-constraint-final}
-	\mu ^2 = \frac{2 i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} (p \partial _{\sigma} \phi - E \partial _{\tau} \phi) .
-\end{equation}
+\begin{multline} \label{eqn:mu-constraint-final}
+	\mu ^2 = \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \big( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \\
+	- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \big) .
+\end{multline}
 
@@
 The constraints are nothing new, they're precisely the same as the ones of regular String Theory.
-What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
+What's new in our analysis is the $\mu ^2$ term, which we will assume to be constant for a first analysis, making it so the solution is given by Fourier transform
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
@@
 \begin{multline} \label{eqn:F-minus-full-sum}
-	F^{-} = 1 - \frac{k \Delta}{2 \e ^{\phi (x)}} = \\
+	F^{-} = 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \\
 	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
@@
 
+Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we got similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
+
 \section{Strings and Quantum Geometry}\label{sec:string-geometry}
@@
 \end{equation}
-and from here we note that if $T' = - T k \Delta / 2$ and $h = g^{-1}$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
+and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
 \begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
@@
 \end{equation}
-The condition $h = g^{-1}$ can be achieved by
+The condition $h = \Delta ^2 / g$ can be achieved by
 \begin{equation} \label{eqn:h=SgS}
-	h_{a b} = S_{a c} g^{c d} S_{d b}
-\end{equation}
-where $\det (S) = \pm 1$ and $S^{\dagger} = S$. This implies that
+	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
+\end{equation}
+This implies that
 \begin{multline} \label{eqn:SgS-implication}
-	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} S_{a c} \varepsilon ^{c c'} S_{d b} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
+	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
 	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
 \end{multline}
-which can be achieved by choosing
+which can be achieved if
 \begin{equation} \label{eqn:S=sigma_y}
-	S_{a c} = i \varepsilon _{a c} = - (\sigma _{y})_{a c}
+	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
 \end{equation}
@@
 \begin{equation} \label{eqn:H=1/(2g)G}
-	H_{\mu \nu} = \frac{1}{2 g} G_{\mu \nu} .
-\end{equation}
+	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
+\end{equation}
+which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
 
@@
 \end{equation}
-whereby assuming the conditions for $h = g^{-1}$ \eqref{eqn:h=SgS} and \eqref{eqn:S=sigma_y} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
+whereby assuming the conditions for $h = \Delta ^2 / g$ \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
 \begin{equation} \label{eqn:bimetric-X-eom-simplified-1}
@@
 which in conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ simplifies further to eq \eqref{eqn:X-eom-simplified} derived in section \ref{sec:inverse-metric-Polyakov}.
-In fact, if we plug in the conditions \eqref{eqn:h=SgS} and \eqref{eqn:S=sigma_y} and $T' = - T k \Delta / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
+In fact, if we plug in the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
 

### 2024-06-08 lqg-strings.tex
added a paragraph about the WS Hamiltonian and momentum operators and rigid rotations of the string

@@
 
+A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
+\begin{align}
+	\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-Hamiltonian}              \\
+	\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-momentum}
+\end{align}
+since those generate $\tau$ and $\sigma$ translations respectively
+\begin{align}
+	\left[ \Hat{H} , \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
+	\left[ \Hat{P} , \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
+\end{align}
+Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \eqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string.
+\emph{Physical states for the KG string have non-conserved WS momentum.} Also, we see that there is no level-matching between left and right-moving modes since those are not distinct in our model.
+
 Let us denote the ground state with momentum $p^{\mu}$ by $\ket{0 ; p}$. Then, the mass-shell condition \eqref{eqn:shifted-mass-spectrum} implies that
@@
 Next we look at the $n$-th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector.
-The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have independent left and right sectors, thus permitting spin-1 states.
+The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have distinct left and right sectors, thus permitting spin-1 states.
 We'll discuss these closed string single excitation states in section \ref{sec:discussion}.
@@
 
-The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a glaring disadvantage: they do not have WS diffeomorphism invariance, making it so it is not clear what WS parameterization should be used and neither if physical predictions can be extracted from them since it is not obvious that different parameterizations describe the same system.
-If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS diffeomorphism invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
+The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a clear disadvantage: they lost WS Weyl symmetry, which makes the equations extracted from them have a dependence on the scale factor $\phi (x)$.
+If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS Weyl invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
 \begin{multline} \label{eqn:emergent-dimensions-action}

### 2024-06-16 lqg-strings.tex
minor addition to ddiscussion section
added a paragraph relating the Delta field to Kalb-Rammond field

@@
 	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
-	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
-\end{multline}
+	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} ,
+\end{multline}
+where $\nabla _{a}$ denotes the 2-dimensional covariant derivative with respect to the Levi-Civita connection $\Gamma _{a b} ^{c}$.
 
@@
 which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
+Since $g_{a b}$ is taken to be the pullback of the background metric $G_{\mu \nu}$, $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, which is a part of the spin-2 spectrum of the closed string, perhaps the quantum area correction field $\Delta _{a b}$ is related to the pullback of the background Kalb-Rammond 2-form, which is the other half of the first excitation of the closed spin-2 spectrum,
+\begin{equation} \label{eqn:Delta-B-relation}
+	\Delta _{a b} \sim \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} ,
+\end{equation}
+thus giving a concrete physical interpretation for the $B_{\mu \nu}$ field as being related directly to quantum geometry.
 

### 2024-06-17 lqg-strings.tex
Added to Einstein-Cartan string section

--- 2024-06-08 lqg-strings.tex
@@
 where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate.
-
-treating the $X$'s as co-ordinates for the bulk background and also as
+As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein-Cartan geometry.
+
+\subsection{Gauging Translations}\label{sec:translation_gauge}
+
+There is a very generic way in which one can introduce translations in the form of matrix valued transformations acting on vector (or one-form) objects [ref wikipedia].
+For instance if we have a vector $\vec{x} = (x,y)$, rotations are given by $2 \times 2$ matrices.
+Now we add a dummy $'r'$ co-ordinate to our vector and set it equal to one, so our new vector is of the form: $\vec{X} = (x,y,r=1)$.
+Now the matrices which act on this vector will be three dimensional.
+One such matrix has the form:
+\begin{equation}
+	\mb{R} = \begin{pmatrix}
+		a & b & t_x \\
+		c & d & t_y \\
+		0 & 0 & 1
+	\end{pmatrix}.
+\end{equation}
+Here the left upper diagonal $2\times 2$ block corresponds to the usual 2d rotations, while the new off-diagonal elements $(t_x, t_y)$ parametrize the amount we wish to displace our original vector $(x,y)$.
+Under the action of $\mb{R}$ (with the rotation component fixed to be identity), our vector becomes:
+\begin{equation}\label{eqn:affine-transform}
+	\mb{R} \vec X = \begin{pmatrix}
+		x + t_x \\
+		y + t_y \\
+		1
+	\end{pmatrix}.
+\end{equation}
+One might point out that the matrix $\mb{R}$ is not symmetric, as one would require of an orthogonal transformation.
+If we make $\mb{R}$ symmetric, then under the above transformation the third (projective) component of the 3-vector will no longer be equal to one.
+\begin{equation}\label{eqn:affine-transform}
+	\mb{R} \vec X = \begin{pmatrix}
+		x + t_x \\
+		y + t_y \\
+		x t_x + y t_y + 1
+	\end{pmatrix}.
+\end{equation}
 

### 2024-06-17 lqg-strings.tex
Moved sections around to improve flow (DV+LdS)
Changed bimetric polyakov subsection title

@@
 
-\subsection{Modified Equations of Motion}\label{sec:modified-eom}
-
-Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
-\begin{equation} \label{eqn:modified-NG-eom}
-	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
-\end{equation}
-and
-\begin{equation} \label{eqn:modified-NG-bc}
-	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
-\end{equation}
-where
-\begin{align} \label{eqn:modified-NG-tau-currents}
-	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
-	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
-\end{align}
-\begin{align} \label{eqn:modified-NG-sigma-currents}
-	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
-	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
-\end{align}
-and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
-
-In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
-\begin{equation} \label{eqn:transverse-'gauge'}
-	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
-\end{equation}
-where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string.
-We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
-\begin{equation} \label{eqn:string-energy}
-	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
-\end{equation}
-and the form of the wave equation maintains its shape as in
-\begin{equation} \label{eqn:corrected-NG-wave-equation}
-	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
-\end{equation}
-where the effective mass density and effective tension are given by
+\section{The Bimetric String}\label{app:bimetric-string}
+
+It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+We can see that this is indeed the case as follows.
+
+Consider a string propagating in a target space whose geometry is described by two bulk metrics.
+There are two ways that a string with two metrics might arise.
+One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
+As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
+However, in this case, we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
+One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
+\begin{equation}\label{eqn:ws-bimetric-interaction}
+	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
+\end{equation}
+Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
+The resulting action would be of the form:
+\begin{equation}\label{eqn:ws-bimetric-action-v1}
+	S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
+\end{equation}
+Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
+
+The second possibility is the following.
+Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
+As a result, we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
+\begin{subequations}\label{eqn:ws-induced-metrics}
 	\begin{align}
-	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
-	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
-\end{align}
-
-Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
-\begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
-\end{equation}
-we find the variable-speed wave equation
-\begin{equation} \label{eqn:simplified-modified-wave-eqn}
-	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
-\end{equation}
-from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
-\begin{equation} \label{eqn:wave-speed-corrected}
-	v = \frac{c}{F^+}.
-\end{equation}
+		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
+		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
+	\end{align}
+\end{subequations}
+We can then write down the combined action for the string worldsheet as:
+\begin{equation}\label{eqn:ws-bimetric-action-v2}
+	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
+\end{equation}
+where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
+
+\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
+
+The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
+One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
+
+Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
+\begin{equation}\label{eqn:polyakov-curved}
+	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
+\end{equation}
+where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
+\begin{align}\label{eqn:polyakov-flat}
+	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
+	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
+	         & + S_{int} [g , h , X].
+\end{align}
+
+\subsection{Worldsheet Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}
+
+In the following we will
+
+Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
+\begin{equation} \label{eqn:variation-wrt-g}
+	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
+\end{equation}
+\begin{multline} \label{eqn:g-em-tensor}
+	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
+\end{multline}
+and completely analogous for the $H_{\mu \nu}$ metric,
+\begin{equation} \label{eqn:variation-wrt-h}
+	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
+\end{equation}
+\begin{multline} \label{eqn:h-em-tensor}
+	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
+\end{multline}
+If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
+\begin{equation} \label{eqn:g-expression}
+	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+\end{equation}
+where the function $f^{(G)}$ is given by
+\begin{equation} \label{eqn:g's-f-function}
+	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
+\end{equation}
+and for $h_{c d}$
+\begin{equation} \label{eqn:h-expression}
+	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
+\end{equation}
+with $f^{(H)}$ given by
+\begin{equation} \label{eqn:h's-f-function}
+	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
+\end{equation}
+If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
+\begin{equation} \label{eqn:double-NG-action}
+	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
+\end{equation}
+and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
+\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
+	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
+\end{equation}
+The condition $h = \Delta ^2 / g$ can be achieved by
+\begin{equation} \label{eqn:h=SgS}
+	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
+\end{equation}
+This implies that
+\begin{multline} \label{eqn:SgS-implication}
+	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
+	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
+\end{multline}
+which can be achieved if
+\begin{equation} \label{eqn:S=sigma_y}
+	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
+\end{equation}
+and if the background metrics are related by
+\begin{equation} \label{eqn:H=1/(2g)G}
+	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
+\end{equation}
+which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
+
+As for the embedding fields equation, continuing to assume no interaction term we get a non-homogeneous wave equation for the coupled metric $F^{a b} _{\mu \nu} = T \sqrt{- g} g^{a b} G_{\mu \nu} + T' \sqrt{- h} h^{a b} H_{\mu \nu}$
+\begin{equation} \label{eqn:variation-wrt-X}
+	\frac{\delta S_{P B}}{\delta X^{\lambda}} = 0
+\end{equation}
+\begin{equation} \label{eqn:bimetric-X-eom}
+	\partial _{a} \left( F^{a b} _{\mu \lambda} \partial _{b} X^{\mu} \right) = \frac{1}{2} \partial _{\lambda} F^{a b} _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} ,
+\end{equation}
+whereby assuming the conditions for $h = \Delta ^2 / g$ \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
+\begin{equation} \label{eqn:bimetric-X-eom-simplified-1}
+	\del _{a} \left( \left( 1 - \frac{k \Delta}{2 (- g)} \right) \sqrt{- g} g^{a b} \del _{b} X^{\mu} \right) = 0 ,
+\end{equation}
+which in conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ simplifies further to eq \eqref{eqn:X-eom-simplified} derived in section \ref{sec:inverse-metric-Polyakov}.
+In fact, if we plug in the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
 
@@
 
-\section{The Bimetric String}\label{app:bimetric-string}
-
-It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
-We can see that this is indeed the case as follows.
-
-Consider a string propagating in a target space whose geometry is described by two bulk metrics.
-There are two ways that a string with two metrics might arise.
-One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
-As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
-However, in this case, we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
-One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
-\begin{equation}\label{eqn:ws-bimetric-interaction}
-	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
-\end{equation}
-Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
-The resulting action would be of the form:
-\begin{equation}\label{eqn:ws-bimetric-action-v1}
-	S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
-\end{equation}
-Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
-
-The second possibility is the following.
-Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
-As a result, we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
-\begin{subequations}\label{eqn:ws-induced-metrics}
+\subsection{Modified Nambu Goto Equations of Motion}\label{sec:modified-eom}
+
+Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+\begin{equation} \label{eqn:modified-NG-eom}
+	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
+\end{equation}
+and
+\begin{equation} \label{eqn:modified-NG-bc}
+	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
+\end{equation}
+where
+\begin{align} \label{eqn:modified-NG-tau-currents}
+	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
+	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+\begin{align} \label{eqn:modified-NG-sigma-currents}
+	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
+	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
+
+In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
+\begin{equation} \label{eqn:transverse-'gauge'}
+	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
+\end{equation}
+where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string.
+We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+\begin{equation} \label{eqn:string-energy}
+	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
+\end{equation}
+and the form of the wave equation maintains its shape as in
+\begin{equation} \label{eqn:corrected-NG-wave-equation}
+	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
+\end{equation}
+where the effective mass density and effective tension are given by
 \begin{align}
-		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
-		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
-	\end{align}
-\end{subequations}
-We can then write down the combined action for the string worldsheet as:
-\begin{equation}\label{eqn:ws-bimetric-action-v2}
-	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
-\end{equation}
-where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
-
-\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
-
-The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
-One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
-
-Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
-\begin{equation}\label{eqn:polyakov-curved}
-	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
-\end{equation}
-where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{align}\label{eqn:polyakov-flat}
-	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
-	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
-	         & + S_{int} [g , h , X].
-\end{align}
-
-\subsection{The Bimetric Polyakov Equations} \label{sec:bimetric-polyakov-eoms}
-
-Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
-\begin{equation} \label{eqn:variation-wrt-g}
-	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
-\end{equation}
-\begin{multline} \label{eqn:g-em-tensor}
-	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
-\end{multline}
-and completely analogous for the $H_{\mu \nu}$ metric,
-\begin{equation} \label{eqn:variation-wrt-h}
-	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
-\end{equation}
-\begin{multline} \label{eqn:h-em-tensor}
-	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
-	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
-\end{multline}
-If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
-\begin{equation} \label{eqn:g-expression}
-	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
-\end{equation}
-where the function $f^{(G)}$ is given by
-\begin{equation} \label{eqn:g's-f-function}
-	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
-\end{equation}
-and for $h_{c d}$
-\begin{equation} \label{eqn:h-expression}
-	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
-\end{equation}
-with $f^{(H)}$ given by
-\begin{equation} \label{eqn:h's-f-function}
-	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
-\end{equation}
-If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
-\begin{equation} \label{eqn:double-NG-action}
-	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
-\end{equation}
-and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
-\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
-	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
-\end{equation}
-The condition $h = \Delta ^2 / g$ can be achieved by
-\begin{equation} \label{eqn:h=SgS}
-	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
-\end{equation}
-This implies that
-\begin{multline} \label{eqn:SgS-implication}
-	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
-	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
-\end{multline}
-which can be achieved if
-\begin{equation} \label{eqn:S=sigma_y}
-	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
-\end{equation}
-and if the background metrics are related by
-\begin{equation} \label{eqn:H=1/(2g)G}
-	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
-\end{equation}
-which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
-
-As for the embedding fields equation, continuing to assume no interaction term we get a non-homogeneous wave equation for the coupled metric $F^{a b} _{\mu \nu} = T \sqrt{- g} g^{a b} G_{\mu \nu} + T' \sqrt{- h} h^{a b} H_{\mu \nu}$
-\begin{equation} \label{eqn:variation-wrt-X}
-	\frac{\delta S_{P B}}{\delta X^{\lambda}} = 0
-\end{equation}
-\begin{equation} \label{eqn:bimetric-X-eom}
-	\partial _{a} \left( F^{a b} _{\mu \lambda} \partial _{b} X^{\mu} \right) = \frac{1}{2} \partial _{\lambda} F^{a b} _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} ,
-\end{equation}
-whereby assuming the conditions for $h = \Delta ^2 / g$ \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
-\begin{equation} \label{eqn:bimetric-X-eom-simplified-1}
-	\del _{a} \left( \left( 1 - \frac{k \Delta}{2 (- g)} \right) \sqrt{- g} g^{a b} \del _{b} X^{\mu} \right) = 0 ,
-\end{equation}
-which in conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ simplifies further to eq \eqref{eqn:X-eom-simplified} derived in section \ref{sec:inverse-metric-Polyakov}.
-In fact, if we plug in the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
+	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
+	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
+\end{align}
+
+Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
+\begin{equation} \label{eqn:sigma-parameterization}
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
+\end{equation}
+we find the variable-speed wave equation
+\begin{equation} \label{eqn:simplified-modified-wave-eqn}
+	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
+\end{equation}
+from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
+\begin{equation} \label{eqn:wave-speed-corrected}
+	v = \frac{c}{F^+}.
+\end{equation}
 

### 2024-06-17 lqg-strings.tex
Added text about relation of scalar density to Kalb-Ramond field.

@@
 
-\subsection{Worldsheet Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}
-
-In the following we will
+\subsection{(Worldsheet) Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}
+
+In the following we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified with the antisymmetric tensor $\epsilon_{ac}$ living on the worldsheet.
+The worldsheet antisymmetric tensor can itself be understood as arising from the pullback of a bulk antisymmetric tensor.
+Now, in string theory there is already a very important antisymmetric bulk tensor called the Kalb-Ramond field.
 

### 2024-06-18 lqg-strings.tex
Moved "two expressions for area" section to appendix
relocated some stuff and rewrote what needed to be rewritten

--- 2024-06-17 lqg-strings.tex
@@
 
-\subsection{Modified Equations of Motion}\label{sec:modified-eom}
-
-Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
-\begin{equation} \label{eqn:modified-NG-eom}
-	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
-\end{equation}
-and
-\begin{equation} \label{eqn:modified-NG-bc}
-	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
-\end{equation}
-where
-\begin{align} \label{eqn:modified-NG-tau-currents}
-	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
-	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
-\end{align}
-\begin{align} \label{eqn:modified-NG-sigma-currents}
-	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
-	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
-	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
-\end{align}
-and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
-
-In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
-\begin{equation} \label{eqn:transverse-'gauge'}
-	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
-\end{equation}
-where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string.
-We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
-\begin{equation} \label{eqn:string-energy}
-	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
-\end{equation}
-and the form of the wave equation maintains its shape as in
-\begin{equation} \label{eqn:corrected-NG-wave-equation}
-	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
-\end{equation}
-where the effective mass density and effective tension are given by
+\section{The Bimetric String}\label{app:bimetric-string}
+
+It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+We can see that this is indeed the case as follows.
+
+Consider a string propagating in a target space whose geometry is described by two bulk metrics.
+There are two ways that a string with two metrics might arise.
+One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
+As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
+However, in this case, we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
+One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
+\begin{equation}\label{eqn:ws-bimetric-interaction}
+	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
+\end{equation}
+Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
+The resulting action would be of the form:
+\begin{equation}\label{eqn:ws-bimetric-action-v1}
+	S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
+\end{equation}
+Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
+
+The second possibility is the following.
+Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
+As a result, we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
+\begin{subequations}\label{eqn:ws-induced-metrics}
 	\begin{align}
-	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
-	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
-\end{align}
-
-Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
-\begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
-\end{equation}
-we find the variable-speed wave equation
-\begin{equation} \label{eqn:simplified-modified-wave-eqn}
-	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
-\end{equation}
-from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
-\begin{equation} \label{eqn:wave-speed-corrected}
-	v = \frac{c}{F^+}.
-\end{equation}
-
-\section{Inverse Metric Polyakov} \label{sec:inverse-metric-Polyakov}
-
-In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov action.
-We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
+		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
+		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
+	\end{align}
+\end{subequations}
+We can then write down the combined action for the string worldsheet as:
+\begin{equation}\label{eqn:ws-bimetric-action-v2}
+	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
+\end{equation}
+where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
+
+\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
+
+The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
+One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
+
+Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
+\begin{equation}\label{eqn:polyakov-curved}
+	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
+\end{equation}
+where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
+\begin{align}\label{eqn:polyakov-flat}
+	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
+	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
+	         & + S_{int} [g , h , X].
+\end{align}
+
+\subsection{(Worldsheet) Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}
+
+In the following, we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified as being the determinant of (a tensor proportional to) the antisymmetric tensor $\widetilde{\varepsilon}_{a c}$ living on the worldsheet.
+The worldsheet antisymmetric tensor can itself be understood as arising from the pullback of a bulk antisymmetric tensor.
+Now, in string theory, there is already a very important antisymmetric bulk tensor called the Kalb-Ramond field.
+
+Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
+\begin{equation} \label{eqn:variation-wrt-g}
+	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
+\end{equation}
+\begin{multline} \label{eqn:g-em-tensor}
+	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
+\end{multline}
+and completely analogous for the $H_{\mu \nu}$ metric,
+\begin{equation} \label{eqn:variation-wrt-h}
+	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
+\end{equation}
+\begin{multline} \label{eqn:h-em-tensor}
+	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
+\end{multline}
+If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
+\begin{equation} \label{eqn:g-expression}
+	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+\end{equation}
+where the function $f^{(G)}$ is given by
+\begin{equation} \label{eqn:g's-f-function}
+	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
+\end{equation}
+and for $h_{c d}$
+\begin{equation} \label{eqn:h-expression}
+	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
+\end{equation}
+with $f^{(H)}$ given by
+\begin{equation} \label{eqn:h's-f-function}
+	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
+\end{equation}
+If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
+\begin{equation} \label{eqn:double-NG-action}
+	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
+\end{equation}
+and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
+\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
+	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
+\end{equation}
+The condition $h = \Delta ^2 / g$ can be achieved by
+\begin{equation} \label{eqn:h=SgS}
+	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
+\end{equation}
+This implies that
+\begin{multline} \label{eqn:SgS-implication}
+	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
+	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
+\end{multline}
+which can be achieved if
+\begin{equation} \label{eqn:S=sigma_y}
+	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
+\end{equation}
+and if the background metrics are related by
+\begin{equation} \label{eqn:H=1/(2g)G}
+	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .
+\end{equation}
+This makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
+Now, since the WS metric $g_{a b}$ is taken as the pullback of the bulk metric $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, which is part of the closed string spin-2 spectrum, then it would make sense for the WS area 2-form $\Delta _{a b}$ to be (at least related to) the pullback of the Kalb-Ramond field, which is the other half of the closed string rank 2 tensor field excitations,
+\begin{equation} \label{eqn:Delta-B-relation}
+	\Delta _{a b} \sim \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} .
+\end{equation}
+
+If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-flat}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-NG-action}:
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 \end{multline}
-One might think this action is incomplete since we only applied the correction to the determinant and didn't change the inverse metric $g^{a b}$, however the correction \ref{eqn:inverse-metric-correction} is a correction to the \emph{area} of the WS, not its metric.
-Moreover, there are other good reasons for this form of the Polyakov action: the first is that the action in this form, as we shall see, reduces neatly to the area-corrected Nambu-Goto action \eqref{eqn:modified-NG-action}, and the second comes from a more rigorous bimetric Polyakov string analysis which will be done in appendix \ref{app:bimetric-string}, where we show that starting from a bimetric Polyakov string one can derive the action \eqref{eqn:inverse-metric-Polyakov}.
-
+
+\section{Inverse Metric Polyakov} \label{sec:inverse-metric-Polyakov}
+
+In this section, we explore the action \eqref{eqn:inverse-metric-Polyakov} derived previously.
 This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables.
-This time, however, we lose WS Weyl symmetry, since the second term has inverse determinant multiplied by inverse metric.
+However, the price to pay is that we don't have WS Weyl symmetry since the second term has inverse determinant multiplied by inverse metric.
 
@@
 \begin{equation} \label{eqn:inverse-area-f}
-	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
-\end{equation}
-
-As for variation w.r.t the embbeding fields $X^{\lambda}$, we have
+	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
+\end{equation}
+just like the regular ST literature.
+
+As for variation \wrt the embbeding fields $X^{\lambda}$, we have
 \begin{equation} \label{eqn:vary-wrt-X}
@@
 
-Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$.
-By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
+Equation (\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$.
+By using the ansatz in eq (\ref{eqn:X-eom-simplified}), it becomes
 \begin{equation}
@@
 At first glance, it seems problematic that we have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$.
-With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
+With this choice, we thus turned eq (\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
 \begin{equation} \label{eqn:X-Klein-Gordon-eqn}
@@
 \end{equation}
-can be used to find the explicit dependence of $\mu ^2$ with the quantum geometry parameters $k \Delta$ as in
+can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as in
 \begin{multline} \label{eqn:mu-constraint-final}
@@
 \end{multline}
-
-\subsection{Relation With The Nambu-Goto Analysis} \label{sec:relation-with-NG-case}
-
-At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string.
-However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found).
-While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.
-
-Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq(\ref{eqn:simplified-modified-wave-eqn}) obtained in sec(\ref{sec:modified-eom}), renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t , x) \rightarrow (\tau (t , x) , \sigma (t , x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
-\begin{multline} \label{eqn:new-coordinates-constraints-quadratic}
-	\ \ \ \ \ \ \ \ \ \ (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \\
-	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma , \ \ \ \ \ \ \ \ \ \ \ \
-\end{multline}
-or more compactly,
-\begin{multline} \label{eqn:new-coordinates-constraints-compact}
-	\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \partial _{t} \tau = v \partial _{x} \sigma \\
-	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ,
-\end{multline}
-which is equivalent to
-\begin{multline} \label{eqn:new-coordinates-constraints-second-order}
-	\ \ \ \ \ \ \ \ \ \ \ \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau = \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \\
-	\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . \ \ \ \ \ \ \
-\end{multline}
-This turns eq(\ref{eqn:simplified-modified-wave-eqn}) into
-\begin{multline} \label{eqn:modified-wave-eqn-new}
-	\partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \\
-	+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \\
-	+ \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
-\end{multline}
-Next, we introduce $X^{\mu} = \kappa (\tau , \sigma) W^{\mu} (\tau , \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
-This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$.
-With this, eq(\ref{eqn:modified-wave-eqn-new}) turns into a Klein-Gordon equation
-\begin{equation}
-	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0 ,
-\end{equation}
-with \textquotedblleft mass" squared given by
-\begin{equation}
-	\mu ^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
-\end{equation}
-and $\tau (t , x)$ satisfying constraints(\ref{eqn:new-coordinates-constraints-compact}).
-This shows that our action(\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the inverse area corrected Nambu-Goto action(\ref{eqn:modified-NG-action}).
 
@@
 
-When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
+When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
 \begin{align}
@@
 , .
-\}$ being replaced by commutators $[ .
+\}$ being replaced by commutators $\{ .
 , .
-] = i \hbar \{ .
+\} \rightarrow - i [ .
 , .
-\}$:
+]$:
 \begin{align}
@@
 
-\subsection{Two Expressions for Area}\label{eqn:area-formulae}
+\subsection{}\label{sec:}
+
+\section{Physical Implications}
+
+\section{Discussion} \label{sec:discussion}
+
+We have presented in this work a possible way to formulate string theory in background independent manner.
+
+In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors.
+Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to?
+Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+\begin{equation} \label{eqn:connection-string-vector-excitation}
+	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
+\end{equation}
+Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
+\begin{equation} \label{eqn:AEF-string-vector-excitation}
+	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
+\end{equation}
+
+\subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}
+
+The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a clear disadvantage: they lost WS Weyl symmetry, which makes the equations extracted from them have a dependence on the scale factor $\phi (x)$.
+If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS Weyl invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
+\begin{multline} \label{eqn:emergent-dimensions-action}
+	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
+\end{multline}
+where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
+\gg m_{d}$.
+This is Afshordi's model \cite{Afshordi-emergent}.
+Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
+\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
+	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
+\end{equation}
+so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
+\begin{equation} \label{eqn:X-masses-constraint}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
+\end{equation}
+where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
+
+Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
+
+By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
+\begin{equation} \label{eqn:emergent-dimensions-g}
+	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+with $f$ given by
+\begin{equation} \label{eqn:emergent-dimensions-f}
+	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier.
+By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.
+
+One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
+\begin{multline} \label{eqn:emergent-dimensions-curved}
+	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
+\end{multline}
+where the mass parameters will be constrained as in
+\begin{equation} \label{eqn:X-masses-constraint-2}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
+\end{equation}
+since those are the ones that show up in the $X^{\mu}$ equations of motion
+\begin{multline}
+	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
+	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
+\end{multline}
+
+In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
+We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
+\begin{equation} \label{eqn:mu0-phi-relation}
+	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
+\end{equation}
+where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
+
+\begin{acknowledgments}
+
+\end{acknowledgments}
+
+\appendix
+
+\section{Two Expressions for Area}\label{eqn:area-formulae}
 
@@
 
-\subsection{}\label{sec:}
-
-\section{Physical Implications}
-
-\section{Discussion} \label{sec:discussion}
-
-We have presented in this work a possible way to formulate string theory in background independent manner.
-
-In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors.
-Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to?
-Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
-\begin{equation} \label{eqn:connection-string-vector-excitation}
-	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
-\end{equation}
-Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
-\begin{equation} \label{eqn:AEF-string-vector-excitation}
-	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
-\end{equation}
-
-\subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}
-
-The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a clear disadvantage: they lost WS Weyl symmetry, which makes the equations extracted from them have a dependence on the scale factor $\phi (x)$.
-If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS Weyl invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
-\begin{multline} \label{eqn:emergent-dimensions-action}
-	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
-	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
-\end{multline}
-where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
-\gg m_{d}$.
-This is Afshordi's model \cite{Afshordi-emergent}.
-Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
-\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
-	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
-\end{equation}
-so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
-\begin{equation} \label{eqn:X-masses-constraint}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
-\end{equation}
-where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
-
-Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
-We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
-
-By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
-\begin{equation} \label{eqn:emergent-dimensions-g}
-	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
-\end{equation}
-with $f$ given by
-\begin{equation} \label{eqn:emergent-dimensions-f}
-	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
-\end{equation}
-from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier.
-By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.
-
-One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
-\begin{multline} \label{eqn:emergent-dimensions-curved}
-	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
-	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
-\end{multline}
-where the mass parameters will be constrained as in
-\begin{equation} \label{eqn:X-masses-constraint-2}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
-\end{equation}
-since those are the ones that show up in the $X^{\mu}$ equations of motion
-\begin{multline}
-	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
-	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
-\end{multline}
-
-In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
-We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
-\begin{equation} \label{eqn:mu0-phi-relation}
-	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
-\end{equation}
-where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
-
-\begin{acknowledgments}
-
-\end{acknowledgments}
-
-\appendix
-
-\section{Worldsheet Action in Terms of Transverse Velocity}\label{app:transverse-action}
-
-\section{The Bimetric String}\label{app:bimetric-string}
-
-It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
-We can see that this is indeed the case as follows.
-
-Consider a string propagating in a target space whose geometry is described by two bulk metrics.
-There are two ways that a string with two metrics might arise.
-One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$.
-As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields.
-However, in this case, we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions.
-One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
-\begin{equation}\label{eqn:ws-bimetric-interaction}
-	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
-\end{equation}
-Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields.
-The resulting action would be of the form:
-\begin{equation}\label{eqn:ws-bimetric-action-v1}
-	S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
-\end{equation}
-Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
-
-The second possibility is the following.
-Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and \emph{two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$.
-As a result, we would now get two different induced metrics on the \emph{same} string worldsheet, given by:
-\begin{subequations}\label{eqn:ws-induced-metrics}
+\section{Modified Nambu Goto Equations of Motion}\label{sec:modified-eom}
+
+Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+\begin{equation} \label{eqn:modified-NG-eom}
+	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
+\end{equation}
+and
+\begin{equation} \label{eqn:modified-NG-bc}
+	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
+\end{equation}
+where
+\begin{align} \label{eqn:modified-NG-tau-currents}
+	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
+	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+\begin{align} \label{eqn:modified-NG-sigma-currents}
+	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
+	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
+	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
+\end{align}
+and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.
+
+In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
+\begin{equation} \label{eqn:transverse-'gauge'}
+	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
+\end{equation}
+where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string.
+We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
+\begin{equation} \label{eqn:string-energy}
+	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
+\end{equation}
+and the form of the wave equation maintains its shape as in
+\begin{equation} \label{eqn:corrected-NG-wave-equation}
+	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
+\end{equation}
+where the effective mass density and effective tension are given by
 \begin{align}
-		g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
-		h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
-	\end{align}
-\end{subequations}
-We can then write down the combined action for the string worldsheet as:
-\begin{equation}\label{eqn:ws-bimetric-action-v2}
-	S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
-\end{equation}
-where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the \emph{same} worldsheet.
-
-\subsection{Bimetric Polyakov Action}\label{sec:bimetric-polyakov}
-
-The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
-One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
-
-Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
-\begin{equation}\label{eqn:polyakov-curved}
-	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
-\end{equation}
-where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{align}\label{eqn:polyakov-flat}
-	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
-	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
-	         & + S_{int} [g , h , X].
-\end{align}
-
-\subsection{The Bimetric Polyakov Equations} \label{sec:bimetric-polyakov-eoms}
-
-Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
-\begin{equation} \label{eqn:variation-wrt-g}
-	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
-\end{equation}
-\begin{multline} \label{eqn:g-em-tensor}
-	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
-\end{multline}
-and completely analogous for the $H_{\mu \nu}$ metric,
-\begin{equation} \label{eqn:variation-wrt-h}
-	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
-\end{equation}
-\begin{multline} \label{eqn:h-em-tensor}
-	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
-	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
-\end{multline}
-If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
-\begin{equation} \label{eqn:g-expression}
-	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
-\end{equation}
-where the function $f^{(G)}$ is given by
-\begin{equation} \label{eqn:g's-f-function}
-	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
-\end{equation}
-and for $h_{c d}$
-\begin{equation} \label{eqn:h-expression}
-	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
-\end{equation}
-with $f^{(H)}$ given by
-\begin{equation} \label{eqn:h's-f-function}
-	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
-\end{equation}
-If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
-\begin{equation} \label{eqn:double-NG-action}
-	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
-\end{equation}
-and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
-\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
-	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
-\end{equation}
-The condition $h = \Delta ^2 / g$ can be achieved by
-\begin{equation} \label{eqn:h=SgS}
-	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
-\end{equation}
-This implies that
-\begin{multline} \label{eqn:SgS-implication}
-	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
-	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
-\end{multline}
-which can be achieved if
-\begin{equation} \label{eqn:S=sigma_y}
-	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
-\end{equation}
-and if the background metrics are related by
-\begin{equation} \label{eqn:H=1/(2g)G}
-	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
-\end{equation}
-which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.
-
-As for the embedding fields equation, continuing to assume no interaction term we get a non-homogeneous wave equation for the coupled metric $F^{a b} _{\mu \nu} = T \sqrt{- g} g^{a b} G_{\mu \nu} + T' \sqrt{- h} h^{a b} H_{\mu \nu}$
-\begin{equation} \label{eqn:variation-wrt-X}
-	\frac{\delta S_{P B}}{\delta X^{\lambda}} = 0
-\end{equation}
-\begin{equation} \label{eqn:bimetric-X-eom}
-	\partial _{a} \left( F^{a b} _{\mu \lambda} \partial _{b} X^{\mu} \right) = \frac{1}{2} \partial _{\lambda} F^{a b} _{\mu \nu} \partial _{a} X^{\mu} \partial _{b} X^{\nu} ,
-\end{equation}
-whereby assuming the conditions for $h = \Delta ^2 / g$ \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} and flat background $G_{\mu \nu} = \eta _{\mu \nu}$ gets simplified to
-\begin{equation} \label{eqn:bimetric-X-eom-simplified-1}
-	\del _{a} \left( \left( 1 - \frac{k \Delta}{2 (- g)} \right) \sqrt{- g} g^{a b} \del _{b} X^{\mu} \right) = 0 ,
-\end{equation}
-which in conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ simplifies further to eq \eqref{eqn:X-eom-simplified} derived in section \ref{sec:inverse-metric-Polyakov}.
-In fact, if we plug in the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ into the bimetric Polyakov action \eqref{eqn:polyakov-flat} we recover precisely the action \eqref{eqn:inverse-metric-Polyakov} of section \ref{sec:inverse-metric-Polyakov}, thus showing that the form of area corrected Polyakov action discussed there can be cast as a special case of the interactionless bimetric string.
+	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
+	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
+\end{align}
+
+Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
+\begin{equation} \label{eqn:sigma-parameterization}
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
+\end{equation}
+we find the variable-speed wave equation
+\begin{equation} \label{eqn:simplified-modified-wave-eqn}
+	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
+\end{equation}
+from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
+\begin{equation} \label{eqn:wave-speed-corrected}
+	v = \frac{c}{F^+}.
+\end{equation}
+
+\section{Relating Nambu-Goto and Polyakov analysis} \label{sec:relation-with-NG-case}
+
+At first glance, our analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string.
+However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we found in section \ref{sec:inverse-metric-Polyakov}).
+While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.
+
+Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq (\ref{eqn:simplified-modified-wave-eqn}) obtained in section \ref{sec:modified-eom}, renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t , x) \rightarrow (\tau (t , x) , \sigma (t , x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
+\begin{multline} \label{eqn:new-coordinates-constraints-quadratic}
+	\ \ \ \ \ \ \ \ \ \ (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \\
+	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma , \ \ \ \ \ \ \ \ \ \ \ \
+\end{multline}
+or more compactly,
+\begin{multline} \label{eqn:new-coordinates-constraints-compact}
+	\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \partial _{t} \tau = v \partial _{x} \sigma \\
+	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ,
+\end{multline}
+which is equivalent to
+\begin{multline} \label{eqn:new-coordinates-constraints-second-order}
+	\ \ \ \ \ \ \ \ \ \ \ \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau = \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \\
+	\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . \ \ \ \ \ \ \
+\end{multline}
+This turns eq (\ref{eqn:simplified-modified-wave-eqn}) into
+\begin{multline} \label{eqn:modified-wave-eqn-new}
+	\partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \\
+	+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \\
+	+ \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
+\end{multline}
+Next, we introduce $X^{\mu} = \kappa (\tau , \sigma) W^{\mu} (\tau , \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
+This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$.
+With this, eq (\ref{eqn:modified-wave-eqn-new}) turns into a Klein-Gordon equation
+\begin{equation}
+	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0 ,
+\end{equation}
+with \textquotedblleft mass" squared given by
+\begin{equation}
+	\mu ^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
+\end{equation}
+and $\tau (t , x)$ satisfying constraints (\ref{eqn:new-coordinates-constraints-compact}).
+This shows that our analysis of the action (\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the analysis of the inverse area corrected Nambu-Goto action (\ref{eqn:modified-NG-action}).
 

### 2024-06-18 lqg-strings.tex
used subequation environment on places where there was multiple eqns

@@
 When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution.
@@
 After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
-\begin{equation} \label{eqn:expansion-modes-bracket-0}
-	\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\} = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\}
-\end{equation}
-\begin{equation} \label{eqn:expansion-modes-bracket-1}
-	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} ,
-\end{equation}
+\begin{subequations}
+	\begin{align}
+		\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\}       & = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\} \label{eqn:expansion-modes-bracket-0} \\
+		\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} & = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} , \label{eqn:expansion-modes-bracket-1}
+	\end{align}
+\end{subequations}
 from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 \begin{equation} \label{eqn:harmonic-bracket-relations}
@@
 The algebra is given by
+\begin{subequations}
 	\begin{equation} \label{eqn:L-brackets-0}
@@
 	\end{equation}
+\end{subequations}
 
@@
 ]$:
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 
@@
 For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
+\begin{subequations}
 	\begin{align}
 		\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
-	\Hat{p}_{\mu} \ket{0 ; 0} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
-\end{align}
+		\Hat{p}_{\mu} \ket{0 ; x} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
+	\end{align}
+\end{subequations}
 in position representation and
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 in momentum representation.
@@
 When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
+\begin{subequations}
 	\begin{equation} \label{eqn:L-constraint-quantum-1}
@@
 	\end{equation}
+\end{subequations}
 $\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators.
@@
 The commutation relations between the constraints are inherited by the Poisson brackets
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 The commutator (\ref{eqn:L-commutator-1}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutator-2}) have ordering ambiguities for $|m| = |k|$ and/or $|n| = |p|$, so we add the anomalous terms
@@
 Also, because of the symmetry in the indices we have that $C_{- n} = C_{n}$ and $D_{- k} = D_{k}$.
-Using the Jacobi identity
-\begin{multline} \label{eqn:L-Jacobi-identity}
-	\left[ \Hat{\widetilde{L}}_{n , m} , \left[ \Hat{\widetilde{L}}_{k , p} , \Hat{\widetilde{L}}_{r , s} \right] \right] + \\
-	+ \left[ \Hat{\widetilde{L}}_{r , s} , \left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] \right] + \\
-	+ \left[ \Hat{\widetilde{L}}_{k , p} , \left[ \Hat{\widetilde{L}}_{r , s} , \Hat{\widetilde{L}}_{n , m} \right] \right] = 0
-\end{multline}
-we get the difference equation
+Using the Jacobi identity we get the difference equation
 \begin{equation} \label{eqn:F-difference-eqn}
@@
 A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 since those generate $\tau$ and $\sigma$ translations respectively
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \eqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string.
@@
 We can decompose the polarization into a symmetric traceless part $G_{\mu \nu}$, an anti-symmetric part $B_{\mu \nu}$ and a trace part $\Phi \eta _{\mu \nu}$ given by
+\begin{subequations}
 	\begin{align}
@@
 	\end{align}
+\end{subequations}
 $\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-known types of background fields: the spacetime metric $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$, all of those having squared mass given by eq \eqref{eqn:nth-spin-2-mass-shell}.

### 2024-06-19 lqg-strings.tex
added a subsection on discussion about the explicit form of the pullback of the Kalb-Ramond field

@@
 
+\subsection{Worldsheet Kalb-Ramond field and Quantum of Area} \label{sec:WS-Kalb-Ramond-QoA}
+
+If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov}, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
+This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
+The more complete picture would be thus to consider the string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
+\begin{multline} \label{eqn:area-corrected-K-R-action}
+	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
+	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \widetilde{\varepsilon}^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
+\end{multline}
+where we can rewrite $\widetilde{\varepsilon}^{a b}$ in terms of $\Delta ^{a b}$ as
+\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
+	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
+	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
+\end{multline}
+By varying this action \wrt $\Delta ^{c d}$ we get
+\begin{equation} \label{}
+	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
+\end{equation}
+with $\widetilde{f}$ given by
+\begin{multline} \label{eqn:1/f-tilde}
+	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
+\end{multline}
+where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
+\begin{equation} \label{eqn:f-tilde}
+	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
+\end{equation}
+from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
+\begin{equation} \label{eqn:WS-b-field}
+	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \widetilde{\varepsilon}_{a b} ,
+\end{equation}
+or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
+\begin{equation} \label{eqn:Delta-b-relation}
+	\Delta _{a b} = \sqrt{\Delta} \widetilde{\varepsilon}_{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
+\end{equation}
+
 \subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}

### 2024-06-19 lqg-strings.tex
sparated the paragraph on closed string spin-1 states into its own subsection and added a paragraph on how to restore Weyl symmetry in sec 5

@@
 This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables.
-However, the price to pay is that we don't have WS Weyl symmetry since the second term has inverse determinant multiplied by inverse metric.
+This action at first glance does not have WS Weyl invariance since the second term has inverse determinant multiplied by inverse metric, however, if one wishes to restore Weyl symmetry one just needs to require that under a Weyl transformation, the $\Delta _{a b}$ field also transforms like the metric \ie
+\begin{subequations}
+	\begin{align}
+		g_{a b}       & \rightarrow \Lambda (x) g_{a b} \label{eqn:g-Weyl-transform}             \\
+		\Delta _{a b} & \rightarrow \Lambda (x) \Delta _{a b} , \label{eqn:Delta-Weyl-transform}
+	\end{align}
+\end{subequations}
+however, we will not work under this assumption, since we expect that Weyl symmetry is broken near the Planck scale due to the discreteness of space-time.
 
@@
 
+\subsection{Closed String Spin-1 States} \label{sec:spin-1-states}
+
 In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors.
@@
 
-The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a clear disadvantage: they lost WS Weyl symmetry, which makes the equations extracted from them have a dependence on the scale factor $\phi (x)$.
-If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS Weyl invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
+There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi-emergent} model, with the action being
 \begin{multline} \label{eqn:emergent-dimensions-action}

### 2024-06-19 lqg-strings.tex
Added to section on string holography. Changed section title.

@@
 \usepackage{parskip}
-\setlength{\parindent}{15pt}
+% \setlength{\parindent}{15pt}
 
@@
 
-\section{Strings and Quantum Geometry}\label{sec:string-geometry}
+\section{Holography From Classical Strings}\label{sec:string-geometry}
 
@@
 In this section we present a possible action in which the bulk geometry is encoded in the string action in terms of a connection living on the worldsheet.
+We will explore the natural consequences which follow from considering the symmetries of this action.
 
 First let us recall the form of the Polyakov action for the bosonic string \eqref{eqn:polyakov-action}:
-
 \begin{equation*}
@@
 \end{equation*}
-
 If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$.
 The resulting action would now have the form:
-
 \begin{equation}\label{eqn:polyakov-gauged}
@@
 \end{equation}
-
 where the covariant derivative $\mc{D}_a$ is of the form:
@@
 where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling.
-A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming
-
-Let us begin by writing down the action of a string propagating in a background geometry.
-The background geometry is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$.
-Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming under the gauge group $\mc G$.
+But we will see that this is not a problem.
+In fact, in order to be able to couple the string to an \emph{arbitrarily} curved geometry we will find that we \emph{require} the $X^\mu$ to transform as vectors under the action of some \emph{local} gauge field.
+
+Our goal is to write down the action of a string propagating in a background geometry.
+One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet.
+However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones.
+An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $\tilde E_\mu^I \tilde E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat co-ordinates).
+This, however, leaves open the question of what role the bulk connection should play in this picture.
+
+Further, we can ask what is the physical effect of having a non-trivial connection in the bulk in terms of the local geometry.
+The bulk connection tells us how the vielbein transforms from point to point and thus effectively measures how much the bulk metric changes from point to point.
+So, for instance, the connection which describes the geometry around a Kerr black hole also encodes how the local tetrad frame rotates as one moves around the axisymmetric axis of the black hole.
+All of these considerations lead us to the premise that if one wishes to describes the bulk geometry in terms of connection variables, then it is only natural to describe the worldsheet geometry in terms of connection variables and to use the tools that come along with having a gauge connection to understand how the worldsheet geometry can couple to the bulk geometry.
+
+Therefore, now will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
 $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet.
-Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet.
-But these fields are not really scalars.
-They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.
+Now if one adopts the ``sigma model'' point of view then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet.
+But we know that these fields are not a collection of $d+1$ independent scalars.
+They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time.
+However, the symmetries of a flat background include not only Lorentz transformations bulk also translations.
+The string action is required to be invariant under both of these:
+\begin{align*}
+	X^\mu & \rarrow X^\mu + \delta X^\mu; \quad \delta X^\mu \in \mbb{R}^{3,1} \\
+	X^\mu & \rarrow \Lambda^\mu{}_\nu X^\mu; \quad \Lambda^\mu{}_\nu \in \mathrm{SO}(3,1)
+\end{align*}
+where $\delta X^\mu$ is some arbitrary vector in Minkowski space.
 

### 2024-06-20 lqg-strings.tex
Continued section on stringy holography

@@
 
-Therefore, now will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+Therefore, now we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
 $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet.
@@
 where $\delta X^\mu$ is some arbitrary vector in Minkowski space.
+The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $\mbb{P}^{3,1}$, the Poincaré group in $3+1$ dimensions.
+Of course, these are good symmetries only if our background is flat.
+An arbitrarily curved background can have one or more Killing vectors depending on how much symmetry the geometry has, but \emph{in general} even that need not be the case.
+The best one can hope for is some notion of local flatness is some finite subregion of the background manifold.
+Moreoever the entire purpose of this work to try and understand how to write down a string action in an \emph{arbitrarily curved} background, assuming that such a thing is even possible.
+
+Even in an arbitrarily curved background, however, symmetry still plays a very important role.
+Even if we have discarded \textbf{global} symmetries, that still leaves us with \textbf{local} symmetries in the form of diffeomorphisms under which must the action must remain invariant.
+If, in addition, we have fields such as a gauge connection and an associated vielbein living in the background, then we also have to take local gauge transformations of these objects into account.
+However, diffeomorphisms and gauge transformations are not independent of each other.
+A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which has a differentiable (and invertible) map.
+In more pedestrian language, a diffeomorphism is an (invertible) change of co-ordinates on a manifold.
+
+Now, while we do not have definite proof of this statement
 

### 2024-06-21 lqg-strings.tex
Lot of reorganization, added references, more content, many edits.

@@
 There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.
-The first of these is string theory, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
+We discuss each in turn below giving a bird's eye view of research spanning a period of nearly sixty years.
+
+The first of these is \emph{string theory}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
 However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.
 
-One of the primary criticisms of string theory is its apparent lack of ``background independence''.
-This is more general than the principle of \emph{general covariance} which states that physics should be independent of the choice of co-ordinates.
-Background independence is the statement that any \emph{quantum} theory of gravity - which, presumably, should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry - should provide a description of physics which is independent, not only of the choice of co-ordinates, but also of the choice of background manifold on which those co-ordinates live.
-On the face of it string theory, at least in its conventional form, does not satisfy this principle.
-
-It is sometimes argued that string theory is, in fact, background independent since the equations of motion which arise when the (Bosnic) string is coupled to the metric of the ``worldvolume'' (the background manifold in which the string is propagating) turn out to include Einstein's field equations for gravity.
-In  other words, Weyl invariance - one of the fundamental symmetries of the string worldsheet, \emph{requires} \todo{insert refs} that the background geometry must satisfy Einstein's equations.
-While technically correct, it begs the question, if general relativity ``emerges'' from string theory then why is it not possible to quantize the string on an arbitrary background to begin with?
-As anybody who has studied the basics of string theory knows, the standard quantization procedure \emph{assumes} that the worldvolume has a flat metric.
-It is, thus far, not technically feasible to do away with this assumption.
-
-There is another sense in which string theory falls short of being a theory of quantum gravity.
-This, however, rests upon a philosophical perspective, about the nature of quantum gravity, which one may or may not choose to subscribe to.
-This is the viewpoint that in any quantum theory of gravity, geometry itself must be quantized.
-Again, one might say that gravitons - the quantum perturbations of the metric - are ``quanta of geometry''.
-However, gravitons \emph{live} upon some background manifold.
-Moreover, as mentioned, they are \emph{perturbative} by construction.
-Gravitons cannot provide a quantum description of geometry, anymore than quantizing water waves can provide a picture of the molecular structure of water\footnote{This viewpoint has been most clearly articulated by Jacobson \cite{Jacobson1995Thermodynamics}}.
-These considerations bring us to the second major\footnote{the characterization of LQG as a ``major'' approach is the our choice and not necessarily reflective of the consensus in the broader quantum gravity community.} approach towards a quantum theory of gravity, known as Loop Quantum Gravity or LQG for short.
-
-LQG arose almost by accident, something it has in common with string theory.
+The second approach is called \emph{loop quantum gravity} or ``LQG'' for short.
+LQG is ostensibly meant to be a theory of ``pure quantum gravity'', that is gravity without any matter.
+Matter can always be ``added'' in by hand into the framework but is not present to begin with.
+LQG is also built upon a rigorous mathematical framework which applies the well-established Dirac procedure of quantization to canonical (ADM) Einstein gravity, and this is crucial, written in terms of Ashtekar variables which is a connection based approach as opposed to the conventional metric formalism.
+LQG has concrete predictions such as discreteness of physical areas \cite{Rovelli1993Area,Rovelli1994Discreteness}, and also has rigorous mathematical results which reproduce the black hole entropy formulae for Einstein gravity \cite{Rovelli1996Black}.
+Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
+
 Traditionally, there are two ways in which a classical theory can be quantized.
@@
 This approach respects spacetime covariance since here the central object is the action which is invariant under spacetime transformations by construction.
+String theory is an example of such a formalism.
+
 The Hamiltonian approach, on the other hand, involves making a choice of a spacelike surface $\Sigma_t$ and a corresponding timelike vector $t^\mu$, normal to $\Sigma_t$ (here $t$ is a continuous parameter which labels the family of surfaces).
 This approach, therefore, necessarily does not respect spacetime covariance since it involves making a specific choice of the foliation of the background into spacelike surfaces.
+Loop quantum gravity is built upon this approach to quantization.
 
@@
 The gravity Hamiltonian turns out to be a sum of two constraints known as the diffeomorphism (or ``momentum'') constraint $H_{diff}$ and the Hamiltonian constraint $H_{ham}$:
-
 \begin{equation}
@@
 \end{equation}
-
 and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$.
 The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$ , must be annihilated by these constraints:
-
 \begin{equation}
@@
 \end{equation}
-
 While this procedure is straightforward in principle, in practice is was impossible to implement in the quantum theory due to highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
-This unfortunate state of affairs persisted until the 1980s when Abhay Ashtekar recast general relativity as a theory of a Minkowski tetrad $E^I_\mu$ and a self-dual $\sltwoc$ connection $A_\mu^{IJ}$.
+This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a theory of a Minkowski tetrad $E^I_\mu$ and a self-dual $\sltwoc$ connection $A_\mu^{IJ}$.
 Ashtekar realised that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables.
-It was quickly realised by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states.
-
-Following this, work by Rovelli and Smolin \todo{insert ref} and by Ashtekar, Rovelli and Smolin demonstrated the most remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two dimensional surfaces and volumes of three dimensional regions.
+It was quickly realised by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory \cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states \cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.
+
+Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two dimensional surfaces and volumes of three dimensional regions.
 Moreover, these operators could be diagonlized exactly in the spin-network basis and a lower bound on the smallest possible quantum of area and quantum of volume could be derived.
-This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression.
-
-\todo[inline]{Insert brief intro to spin nets}
-
-The following is the outline of the paper.
-In \autoref{sec:intro} we recall the Nambu-Goto action and its symmetries.
-We explain how the bulk (embedding manifold) geometry is coupled to the worldsheet geometry and the conventional argument for the statement that string theory describes not only the object but also its background (the geometry it is propagating) in and is therefore a complete theory of quantum gravity.
-We critique this claim and explain in what way LQG might provide a resolution of some of the puzzles of string theory.
-In \autoref{sec:modified-ng} we present a phenomenological modification of the Nambu-Goto action based on the observation from LQG that there exists a non-zero, positive, eigenvalue of the area operator.
-We show that this action can be expanded in terms of a small coupling constant $g = l_{pl}/l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $g \ll 1$.
-We point out that the lowest order correction to the NG action can be viewed as a bimetric action for the string.
-We derive the classical equations of motion for this area-corrected NG action.
-In \autoref{sec:inverse-metric-Polyakov} we construct the Polyakov version of the modified NG action, show that the equations of motion it yields are the same as those coming from the modified NG action.
-Further we solve the string equations of motion to find the fundamental modes and perform the quantization of the Bosonic string in the usual manner.
-In \autoref{sec:string-geometry} we describe how to construct an action for the Bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
-We discuss possible avenues for quantizing this action and further studying its implications for the relationship between string theory and LQG.
-
-In \autoref{app:bimetric-string} we discuss further the bimetric extension of the string action in both the Nambu-Goto and Polyakov version.
-
-\section{Strings in Background Fields and Emergent Gravity}\label{sec:strings-gravity}
-
-Let us begin by recalling the Polyakov action for the bosonic string.
-
-\begin{equation}\label{eqn:polyakov-action}
-	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
-\end{equation}
-
-Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.
-
-Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
-Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
-
-The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$.
-Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background.
-It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds.
-The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
-
-\begin{equation}\label{eqn:polyakov-gravity}
-	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
-\end{equation}
-
-where the bulk metric is now a function of the bulk co-ordinates $G_{\mu\nu}(X)$.
-Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$.
-However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string.
-One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.
-
-Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), that the garviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry.
-The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
-\begin{equation}\label{eqn:ricci-flat}
-	\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
-\end{equation}
-Therefore we find that conformal invariance of the string worldsheet \emph{implies} that the background geometry in which the string propagates satisfies the \emph{vacuum} Einstein equations.
-It is this result which is often cited as evidence for the claim that string theory is a \emph{background independent} theory of quantum gravity.
-
-In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent. Our reasons are the following:
+This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity.
+One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4 $ for the Bekenstein-Hawking entropy.
+
+One of the primary criticisms of string theory is its apparent lack of ``background independence''.
+This is more general than the principle of \emph{general covariance} which states that physics should be independent of the choice of co-ordinates.
+Background independence is the statement that any \emph{quantum} theory of gravity should provide a description of physics which is independent, not only of the choice of co-ordinates, but also of the choice of background manifold on which those co-ordinates live.
+Such a theory should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry.
+On the face of it, string theory, at least in its conventional form, does not satisfy this principle.
+The great virtue of LQG on the other hand, is that it respects background independence as a sacred principle and proceeds to quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.
+
+Some will argue that string theory is, indeed, background independent.
+The argument for this is as follows.
+When coupled to the string action, background fields are treated as external ``coupling constants'' and can therefore be subject to a renormalization group analysis.
+The fixed point of this analysis, remarkably enough, requires one to impose the condition that the background metric obeys Einstein's field equations (more precisely that the background is \emph{Ricci flat}.
+This is explained in greater detail in Appendix \ref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent.
+Our reasons are the following:
 
@@
 	\item While the conformal invariance of the string worldsheet implies that the background is Ricci flat, this, in itself, is not very surprising.
-After all conformal invariance of worldsheet is equivalent to the statement of diffeomorphism invariance of the worldsheet, and in order for this to be consistent with the bulk geometry, the bulk geometry should also have a description in terms of diffeomorphism invariant physics.
-The simplest form of this requirement is that the background should satisfy the vacuum Einstein equations \todo{Does this make sense?
-Check!}.
+After all conformal invariance of worldsheet is equivalent to the statement of diffeomorphism invariance of the worldsheet, and in order for this to be consistent with the bulk geometry, the bulk geometry should also have a description in terms of a diffeomorphism invariant theory, the simplest example of which is Einstein gravity.
+However, this by itself is not sufficient to characterize string theory as being background independent.
+Neither do we have an understanding of how to quantize a string for which the bulk is arbitrarily curved to begin with.
+Nor does this tell us the microscopic mechanism of ``string condensation'' via which an arbitrary curved geometry is supposed to arise.
+
 	\item One can ask what is the quantum mechanical description of the bulk geometry?
@@
 
-Despite all the concerns string theory has emerged as the primary candidate for a theory of quantum gravity.
-There are good reasons for this.
-AdS/CFT - the most concrete version of a \emph{non-perturbative} theory of quantum gravity - arose out of string theory.
-AdS/CFT is also far from being a complete quantum theory of quantum gravity.
-Our universe, for instance, is described by a positive cosmological constant $\Lambda > 0$ rather than $\Lambda < 0$ as is implied by the ``Anti-deSitter'' part of the correspondence.
-However, the correspondence has passed numerous checks and is now considered part of the established canon.
+Despite all these concerns string theory has emerged as the primary candidate for a theory of quantum gravity.
+\emph{There are good reasons for this}.
+AdS/CFT - in our opinion, the most concrete example of a \emph{non-perturbative} theory of quantum gravity - arose out of string theory \cite{Maldacena1998The-Large,Witten1998Anti,Aharony1999Large,Gubser1998Gauge}.
+AdS/CFT is a particular realization of quantum gravity rather than a theory of quantum gravity per se.
+
+Anti-deSitter space describes a universe with a negative cosmological constant ($\Lambda < 0$) whereas the one we inhabit appears to have a small but positive cosmological constant ($\Lambda > 0$).
+Of course, nowhere in the literature of the AdS/CFT correspondence is it implied that it is the AdS bulk which corresponds to our physical universe.
+If anything our physical universe will turn out to live on the boundary of an anti-deSitter bulk.
+
+AdS spaces do arise in actual physical phenomena in \emph{our} universe \cite{Bardeen1999The-Extreme,Guica2009The-Kerr/CFT}.
+The correspondence itself has passed numerous checks and is now considered part of the established canon.
 Moreoever, it has led to numerous theoretical insights.
-We have gained a deep understanding of the properties of real world systems referred to as ``strange metals'' \todo{insert refs} by studying their dual gravitational theories.
-The significance of quantum error correction and quantum information for a theory of quantum gravity was also first most clearly illuminated via AdS/CFT \todo{insert refs}.
-For these, are other reasons too numerous to mention here, most theorists still regard string theory as the primary (or even the sole) candidate for a theory of quantum gravity.
-
-On the other hand LQG is also built upon a rigorous mathematical framework which follows the well-established rules of quantization\footnote{Though there are those who disagree with this assertion \todo[inline]{insert refs}}.
-Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
+We have gained a deep understanding of the properties of real world systems referred to as ``strange metals'' \cite{Hartnoll2016Holographic,Sachdev2010Strange,Sachdev2015Bekenstein-Hawking} by studying their dual gravitational theories.
+The significance of quantum error correction and quantum information for a theory of quantum gravity was also first most clearly illuminated via AdS/CFT \cite{Almheiri2014Bulk,Pastawski2015Holographic}.
+For these, and other reasons too numerous to mention here, many theorists still regard string theory as the primary (or even the sole) candidate for a theory of quantum gravity.
 
 Thus, we are now at an impasse.
-We have two theories, both built upon rigorous mathematical foundations, but which do not appear to be concordant with each other.
+We have two theories, both built upon strong mathematical foundations, but which do not appear to be in concordance with each other.
 There are two possibilities.
-The first is that one of the two approaches is fundamentally flawed in some way and must be rejected.
+The first is that one of the two approaches is fundamentally flawed in some way and must be rejected altogether.
 The second is that we are missing some crucial ingredient which would allow us to find a missing link between the two theories.
@@
 We now wish to understand how to construct a worldsheet action which will reflect this central dogma.
+
+The following is the outline of the paper.
+In \autoref{sec:modified-ng} we recall the Nambu-Goto action and suggest a simple modification which incorporates our central dogma, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $g = l_{pl}/l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $g \ll 1$.
+We point out that the lowest order correction to the NG action can be viewed as a form of bimetric gravity.
+In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity.
+We find both, the Nambu-Goto and the Polaykov forms of this action.
+Further we show that the phenomenological constant $\Delta$ introduce earlier can be viewed as the modulus of Kalb-Ramond field pulled back to the worldsheet.
+
+In \autoref{sec:inverse-metric-Polyakov} we construct the Polyakov version of the modified NG action, show that the equations of motion it yields are the same as those coming from the modified NG action.
+Further we solve the string equations of motion to find the fundamental modes and perform the quantization of the bosonic string in the usual manner.
+In \autoref{sec:quantum-kg-string} we ...
+
+In \autoref{sec:holographic-strings} we describe how to construct an action for the bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
+We discuss possible avenues for quantizing this action and further studying its implications for the relationship between string theory and LQG.
+
+There are various appendices containing details of calculations and background information.
+In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
+Appendix \ref{sec:relation-with-NG-case} shows how the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
 
@@
 
-\section{The Bimetric String}\label{app:bimetric-string}
+\section{The Bimetric String}\label{sec:bimetric-string}
 
@@
 
-\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}
+\section{The Quantum Klein-Gordon String} \label{sec:quantum-kg-string}
 
@@
 
-\section{Holography From Classical Strings}\label{sec:string-geometry}
+\section{Holography From Classical Strings}\label{sec:holographic-strings}
 
@@
 However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system.
-Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that to the Bosonic string.
-In this section we present a possible action in which the bulk geometry is encoded in the string action in terms of a connection living on the worldsheet.
-We will explore the natural consequences which follow from considering the symmetries of this action.
+Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that geometry to the geometry of the string worldsheet.
+In this section we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet, but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.
+We will explore the natural consequences which follow from considering the symmetries of such an action.
 
@@
 Even in an arbitrarily curved background, however, symmetry still plays a very important role.
-Even if we have discarded \textbf{global} symmetries, that still leaves us with \textbf{local} symmetries in the form of diffeomorphisms under which must the action must remain invariant.
+Even if we have discarded \emph{global} symmetries, that still leaves us with \emph{local} symmetries in the form of diffeomorphisms under which must the action must remain invariant.
 If, in addition, we have fields such as a gauge connection and an associated vielbein living in the background, then we also have to take local gauge transformations of these objects into account.
+
 However, diffeomorphisms and gauge transformations are not independent of each other.
@@
 In more pedestrian language, a diffeomorphism is an (invertible) change of co-ordinates on a manifold.
-
-Now, while we do not have definite proof of this statement
-
-The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}.
-If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $\mathrm{SO}(d,1)$ just takes one point in Minkowski to another point in Minkowski.
-The overall geometry is invariant under $\mathrm{SO}(d,1)$.
-Now, consider the case when the background geometry is not flat.
-Immediately you can see that the $X$'s can no longer be treated as elements of a $\mathrm{SO}(d,1)$ vector under \textbf{global} Lorentz transformations.
+A gauge transformation is a redefinition of the local fields which live on the underlying manifold.
+In fact, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' co-ordinate transformations and gauge representing ``active'' co-ordinate transformations.
+Therefore, given any spacetime the only question is \emph{which} gauge group is required to capture the full information about diffeomorphisms of that spacetime.
 
@@
 Let us remind ourselves what we're trying to do here.
-We want a gauge field, which lives on the background geometry and which encodes the background geometry, to somehow make an appearance in the action of a Bosonic string.
+We want a gauge field, which lives on the background geometry and which encodes the background geometry, to somehow make an appearance in the action of a bosonic string.
 There is an obvious connection $\mc{A}_a^{IJ}$ living on the worldsheet which is the pullback from $M$ to $\Sigma$ of the connection $A_{\mu}^{IJ}$.
@@
 \appendix
+
+\section{Strings in Background Fields and Emergent Gravity}\label{sec:strings-gravity}
+
+Let us begin by recalling the Polyakov action for the bosonic string.
+\begin{equation}\label{eqn:polyakov-action}
+	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
+\end{equation}
+Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.
+
+Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
+Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
+
+The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$.
+Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background.
+It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds.
+The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
+\begin{equation}\label{eqn:polyakov-gravity}
+	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
+\end{equation}
+where the bulk metric is now a function of the bulk co-ordinates $G_{\mu\nu}(X)$.
+Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$.
+However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string.
+One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.
+
+Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), that the garviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry.
+The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
+\begin{equation}\label{eqn:ricci-flat}
+	\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
+\end{equation}
+Therefore we find that conformal invariance of the string worldsheet \emph{implies} that the background geometry in which the string propagates satisfies the \emph{vacuum} Einstein equations.
+It is this result which is often cited as evidence for the claim that string theory is a \emph{background independent} theory of quantum gravity.
 

### 2024-06-21 lqg-strings.tex
Added acknowledgments

@@
 \begin{acknowledgments}
-
+DV would like to thank Thomas van Riet for going over an early draft of this work and for his valuable comments.
+DV and LdS would both like to thank David Schmitt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb-Ramond field.
+Finally we would like to humbly dedicate this work to the memory of the victims of the genocide in Gaza.
 \end{acknowledgments}

### 2024-06-21 lqg-strings.tex
moved emergent dimensions section into main text, made changes where approppriate and added a missing word in the introduction

--- 2024-06-21 lqg-strings.tex
@@
 Central to this approach was the ADM (Arnowitt-Deser-Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein-Hilbert action $S_{EH}$.
-The resulting phase is co-ordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of a the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following.
+The resulting phase space is co-ordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of a the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following.
 Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}.
@@
 revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \cite{Balthazar-t-backgrounds}.
-We'll come back to this in \autoref{sec:discussion}.
+We'll come back to this in \autoref{sec:emergent-dimensions}.
 
@@
 Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we got similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
+
+\section{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}
+
+There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi-emergent} model, with the action being
+\begin{multline} \label{eqn:emergent-dimensions-action}
+	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
+\end{multline}
+where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
+\gg m_{d}$.
+This is Afshordi's model \cite{Afshordi-emergent}.
+Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
+\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
+	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
+\end{equation}
+so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
+\begin{equation} \label{eqn:X-masses-constraint}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
+\end{equation}
+where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
+
+Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
+
+By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
+\begin{equation} \label{eqn:emergent-dimensions-g}
+	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+with $f$ given by
+\begin{equation} \label{eqn:emergent-dimensions-f}
+	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
+\end{equation}
+from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier.
+By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.
+
+One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
+\begin{multline} \label{eqn:emergent-dimensions-curved}
+	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
+	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
+\end{multline}
+where the mass parameters will be constrained as in
+\begin{equation} \label{eqn:X-masses-constraint-2}
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
+\end{equation}
+since those are the ones that show up in the $X^{\mu}$ equations of motion
+\begin{multline}
+	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
+	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
+\end{multline}
+
+In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
+We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
+\begin{equation} \label{eqn:mu0-phi-relation}
+	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
+\end{equation}
+where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
 
@@
 
-In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors.
-Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to?
-Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+In section \ref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being invariant under rigid rotations of the string.
+Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to?
+Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
 \begin{equation} \label{eqn:connection-string-vector-excitation}
@@
 
-\subsection{Emergent Dimensions and LQG} \label{sec:emergent-dimensions}
-
-There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi-emergent} model, with the action being
-\begin{multline} \label{eqn:emergent-dimensions-action}
-	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
-	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
-\end{multline}
-where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
-\gg m_{d}$.
-This is Afshordi's model \cite{Afshordi-emergent}.
-Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
-\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
-	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
-\end{equation}
-so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
-\begin{equation} \label{eqn:X-masses-constraint}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
-\end{equation}
-where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
-
-Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
-We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
-
-By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
-\begin{equation} \label{eqn:emergent-dimensions-g}
-	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
-\end{equation}
-with $f$ given by
-\begin{equation} \label{eqn:emergent-dimensions-f}
-	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
-\end{equation}
-from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier.
-By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.
-
-One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
-\begin{multline} \label{eqn:emergent-dimensions-curved}
-	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
-	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
-\end{multline}
-where the mass parameters will be constrained as in
-\begin{equation} \label{eqn:X-masses-constraint-2}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
-\end{equation}
-since those are the ones that show up in the $X^{\mu}$ equations of motion
-\begin{multline}
-	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
-	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
-\end{multline}
-
-In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
-We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
-\begin{equation} \label{eqn:mu0-phi-relation}
-	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
-\end{equation}
-where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
-
 \begin{acknowledgments}
-
+	DV would like to thank Thomas van Riet for going over an early draft of this work and for his valuable comments.
+DV and LdS would both like to thank David Schmidtt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb-Ramond field.
+Finally, we would like to humbly dedicate this work to the memory of the victims of the genocide in Gaza.
 \end{acknowledgments}

### 2024-06-22 lqg-strings.tex
made some changes in the introduction and wrote the paragraphs about inver metric Polyakov, quantum KG string and emergent dimensions

@@
 Central to this approach was the ADM (Arnowitt-Deser-Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein-Hilbert action $S_{EH}$.
-The resulting phase space is co-ordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of a the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following.
+The resulting phase space is coordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following.
 Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}.
@@
 \end{equation}
-While this procedure is straightforward in principle, in practice is was impossible to implement in the quantum theory due to highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
-This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a theory of a Minkowski tetrad $E^I_\mu$ and a self-dual $\sltwoc$ connection $A_\mu^{IJ}$.
-Ashtekar realised that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables.
-It was quickly realised by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory \cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states \cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.
+While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
+This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a theory of a densitized Minkowski tetrad
+\begin{equation} \label{eqn:densitized-tetrad}
+	\widetilde{E}^{\mu} _I = \frac{1}{\sqrt{- g}} e^{\mu} _I
+\end{equation}
+and the self-dual part of the $\sltwoc$ spin-connection
+\begin{equation} \label{eqn:self-dual-spin-connection}
+	A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{i}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu} .
+\end{equation}
+Ashtekar realized that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables.
+It was quickly realized by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory \cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states \cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.
 
 Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two dimensional surfaces and volumes of three dimensional regions.
-Moreover, these operators could be diagonlized exactly in the spin-network basis and a lower bound on the smallest possible quantum of area and quantum of volume could be derived.
+Moreover, these operators could be diagonlized exactly in the spin-network basis and a discrete spectrum for quantum of area and quantum of volume could be derived.
 This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity.
-One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4 $ for the Bekenstein-Hawking entropy.
+One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.
 
@@
 On the face of it, string theory, at least in its conventional form, does not satisfy this principle.
-The great virtue of LQG on the other hand, is that it respects background independence as a sacred principle and proceeds to quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.
+The great virtue of LQG on the other hand, is that it respects background independence by construction and proceeds to quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.
 
@@
 Before proceeding let us state our ``central dogma''.
-We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators - such as those which measure the area and volume of a given region of space - exist, have discrete spectra and are gapped, \ie, the smallest eigenvalue is greater than zero.
-We now wish to understand how to construct a worldsheet action which will reflect this central dogma.
+We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators - such as those that measure the area and volume of a given region of space - exist and have discrete spectra, thus the transition from no area/volume to some area/volume is a discrete jump rather than a continuous one.
+We now wish to understand how to construct a worldsheet action which reflects this central dogma.
 
 The following is the outline of the paper.
-In \autoref{sec:modified-ng} we recall the Nambu-Goto action and suggest a simple modification which incorporates our central dogma, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $g = l_{pl}/l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $g \ll 1$.
-We point out that the lowest order correction to the NG action can be viewed as a form of bimetric gravity.
+In \autoref{sec:modified-ng} we recall the Nambu-Goto action and suggest a simple modification which incorporates our central dogma, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
+We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.
 In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity.
 We find both, the Nambu-Goto and the Polaykov forms of this action.
-Further we show that the phenomenological constant $\Delta$ introduce earlier can be viewed as the modulus of Kalb-Ramond field pulled back to the worldsheet.
-
-In \autoref{sec:inverse-metric-Polyakov} we construct the Polyakov version of the modified NG action, show that the equations of motion it yields are the same as those coming from the modified NG action.
-Further we solve the string equations of motion to find the fundamental modes and perform the quantization of the bosonic string in the usual manner.
-In \autoref{sec:quantum-kg-string} we ...
+Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.
+
+In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified NG action derived from the bimetric analysis and point out its consequences for the equations of motion.
+Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
+In \autoref{sec:quantum-kg-string} we follow the route of canonical covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.
+
+In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi-emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
+We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
 
 In \autoref{sec:holographic-strings} we describe how to construct an action for the bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
-We discuss possible avenues for quantizing this action and further studying its implications for the relationship between string theory and LQG.
+We discuss possible avenues for quantizing this action and further study its implications for the relationship between string theory and LQG.
 
@@
 In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
-Appendix \ref{sec:relation-with-NG-case} shows how the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
+Appendix \ref{sec:relation-with-NG-case} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
 

### 2024-06-22 lqg-strings.tex
made some changes to section II

@@
 \begin{equation*}
-	\sqrt{- h} \rightarrow \sqrt{- (h + g \Delta)}.
+	\sqrt{- h} \rightarrow \sqrt{- (h + k \Delta)}.
 \end{equation*}
-Here, $g = l_{pl}/l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of some worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the spin foam pierces the WS.
-In the limit that $l_s \gg l_{pl}$, $g \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
+Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of some worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the spin foam pierces the WS.
+In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
 In this limit we can expand the integrand as follows:
 \begin{equation} \label{eqn:inverse-metric-correction}
-	\sqrt{- (h + g \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{g \Delta}{(- h)} + \mc{O}(g^2/h^2)\right).
-\end{equation}
-Presumably the limit $g \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
-Thus in this limit $ g^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections.
+	\sqrt{- (h + g \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
+\end{equation}
+Presumably the limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
+Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections.
 The final area corrected Nambu-Goto action becomes:
 \begin{equation} \label{eqn:modified-NG-action}
-	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} \frac{g \Delta}{\sqrt{- h}} \right).
+	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} \frac{k \Delta}{\sqrt{- h}} \right).
 \end{equation}
@@
 \begin{equation} \label{eqn:modified-NG-action-v2}
-	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {g \Delta}{\sqrt{- (h^{-1})}} \right),
+	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {k \Delta}{\sqrt{- (h^{-1})}} \right),
 \end{equation}
@@
 As such, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
-If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $g \Delta/2$ is mapped to $2/(g\Delta)$:
+If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $k \Delta / 2$ is mapped to $2 / (k \Delta)$:
 \begin{align} \label{eqn:modified-NG-action-v3}
-	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{g \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
-	                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {g' \Delta'}\sqrt{- (h')^{-1}} \right),
-\end{align}
-which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as make the replacements $T \rightarrow T' = \frac{1}{2} g T $, $ \frac{1}{2} {g \Delta} \rarrow \frac{1}{2} {g' \Delta'} = \frac{2} {g \Delta}$ and $\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x$ (or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
-This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($g' \gg 1$) and weak coupling ($g \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
-
-Now, one might object and say that having an action which is the sum of Nambu-Goto actions for two different metrics seems strange.
-However, such actions have been extensively studied under the heading of ``bimetric gravity'', with the earliest work dating as far back as 1940 in two papers \cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER').
+	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{k \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
+	                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {k' \Delta'}\sqrt{- (h')^{-1}} \right),
+\end{align}
+which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as we make the replacements
+\begin{subequations}
+	\begin{equation} \label{eqn:T'}
+		T \rightarrow T' = \frac{1}{2} k T
+	\end{equation}
+	\begin{equation} \label{eqn:k-Delta}
+		\frac{1}{2} {k \Delta} \rarrow \frac{1}{2} {k' \Delta'} = \frac{2} {k \Delta}
+	\end{equation}
+	\begin{equation} \label{eqn:d2x}
+		\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x
+	\end{equation}
+\end{subequations}
+(or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
+
+Now, one might object and say that having an action which is the sum of two Nambu-Goto actions seems strange.
+However, similar actions have been extensively studied under the heading of ``bimetric gravity'', with the earliest work dating as far back as 1940 in two papers \cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER').
 In 2010, bimetric gravity gained great popularity due to the seminal paper \cite{de-Rham2011Resummation} which showed that by introducing a second \emph{reference} metric into a model for massive gravity one can get rid of the Boulware-Deser ghost \cite{Boulware1972Can-Gravitation} which otherwise plagues theories with massive gravitons.

### 2024-06-22 lqg-strings.tex
made some changes in section III

@@
 	\begin{equation} \label{eqn:T'}
-		T \rightarrow T' = \frac{1}{2} k T
+		T \rightarrow T' = - \frac{1}{2} k T
 	\end{equation}
@@
 
-Consider a string propagating in a target space whose geometry is described by two bulk metrics.
 There are two ways that a string with two metrics might arise.
@@
 
-In the following, we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified as being the determinant of (a tensor proportional to) the antisymmetric tensor $\widetilde{\varepsilon}_{a c}$ living on the worldsheet.
-The worldsheet antisymmetric tensor can itself be understood as arising from the pullback of a bulk antisymmetric tensor.
-Now, in string theory, there is already a very important antisymmetric bulk tensor called the Kalb-Ramond field.
+In the following, we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified as being the determinant of (a tensor proportional to) the antisymmetric symbol $\varepsilon _{a c}$ living on the worldsheet.
+The worldsheet antisymmetric symbol can itself be understood as arising from the pullback of a bulk antisymmetric tensor.
+Now, in string theory, there is already a very important antisymmetric background tensor: the Kalb-Ramond field.
 
@@
 \end{equation}
-This implies that
+By writing the inverse metric $g^{a b}$ in terms of Levi-Civita symbols $g^{a b} = \varepsilon ^{a c} \varepsilon ^{b d} g_{c d} / 2 g$, this implies that
 \begin{multline} \label{eqn:SgS-implication}
-	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
+	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
 	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
 \end{multline}
-which can be achieved if
+which can be achieved if the expression in parenthesis vanishes. For this end, the most natural possibility is
 \begin{equation} \label{eqn:S=sigma_y}
-	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
-\end{equation}
-and if the background metrics are related by
+	\Delta _{a c} = \sqrt{\Delta} \varepsilon _{a c}
+\end{equation}
+since we must have that $\det (\Delta _{a b}) = \Delta$ and $\Delta _{a c} \varepsilon ^{c c'} \sim \delta ^{c'} _{a}$, and also if the background metrics are related by
 \begin{equation} \label{eqn:H=1/(2g)G}
@@
 \end{equation}
-just like the regular ST literature.
+just like the regular ST literature, thus the constraints are unchanged by our correction.
 

### 2024-06-22 lqg-strings.tex
made some changes to section IV

@@
 \usepackage{parskip}
-% \setlength{\parindent}{15pt}
+\setlength{\parindent}{15pt}
 
@@
 \end{equation}
-from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
+from which we can use the freedom in the conformal factor to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
 \begin{equation} \label{eqn:derivatives-F-minus}
@@
 \end{equation}
-At first glance, it seems problematic that we have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$.
+It may seem problematic to have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$.
 With this choice, we thus turned eq (\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
@@
 \end{equation}
-can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as in
+can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as
 \begin{multline} \label{eqn:mu-constraint-final}
@@
 
-From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}.
-The constraints are nothing new, they're precisely the same as the ones of regular String Theory.
-What's new in our analysis is the $\mu ^2$ term, which we will assume to be constant for a first analysis, making it so the solution is given by Fourier transform
+From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq \eqref{eqn:inverse-area-em-tensor}.
+The constraints are nothing new, they're the same as the ones of regular String Theory.
+What's new in our analysis is the $\mu ^2$ term, which we take as being constant for a first analysis, making it so the solution is given by Fourier transform
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
@@
 
-Looking closer at our Virasoro-like \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
+Looking closer at our constraints \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
 \begin{multline} \label{eqn:string-rest-mass-classical-1}
@@
 to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$.
-After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
+After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the expected
 \begin{subequations}
@@
 \begin{equation} \label{eqn:harmonic-bracket-relations}
-	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
+	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|n| , |p|} \eta ^{\mu \nu} .
 \end{equation}
@@
 
-Having the bracket relations between the vibrational modes of the string, we can now calculate the constraint algebra, which we shall refer to as the Virasoro-Klein-Gordon Algebra.
+Having the bracket relations between the vibrational modes of the string, we can now calculate the constraints algebra, which we shall refer to as the Virasoro-Klein-Gordon Algebra.
 For simplicity, since $E_{n} = \sqrt{n^2 + \mu ^2} > 0$, we shall work with the normalized harmonic oscillator modes $a^{\mu} _{n}$ instead of the expansion modes $\alpha ^{\mu} _{n}$.
-The algebra is given by
+Then, the algebra in terms of said normalized modes is given by
 \begin{subequations}

### 2024-06-22 lqg-strings.tex
made changes in section V and added a table with values for the normal-ordering constant

@@
 \end{subequations}
-in position representation and
+in position representation $\ket{0 ; x} \equiv \ket{0} \otimes \psi (x)$ and
 \begin{subequations}
@@
 \end{subequations}
-in momentum representation.
+in momentum representation $\ket{0 ; p} \equiv \ket{0} \otimes \psi (p)$.
 
@@
 
-When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
+When translating the constraints as quantum operators, we impose them strongly, requiring that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$ since said constraints are not self-adjoint:
 \begin{subequations}
@@
 \end{equation}
-for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
+for some constant $a$.
+Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by this constant
 \begin{multline} \label{eqn:shifted-mass-spectrum}
@@
 	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
-	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} .
-\end{multline}
+	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} ,
+\end{multline}
+which is easily computable given a value for $\mu$. Below we provide a table with the value of $a$ for different spacetime dimensionalities $D$ and mass parameters $\mu$.
+\begin{table}[h] \label{tab:normal-ordering-constant}
+	\begin{tabular}{|l|l|l|l|l|l|}
+		\hline
+		        & $\mu = 1$ & $\mu = 2$ & $\mu = 3$ & $\mu = 4$ & $\mu = 5$ \\ \hline
+		$D = 2$ & $-4.24$   & $-5.37$   & $-6.96$   & $-8.73$   & $-10.59$  \\ \hline
+		$D = 3$ & $-18.44$  & $-20.78$  & $-24.58$  & $-29.20$  & $-34.27$  \\ \hline
+		$D = 4$ & $-48.62$  & $-52.11$  & $-58.23$  & $-66.13$  & $-75.19$  \\ \hline
+		$D = 5$ & $-100.79$ & $-105.39$ & $-113.79$ & $-125.09$ & $-138.49$ \\ \hline
+		$D = 6$ & $-180.96$ & $-186.63$ & $-197.25$ & $-211.95$ & $-229.84$ \\ \hline
+	\end{tabular}
+	\caption{values of $a$ for different spacetime dimensionalities and mass parameters. Visibly, the dependence in $D$ is much stronger than the dependence in $\mu$.}
+\end{table}
 
@@
 Next, by calculating the vacuum expectation value (VEV) of the commutator \eqref{eqn:L-commutator-2} with $|m| \neq |k|$ and $n = p = 1$, we find that $F_{1} = 0$, thus both sequences $C_{n} = D_{n} = 0$ vanish and we conclude that the quantum version of our algebra \emph{has no anomalies}.
-This is a relevant result, since it could mean our model doesn't need a specific number of dimensions to work, which will be explored again later in section \ref{sec:discussion}.
+This is a relevant result, since it could mean our model doesn't need a specific number of dimensions to work, which will be explored again later in section \ref{sec:emergent-dimensions}.
 

### 2024-06-22 lqg-strings.tex
made changes to section VI

@@
 \end{multline}
-while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ implies that
+while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that
 \begin{equation} \label{eqn:zeta-p-psi}
@@
 
-Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
-We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
+Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
+$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais:2013sdr},\cite{Witten:1988hc},\cite{Carlip:1998uc}).
+We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
 
@@
 In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$.
-We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
+We now explore this claim: since we could be dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a \emph{worldsheet dilaton}, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
 \begin{equation} \label{eqn:mu0-phi-relation}

### 2024-06-22 lqg-strings.tex
moved the section about the explicit expression for Delta field to main text, made the approppriate changes and changed some stuff in said section

@@
 
-In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified NG action derived from the bimetric analysis and point out its consequences for the equations of motion.
+In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion.
+We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field.
 Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
@@
 We'll come back to this in \autoref{sec:emergent-dimensions}.
+
+\subsection{Worldsheet Kalb-Ramond field and Quantum of Area} \label{sec:WS-Kalb-Ramond-QoA}
+
+If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
+This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
+The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
+\begin{multline} \label{eqn:area-corrected-K-R-action}
+	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
+	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
+\end{multline}
+where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
+\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
+	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
+	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
+\end{multline}
+By varying this action \wrt $\Delta ^{c d}$ we get
+\begin{equation} \label{eqn:Delta-pullback}
+	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
+\end{equation}
+with $\widetilde{f}$ given by
+\begin{multline} \label{eqn:1/f-tilde}
+	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
+\end{multline}
+where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
+\begin{equation} \label{eqn:f-tilde}
+	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
+\end{equation}
+from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
+\begin{equation} \label{eqn:WS-b-field}
+	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b} ,
+\end{equation}
+or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
+\begin{equation} \label{eqn:Delta-b-relation}
+	\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
+\end{equation}
+We thus see that the pullback of the Kalb-Ramond field is actually a tensor \emph{density} of weight $- 1$, since the coefficient in eq \eqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.
 
@@
 
-\subsection{Worldsheet Kalb-Ramond field and Quantum of Area} \label{sec:WS-Kalb-Ramond-QoA}
-
-If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov}, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
-This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
-The more complete picture would be thus to consider the string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
-\begin{multline} \label{eqn:area-corrected-K-R-action}
-	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
-	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \widetilde{\varepsilon}^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
-\end{multline}
-where we can rewrite $\widetilde{\varepsilon}^{a b}$ in terms of $\Delta ^{a b}$ as
-\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
-	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
-	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
-	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
-\end{multline}
-By varying this action \wrt $\Delta ^{c d}$ we get
-\begin{equation} \label{}
-	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
-\end{equation}
-with $\widetilde{f}$ given by
-\begin{multline} \label{eqn:1/f-tilde}
-	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
-	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
-\end{multline}
-where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
-\begin{equation} \label{eqn:f-tilde}
-	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
-\end{equation}
-from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
-\begin{equation} \label{eqn:WS-b-field}
-	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \widetilde{\varepsilon}_{a b} ,
-\end{equation}
-or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
-\begin{equation} \label{eqn:Delta-b-relation}
-	\Delta _{a b} = \sqrt{\Delta} \widetilde{\varepsilon}_{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
-\end{equation}
-
 \begin{acknowledgments}

### 2024-06-22 lqg-strings.tex
Fixed one reference, other minor changes.

@@
 
-In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi-emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
+In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
 We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
@@
 
-There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi-emergent} model, with the action being
+There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi2014emergent} model, with the action being
 \begin{multline} \label{eqn:emergent-dimensions-action}
@@
 \gg m_{d}$.
-This is Afshordi's model \cite{Afshordi-emergent}.
+This is Afshordi's model \cite{Afshordi2014emergent}.
 Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
@@
 The string action is required to be invariant under both of these:
-\begin{align*}
+\begin{subequations}\label{eqn:poincare-symmetries}
+	\begin{align}
 		X^\mu & \rarrow X^\mu + \delta X^\mu; \quad \delta X^\mu \in \mbb{R}^{3,1} \\
 		X^\mu & \rarrow \Lambda^\mu{}_\nu X^\mu; \quad \Lambda^\mu{}_\nu \in \mathrm{SO}(3,1)
-\end{align*}
+	\end{align}
+\end{subequations}
 where $\delta X^\mu$ is some arbitrary vector in Minkowski space.
@@
 Even in an arbitrarily curved background, however, symmetry still plays a very important role.
-Even if we have discarded \emph{global} symmetries, that still leaves us with \emph{local} symmetries in the form of diffeomorphisms under which must the action must remain invariant.
+Even if we have discarded \emph{global} symmetries, that still leaves us with \emph{local} symmetries in the form of diffeomorphisms under which the action must remain invariant.
 If, in addition, we have fields such as a gauge connection and an associated vielbein living in the background, then we also have to take local gauge transformations of these objects into account.
@@
 A gauge transformation is a redefinition of the local fields which live on the underlying manifold.
-In fact, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' co-ordinate transformations and gauge representing ``active'' co-ordinate transformations.
-Therefore, given any spacetime the only question is \emph{which} gauge group is required to capture the full information about diffeomorphisms of that spacetime.
+In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' co-ordinate transformations and gauge representing ``active'' co-ordinate transformations.
+
+We will assume henceforth that the Poincaré group is the gauge group which must be promoted from being a \emph{global} symmetry to being a \emph{local} symmetry of the background spacetime.
 

### 2024-06-22 lqg-strings.tex
added section in discussions about the equivalence of area corrected NG action with BI model. Going to sleep now, tomorrow I'll check your part

@@
 What we would like to do is to modify the string action in a way which incorporates the insight from LQG that at the Planck scale there is a minimum quantum of area.
-One simple way in which to do this is to modify the integrand in \eqref{eqn:ng-action} as follows:
-\begin{equation*}
-	\sqrt{- h} \rightarrow \sqrt{- (h + k \Delta)}.
-\end{equation*}
+One simple way in which to do this is to modify the action \eqref{eqn:ng-action} as follows:
+\begin{equation} \label{eqn:NG-area-corrected}
+	S_{M N G} = - T \int \diff ^2 x \sqrt{- (h + k \Delta)}.
+\end{equation}
 Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of some worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the spin foam pierces the WS.
@@
 \begin{equation} \label{eqn:inverse-metric-correction}
-	\sqrt{- (h + g \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
+	\sqrt{- (h + k \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
 \end{equation}
 Presumably the limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
-Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections.
+Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(k^2/h^2)$ corrections.
 The final area corrected Nambu-Goto action becomes:
@@
 
+\subsection{Is the Area-Corrected Nambu-Goto Action a Born-Infeld Model?} \label{sec:area-corrected-BI}
+
+The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model
+\begin{equation} \label{eqn:BI-action}
+	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
+\end{equation}
+with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string.
+Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
+\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
+	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
+\end{equation}
+thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
+Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
+Also, we have a direct relation between string tension and scale
+\begin{equation} \label{eqn:k-T}
+	\frac{l_p}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
+\end{equation}
+
 \begin{acknowledgments}
 	DV would like to thank Thomas van Riet for going over an early draft of this work and for his valuable comments.
-DV and LdS would both like to thank David Schmidtt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb-Ramond field.
+DV and LdS would both like to thank David Schmidtt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb-Ramond field, and also the equivalence of the area corrected action with a Born-Infeld model in the worldsheet.
 Finally, we would like to humbly dedicate this work to the memory of the victims of the genocide in Gaza.

### 2024-06-22 lqg-strings.tex
Added refs, edited/added to holographic string section.

@@
 
-The first of these is \emph{string theory}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
+The first of these is \emph{string theory} \cite{Polchinski1998String,Polchinski2007String}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces and their interactions, including gravity.
 However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.
 
-The second approach is called \emph{loop quantum gravity} or ``LQG'' for short.
+The second approach is called \emph{loop quantum gravity} or ``LQG'' for short \cite{Rovelli1998Loop,Rovelli2015Covariant}.
 LQG is ostensibly meant to be a theory of ``pure quantum gravity'', that is gravity without any matter.
@@
 So, for instance, the connection which describes the geometry around a Kerr black hole also encodes how the local tetrad frame rotates as one moves around the axisymmetric axis of the black hole.
-All of these considerations lead us to the premise that if one wishes to describes the bulk geometry in terms of connection variables, then it is only natural to describe the worldsheet geometry in terms of connection variables and to use the tools that come along with having a gauge connection to understand how the worldsheet geometry can couple to the bulk geometry.
+All of these considerations lead us to the premise that \emph{if one wishes to describes the bulk geometry in terms of connection variables, then it is only natural to describe the worldsheet geometry in terms of connection variables} and to use the tools that come along with having a gauge connection to understand how the worldsheet geometry can couple to the bulk geometry.
 
@@
 where $\delta X^\mu$ is some arbitrary vector in Minkowski space.
-The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $\mbb{P}^{3,1}$, the Poincaré group in $3+1$ dimensions.
+The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $ISO^{3,1}$, the Poincaré group in $3+1$ dimensions.
 Of course, these are good symmetries only if our background is flat.
@@
 Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
-When we travel along some path $\mc{C} \subset M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in \mathrm{SO}(d,1)$.
+
+% When we travel along some path $\mc{C} \subset M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in SO(d,1)$.
 This group element arises from taking the holonomy of a $\mf{so}(d,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.
 
-Let us remind ourselves what we're trying to do here.
+% Let us remind ourselves what we're trying to do here.
 We want a gauge field, which lives on the background geometry and which encodes the background geometry, to somehow make an appearance in the action of a bosonic string.
@@
 
-The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\tau , \sigma)$ living on the worldsheet $\Sigma$.
+% The end result is that we now have a gauge field $\mc{A}_a^{IJ}(\tau , \sigma)$ living on the worldsheet $\Sigma$.
 Here the lower index $a$ is the worldsheet index and $I , J$ labels the generators of the Lie algebra $\mf{so}(d,1)$.
@@
 The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:
-
-\begin{equation}\label{eqn:covariant-deriv-v2}
-	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
-\end{equation}
-where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$.
+% \begin{equation}\label{eqn:covariant-deriv-v2}
+% 	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
+% \end{equation}
+% where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$.
 We should therefore think of the embedding fields as $d+1$ dimensional vectors living in the fundamental representation of $\mathrm{SO}(d,1)$.
@@
 
-\subsection{The Einstein-Cartan String}\label{sec:cartan-string}
-
-The careful reader will have noticed that there is a serious difficulty in the above argument.
+There is a difficulty in the above argument.
 The bulk geometry is $d+1$ dimensional, therefore there are $d+1$ embedding fields.
-We have taken these fields $X^\mu$ and cast them as
-components of a $SO(d,1)$ vector.
+We have taken these fields $X^\mu$ and cast them as components of a $\mf{so}(d,1)$ vector.
 Let us pick an arbitrary point $P_0$ on the bulk manifold and call it the ``origin''.
 At $P_0$ the co-ordinates are all zero $\vec X_0 = (0,0,\ldots,0)$.
-If we start acting with infinitesimal $SO(d,1)$ transformations on $\vec X_0$, the resulting surface will correspond to a ``constant energy'' hyperboloid in the bulk.
+If we start acting with infinitesimal $\mf{iso}(d,1)$ transformations on $\vec X_0$, the resulting surface will correspond to a ``constant energy'' hyperboloid in the bulk.
 This is because $SO(d,1)$ contains only boosts and rotations.
@@
 This is where we run into a problem.
-There is no way to express translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$.
+There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$.
 In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold.
@@
 
-There is a very generic way in which one can introduce translations in the form of matrix valued transformations acting on vector (or one-form) objects [ref wikipedia].
-For instance if we have a vector $\vec{x} = (x,y)$, rotations are given by $2 \times 2$ matrices.
+If one wants to treat the $X$'s as elements of a vector which transforms under both translations and rotations as in \eqref{eqn:poincare-symmetries}, we must extend the number of spacetime dimensions by one, introducing an ``auxiliary'' dimension whose value is initially set to be $X^r = 1$.
+Thus we have:
+\begin{equation}
+	\begin{pmatrix}
+		X^\mu \\
+		1
+	\end{pmatrix} \rarrow \begin{pmatrix}
+							X'^\mu \\
+							1
+						  \end{pmatrix} = \begin{pmatrix}
+											\Lambda^\mu{}_\mu & \delta X^\mu \\
+											0  & 1
+						  				  \end{pmatrix} \begin{pmatrix}
+											X^\mu \\
+											1
+										  \end{pmatrix}
+\end{equation}
+Now, one might be inclined to treat the new co-ordinate $X^r$ as purely an auxiliary variable which will not affect the physics.
+However, if we stare at the expression $X^r = 1$ for a moment, we will realise that this expression is the same form as the Dirichlet boundary condition for the end-points of a string.
+And, from what we know about strings with Dirichlet boundary conditions is that the constraint surface on which the end-points live will end up behaving like a dynamical object or ``D-brane'' \cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background}.
+In our case we now have a new enlarged bulk $\mb{M}$ with $d+1$ space dimensions - treating the auxiliary variable as a co-ordinate which can vary - and one time dimensions, or $d+2$ dimensions in total.
+If we fix $X^r = 1$, that leaves us with a $d+1$ submanifold $\mb{\Gamma} \in \mb{M}$ on which the string end-point is free to move.
+
+However, in our case, the condition $X^r = 1$ is much stronger than the Dirichlet boundary condition, because it applies not only to the end-points of the string, but to every point of the worldsheet.
+In other words, the \emph{entire} string worldsheet is confined to move only along the $d+1$ dimensional submanifold $\mb{\Gamma}$.
+Now, one can ask what should the form of the action for a string moving in this enlarged bulk look like?
+Well, it will be of the same form \eqref{eqn:polyakov-gauged}, only now the worldsheet connection is an $\mf{iso}(d,1)$ valued one-form, with the embedding fields the enlarged $d+2$ dimensional set.
+
+% instance if we have a vector $\vec{x} = (x,y)$, rotations are given by $2 \times 2$ matrices.
 Now we add a dummy $'r'$ co-ordinate to our vector and set it equal to one, so our new vector is of the form: $\vec{X} = (x,y,r=1)$.
@@
 One such matrix has the form:
-\begin{equation}
-	\mb{R} = \begin{pmatrix}
-		a & b & t_x \\
-		c & d & t_y \\
-		0 & 0 & 1
-	\end{pmatrix}.
-\end{equation}
-Here the left upper diagonal $2\times 2$ block corresponds to the usual 2d rotations, while the new off-diagonal elements $(t_x, t_y)$ parametrize the amount we wish to displace our original vector $(x,y)$.
+% \begin{equation}
+% 	\mb{R} = \begin{pmatrix}
+% 		a & b & t_x \\
+% 		c & d & t_y \\
+% 		0 & 0 & 1
+% 	\end{pmatrix}.
+% \end{equation}
+% Here the left upper diagonal $2\times 2$ block corresponds to the usual 2d rotations, while the new off-diagonal elements $(t_x, t_y)$ parametrize the amount we wish to displace our original vector $(x,y)$.
 Under the action of $\mb{R}$ (with the rotation component fixed to be identity), our vector becomes:
-\begin{equation}\label{eqn:affine-transform}
-	\mb{R} \vec X = \begin{pmatrix}
-		x + t_x \\
-		y + t_y \\
-		1
-	\end{pmatrix}.
-\end{equation}
-One might point out that the matrix $\mb{R}$ is not symmetric, as one would require of an orthogonal transformation.
+% \begin{equation}\label{eqn:affine-transform}
+% 	\mb{R} \vec X = \begin{pmatrix}
+% 		x + t_x \\
+% 		y + t_y \\
+% 		1
+% 	\end{pmatrix}.
+% \end{equation}
+% One might point out that the matrix $\mb{R}$ is not symmetric, as one would require of an orthogonal transformation.
 If we make $\mb{R}$ symmetric, then under the above transformation the third (projective) component of the 3-vector will no longer be equal to one.
-\begin{equation}\label{eqn:affine-transform}
-	\mb{R} \vec X = \begin{pmatrix}
-		x + t_x \\
-		y + t_y \\
-		x t_x + y t_y + 1
-	\end{pmatrix}.
-\end{equation}
+% \begin{equation}\label{eqn:affine-transform}
+% 	\mb{R} \vec X = \begin{pmatrix}
+% 		x + t_x \\
+% 		y + t_y \\
+% 		x t_x + y t_y + 1
+% 	\end{pmatrix}.
+% \end{equation}
 

### 2024-06-22 lqg-strings.tex
Added Derek Wise reference, todolist, logical chain of thought leading to this picture.

@@
 Well, it will be of the same form \eqref{eqn:polyakov-gauged}, only now the worldsheet connection is an $\mf{iso}(d,1)$ valued one-form, with the embedding fields the enlarged $d+2$ dimensional set.
+
+\textbf{todo:}
+
+\begin{itemize}
+	\item Describe iso(d,1) connection decomposition into Lorentz piece and translation piece using \cite{Wise2010MacDowell-Mansouri} as reference.
+	\item Explain why deSitter, anti-deSitter and flat space are the only consistent solutions for the enlarged bulk geometry.
+	\item Recall once again the steps which led us here. 
+\end{itemize}
+
+\textbf{Steps which led us here}
+
+\begin{itemize}
+	\item We adopt the central result of LQG which is quantization of area
+	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
+	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
+	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
+	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
+	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
+\end{itemize}
 
@@
 
-\subsection{}\label{sec:}
-
-\section{Physical Implications}
-
 \section{Discussion} \label{sec:discussion}

### 2024-06-22 lqg-strings.tex
Added references for Born-Infeld model in string theory and fixed other references

@@
 
+\subsection{Area-Corrected Nambu-Goto Action and Born-Infeld Electrodynamics} \label{sec:area-corrected-BI}
+
+The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
+\begin{equation} \label{eqn:BI-action}
+	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
+\end{equation}
+with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string.
+Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
+\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
+	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
+\end{equation}
+thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
+Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
+Also, we have a direct relation between string tension and scale
+\begin{equation} \label{eqn:k-T}
+	\frac{l_p}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
+\end{equation}
+
 \subsection{Simplifying The Equations of Motion} \label{sec:solving-eoms-inverse-area}
@@
 We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
-$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais:2013sdr},\cite{Witten:1988hc},\cite{Carlip:1998uc}).
+$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Witten1998Anti},\cite{Carlip2003Quantum}).
 We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
@@
 
-\subsection{Is the Area-Corrected Nambu-Goto Action a Born-Infeld Model?} \label{sec:area-corrected-BI}
-
-The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model
-\begin{equation} \label{eqn:BI-action}
-	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
-\end{equation}
-with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string.
-Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
-\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
-	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
-\end{equation}
-thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
-Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
-Also, we have a direct relation between string tension and scale
-\begin{equation} \label{eqn:k-T}
-	\frac{l_p}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
-\end{equation}
-
 \begin{acknowledgments}

### 2024-06-23 lqg-strings.tex
made some changes in your section, your appendices and in the introduction

@@
 We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field.
-Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
-In \autoref{sec:quantum-kg-string} we follow the route of canonical covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.
+Furthermore, we explore an equivalence between our proposed model and the Born-Infeld model in $1 + 1$ dimensions.
+We conclude this section by solving the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
+In \autoref{sec:quantum-kg-string} we follow the route of covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.
 
@@
 \begin{equation} \label{eqn:k-T}
-	\frac{l_p}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
+	\frac{l_{pl}}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
 \end{equation}
@@
 We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
-$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Witten1998Anti},\cite{Carlip2003Quantum}).
+$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Carlip2003Quantum}).
 We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
@@
 
-Uptil now we have studied a phenomenological modification of the string action.
+Until now we have studied a phenomenological modification of the string action.
 However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system.
 Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that geometry to the geometry of the string worldsheet.
-In this section we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet, but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.
+In this section, we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.
 We will explore the natural consequences which follow from considering the symmetries of such an action.
@@
 \begin{equation}\label{eqn:covariant-deriv-v1}
-	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
-\end{equation}
-where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling.
+	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + k \mc{A}_{a}^\mu{}_\nu X^\nu,
+\end{equation}
+where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $k$ is the gauge coupling.
 A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming under the gauge group $\mc G$.
@@
 Our goal is to write down the action of a string propagating in a background geometry.
-One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet.
+One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry.
 However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones.
-An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $\tilde E_\mu^I \tilde E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat co-ordinates).
+An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates).
 This, however, leaves open the question of what role the bulk connection should play in this picture.
@@
 
-Therefore, now we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$.
+Therefore, now we will require that the bulk connection $\mc{A}_{\mu} ^{I J}$ and the bulk vielbein $E^{\mu} _{I}$ can be pulled back onto a connection $\mc{A}_{a}^{I J}$ and a dyad $e^a_I$, respectively, living on the string worldsheet $\Sigma$.
 $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet.
@@
 
-However, diffeomorphisms and gauge transformations are not independent of each other.
-A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which has a differentiable (and invertible) map.
-In more pedestrian language, a diffeomorphism is an (invertible) change of co-ordinates on a manifold.
+However, diffeomorphisms and gauge transformations are not distinct concepts.
+A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which is a differentiable (and invertible, with inverse also differentiable) map.
+In more pedestrian language, a diffeomorphism from $\mc{M}$ to itself is an (invertible) change of coordinates on a manifold $\mc{M}$.
 A gauge transformation is a redefinition of the local fields which live on the underlying manifold.
-In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' co-ordinate transformations and gauge representing ``active'' co-ordinate transformations.
+In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' coordinate transformations and gauge representing ``active'' coordinate transformations.
+From the viewpoint of the formalism of Principal Fiber Bundles, where the gauge symmetry arises from a structure that locally looks like a Cartesian product of the base manifold $\mc{M}$ and the gauge group $G$, $\mc{M} \times G$, gauge transformation arise from local reparameterizations of the group component at each point of the base manifold, so it is a diffeomorphism in the \textquotedblleft enlarged" space $\mc{M} \times G$.
 
@@
 
-Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
+Instead of viewing the fields $X^{\mu}$ as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
 
@@
 For instance, one can take the embedding manifold to be a two-dimensional sphere $S^2$.
-Then the co-ordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$.
+Then the coordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$.
 The action for this system would be:
@@
 This is where we run into a problem.
-There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$.
+There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix-valued group on a point living in $\mbb{R}^{d+1}$.
 In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold.
@@
 Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
-Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
+Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to the description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
 
@@
 \end{equation}
-where the bulk metric is now a function of the bulk co-ordinates $G_{\mu\nu}(X)$.
+where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$.
 Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$.
@@
 
-Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), that the garviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry.
+Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), the graviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry.
 The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
@@
 Let $(\tau,\sigma)$ be the location of a point on the worldsheet and $X^\mu(\tau, \sigma)$ be the location of that same point in terms of co-ordinates on $\mc M$.
-Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of the embedding fields and their derivatives:
+Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of derivatives of the embedding fields (the pullback):
 
 \begin{equation}\label{eqn:ws-metric}
-	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} g_{\mu\nu},
-\end{equation}
-where $g_{\mu\nu}$ is the metric in the ambient space $\mc M$.
-Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{\det(h)}$ and integrating over that patch:
+	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu},
+\end{equation}
+where $G_{\mu\nu}$ is the metric in the ambient space $\mc M$.
+Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{- \det(h)}$ and integrating over that patch:
 \begin{equation}\label{eqn:patch-area-v1}
-	A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{\det(h)}.
+	A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{- \det(h)}.
 \end{equation}
@@
 In LQG we don't have a notion of embedding fields.
-Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding co-ordinates of the curves and surface turn to not be needed.
-When promoting classical observables into quantum operators acting on lines and surfaces the embedding co-ordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.
+Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding coordinates of the curves and surface turn to not be needed.
+When promoting classical observables into quantum operators acting on lines and surfaces the embedding coordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.
 
@@
 \begin{equation}
-	A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e_\mu \wedge e_\nu) dx^\mu \wedge dx^\nu,
-\end{equation}
-the trace is taken over the ``internal'' Lorentz indices.
-
-Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x_a$ of the embedding co-ordinates and the vielbein $e_\mu^I$.
+	A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e \wedge e),
+\end{equation}
+where $e = e_{\mu} \diff x^{\mu}$ and the trace is taken over the ``internal'' Lorentz indices.
+
+Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x^a$ of the embedding co-ordinates and the vielbein $e_\mu^I$.
 This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.
@@
 Starting with the bulk vielbein $e_\mu^I$, we perform a local Lorentz transformation such that two ``legs'' of the vielbein are tangent to the worldsheet surface.
-We then project down the vielbein $e_\mu^I$ to a dyad $e_a^i$ living in the tangent space of the worldsheet, in terms of which the worldsheet metric can be written as:
+We then project down the vielbein $e_\mu^I$ to a dyad $e_a^I$ living in the tangent space of the worldsheet, in terms of which the worldsheet metric can be written as:
 \begin{equation}
-	h_{ab} = e_a^i e_b^j \eta_{ij},
-\end{equation}
-where $\eta_{ij}$ is the flat $(1+1)$ Minkowski metric. The determinant then becomes:
+	h_{ab} = e_a^I e_b^J \eta_{I J},
+\end{equation}
+where $\eta_{I J}$ is the flat Minkowski metric in group space. The determinant then becomes:
 \begin{align}\label{eqn:area-vielbein}
@@
 	           \end{vmatrix} = \begin{vmatrix}
-		                           e_x{}^i e_x{}^j & e_x{}^i e_y{}^j \\
-		                           e_y{}^i e_x{}^j & e_y{}^i e_y{}^j
-	                           \end{vmatrix} \eta_{ij} \nonumber        \\
-	       & = \vec e_x{}^2 \vec e_y{}^2 - (\vec e_x \cdot \vec e_y)^2,
-\end{align}
-where $\vec e_x \cdot \vec e_y = e_x{}^i e_y{}^j \eta_{ij}$.
-It is clear by comparing the two expressions \eqref{eqn:area-embedding} and \eqref{eqn:area-vielbein} that we have the following correspondence between the vielbein the $X$ derivatives:
+		                           e_t^I e_t^J & e_t^I e_x^J \\
+		                           e_x^I e_t^J & e_x^I e_x^J
+	                           \end{vmatrix} \eta_{I J} \nonumber       \\
+	       & = \vec e_t{}^2 \vec e_x{}^2 - (\vec e_t \cdot \vec e_x)^2,
+\end{align}
+where $\vec e_t \cdot \vec e_x = e_t^I e_x^J \eta_{I J}$.
+It is clear by comparing the two expressions \eqref{eqn:area-embedding} and \eqref{eqn:area-vielbein} that we have the following correspondence between the vielbein and the $X$ derivatives:
 \begin{equation}
@@
 \end{equation}
-In other words we can identify the vielbein with the derivatives of the embedding fields.
+In other words, we can directly identify the zweibein with the derivatives of the embedding fields.
 Of course, this is not altogether surprising.
-If we consider any manifold on which we have some set of fields $\{X^I(x^\mu)\}$, where $I$ is valued in the Lie algebra ${\mc g}$ of some group $\mc G$, as a function of some  ``fiducial'' co-ordinates $\{x^\mu\}$, then we can always define a set of ${\mc g}$ valued vector fields:
+If we consider any manifold on which we have some set of fields $\{X^I(x^\mu)\}$, where $I$ is valued in the Lie algebra $\mf{g}$ of some group $\mc G$, as a function of some  ``fiducial'' co-ordinates $\{x^\mu\}$, then we can always define a set of $\mf{g}$-valued vector fields:
 $$
@@
 $$
-In the usual formulation of the string action the embedding fields are \emph{not} Lie-algebra valued but are co-ordinate fields on what is generally taken to be a flat background.
-In order for this correspondence between vielbein and $X$ derivatives to work we have to view the $X$ fields as taking values in a Lie algebra.
-But these same $X$ fields \emph{also} serve as local co-ordinates for the bulk.
-In order for the co-ordinates to change from point to point in the bulk geometry, we must therefore require that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely!
+In the usual formulation of the string action, the embedding fields are \emph{not} Lie-algebra valued but are c-ordinate fields on what is generally taken to be a flat background.
+For this correspondence between vielbein and pullback Jacobian to work we have to view the $X$ fields as taking values in a Lie algebra.
+But these same $X$ fields \emph{also} serve as local coordinates for the bulk.
+If we want the coordinates to change from point to point in the bulk geometry, we must therefore require that the connection $\mc A$ in \eqref{eqn:covariant-deriv-v2} can never vanish completely!
 If $\mc A$ vanishes then that will imply that the fields $X$ don't change from one point to the next and cannot therefore be viewed as co-ordinate functions.
@@
 
-Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+Following the procedure done in \cite{Zwiebach2009A-First}, the correction (\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
 \begin{equation} \label{eqn:modified-NG-eom}

### 2024-06-27 lqg-strings.tex
iso(3,1) connection added, changed roman to arabic numerals, switched to section wise equation numbering, removed 'draft' in preamble.

@@
 \RequirePackage[final]{graphicx}
-\documentclass[twocolumn,draft,aps,prd,10pt,nofootinbib,nobibnotes]{revtex4-2}
+\documentclass[twocolumn,aps,prd,10pt,nofootinbib,nobibnotes]{revtex4-2}
 
@@
 
+% Added Jun 27, 2024 for section wise equation numbering
+\usepackage{amsmath}
+\numberwithin{equation}{section}
+\renewcommand{\thesection}{\arabic{section}}
+%
+
 \usepackage{enumerate}
@@
 \newcommand{\N}{\mathcal{N}}
+\newcommand{\ep}{\epsilon}
 % \newcommand{\H}{\mathcal{H}}
@@
 \end{equation}
-Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
+Since all 2-dimensional metrics are conformally flat \cite{Schottenloher2008A-Mathematical}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
 \begin{equation} \label{eqn:X-eom-simplified}
@@
 
+\subsection{Gauging Translations}\label{sec:translation_gauge}
+
 This is where we run into a problem.
@@
 Now we have $d+2$ embedding fields which we can write as:
-\begin{equation}
+\begin{equation}\label{eqn:enlarged-Xs}
 	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
@@
 As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein-Cartan geometry.
-
-\subsection{Gauging Translations}\label{sec:translation_gauge}
 
@@
 Now, one can ask what should the form of the action for a string moving in this enlarged bulk look like?
-Well, it will be of the same form \eqref{eqn:polyakov-gauged}, only now the worldsheet connection is an $\mf{iso}(d,1)$ valued one-form, with the embedding fields the enlarged $d+2$ dimensional set.
+Well, it will be of the same form \eqref{eqn:polyakov-gauged}, only now the worldsheet connection is an $\mf{iso}(d,1)$ valued one-form, with the embedding fields living in the enlarged $d+2$ dimensional set.
+
+\subsection{The Einstein-Cartan String}\label{sec:einstein-cartan-string}
+
+It is useful to see the explicit form of a $\mf{iso}(3,1)$ gauge connection. The elements of the Lie algeba of $\mf{iso}(3,1)$ have the following form \cite{Wise2010MacDowell-Mansouri}
+\begin{align}\label{eqn:poincare-lie-algeba}
+	T^A{}_B & := \begin{pmatrix}
+		0 & b^1 & b^2 & b^3 & p^0/l \\
+		b^1 & 0 & j^3 & -j^2 & p^1/l \\
+		b^2 & -j^3 & 0 & j^1 & p^2/l \\
+		b^3 & j^2 & -j^1 & 0 & p^3/l \\
+		-\ep p^0/l & -\ep p^1/l & -\ep p^2/l & -\ep p^3/l & 0
+	\end{pmatrix} \nonumber \\
+	& = j^i J_i + b^i B_i + \frac{1}{l}p^a P_a,
+\end{align} 
+where $J_i, B_i$ are the generators of rotations and boosts respectively.
+$P_a := (P_0, P_i)$ are the generators of translations.
+The parameter $\ep$ takes values in $\{-1,0,1\}$.
+Strictly speaking the above expression corresponds to an $\mf{iso}(3,1)$ Lie algebra generator only when $\ep = 0$.
+$l$ is a length scale which must be introduced so that the components of the ``vector'' $(p^0, p^i)$ can be viewed as components of a translation vector along the $3+1$ dimensional geometry $\mb{\Gamma}$.
+Similarly the boosts and rotations describe
+where $J_i, B_i$ are the generators of rotations and boosts respectively. $P_a := (P_0, P_i)$ are the generators of translations. The parameter $\ep$ takes values in $\{-1,0,1\}$.
+
+Strictly speaking the above expression corresponds to an $\mf{iso}(3,1)$ Lie algebra generator only when $\ep = 0$.
+$l$ is a length scale which must be introduced so that the components $(p^0, p^i)$ can be viewed as components of a ``translation vector'' living in the tangent space of the $3+1$ dimensional geometry $\mb{\Gamma}$.
+Similarly the boosts and rotations generators are for objects living in $\mb{\Gamma}$.
+
+Let us write down the gauged Polyakov action for the Poincaré lie algebra valued connection $\mc{A}_a$ whose components are given in \eqref{eqn:poincare-lie-algeba}:
+\begin{equation}\label{eqn:poincare-polyakov}
+	S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B \eta_{AB},
+\end{equation}
+where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \eqref{eqn:enlarged-Xs}) and $\eta_{AB}$ is the flat metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \eqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
+\begin{equation}\label{eqn:covariant-deriv-v2}
+	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + k \mc{A}_{a}^A{}_B X^B.
+\end{equation}
+Now, we will expand out the action \eqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately. It is clear that the resulting expression will be sum of three terms:
+\begin{align}
+	S'_{P} & = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \left( \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu} + \right. \nonumber \\
+	& \left. \mc{D}_a X^\mu \mc{D}_b X^r \eta_{\mu r} + \mc{D}_a X^r \mc{D}_b X^r \eta_{rr} \right)
+\end{align}
 
@@
 \begin{itemize}
-	\item Describe iso(d,1) connection decomposition into Lorentz piece and translation piece using \cite{Wise2010MacDowell-Mansouri} as reference.
 	\item Explain why deSitter, anti-deSitter and flat space are the only consistent solutions for the enlarged bulk geometry.

### 2024-06-27 lqg-strings.tex
Completed holography section

@@
 \begin{equation}\label{eqn:polyakov-gauged}
-	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu},
-\end{equation}
-where the covariant derivative $\mc{D}_a$ is of the form:
+	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} D_a X^\mu D_b X^\nu \eta_{\mu\nu},
+\end{equation}
+where the covariant derivative $D_a$ is of the form:
 \begin{equation}\label{eqn:covariant-deriv-v1}
-	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + k \mc{A}_{a}^\mu{}_\nu X^\nu,
+	D_a X^\mu(\tau , \sigma) = \partial_a X^\mu + k \mc{A}_{a}^\mu{}_\nu X^\nu,
 \end{equation}
@@
 Strictly speaking the above expression corresponds to an $\mf{iso}(3,1)$ Lie algebra generator only when $\ep = 0$.
+The case when $\ep = \pm 1$ will be motivated and discussed later.
 $l$ is a length scale which must be introduced so that the components $(p^0, p^i)$ can be viewed as components of a ``translation vector'' living in the tangent space of the $3+1$ dimensional geometry $\mb{\Gamma}$.
@@
 \end{equation}
-Now, we will expand out the action \eqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately. It is clear that the resulting expression will be sum of three terms:
-\begin{align}
-	S'_{P} & = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \left( \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu} + \right. \nonumber \\
-	& \left. \mc{D}_a X^\mu \mc{D}_b X^r \eta_{\mu r} + \mc{D}_a X^r \mc{D}_b X^r \eta_{rr} \right)
-\end{align}
-
-\textbf{todo:}
-
-\begin{itemize}
-	\item Explain why deSitter, anti-deSitter and flat space are the only consistent solutions for the enlarged bulk geometry.
-	\item Recall once again the steps which led us here.
-\end{itemize}
-
-\textbf{Steps which led us here}
-
-\begin{itemize}
-	\item We adopt the central result of LQG which is quantization of area
-	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
-	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
-	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
-	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
-	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
-\end{itemize}
+Now, we will expand out the action \eqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately.
+It is clear that the resulting expression will be sum of three terms, with the first term being the (gauged) Polyakov action for the string on $\mb{\Gamma}$, terms describing the coupling of the string on $\mb{\Gamma}$ with fluctuations along the extra dimensions $X^r$ and finally a Polyakov like term for the lone extra dimension.
+We can write this schematically as:
+\begin{equation}\label{eqn:poincare-polyakov-decomp}
+	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r].
+\end{equation}
+One can now argue along the same lines as the original arguments which led to the discovery of D-branes \cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background} to say that the extra dimension $X^r$ will become dynamical in the full theory even though it began life only as a classical constraint on the string worldsheet's location.
+This will imply that while most of the time the string will remain confined to $\mb{\Gamma}$, fluctuations along $X^r$ can cause the string to leave the ``brane'' and venture out into the bulk $\mb{M}$.
+If this is truly the case then the geometry of the enlarged bulk $\mb{M}$ will be essential for a description of the full string dynamics.
+
+This is where the non-zero value of $\ep$ mentioned in \eqref{eqn:poincare-lie-algeba} come into play.
+It turns out that for $\ep = +1$ ($\ep = -1$) the connection in \eqref{eqn:poincare-lie-algeba} describes a $\mf{so}(4,1)$ ($\mf{so}(3,2)$) connection respectively.
+These describe the symmetries of (asymptotically) deSitter and anti-deSitter spacetimes respectively.
+The length scale $l$ determines the value of the effective cosmological constant in the dS (adS) geometries:
+\begin{equation}\label{eqn:cosmological-constant}
+	\lambda = \frac{3 \ep}{l^2}.
+\end{equation}
+One might ask what is the motivation for introducing dS (adS) geometries into the discussion.
+The main motivation of course is the Maldacena or adS/CFT correspondence.
+The adS spacetime is usually understood to arise as a consequence of non-perturbative effects which nobody really has a proper understanding of as yet.
+One might hope that for a correspondence which has passed all possible checks uptil now, there should be some way to realise it in the classical theory also.
+
+What our discussion in this section shows, however, is that such a classical description is possible if we switch from the metric based approach to the connection based one for describing the background geometry and its coupling to the string worldsheet.
+
+% \begin{align}
+% 	S'_{P} & = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \left( \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu} + \right. \nonumber \\
+% 	& \left. \mc{D}_a X^\mu \mc{D}_b X^r \eta_{\mu r} + \mc{D}_a X^r \mc{D}_b X^r \eta_{rr} \right)
+% \end{align}
 
@@
 
+\textbf{Steps which led us here}
+
+\begin{itemize}
+	\item We adopt the central result of LQG which is quantization of area
+	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
+	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
+	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
+	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
+	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
+\end{itemize}
+
 \subsection{Closed String Spin-1 States} \label{sec:spin-1-states}

### 2024-06-30 lqg-strings.tex
removed affiliation, added to discussion section, minor edit section 2

@@
 \email{dvaid79@gmail.com}
-\affiliation{National Institute of Technology, Karnataka, India}
+\affiliation{}
 \author{Luigi Teixeira de Sousa}
@@
 	The second is an action in which the background geometry is described in terms of the pullback of the connection which describes the bulk geometry to the worldsheet.
-The resulting action is in the form of a gauged sigma model, where the spacetime co-ordinates are now SO(D,1) vectors.
+The resulting action is in the form of a gauged sigma model, where the spacetime co-ordinates are now vectors which transform under $ISO(D,1)$.
 We find that for the particular case of a constant background connection the action reduces to the bimetric action discussed above.
@@
 \end{equation}
-Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of some worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the spin foam pierces the WS.
+Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.
 In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
@@
 
-We have presented in this work a possible way to formulate string theory in background independent manner.
+In this article we have presented a phenomenological modification of the Nambu-Goto action, inspired on the one hand, by the central result of loop quantum gravity, according to which area and other geometric observables are quantized at the Planck scale.
+In particular the spectrum of the area operator is discrete and the smallest eigenvalue is non-zero (of the order $l_{pl}^2 \sim 10^{-68}\,\text{m}^2$).
+On the other hand we also took as a working hypothesis the statement that string theory, or some suitable version of it, provides the correct description of the low energy physics of the world around us.
+We then searched for the way in which both of these paradigms can be incorporated into a single theoretical model.
+The form of the action shown in \eqref{eqn:NG-area-corrected} appears, at least superficially
+
+Let us recall the steps which have led us here.
+Our original motivation was to continue to expand on the work which was started by one of us several years ago \cite{Vaid2017Connecting} and ask whether it is possible to construct an alternative to the usual action for the bosonic string in which the 2d geometry of the string worldsheet is coupled to the bulk geometry, not through the bulk metric $G_{\mu\nu}$, but through the pullback of a bulk connection to the worldsheet.
+This allows us to define a covariant derivative on the worldsheet which acts on the embedding co-ordinate fields $X^\mu$
 
@@
 \begin{itemize}
-	\item We adopt the central result of LQG which is quantization of area
+	\item We adopt the central result of LQG which is quantization of area. 
 	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.

### 2024-07-03 lqg-strings.tex
Formatted labels for consistency, added to discussion section, added many references and one figure.

@@
 In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
-Appendix \ref{sec:relation-with-NG-case} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
+Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
 
@@
 One simple way in which to do this is to modify the action \eqref{eqn:ng-action} as follows:
-\begin{equation} \label{eqn:NG-area-corrected}
+\begin{equation} \label{eqn:ng-area-corrected}
 	S_{M N G} = - T \int \diff ^2 x \sqrt{- (h + k \Delta)}.
 \end{equation}
-Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.
+Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}.
 In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry.
@@
 The final area corrected Nambu-Goto action becomes:
-\begin{equation} \label{eqn:modified-NG-action}
+\begin{equation} \label{eqn:modified-ng-action}
 	S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} \frac{k \Delta}{\sqrt{- h}} \right).
@@
 
-The action eq \eqref{eqn:modified-NG-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars.
+The action eq \eqref{eqn:modified-ng-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars.
 At first glance it might seem to not be WS reparameterization invariant because of the second term, however, this is corrected by the fact that $\Delta$ is a scalar \emph{density} of weight 2, thus counteracting the inverse metric determinant.
 Moreover, if we look at that expression we see that it can be written as:
-\begin{equation} \label{eqn:modified-NG-action-v2}
+\begin{equation} \label{eqn:modified-ng-action-v2}
 	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {k \Delta}{\sqrt{- (h^{-1})}} \right),
@@
 where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$.
-As such, in the expression \eqref{eqn:modified-NG-action} we can see a duality between the first and second terms.
-If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-NG-action}, but with the difference that the factor of $k \Delta / 2$ is mapped to $2 / (k \Delta)$:
-\begin{align} \label{eqn:modified-NG-action-v3}
+As such, in the expression \eqref{eqn:modified-ng-action} we can see a duality between the first and second terms.
+If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-ng-action}, but with the difference that the factor of $k \Delta / 2$ is mapped to $2 / (k \Delta)$:
+\begin{align} \label{eqn:modified-ng-action-v3}
 	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{k \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
@@
 \end{align}
-which has the same form as the original action \eqref{eqn:modified-NG-action}, as long as we make the replacements
+which has the same form as the original action \eqref{eqn:modified-ng-action}, as long as we make the replacements
 \begin{subequations}
@@
 
-It would be natural to suspect that the action \eqref{eqn:modified-NG-action-v2} might be related to bimetric gravity in the target space of the string.
+It would be natural to suspect that the action \eqref{eqn:modified-ng-action-v2} might be related to bimetric gravity in the target space of the string.
 We can see that this is indeed the case as follows.
@@
 where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{align}\label{eqn:polyakov-flat}
+\begin{align}\label{eqn:polyakov-bimetric}
 	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
@@
 If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
-\begin{equation} \label{eqn:double-NG-action}
+\begin{equation} \label{eqn:double-ng-action}
 	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
 \end{equation}
-and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
-\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
+and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-ng-action}
+\begin{equation} \label{eqn:area-corrected-ng-from-bimetric}
 	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
@@
 
-If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-flat}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-NG-action}:
+If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 
-If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
+If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-ng-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
 This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
@@
 
-The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
+The Nambu-Goto area-corrected action before approximations \eqref{eqn:ng-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
 \begin{equation} \label{eqn:BI-action}
@@
 \end{equation}
-thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
+thus the action \eqref{eqn:ng-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
 Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
@@
 We then searched for the way in which both of these paradigms can be incorporated into a single theoretical model.
-The form of the action shown in \eqref{eqn:NG-area-corrected} appears, at least superficially
+The form of the action shown in \eqref{eqn:ng-area-corrected} appears, at least superficially, as the simplest possible modification of the Nambu-Goto action which incorporates a minimum eigenvalue for the area.
+This value is encoded in the modulus of the $\Delta(x)$ field.
+In the process we introduced a new coupling parameter $ k = l_{pl}/l_s$ which is the ratio of the string scale to the Planck scale.
+
+Assuming that $l_{pl} \ll l_s$, we have $k \ll 1$ and consequently \eqref{eqn:ng-area-corrected} can be expanded as a power series in $k$.
+Keeping only the term linear in $k$, we obtain an action which is the sum of two copies of the Nambu-Goto action, one for the original metric $h_{ab}$ and the second for the inverse metric $h^{ab}$.
+We then pointed out the similarity between this expression and previous studies of \emph{bimetric gravity} \cite{Hassan2012Bimetric}.
+We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before by \cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the \emph{bulk} geometry rather than a bimetric action for the worldshee, itself, of the type given in \eqref{eqn:modified-ng-action-v2}.
+
+The bimetric viewpoint for the area-corrected Nambu-Goto action is more than just an interesting curiosity.
+This perspective allows us to construct the Polyakov action for the bimetric string in \eqref{eqn:polyakov-bimetric}.
+Of course, one would expect that the (area-corrected) Polaykov and Nambu-Goto formulations should be physically equivalent.
+Imposing this requirement leads us to the conclusion that the object $\Delta$ in \eqref{eqn:ng-area-corrected} must be worldsheet two-form (antisymmetric tensor) corresponding to the pullback of the \emph{bulk} Kalb-Ramond field.
+All of this eventually leads us to recognise the relation of our proposed action \eqref{eqn:ng-area-corrected} to the Born-Infeld action \eqref{eqn:BI-action} which arises when one studies the dynamics of D-branes in string theory.
+
+Let us make one crucial observation here.
+In the expression \eqref{eqn:ng-area-corrected} we originally took $\Delta$ to a constant representing the smallest quantum of area.
+It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form.
 
@@
 
+\subsection{Strings = Matter \& Loops = Gravity}\label{eqn:strings-loops}
+
+We want to conclude this discussion by pointing out some complementary aspects of the historical development of both string theory and loop quantum gravity which should already have been a hint many years ago that the two would eventually turn out to be intimately related.
+
+String theory arose from attempts to understand the Regge slope behavior of high energy scattering.
+Tullio Regge \cite{Regge1959Introduction,Chew1962S-Matrix,Chew1961Principle} had predicted in 1959 that when considering high energy scattering the mass squared $M^2$ and angular momentum $J$ of mesonic and hadronic resonances satisfy a linear relationship\footnote{Though a more complete analysis of recent experimental data \cite{Tang2000Properties,Chen2018Concavity} shows that the trajectories actually turn out to be nonlinear and intersecting.} of the form:
+\begin{equation}\label{eqn:regge-slope}
+	J = \alpha(0) + \alpha' M^2,
+\end{equation}
+where $\alpha'$ is generally referred to as the ``Regge slope''. One such trajectory is shown in \autoref{fig:chew-frautschi-plot-p2}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.35]{chew-frautschi-plot-p2.png}
+	\caption{A Chew-Frautchi plot of $M^2$ vs $\alpha(M^2) \sim J$  for several high energy resonances. Figure courtesy \cite{Desgrolard2001Exchange-Degenerate} \todo{Pending permission from authors.}}.
+	\label{fig:chew-frautschi-plot-p2}
+\end{figure}
+In 1968, Gabriele Veneziano discovered \cite{Veneziano1968Construction} an explicit analytic expression for the scattering amplitude which exhibited Regge behavior and satisfied certain consistency conditions known as ``crossing symmetry''.
+Soon after works by Nambu \cite{Nambu1969Quark}, Nielsen \cite{Nielsen1970An-Almost} and Susskind \cite{Susskind1970Dual} proposed a string like model for Regge behavior.
+
+What this very brief history of the early years of string theory tells us is that the theory arose from trying to understand particle scattering.
+This, in part, explains why string theorists didn't pay much attention to the question of background independence of string theory during its early decades.
+For particle physicists the flat Minkowski background was a given and so it was natural for them to begin to quantize the string by assuming the flat Minkowski metric for the bulk geometry.
+
+In stark contrast to this perspective, loop quantum gravity arose from the desire of relativists to quantize gravity in a manifestly background independent manner.
+
 \begin{acknowledgments}
@@
 
-Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
+Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-bimetric}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion.
 Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to the description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.
@@
 
-Following the procedure done in \cite{Zwiebach2009A-First}, the correction (\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
-\begin{equation} \label{eqn:modified-NG-eom}
+Following the procedure done in \cite{Zwiebach2009A-First}, the correction (\ref{eqn:modified-ng-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
+\begin{equation} \label{eqn:modified-ng-eom}
 	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
@@
 and
-\begin{equation} \label{eqn:modified-NG-bc}
+\begin{equation} \label{eqn:modified-ng-bc}
 	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
@@
 where
-\begin{align} \label{eqn:modified-NG-tau-currents}
+\begin{align} \label{eqn:modified-ng-tau-currents}
 	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
@@
 \end{align}
-\begin{align} \label{eqn:modified-NG-sigma-currents}
+\begin{align} \label{eqn:modified-ng-sigma-currents}
 	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
@@
 and the form of the wave equation maintains its shape as in
-\begin{equation} \label{eqn:corrected-NG-wave-equation}
+\begin{equation} \label{eqn:corrected-ng-wave-equation}
 	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
@@
 
-Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
+Rewriting eq(\ref{eqn:corrected-ng-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta / 2 (- h)$)
 \begin{equation} \label{eqn:sigma-parameterization}
@@
 
-\section{Relating Nambu-Goto and Polyakov analysis} \label{sec:relation-with-NG-case}
+\section{Relating Nambu-Goto and Polyakov analysis} \label{sec:polyakov-ng-relation}
 
@@
 and $\tau (t , x)$ satisfying constraints (\ref{eqn:new-coordinates-constraints-compact}).
-This shows that our analysis of the action (\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the analysis of the inverse area corrected Nambu-Goto action (\ref{eqn:modified-NG-action}).
+This shows that our analysis of the action (\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the analysis of the inverse area corrected Nambu-Goto action (\ref{eqn:modified-ng-action}).
 

### 2024-07-09 lqg-strings.tex
Added to discussion section

@@
 
-In this article we have presented a phenomenological modification of the Nambu-Goto action, inspired on the one hand, by the central result of loop quantum gravity, according to which area and other geometric observables are quantized at the Planck scale.
+In this article we have presented a phenomenological modification of the Nambu-Goto action \emph{inspired by the central result of loop quantum gravity, according to which area and other geometric observables are quantized at the Planck scale}.
 In particular the spectrum of the area operator is discrete and the smallest eigenvalue is non-zero (of the order $l_{pl}^2 \sim 10^{-68}\,\text{m}^2$).
@@
 In the expression \eqref{eqn:ng-area-corrected} we originally took $\Delta$ to a constant representing the smallest quantum of area.
-It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form.
-
-Let us recall the steps which have led us here.
-Our original motivation was to continue to expand on the work which was started by one of us several years ago \cite{Vaid2017Connecting} and ask whether it is possible to construct an alternative to the usual action for the bosonic string in which the 2d geometry of the string worldsheet is coupled to the bulk geometry, not through the bulk metric $G_{\mu\nu}$, but through the pullback of a bulk connection to the worldsheet.
-This allows us to define a covariant derivative on the worldsheet which acts on the embedding co-ordinate fields $X^\mu$
-
-\textbf{Steps which led us here}
-
-\begin{itemize}
-	\item We adopt the central result of LQG which is quantization of area. 
-	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
-	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
-	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
-	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
-	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
-\end{itemize}
-
-\subsection{Closed String Spin-1 States} \label{sec:spin-1-states}
-
-In section \ref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being invariant under rigid rotations of the string.
-Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to?
-Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
-\begin{equation} \label{eqn:connection-string-vector-excitation}
-	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
-\end{equation}
-Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
-\begin{equation} \label{eqn:AEF-string-vector-excitation}
-	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
-\end{equation}
+It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form!
 
@@
 
-We want to conclude this discussion by pointing out some complementary aspects of the historical development of both string theory and loop quantum gravity which should already have been a hint many years ago that the two would eventually turn out to be intimately related.
+We would also like to inform the discussion by pointing out some complementary aspects of the historical development of both string theory and loop quantum gravity which should already have been a hint many years ago that the two would eventually turn out to be intimately related.
 
@@
 This, in part, explains why string theorists didn't pay much attention to the question of background independence of string theory during its early decades.
-For particle physicists the flat Minkowski background was a given and so it was natural for them to begin to quantize the string by assuming the flat Minkowski metric for the bulk geometry.
+For particle physicists the flat Minkowski background was a given - the entire machinery of Feynman diagrams and perturbation theory was built with the implicit assumption of a flat background manifold.
+The ``string'' in the first conception was solely meant to be a description of bound states of mesons and hadrons.
+From the abstract of Susskind's 1970 paper \cite{Susskind1970Dual} we quote
+
+\begin{quote}
+	\emph{A theory of mesons is based on the experimentally observed linear level spacing of hadron excitations.
+The theory uses a model for the internal structure of mesons consisting of a system of harmonic vibrations.
+Roughly speaking, a meson is described by the degrees of freedom of a four-dimensional rubber band with a quark pair embedded in it.}
+\end{quote}
+
+It was realized only later \cite{Scherk1974bDual} that excitations of the string included a spin-2 object which could be identified with a graviton.
 
 In stark contrast to this perspective, loop quantum gravity arose from the desire of relativists to quantize gravity in a manifestly background independent manner.
+
+\textbf{Steps which led us here}
+
+\begin{itemize}
+	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
+	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
+	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
+	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
+	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
+\end{itemize}
+
+\subsection{Closed String Spin-1 States} \label{sec:spin-1-states}
+
+In section \ref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being invariant under rigid rotations of the string.
+Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to?
+Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+\begin{equation} \label{eqn:connection-string-vector-excitation}
+	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
+\end{equation}
+Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
+\begin{equation} \label{eqn:AEF-string-vector-excitation}
+	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
+\end{equation}
 

### 2024-07-13 lqg-strings.tex
added the explicit decomposotion of the expanded Polyakov-Poincare action

@@
 \begin{equation}\label{eqn:poincare-polyakov}
-	S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B \eta_{AB},
-\end{equation}
-where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \eqref{eqn:enlarged-Xs}) and $\eta_{AB}$ is the flat metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \eqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
+	S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B G_{AB},
+\end{equation}
+where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \eqref{eqn:enlarged-Xs}) and $G_{AB}$ is the expanded metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \eqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
 \begin{equation}\label{eqn:covariant-deriv-v2}
@@
 \begin{equation}\label{eqn:poincare-polyakov-decomp}
-	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r].
-\end{equation}
+	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r] ,
+\end{equation}
+or more explicitly as
+\begin{multline} \label{eqn:poincare-polyakov-decomp-explicit}
+	S' _{P} [X^{\mu} , X^{r}] = -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \\
+	- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r} - \\
+	- \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r} ,
+\end{multline}
+where we can see a natural decomposition of the expanded bulk metric $G_{A B}$ as a $(d+1)$-dimensional tensor $\eta _{\mu \nu}$, a $(d+1)$-dimensional vector $V_{\mu} = G_{\mu r}$ and a scalar $V = G_{r r}$, akin to the ADM decomposition of the metric in standard GR literature.
+
 One can now argue along the same lines as the original arguments which led to the discovery of D-branes \cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background} to say that the extra dimension $X^r$ will become dynamical in the full theory even though it began life only as a classical constraint on the string worldsheet's location.

### 2024-07-17 lqg-strings.tex
merging with Luigi's last commit

--- 2024-07-09 lqg-strings.tex
@@
 
-\subsection{Strings = Matter \& Loops = Gravity}\label{eqn:strings-loops}
-
-We would also like to inform the discussion by pointing out some complementary aspects of the historical development of both string theory and loop quantum gravity which should already have been a hint many years ago that the two would eventually turn out to be intimately related.
-
-String theory arose from attempts to understand the Regge slope behavior of high energy scattering.
-Tullio Regge \cite{Regge1959Introduction,Chew1962S-Matrix,Chew1961Principle} had predicted in 1959 that when considering high energy scattering the mass squared $M^2$ and angular momentum $J$ of mesonic and hadronic resonances satisfy a linear relationship\footnote{Though a more complete analysis of recent experimental data \cite{Tang2000Properties,Chen2018Concavity} shows that the trajectories actually turn out to be nonlinear and intersecting.} of the form:
-\begin{equation}\label{eqn:regge-slope}
-	J = \alpha(0) + \alpha' M^2,
-\end{equation}
-where $\alpha'$ is generally referred to as the ``Regge slope''. One such trajectory is shown in \autoref{fig:chew-frautschi-plot-p2}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[scale=0.35]{chew-frautschi-plot-p2.png}
-	\caption{A Chew-Frautchi plot of $M^2$ vs $\alpha(M^2) \sim J$  for several high energy resonances. Figure courtesy \cite{Desgrolard2001Exchange-Degenerate} \todo{Pending permission from authors.}}.
-	\label{fig:chew-frautschi-plot-p2}
-\end{figure}
-In 1968, Gabriele Veneziano discovered \cite{Veneziano1968Construction} an explicit analytic expression for the scattering amplitude which exhibited Regge behavior and satisfied certain consistency conditions known as ``crossing symmetry''.
-Soon after works by Nambu \cite{Nambu1969Quark}, Nielsen \cite{Nielsen1970An-Almost} and Susskind \cite{Susskind1970Dual} proposed a string like model for Regge behavior.
-
-What this very brief history of the early years of string theory tells us is that the theory arose from trying to understand particle scattering.
-This, in part, explains why string theorists didn't pay much attention to the question of background independence of string theory during its early decades.
-For particle physicists the flat Minkowski background was a given - the entire machinery of Feynman diagrams and perturbation theory was built with the implicit assumption of a flat background manifold.
-The ``string'' in the first conception was solely meant to be a description of bound states of mesons and hadrons.
-From the abstract of Susskind's 1970 paper \cite{Susskind1970Dual} we quote
-
-\begin{quote}
-	\emph{A theory of mesons is based on the experimentally observed linear level spacing of hadron excitations.
-The theory uses a model for the internal structure of mesons consisting of a system of harmonic vibrations.
-Roughly speaking, a meson is described by the degrees of freedom of a four-dimensional rubber band with a quark pair embedded in it.}
-\end{quote}
-
-It was realized only later \cite{Scherk1974bDual} that excitations of the string included a spin-2 object which could be identified with a graviton.
-
-In stark contrast to this perspective, loop quantum gravity arose from the desire of relativists to quantize gravity in a manifestly background independent manner.
-
 \textbf{Steps which led us here}

### 2024-07-17 strings-loops-history.tex
merging with Luigi's last commit

\subsection{Strings = Matter \& Loops = Gravity}\label{eqn:strings-loops}

We would also like to inform the discussion by pointing out some complementary aspects of the historical development of both string theory and loop quantum gravity which should already have been a hint many years ago that the two would eventually turn out to be intimately related.

\textbf{The String Theory Perspective}

String theory arose from attempts to understand the Regge slope behavior of high energy scattering. Tullio Regge \cite{Regge1959Introduction,Chew1962S-Matrix,Chew1961Principle} had predicted in 1959 that when considering high energy scattering the mass squared $M^2$ and angular momentum $J$ of mesonic and hadronic resonances satisfy a linear relationship\footnote{Though a more complete analysis of recent experimental data \cite{Tang2000Properties,Chen2018Concavity} shows that the trajectories actually turn out to be nonlinear and intersecting.} of the form:
\begin{equation}\label{eqn:regge-slope}
	J = \alpha(0) + \alpha' M^2,
\end{equation}
where $\alpha'$ is generally referred to as the ``Regge slope''. One such trajectory is shown in \autoref{fig:chew-frautschi-plot-p2}.

\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.35]{chew-frautschi-plot-p2.png}
	\caption{A Chew-Frautchi plot of $M^2$ vs $\alpha(M^2) \sim J$  for several high energy resonances. Figure courtesy \cite{Desgrolard2001Exchange-Degenerate} \todo{Pending permission from authors.}}.
	\label{fig:chew-frautschi-plot-p2}
\end{figure}
In 1968, Gabriele Veneziano discovered \cite{Veneziano1968Construction} an explicit analytic expression for the scattering amplitude which exhibited Regge behavior and satisfied certain consistency conditions known as ``crossing symmetry''. Soon after works by Nambu \cite{Nambu1969Quark}, Nielsen \cite{Nielsen1970An-Almost} and Susskind \cite{Susskind1970Dual} proposed a string like model for Regge behavior.

What this very brief history of the early years of string theory tells us is that the theory arose from trying to understand particle scattering. This, in part, explains why string theorists didn't pay much attention to the question of background independence of string theory during its early decades. For particle physicists the flat Minkowski background was a given - the entire machinery of Feynman diagrams and perturbation theory was built with the implicit assumption of a flat background manifold. The ``string'' in the first conception was solely meant to be a description of bound states of mesons and hadrons. From the abstract of Susskind's 1970 paper \cite{Susskind1970Dual} we quote

\begin{quote}
	\emph{A theory of mesons is based on the experimentally observed linear level spacing of hadron excitations. The theory uses a model for the internal structure of mesons consisting of a system of harmonic vibrations. Roughly speaking, a meson is described by the degrees of freedom of a four-dimensional rubber band with a quark pair embedded in it.}
\end{quote}

It was realized only later \cite{Scherk1974bDual} that excitations of the string included a spin-2 object which could be identified with a graviton.

\textbf{The Loop Quantum Gravity Perspective}

It is clear from the above discussion that the discovery of a spin-2 excitation in the spectrum of the closed bosonic string was something unexpected since the theory was always formulated on a flat background. Gravity was never intended to be a part of the framework. The resulting spin-2 excitation is therefore, correctly interpreted as the quantization of metric perturbations around a flat background.

In stark contrast, loop quantum gravity arose from the desire of relativists to quantize gravity in a manifestly background independent manner. Einstein's great insight was that co-ordinates were ``unphysical''. They are arbitrary labels which we assign to describe physical systems around us.

### 2024-07-17 lqg-strings.tex
Completed my part of discussion

@@
 Our goal is to write down the action of a string propagating in a background geometry.
-One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry.
+One might argue that the expression \eqref{eqn:polyakov-curved-bulk}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry.
 However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones.
-An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates).
+An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-curved-bulk} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates).
 This, however, leaves open the question of what role the bulk connection should play in this picture.
@@
 We then pointed out the similarity between this expression and previous studies of \emph{bimetric gravity} \cite{Hassan2012Bimetric}.
-We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before by \cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the \emph{bulk} geometry rather than a bimetric action for the worldshee, itself, of the type given in \eqref{eqn:modified-ng-action-v2}.
+We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before by \cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the \emph{bulk} geometry rather than a bimetric action for the worldsheet, itself, of the type given in \eqref{eqn:modified-ng-action-v2}.
 
@@
 
-\textbf{Steps which led us here}
-
-\begin{itemize}
-	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
-	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
-	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
-	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
-	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
-\end{itemize}
+After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}
+
+Ultimately one cannot be satisfied with the heuristic action of the form \eqref{eqn:ng-area-corrected}.
+Therefore in \autoref{sec:holographic-strings} we attempt to build, from the ground up, a modified string action which incorporates the following chain of thought.
+We seek to describe the behavior of a string in an arbitrarily curved background geometry at a \emph{classical} level.
+For this an action of the form \eqref{eqn:polyakov-curved} is unsuitable because that action treats the bulk metric as non-dynamical variables.
+Connection variables are used in LQG to describe the geometry of a manifold.
+The coupling of the string worldsheet to the bulk geometry should reflect this fact.
+This leads us to an action of the form \eqref{eqn:poincare-polyakov}.
+This action no longer possess the global Poincaré symmetry of the original Polyakov action.
+However it is invariant under \emph{local} Poincaré gauge transformations.
+
+For an arbitrarily (or even a minor deviation from flat space) curved bulk geometry, global Poincaré symmetry of embedding fields is not meaningful.
+Local Poincaré symmetry, on the other hand, provides a perfectly adequate framework \cite{Hehl2023Four} for constructing a theory of gravity on an arbitrary bulk.
+Thus we conjecture that the bulk theory is that of gauged Poincaré gravity.
+
+Finally, the interpretation of embedding fields as co-ordinate fields on the bulk and \emph{also} as vectors living in the fundamental representation of the Poincaré group necessitates the introduction of an ``auxiliary'' co-ordinate which has the natural interpretation as a holographic or scale direction.
 
@@
 The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
-\begin{equation}\label{eqn:polyakov-gravity}
+\begin{equation}\label{eqn:polyakov-curved-bulk}
 	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
@@
 where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$.
-Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$.
+Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-curved-bulk} does not contain any terms with time derivatives of $G_{\mu\nu}$.
 However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string.

### 2024-07-17 lqg-strings.tex
Added reference to Altaisky's work on Poincaré spin networks and its possible relevance to our work.

@@
 \newcommand{\sltwoc}{\mathfrak{sl}(2,\mathbb{C})}
+% \newcommand{\sutwo}{SU(2)}
 
@@
 
+\subsection{Poincaré Spin Networks}\label{sec:poincare-networks}
+
+The above considerations feed back into our understanding of the bulk gravity theory.
+Recall, that we started with LQG in which the gauge group for the $3+1$ dimensional bulk is $\sltwoc$.
+However, our considerations regarding viewing the embedding fields as representations of the Poincaré group imply that the bulk is $4+1$ dimensional, when one includes the emergent (spacelike) holographic direction, and therefore the gravitational theory for the full bulk should be gauge theory of the Poincaré group.
+Now, if we wish to construct the resulting spin-network and spin-foam states for the bulk by following the LQG quantization procedure, what we end up with will not be the usual $ \mf{su}(2) $ ($ \mf{sl}(2,\C)$) spin-networks (spin-foams), but \emph{Poincaré spin-foams} of the kind recently discussed in a work by Altaisky \cite{Altaisky2024Poincare}.
+
+This suggests that it might make greater sense to use Poincaré spin foams rather than Lorentzian spin foams to describe the behaviour of quantum geometry at the Planck scale.
+Though even with such a change, the fundamental result of LQG - quantization of areas - which underpins this work, will likely not be affected.
+
 \subsection{Closed String Spin-1 States} \label{sec:spin-1-states}

### 2024-07-18 arXiv-submission-v1/lqg-strings.tex
Almost there. Started arXiv submission

--- 2024-07-17 lqg-strings.tex
@@
 
-In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
+In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014Emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
 We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
@@
 	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) + \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
 \end{multline}
@@
 	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
-	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
+	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) + \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
 \end{multline}
@@
 \end{equation}
-The condition $h = \Delta ^2 / g$ can be achieved by
+The condition $h = \Delta ^2 / g$ can be achieved if there exists a matrix $\Delta_{ab}$, such that:
 \begin{equation} \label{eqn:h=SgS}
@@
 \end{equation}
-just like the regular ST literature, thus the constraints are unchanged by our correction.
+just like the regular string theory literature, thus the constraints are unchanged by our correction.
 
@@
 revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \cite{Balthazar-t-backgrounds}.
-We'll come back to this in \autoref{sec:emergent-dimensions}.
+We will come back to this fact in \autoref{sec:emergent-dimensions}.
 
@@
 If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-ng-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
-This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
-The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
+This happens because, as we explored in section \autoref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for without any coupling to an antisymmetric bulk tensor.
+The more complete picture would be thus to consider the (area-corrected) string now explicitly coupled to a bulk Kalb-Ramond field \cite{Tong2009Lectures}
 \begin{multline} \label{eqn:area-corrected-K-R-action}
@@
 \end{equation}
-This in actuality will differ from the normal ST literature by a factor of $1 / 2$ in the momentum term, but this is needed for the Poisson brackets to give the expected results.
+This in actuality will differ from the normal string theory literature by a factor of $1 / 2$ in the momentum term, but this is needed for the Poisson brackets to give the expected results.
 
@@
 	\end{tabular}
-	\caption{values of $a$ for different spacetime dimensionalities and mass parameters. Visibly, the dependence in $D$ is much stronger than the dependence in $\mu$.}
+	\caption{values of $a$ for different spacetime dimensionalities and mass parameters. Visibly, the dependence on $D$ is much stronger than the dependence on $\mu$.}
 \end{table}
@@
 
-There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi2014emergent} model, with the action being
+There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in section \ref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft emergent dimension" \cite{Afshordi2014Emergent} model, with the action being
 \begin{multline} \label{eqn:emergent-dimensions-action}
@@
 \gg m_{d}$.
-This is Afshordi's model \cite{Afshordi2014emergent}.
+This is Afshordi's model \cite{Afshordi2014Emergent}.
 Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
@@
 In the expression \eqref{eqn:ng-area-corrected} we originally took $\Delta$ to a constant representing the smallest quantum of area.
-It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form!
-
-After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}
+It is only \emph{later}, in \autoref{sec:inverse-metric-Polyakov}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form \eqref{eqn:Delta-b-relation}!
+
+We then proceeded to explore the equations of motion in \autoref{sec:quantum-kg-string} resulting from the Polyakov form of the area-corrected string action .
+We found that the constraint algebra must be modified due to the existence of a minimal area and the resulting modification gives us \emph{two-index} Virasoro generators.
+We found the algebra of generators to be anomaly free implying that the area-corrected string action is consistent in any number of spacetime dimensions.
+
+We then explored the possible relation between our model and the ``emergent dimensions'' model put forward by Afshordi in \cite{Afshordi2014Emergent} in \autoref{sec:emergent-dimensions}.
 
@@
 Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to?
-Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
+Well, in section \ref{sec:gauging-lt} we discussed a possible formulation of string theory in terms of a Poincaré connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection \cite{Bodendorfer-LQG} formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
 \begin{equation} \label{eqn:connection-string-vector-excitation}

### 2024-07-18 lqg-strings.tex
Revert "Almost there. Started arXiv submission"
This reverts commit fb489d34e3d08b61099baf0091dac39c65c3a114.

@@
 
-Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two dimensional surfaces and volumes of three dimensional regions.
-Moreover, these operators could be diagonlized exactly in the spin-network basis and a discrete spectrum for quantum of area and quantum of volume could be derived.
+Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two-dimensional surfaces and volumes of three-dimensional regions.
+Moreover, these operators could be diagonalized exactly in the spin-network basis and a discrete spectrum for quantum of area and quantum of volume could be derived.
 This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity.
 One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.
+
+One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$ \footnote{Here, the index convention followed is that lowercase $i , j , k$ refer to 3-dimensional flat internal ($\mf{su}(2)$) indices and lowercase $a , b , c$ refer to 3-dimensional curved spacetime indices} can no longer be a continuous function of spacetime, rather it becomes a \emph{distribution}, assuming a constant value on one patch of space, then another value at another patch, etc \cite{Bodendorfer-LQG,Rovelli2015Covariant}.
+The consequence of this non-continuous distributional nature of the connection is that the triad (or Ashtekar electric field) operator, which formally would be
+\begin{equation} \label{eqn:triad-operator}
+	\Hat{\widetilde{E}}{}^{a} _{i} = - 8 \pi i \hbar G \frac{\delta}{\delta A^{i} _{a}}
+\end{equation}
+becomes ill-defined since $A^{i} _{a}$ is non-continuous (in particular, at the edges of a polyhedra it changes abruptly), so the triad needs to be \emph{smeared} over a surface where $A^{i} _{a}$ is constant
+\begin{equation} \label{eqn:triad-flux-operator}
+	\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}} ,
+\end{equation}
+where $\diff S_{a} = \diff \sigma ^{b} \wedge \diff \sigma ^{c} \varepsilon _{a b c}$. This naturally leads to the \emph{area operator} of said surface
+\begin{equation} \label{eqn:area-operator}
+	\Hat{A} (S) = - 8 \pi i l_{pl} ^2 \beta \int _{S} \sqrt{\diff S_{a} \diff S_{b} \frac{\delta}{\delta A^{i} _{a}} \frac{\delta}{\delta A_{b i}}} .
+\end{equation}
+Notably, since $A^{i} _{a}$ is a $\mf{su}(2)$-valued connection, in the basis which diagonalises the area operator (the \emph{spin network} basis \cite{Bodendorfer-LQG}) $\ket{\Tr (h^{(j)} _{c} (A))}$, the eigenvalues of the area operator are just proportional to \emph{angular momentum} eigenvalues
+\begin{equation} \label{eqn:area-eigenvalues}
+	\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))} ,
+\end{equation}
+with $j$ being the representation label of $\mf{su}(2)$ along the spin network edge piercing the surface under consideration. Thus, spin network edges carry angular momenta.
 
@@
 
-We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}).
+We now seek to quantize the Klein-Gordon string by means of covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures,Green2012Superstring}.
 The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ .
@@
 
-After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}
+After exploring the equations of motion of the area corrected string, we found that said equations can be recast as a set of Klein-Gordon equations, which for a first analysis we assumed to have constant coefficient $\mu$, however that need not be the case.
+The solution of these equations and their consequences for the constraints lead us to a modified \textquotedblleft Virasoro-Klein-Gordon" algebra, where the algebra modes have two indices, which in turn resulted in a truncated solution.
+This also had the effect of not having distinct left and right moving modes, thus there was no level-matching prohibiting spin-1 states for the closed string, which we postulated to maybe be related to the Ashtekar variables of the background geometry.
+The quantisation of the KG string and the Virasoro-Klein-Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu} , B_{\mu \nu} , \Phi$ fields as part of the spin-2 spectrum.
+
+We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into String Theory by considering Afshordi's Emergent Spacetime and Evolving Dimensions model with some key insights from LQG complementing said model, creating a more concrete picture of the mechanism behind the emerging dimensions and how ultimately spacetime (and thus the true quantum gravitational field) might be actually $(2+1)$-dimensional at the Planck scale.
 

### 2024-07-18 arXiv-submission-v1/lqg-strings.tex
Created arXiv-submit folder. Last checks before submission.

--- 2024-07-17 lqg-strings.tex
@@
 
-After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}
+After exploring the equations of motion of the area corrected string, we found that said equations can be recast as a set of Klein-Gordon equations, which for a first analysis we assumed to have constant coefficient $\mu$, however that need not be the case.
+The solution of these equations and their consequences for the constraints lead us to a modified \textquotedblleft Virasoro-Klein-Gordon" algebra, where the algebra modes have two indices, which in turn resulted in a truncated solution.
+This also had the effect of not having distinct left and right moving modes, thus there was no level-matching prohibiting spin-1 states for the closed string, which we postulated to maybe be related to the Ashtekar variables of the background geometry.
+The quantisation of the KG string and the Virasoro-Klein-Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu} , B_{\mu \nu} , \Phi$ fields as part of the spin-2 spectrum.
+
+We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into string theory by considering Afshordi's ``emergent dimensions’’ model \cite{Afshordi2014Emergent} with some key insights from LQG complementing said model, creating a more concrete picture of the mechanism behind the emerging dimensions.
 

### 2024-08-28 temp/lqg-strings.tex
Changed title to reflect conclusion, revised abstract

--- 2024-07-18 arXiv-submission-v1/lqg-strings.tex
@@
 
-In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014Emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
+In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
 We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
@@
 from which we can extract the metric $g_{c d}$ as
-\begin{equation} \label{eqn:ws-metric}
+\begin{equation} \label{eqn:ws-metric-v2}
 	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,

### 2024-09-27 lqg-strings.tex
Made some changes to the layout of the introduction to improve readability.

@@
 
-\title{Quantizing the Bosonic String on a Loop Quantum Gravity Background}
+\title{A Loop Quantm Gravity Inspired Action for the Bosonic String and a Emergent Dimensions at Large Scales}
 
@@
 
-	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a bosonic string.
-We consider two types of modifications.
-The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geometry and are bounded from below.
+	We propose a modification of the Nambu-Goto action for the bosonic string which is compatible with the existence of a minimum area at the Planck scale.
+The result is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geometry and are bounded from below.
 This leads us to a string action which is similar to that of bimetric gravity.
-We provide formulations of the bimetric string for both the Nambu-Goto (second order) and Polyakov (first order) formulations.
+We provide formulations of the bimetric string action for both the Nambu-Goto (second order) and Polyakov (first order) formulations.
 We explore the classical solutions of this action and its quantization and relate it to the conventional string solutions.
 
-	The second is an action in which the background geometry is described in terms of the pullback of the connection which describes the bulk geometry to the worldsheet.
-The resulting action is in the form of a gauged sigma model, where the spacetime co-ordinates are now vectors which transform under $ISO(D,1)$.
-We find that for the particular case of a constant background connection the action reduces to the bimetric action discussed above.
-We discuss classical solutions and quantization strategies for this action and its implications for the broader program of unifying string theory and loop quantum gravity.
+	We further construct a string action in which the effect of the background geometry is described in terms of the pullback of the bulk connection, which encodes the bulk geometry, to the worldsheet.
+The resulting string action is in the form of a gauged sigma model, where the spacetime co-ordinates are now vectors which transform under the Poincaré group $ISO(D,1)$.
+This requires the introduction of an auxiliary bulk co-ordinate which has a natural interpretation as a holographic or scale direction.
+We discuss possible cosmological implications of such a large scale emergent dimension.
 \end{abstract}
@@
 There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.
-We discuss each in turn below giving a bird's eye view of research spanning a period of nearly sixty years.
 
@@
 Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
+
+In this paper we present a phenomenological modification of the Nambu-Goto action for the bosonic string which has the property that the worldsheet area can never be less than some fixed constant value $\Delta$ which represents the minimum allowed quantum of area predicted by LQG.
+
+The following is the outline of the paper along with a brief summary of what is accomplished in each section.
+For those seeking a rapid review of the principle areas of diffence between the two theories \autoref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.
+
+Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
+We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.
+In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity.
+We find both, the Nambu-Goto and the Polaykov forms of this action.
+Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.
+
+In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion.
+We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field.
+Furthermore, we explore an equivalence between our proposed model and the Born-Infeld model in $1 + 1$ dimensions.
+We conclude this section by solving the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
+In \autoref{sec:quantum-kg-string} we follow the route of covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.
+
+In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014Emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
+We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
+
+In \autoref{sec:holographic-strings} we describe how to construct an action for the bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
+We find that this can be done by viewing the worldsheet embedding co-ordinates $X$'s as living in the fundamental representation of a suitable gauge group $G$.
+Consistency between the dual roles played by the $X$'s as both co-ordinates for the background manifold \emph{and} and as objects which can be parallel transported using a connection, requires that the gauge group $G$ be the Poincaré group $ISO(D+1,1)$.
+In other words the string which originally was embedded in a $D+1$ dimensional background, now lives in a $D+2$ dimensional geometry which has one extra ``emergent'' dimension which has the natural interpretation as a \emph{scaling} dimension.
+We therefore view our construction as providing a natural framework for \emph{classical holography}, where the scale dimension is already built into the theory at the classical level instead of something which arises due to non-perturbative physics.
+
+There are various appendices containing details of calculations and background information.
+In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
+Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
+
+\subsection{Historical Background}\label{sec:history}
 
@@
 
-Before proceeding let us state our ``central dogma''.
+\section{Modified Nambu Goto Action}\label{sec:modified-ng}
+
+Before proceeding let us restate our ``central dogma''.
 We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators - such as those that measure the area and volume of a given region of space - exist and have discrete spectra, thus the transition from no area/volume to some area/volume is a discrete jump rather than a continuous one.
 We now wish to understand how to construct a worldsheet action which reflects this central dogma.
-
-The following is the outline of the paper.
-In \autoref{sec:modified-ng} we recall the Nambu-Goto action and suggest a simple modification which incorporates our central dogma, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
-We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.
-In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity.
-We find both, the Nambu-Goto and the Polaykov forms of this action.
-Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.
-
-In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion.
-We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field.
-Furthermore, we explore an equivalence between our proposed model and the Born-Infeld model in $1 + 1$ dimensions.
-We conclude this section by solving the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints.
-In \autoref{sec:quantum-kg-string} we follow the route of covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.
-
-In \autoref{sec:emergent-dimensions} we complement Afshordi's work \cite{Afshordi2014emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading to a more concrete theory.
-We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.
-
-In \autoref{sec:holographic-strings} we describe how to construct an action for the bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity.
-We discuss possible avenues for quantizing this action and further study its implications for the relationship between string theory and LQG.
-
-There are various appendices containing details of calculations and background information.
-In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
-Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
-
-\section{Modified Nambu Goto Action}\label{sec:modified-ng}
 
@@
 
-We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into String Theory by considering Afshordi's Emergent Spacetime and Evolving Dimensions model with some key insights from LQG complementing said model, creating a more concrete picture of the mechanism behind the emerging dimensions and how ultimately spacetime (and thus the true quantum gravitational field) might be actually $(2+1)$-dimensional at the Planck scale.
+We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into String Theory by considering Afshordi's model \cite{Afshordi2014Emergent} with some key insights from LQG complementing said model, creating a more concrete picture of the mechanism behind the emerging dimensions and how ultimately spacetime (and thus the true quantum gravitational field) might be actually $(2+1)$-dimensional at the Planck scale.
 

### 2024-12-02 lqg-strings.tex
Typo in title fixed
sketched beggining of solving gauged sigma model and made some corrections to Introduction in main text

@@
 
-\title{A Loop Quantm Gravity Inspired Action for the Bosonic String and a Emergent Dimensions at Large Scales}
+\title{A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
 
@@
 While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
-This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a theory of a densitized Minkowski tetrad
+This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory of a dualised $\mathfrak{sl} (2 , \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
+\begin{equation} \label{eqn:self-dual-spin-connection}
+	A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{\beta}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu}
+\end{equation}
+and its conjugate momenta
 \begin{equation} \label{eqn:densitized-tetrad}
-	\widetilde{E}^{\mu} _I = \frac{1}{\sqrt{- g}} e^{\mu} _I
-\end{equation}
-and the self-dual part of the $\sltwoc$ spin-connection
-\begin{equation} \label{eqn:self-dual-spin-connection}
-	A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{i}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu} .
-\end{equation}
+	B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K} _{[ \mu} e^{L} _{\nu ]} ,
+\end{equation}
+which when restricted to a 3-dimensional hypersurface where $* (e \wedge e) = 0$ reduces to
+\begin{equation} \label{eqn:Ashtekar-connection-canonical}
+	A^{i} _{a} = \omega ^{i} _{a} + \beta K^{i} _{a}
+\end{equation}
+\begin{equation} \label{eqn:Ashtekar-E-field-canonical}
+	E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c} ,
+\end{equation}
+with $K^{i} _{a}$ being the triad version of the extrinsic curvature $K_{a b} = \frac{1}{2} \mathcal{L}_{n} q_{a b}$ and $q$ the 3-metric.
 Ashtekar realized that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables.

### 2024-12-06 manim/surf2d.py
Playing around with manim to generate figures for the paper

@@ -1,0 +1,29 @@
+from manim import *
+
+class CurvedSurfaceExample(ThreeDScene):
+    def construct(self):
+        # Set up the scene
+        self.set_camera_orientation(phi=75 * DEGREES, theta=-30 * DEGREES)
+
+        # Create a parametric surface
+        def param_surface(u, v):
+            x = u
+            y = v
+            z = np.sin(u) * np.cos(v)
+            return np.array([x, y, z])
+
+        surface = ParametricSurface(
+            param_surface,
+            u_range=[-3, 3],
+            v_range=[-3, 3],
+            resolution=(30, 30),
+            checkerboard_colors=[BLUE_D, BLUE_E],
+            stroke_width=0.5,
+        )
+
+        # Add the surface to the scene
+        self.add(surface)
+
+        # Animate the camera
+        self.begin_ambient_camera_rotation(rate=0.1)
+        self.wait(10)

### 2024-12-07 lqg-strings.tex
added EoMs and solution of the gauged sigma model to main file

@@
 \begin{equation}\label{eqn:covariant-deriv-v1}
-	D_a X^\mu(\tau , \sigma) = \partial_a X^\mu + k \mc{A}_{a}^\mu{}_\nu X^\nu,
+	D_a X^\mu(\tau , \sigma) = \partial_a X^\mu + \mu \mc{A}_{a}^\mu{}_\nu X^\nu,
 \end{equation}
@@
 		             b^3        & j^2        & -j^1       & 0          & p^3/l \\
-		             -\ep p^0/l & -\ep p^1/l & -\ep p^2/l & -\ep p^3/l & 0
+		             \ep p^0/l & -\ep p^1/l & -\ep p^2/l & -\ep p^3/l & 0
 	             \end{pmatrix} \nonumber \\
@@
 \begin{equation}\label{eqn:covariant-deriv-v2}
-	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + k \mc{A}_{a}^A{}_B X^B.
+	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + \mu \mc{A}_{a}^A{}_B X^B.
 \end{equation}
@@
 What our discussion in this section shows, however, is that such a classical description is possible if we switch from the metric based approach to the connection based one for describing the background geometry and its coupling to the string worldsheet.
+
+\subsection{Gauged Polyakov Equations of Motion}
+
+By varying the action \eqref{eqn:poincare-polyakov}, we get two sets of constraints from the variation of $g_{a b}$ and $A_{a} ^{A B}$, namely the vanishing of the worldsheet energy-momentum and spin-linear-momentum tensors $T_{a b}$ and $\sigma _{a} ^{A B}$
+\begin{multline} \label{eqn:gauged-WS-EM-tensor}
+	T_{a b} : = \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B} - \\
+	- g_{a b} g^{c d} \mc{D}_{c} X^{A} \mc{D}_{d} X^{B} G_{A B} = 0
+\end{multline}
+\begin{equation}
+	\sigma ^{A B} _{a} : = \mc{D}_{a} X^{[A} X^{B]} = 0 .
+\end{equation}
+The former allows us to solve for the worldsheet \textquotedblleft covariant metric" $g_{a b}$ as
+\begin{equation} \label{eqn:gauged-WS-metric}
+	g_{a b} = 2 f \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B}
+\end{equation}
+where
+\begin{equation} \label{eqn:gauged-f-metric}
+	\frac{1}{f} = g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B} ,
+\end{equation}
+while the latter should allow one to solve for $\mc{A}_{a}$ in terms of $X^{A}$.
+
+The variation of the action \wrt $X^{A}$ results in the equation of motion of the embbeding fields
+\begin{multline} \label{eqn:gauged-X-EoM}
+	\mc{D}_{a} [\sqrt{- g} g^{a b} \mc{D}_{b} X^{B} G_{B C}] = \\
+	= \sqrt{g} g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} \partial _{C} G_{A B} ,
+\end{multline}
+which in worldsheet \textquotedblleft covariant conformal gauge" $g^{a b} = \e ^{- \phi} \eta ^{a b}$ and for flat background geometry $G_{A B} = \eta ' _{A B}$ with
+\begin{equation} \label{eqn:flat-bulk-metric}
+	[\eta ' _{A B}] = \begin{bmatrix} [\eta _{\mu \nu}] & 0 \\ 0 & \epsilon \end{bmatrix}
+\end{equation}
+simplifies to
+\begin{equation}
+	\eta ^{a b} \mc{D}_{a} \mc{D}_{b} X^{A} \eta ' _{A B} = 0 .
+\end{equation}
+From here on, we'll work on the case of $\ep = - 1$ (adS background), for which the above equation can be expanded as
+\begin{multline} \label{eqn:expanded-gauged-X-EoM}
+	\eta ^{a b} \big( \del _{a} \del _{b} X^{A} + 2 \mu A^{A} _{a B} \del _{b} X^{B} + \\
+	+ \mu \del _{a} A^{A} _{b B} X^{B} + \mu ^2 A^{A} _{a B} A^{B} _{b C} X^{C} \big) = 0 .
+\end{multline}
+To produce the desired bulk geometry, the background connection can be taken as
+\begin{equation} \label{eqn:adS-bulk-connection}
+	\mc{A}_{\mu} = \begin{bmatrix} 0 & 0 & 0 & 0 & \delta ^{0} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{1} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{2} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{3} _{\mu} \\ - \delta ^{0} _{\mu} & \delta ^{1} _{\mu} & \delta ^{2} _{\mu} & \delta ^{3} _{\mu} & 0 \end{bmatrix} ,
+\end{equation}
+from which the pulledback connection $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$ is thus
+\begin{equation} \label{eqn:adS-WS-connection}
+	\mc{A}_{a} = \begin{bmatrix} 0 & 0 & 0 & 0 & \del _{a} X^{0} \\ 0 & 0 & 0 & 0 & \del _{a} X^{1} \\ 0 & 0 & 0 & 0 & \del _{a} X^{2} \\ 0 & 0 & 0 & 0 & \del _{a} X^{3} \\ - \del _{a} X^{0} & \del _{a} X^{1} & \del _{a} X^{2} & \del _{a} X^{3} & 0 \end{bmatrix} ,
+\end{equation}
+whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
+\begin{multline} \label{eqn:Minkowski-sector-EoM}
+	\eta ^{a b} \del _{a} \del _{b} X^{\mu} + \\
+	+ \frac{\mu \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + k \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} = 0
+\end{multline}
+\begin{multline} \label{eqn:holographic-dim-EoM}
+	\eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} + 4 \mu \e ^{\varphi} - \\
+	- \frac{\mu ^2 \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + \mu \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} X_{\mu} = 0 .
+\end{multline}
+Assuming the perturbations on the string are small $|X^{A}| \ll 1$, we get a massive simplification
+\begin{equation} \label{eqn:simplified-Minkowski-EoM}
+	\eta ^{a b} \del _{a} \del _{b} X^{\mu} = 0
+\end{equation}
+\begin{equation} \label{eqn:simplified-holographic-EoM}
+	\eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} = - 4 \mu \e ^{\varphi} .
+\end{equation}
+Thus, the Minkowski sector behaves like regular ST for small perturbations, and for the holographic dimension we can solve using a Green's function
+\begin{equation} \label{eqn:Xr-GF}
+	X^{r} (x) = - 4 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} ,
+\end{equation}
+with the Green's function satisfying
+\begin{equation} \label{eqn:Greens-function}
+	(\del _{\sigma} ^2 - \del _{\tau} ^2 + 2 \mu ^2 \e ^{\varphi}) G (x ; x') = \delta ^2 (x , x') .
+\end{equation}
+To find this Green's function, we must fix the conformal factor to be of the form $\e ^{\varphi} = f (\tau) - g (\sigma)$, thus allowing us to separate variables in the homogeneous case of eq \eqref{eqn:Greens-function} into
+\begin{equation} \label{eqn:Green-X}
+	X^{\prime \prime} - 2 \mu ^2 g (\sigma) X = - \lambda X
+\end{equation}
+\begin{equation} \label{eqn:Green-T}
+	\ddot{T} - 2 \mu ^2 f (\tau) T = - \lambda T .
+\end{equation}
+These are Schrodinger's equations for potentials given by $\mu f (\tau)$ and $\mu g (\sigma)$, as such if we assume that $f$ and $g$ are harmonic oscillator potentials $f (\tau) = \omega ^2 \tau ^2 / 2$ and $g (\sigma) = k^2 \sigma ^2 / 2$ we can find known solutions for separation constant $\lambda = 2 \mu E = \mu k (2n + 1) = \mu \omega (2n + 1)$, so by the Spectral Theorem our separated spatial and temporal Green's functions are
+\begin{equation} \label{eqn:X-function}
+	X (\sigma , \sigma ') = \sum _{n \geq 0} - \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
+\end{equation}
+\begin{equation} \label{eqn:T-function}
+	T (\tau , \tau ') = \sum _{m \geq 0} - \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} ,
+\end{equation}
+where $X_{n}$ and $T_{m}$ are harmonic oscillator eigenfunctions. With this, the full Green's function $G = T.X$ and the solution for $X^{r}$ are thus
+\begin{equation} \label{eqn:G-function}
+	G (x ; x') = \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
+\end{equation}
+\begin{multline} \label{eqn:Xr-solution}
+	X^{r} (x) = - 4 \mu \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau)}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma)}{\mu k (2 n + 1)} \times \\
+	\times \int \diff ^2 x' T_{m} (\tau ') X_{n} (\sigma ') \left( \frac{\omega ^2 \tau ^{\prime 2}}{2} - \frac{k^2 \sigma ^{\prime 2}}{2} \right) .
+\end{multline}
 
@@
 \end{equation}
-Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
+Another candidate for what the vector excitations could relate to is the Ashtekar electric field $\widetilde{E}^{\mu} _{I}$,
 \begin{equation} \label{eqn:AEF-string-vector-excitation}

### 2025-02-25 lqg-strings.tex
did some minor tweak to the solution of the gauged model and very minor stuff in discussion

@@
 \end{equation}
-from which the pulledback connection $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$ is thus
-\begin{equation} \label{eqn:adS-WS-connection}
-	\mc{A}_{a} = \begin{bmatrix} 0 & 0 & 0 & 0 & \del _{a} X^{0} \\ 0 & 0 & 0 & 0 & \del _{a} X^{1} \\ 0 & 0 & 0 & 0 & \del _{a} X^{2} \\ 0 & 0 & 0 & 0 & \del _{a} X^{3} \\ - \del _{a} X^{0} & \del _{a} X^{1} & \del _{a} X^{2} & \del _{a} X^{3} & 0 \end{bmatrix} ,
-\end{equation}
-whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
+from which the pulledback connection is $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$, whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
 \begin{multline} \label{eqn:Minkowski-sector-EoM}
@@
 \end{equation}
-Thus, the Minkowski sector behaves like regular ST for small perturbations, and for the holographic dimension we can solve using a Green's function
-\begin{equation} \label{eqn:Xr-GF}
-	X^{r} (x) = - 4 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} ,
-\end{equation}
-with the Green's function satisfying
-\begin{equation} \label{eqn:Greens-function}
-	(\del _{\sigma} ^2 - \del _{\tau} ^2 + 2 \mu ^2 \e ^{\varphi}) G (x ; x') = \delta ^2 (x , x') .
-\end{equation}
-To find this Green's function, we must fix the conformal factor to be of the form $\e ^{\varphi} = f (\tau) - g (\sigma)$, thus allowing us to separate variables in the homogeneous case of eq \eqref{eqn:Greens-function} into
-\begin{equation} \label{eqn:Green-X}
-	X^{\prime \prime} - 2 \mu ^2 g (\sigma) X = - \lambda X
-\end{equation}
-\begin{equation} \label{eqn:Green-T}
-	\ddot{T} - 2 \mu ^2 f (\tau) T = - \lambda T .
-\end{equation}
-These are Schrodinger's equations for potentials given by $\mu f (\tau)$ and $\mu g (\sigma)$, as such if we assume that $f$ and $g$ are harmonic oscillator potentials $f (\tau) = \omega ^2 \tau ^2 / 2$ and $g (\sigma) = k^2 \sigma ^2 / 2$ we can find known solutions for separation constant $\lambda = 2 \mu E = \mu k (2n + 1) = \mu \omega (2n + 1)$, so by the Spectral Theorem our separated spatial and temporal Green's functions are
-\begin{equation} \label{eqn:X-function}
-	X (\sigma , \sigma ') = \sum _{n \geq 0} - \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
-\end{equation}
-\begin{equation} \label{eqn:T-function}
-	T (\tau , \tau ') = \sum _{m \geq 0} - \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} ,
-\end{equation}
-where $X_{n}$ and $T_{m}$ are harmonic oscillator eigenfunctions. With this, the full Green's function $G = T.X$ and the solution for $X^{r}$ are thus
-\begin{equation} \label{eqn:G-function}
-	G (x ; x') = \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
-\end{equation}
-\begin{multline} \label{eqn:Xr-solution}
-	X^{r} (x) = - 4 \mu \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau)}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma)}{\mu k (2 n + 1)} \times \\
-	\times \int \diff ^2 x' T_{m} (\tau ') X_{n} (\sigma ') \left( \frac{\omega ^2 \tau ^{\prime 2}}{2} - \frac{k^2 \sigma ^{\prime 2}}{2} \right) .
-\end{multline}
+Thus, the Minkowski sector behaves like regular ST for small perturbations, while the holographic coordinate $X^{r}$ follows a variable-mass Klein-Gordon equation with source.
+Now it should be clear why the choice of $\mu$ for the coupling constant, since in \eqref{eqn:simplified-holographic-EoM} it appears (together with the conformal factor) as a mass term for our perturbation.
+Eq \eqref{eqn:simplified-holographic-EoM} can be solved using the 1d wave equation Green's function to build a perturbation around the homogenous wave equation solution
+\begin{multline} \label{eqn:holo-sol-implicit}
+	X^{r} (x) = X^{r} _{0} (x) - \\ - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) = \\ = X^{r} _{0} (x) + \delta X^{r} (x),
+\end{multline}
+where $X^{r} _{0}$ is a solution for the homogenous wave equation
+\begin{equation} \label{eqn:homo-wave-eqn}
+	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) X^{r} _{0} = 0
+\end{equation}
+and $G (x ; x') = \frac{1}{2} \Theta (\tau - \tau ' - |\sigma - \sigma '|)$ its Green's function
+\begin{equation} \label{eqn:homo-wave-eqn-GF}
+	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) G (x ; x') = \delta ^{2} (x ; x') .
+\end{equation}
+From \eqref{eqn:holo-sol-implicit}, a recursion can be built, leading to a more explicit form
+\begin{multline}
+	X^{r} (x) = X^{r} _{0} (x) + \\ + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \\ \times (2 + \mu X^{r} _{0} (x^{(k)})) ,
+\end{multline}
+with $x^{(0)} \equiv x$.
 
@@
 \end{equation}
-Another candidate for what the vector excitations could relate to is the Ashtekar electric field $\widetilde{E}^{\mu} _{I}$,
+Another candidate for what the vector excitations could relate to is the $D = 3 + 1$ Ashtekar electric field $\widetilde{E}^{a} _{i}$,
 \begin{equation} \label{eqn:AEF-string-vector-excitation}
-	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
+	\widetilde{E}^{a} _{i} \sim (\Hat{a}^{a} _{i})^{\dagger} \ket{0} .
 \end{equation}

### 2025-07-01 AoP/response-to-referee.tex
T2: Add background independence footnotes to Introduction to address referee request
- Added two footnotes addressing reviewer concerns about recent developments in non-perturbative string theory and background independence. Includes 5 new references (Hohm 2017/2018, Maccaferri 2024, Read 2023, Sen-Zwiebach 1994) highlighting recent critiques and advances in string field theory. Progress: T2 steps 1-3 partially complete.
- Removed latex artefacts and added ot gitignore
- Updated memory bank

\documentclass{article}
\def\lettertitle{Author Response to Reviews of}
\def\papertitle{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
\def\authors{Deepak Vaid and Luigi Teixeira de Sousa}
\def\journal{Annals of Physics}
\def\doi{AOP 81029}

\input{AR_to_RC.tex}

We thank the referee for their thorough and constructive review of our manuscript. We have carefully considered all the points raised and provide detailed responses below.

\section{Reviewer \#1}

\subsection{Introduction}

\RC The introduction contrasts string theory and LQG, highlighting their respective strengths and limitations. The discussion of background independence in string theory could benefit from references to more recent critiques or developments such as recent advances in non-perturbative string theory.

\AR We have added the following two footnotes with references to recent critiques of string theory's background independence \cite{Hohm2017Background,Hohm2018Background} and recent advances in non-perturbative string theory \cite{Maccaferri2024String,Sen1994Quantum}:

\emph{Recent work has highlighted fundamental challenges to achieving manifest background independence in string theory. Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance when higher-derivative corrections are included \cite{Hohm2017Background,Hohm2018Background}.}

\emph{Developments in string field theory continue to address these foundational issues \cite{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory. For an overview of the general concept of background independence in quantum gravity see \cite{Read2023Background}.}

\RC The "central dogma" (minimal area $\Delta$) is well-motivated from LQG but could be better contextualized within existing string theory literature, where minimal length scales are discussed. The paper's goals are clearly stated, but the transition to the modified Nambu-Goto action feels abrupt, a smoother connection between LQG's area quantization and the string action would improve this.

\AR

\subsection{Section 2 - Part (a): Action Justification}

\RC The proposed action $S_{MNG}=-T\int dx^2\sqrt{-(h+k \Delta)}$ needs a clearer justification: the author states in a footnote that $\Delta$ is as a scalar density later identified with the Kalb-Ramond field should be, at least, physically justified because the remaining of this section is based in this argument, otherwise it should be rigorously derived.

\AR

\subsection{Section 2 - Part (b): Expansion Parameter}

\RC The expansion in $k=l_{pl}/l_s$ seems sound, but the assumption $k\ll 1$ (Planck scale much smaller than string scale) should be discussed further—does this hold in all regimes?

\AR

\subsection{Section 2 - Part (c): Duality Interpretation}

\RC The duality between $h_{ab}$ and $h^{ab}$ (Eq. 2.6a-2.6c) is intriguing but lacks a deeper physical interpretation. How does this duality manifest in observable string dynamics?

\AR

\subsection{Section 3 - Part (a): Bimetric String and Ghost Avoidance}

\RC The author introduces the connection to bimetric gravity, but the analogy should be strengthened by discussing how the bimetric string avoids issues like the Boulware-Deser ghost.

\AR

\subsection{Section 3 - Part (b): Kalb-Ramond Field Connection}

\RC The link between $\Delta_{ab}$ and the Kalb-Ramond field $B_{\mu\nu}$ (Sec. 3.2) is a highlight, but the derivation of Eq. (3.21) should be detailed for clarity.

\AR

\subsection{Section 3 - Part (c): Bimetric Gravity Background}

\RC The section assumes familiarity with bimetric gravity, a brief review of key concepts would aid readers outside this niche.

\AR

\subsection{Section 4 - Part (a): Physical Meaning of Coupling}

\RC In equations (4.7-4.10) the physical meaning of the coupling between $\phi(x)$, $\Delta$ and $X^\mu$ (akin to a dilaton) needs a more thorough explanation.

\AR

\subsection{Section 4 - Part (b): Born-Infeld Analogy}

\RC The Born-Infeld analogy (Sec. 4.2) should address why the Kalb-Ramond field must be exact.

\AR

\subsection{Section 5 - Part (a): Anomaly-Free Claims}

\RC The covariant quantization procedure seems correct, but the absence of anomalies (Sec. 5.12) is a significant claim that deserves more discussion. How does this compare to standard string theory?

\AR

\subsection{Section 5 - Part (b): Mode Truncation}

\RC The truncation of modes $\alpha_\mu^\nu =0$ for $|n|>d$ due to discreteness needs validation—does this align with other approaches to quantum gravity?

\AR

\subsection{Section 5 - Part (c): Table 1 Context}

\RC Table 1 (values of $a$ for different $D$ and $\mu$) lacks context. A brief explanation of how these values affect the string spectrum would help.

\AR

\subsection{Section 6 - Part (a): Afshordi Model Connection}

\RC The link to Afshordi's model is interesting, but the constraints on $m_\mu$ (Eq. 6.3) feel ad hoc, a better and deeper connection to LQG's discreteness would strengthen this section.

\AR

\subsection{Section 6 - Part (b): Fundamental Spacetime Dimensionality}

\RC The suggestion of (2+1)-dimensional fundamental spacetime (Sec. 6) is speculative and should be better addressed, more evidence or references to support this claim are needed.

\AR

\subsection{Section 7 - Part (a): Holographic Dimension Interpretation}

\RC The physical interpretation of the emergent holographic dimension $X^r$ as a "scaling dimension" needs clarification.

\AR

\subsection{Section 7 - Part (b): AdS/CFT Connection}

\RC The connection to AdS/CFT (Sec. 7.2) lacks concrete evidence, how does this classical construction relate to the original Maldacena's duality?

\AR

\subsection{Discussion - Part (a): Open Questions}

\RC The discussion synthesizes the paper's key results but could better highlight open questions (e.g., experimental signatures, relation to black hole physics), considering the ideas established in the manuscript.

\AR

\subsection{Discussion - Part (b): Anomaly-Free and Ghost-Free Claims}

\RC The claim that the model is anomaly-free and ghost-free (Sec. 5) should be tempered with caveats (e.g., limitations of the truncation scheme).

\AR

\subsection{General: Writing and Typos}

\RC A full review should be done to the writing to correct typos.

\AR

\section{Summary of Major Changes}

% This section will be filled once revisions are complete
\begin{enumerate}
    \item 
    \item 
    \item 
\end{enumerate}

\section{Submission Requirements}

We confirm that we will submit the following files with our revision:
\begin{itemize}
    \item Manuscript source files (LaTeX format)
    \item Figure source files in acceptable formats (TIFF, EPS)
    \item Highlights file (3-5 bullet points, maximum 85 characters each)
\end{itemize}

\bibliographystyle{JHEP3}

\bibliography{../lqg-strings.bib}

\end{document}

### 2025-07-01 lqg-strings.tex
T2: Add background independence footnotes to Introduction to address referee request
- Added two footnotes addressing reviewer concerns about recent developments in non-perturbative string theory and background independence. Includes 5 new references (Hohm 2017/2018, Maccaferri 2024, Read 2023, Sen-Zwiebach 1994) highlighting recent critiques and advances in string field theory. Progress: T2 steps 1-3 partially complete.
- Removed latex artefacts and added ot gitignore
- Updated memory bank

@@
 
-Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
+Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
 We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.
@@
 Such a theory should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry.
-On the face of it, string theory, at least in its conventional form, does not satisfy this principle.
+On the face of it, string theory, at least in its conventional form, does not satisfy this principle \footnote{Recent work has highlighted fundamental challenges to achieving manifest background independence in string theory.
+Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance when higher-derivative corrections are included \cite{Hohm2017Background,Hohm2018Background}.}.
 The great virtue of LQG on the other hand, is that it respects background independence by construction and proceeds to quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.
@@
 The fixed point of this analysis, remarkably enough, requires one to impose the condition that the background metric obeys Einstein's field equations (more precisely that the background is \emph{Ricci flat}.
-This is explained in greater detail in Appendix \ref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent.
+This is explained in greater detail in Appendix \ref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent\footnote{However, developments in string field theory continue to address these foundational issues \cite{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory.
+For an overview of the general concept of background independence in quantum gravity see \cite{Read2023Background}.}.
 Our reasons are the following:

### 2025-07-01 AoP/response-to-referee.tex
T2 - Complete Introduction section reviewer response
- Change response document citation format to author-year with square brackets
- Add bridging text connecting LQG area quantization to modified Nambu-Goto action
- Include 6 foundational minimal length string theory references
- Address reviewer concerns about abrupt transition and contextualization
- Update T2 progress: Introduction section complete (step 3/13)
- Update memory bank

@@
 \documentclass{article}
+\usepackage[square,comma]{natbib}
 \def\lettertitle{Author Response to Reviews of}
@@
 
-\AR We have added the following two footnotes with references to recent critiques of string theory's background independence \cite{Hohm2017Background,Hohm2018Background} and recent advances in non-perturbative string theory \cite{Maccaferri2024String,Sen1994Quantum}:
+\AR We have added the following two footnotes with references to recent critiques of string theory's background independence \citep{Hohm2017Background,Hohm2018Background} and recent advances in non-perturbative string theory \citep{Maccaferri2024String,Sen1994Quantum}:
 
 \emph{Recent work has highlighted fundamental challenges to achieving manifest background independence in string theory.
-Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance when higher-derivative corrections are included \cite{Hohm2017Background,Hohm2018Background}.}
+Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance when higher-derivative corrections are included \citep{Hohm2017Background,Hohm2018Background}.}
 
-\emph{Developments in string field theory continue to address these foundational issues \cite{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory.
-For an overview of the general concept of background independence in quantum gravity see \cite{Read2023Background}.}
+\emph{Developments in string field theory continue to address these foundational issues \citep{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory.
+For an overview of the general concept of background independence in quantum gravity see \citep{Read2023Background}.}
 
@@
 
-\AR
+\AR We have added the following paragraphs, including the new references \citep{Amati1989Canb,Chang2011Minimal,Gross1987Highenergy,Gross1988String,Yoneya1989Interpretation,Yoneya2000String}, after the central dogma statement, in order to make the transition between LQG's area quantization and the modified Nambu-Goto action smoother and to include a comparison with previous minimal length proposals in string theory:
+
+\emph{The key insight is to translate this fundamental discreteness of area from spacetime geometry to the worldsheet of the string itself.
+In LQG, the eigenvalues of the area operator are discrete, meaning physical areas can only take values from a quantized spectrum with minimum eigenvalue $\Delta$.
+For a string worldsheet, this suggests that the total worldsheet area $\mathcal{A} = \int d^2\sigma \sqrt{-h}$ cannot be arbitrarily small but must satisfy $\mathcal{A} \geq \Delta$.}
+
+\emph{Rather than imposing this constraint externally, we incorporate it directly into the action by modifying the area element itself.
+The natural way to ensure the worldsheet area respects LQG's minimal area is to replace the standard area element $\sqrt{-h}$ with $\sqrt{-(h+k\Delta)}$ where $k = l_{pl}/l_s$ is the ratio of Planck to string scales.
+This modification has several appealing features: it reduces to the standard Nambu-Goto action when $k \to 0$, it ensures the worldsheet area can never become arbitrarily small, and it provides a concrete mechanism to incorporate LQG's geometric quantization into string theory.}
+
+\emph{This approach differs from previous minimal length proposals in string theory \citep{Amati1989Canb,Chang2011Minimal,Gross1987Highenergy,Gross1988String,Yoneya1989Interpretation,Yoneya2000String} in that it specifically targets area rather than length, reflecting LQG's emphasis on area as the fundamental geometric observable.}
 
@@
 
-\bibliographystyle{JHEP3}
+\bibliographystyle{apalike}
 

### 2025-07-01 lqg-strings.tex
T2 - Complete Introduction section reviewer response
- Change response document citation format to author-year with square brackets
- Add bridging text connecting LQG area quantization to modified Nambu-Goto action
- Include 6 foundational minimal length string theory references
- Address reviewer concerns about abrupt transition and contextualization
- Update T2 progress: Introduction section complete (step 3/13)
- Update memory bank

@@
 
-Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
+Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}
+
+The key insight is to translate this fundamental discreteness of area from spacetime geometry to the worldsheet of the string itself.
+In LQG, the eigenvalues of the area operator are discrete, meaning physical areas can only take values from a quantized spectrum with minimum eigenvalue $\Delta$.
+For a string worldsheet, this suggests that the total worldsheet area $\mathcal{A} = \int d^2\sigma \sqrt{-h}$ cannot be arbitrarily small but must satisfy $\mathcal{A} \geq \Delta$.
+
+Rather than imposing this constraint externally, we incorporate it directly into the action by modifying the area element itself.
+The natural way to ensure the worldsheet area respects LQG's minimal area is to replace the standard area element $\sqrt{-h}$ with $\sqrt{-(h+k\Delta)}$ where $k = l_{pl}/l_s$ is the ratio of Planck to string scales.
+This modification has several appealing features: it reduces to the standard Nambu-Goto action when $k \to 0$, it ensures the worldsheet area can never become arbitrarily small, and it provides a concrete mechanism to incorporate LQG's geometric quantization into string theory.
+
+This approach differs from previous minimal length proposals in string theory \cite{Amati1989Canb,Chang2011Minimal,Gross1987Highenergy,Gross1988String,Yoneya1989Interpretation,Yoneya2000String} in that it specifically targets area rather than length, reflecting LQG's emphasis on area as the fundamental geometric observable.
+
+We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
 We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.

### 2025-07-02 AoP/response-to-referee.tex
T2: Address referee's Section 2 concerns: action justification, parameter validity, duality interpretation
- Added acknowledgment of ansatz nature in manuscript after S_MNG equation
- Justified k<<1 expansion using LQG spin network emergence picture
- Connected h_ab/h^ab duality to T/S-duality framework as novel feature
- Completed reviewer responses for Section 2(a), 2(b), 2(c) with physical justifications
- Added Luigi's bachelor thesis files
- Updated memory bank

@@
 
-\AR
+\AR We must be honest and state that at present the area modified action is not rigorously derived.
+We have added a paragraph right after the action area-modified action (eqn 2.2.
+in the text) to explain this point:
+
+\emph{At present we do not have a rigorous derivation of this expression.
+It is the simplest possible ansatz one can think of to encode the insight from LQG that at the Planck scale there is a minimum quantum of area.
+What makes us more confident in this ansatz is that it is consistent with the Kalb-Ramond field identification and the minimal area interpretation of the scalar density $\Delta$.
+However, this was not known prior to coming up with the ansatz and only discovered after the fact.}
 
@@
 
-\AR
+\AR We've added the following paragraph right after the expansion parameter $k$ definition to explain our choice of $k \ll 1$:
+
+\emph{If we take $k$ to be an expansion parameter, then it follows that it should also be small.
+The physical justification for this is the following picture.
+The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams.
+The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures.
+In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network.
+When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - i.e.
+where geometry itself is fully quantum - is required.}
 
@@
 
-\AR
+\AR We have added the following paragraph which hopefully addresses this point:
+
+\emph{This duality is reminiscent of, but also distinct from, the T and S dualities in string theory.
+In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$.
+In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$.
+In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$.
+This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.}
 

### 2025-07-02 lqg-strings.tex
T2: Address referee's Section 2 concerns: action justification, parameter validity, duality interpretation
- Added acknowledgment of ansatz nature in manuscript after S_MNG equation
- Justified k<<1 expansion using LQG spin network emergence picture
- Connected h_ab/h^ab duality to T/S-duality framework as novel feature
- Completed reviewer responses for Section 2(a), 2(b), 2(c) with physical justifications
- Added Luigi's bachelor thesis files
- Updated memory bank

@@
 \end{equation}
+At present we do not have a rigorous derivation of this expression.
+It is the simplest possible ansatz one can think of to encode the insight from LQG that at the Planck scale there is a minimum quantum of area.
+What makes us more confident in this ansatz is that it is consistent with the Kalb-Ramond field identification and the minimal area interpretation of the scalar density $\Delta$.
+However, this was not known prior to coming up with the ansatz and only discovered after the fact.
+
 Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}.
@@
 \end{equation}
-Presumably the limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
+
+If we take $k$ to be an expansion parameter, then it follows that it should also be small.
+The physical justification for this is the following picture.
+The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams.
+The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures.
+In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network.
+When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - i.e.
+where geometry itself is fully quantum - is required.
+
+The limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
 Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(k^2/h^2)$ corrections.
@@
 (or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
-This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.
+
+This duality is reminiscent of, but also distinct from, the T and S dualities in string theory.
+In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$.
+In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$.
+In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$.
+This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.
 

### 2025-07-02 AoP/response-to-referee.tex
feat: T2 - complete sections 3-4 reviewer responses for AOP submission
- Add bimetric ghost limitation acknowledgment in manuscript
- Expand dilaton coupling explanation after eq 4.10
- Remove tangential exactness discussion from Born-Infeld section
- Complete all section 3-4 response document entries
- Ready for section 5 reviewer responses
- Updated memory bank

@@
 
-\AR
+\AR We had already mentioned the Boulware-Deser ghost avoidance in Section 2, right after the section when we talk about duality between the area metric and its inverse.
+As for how this would affect string theory, we feel that a proper discussion of this issue would be beyond the scope of this paper and would require a separate paper in its own right.
+We have added the following paragraph in Section 3 addressing this point, right after "Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''":
+
+\emph{As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware-Deser ghost in theories of massive gravity.
+However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.}
 
@@
 
-\AR
+\AR \AR The derivation of the relation between $\Delta_{ab}$ and the Kalb-Ramond field $B_{\mu\nu}$ is detailed in Section 4a, specifically in equations (4.12) and (4.13).
+Equation (4.12) shows the area-corrected string action coupled to the Kalb-Ramond field, while equation (4.13) demonstrates that by varying this action with respect to $\Delta^{cd}$, we obtain $\Delta_{cd} = \widetilde{f} \partial_c X^\mu \partial_d X^\nu B_{\mu\nu}$, establishing the explicit connection between the worldsheet quantum of area tensor and the pullback of the bulk Kalb-Ramond field.
 
@@
 
-\AR
+\AR We agree that a comprehensive review of bimetric gravity would aid readers unfamiliar with this area.
+However, we feel that including such a review would take the paper too far afield from its main focus on the LQG-inspired string action.
+We have provided the key reference to seminal works \citep{de-Rham2011Resummation, Hassan2012Bimetric} for readers who wish to explore bimetric gravity in greater detail.
 
@@
 
-\AR
+\AR We have expanded the paragraph following eqn 4.10, from the following:
+
+\emph{revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \citep{Balthazar-t-backgrounds}.}
+
+to:
+
+\emph{revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields.
+The coupling term $\frac{(2\partial_a \phi - \partial_a \ln(\Delta))}{\frac{2e^{2\phi}}{k\Delta} - 1}$ shows how the area quantization correction modifies the propagation of embedding coordinates - the numerator combines gradients from both conformal and quantum geometric effects, while the denominator represents the modification to the wave operator due to LQG's minimal area constraint.
+This behavior is much akin to the dilaton field \citep{Balthazar-t-backgrounds}.}
 
@@
 
-\AR
+\AR The mention of exactness in the Born-Infeld analogy section is an additional observation rather than a requirement for the analogy itself.
+The core point is the structural similarity between our area-corrected action and the Born-Infeld form, where $\Delta _{ab}$ plays the role of a field strength.
+The exactness condition and its implications for background torsion, while potentially interesting, are not essential to this analogy and can be omitted without affecting the main argument.
+We have accordingly edited the paragraph following eqn 4.10 to omit the reference to exactness and torsion, from:
+
+\emph{thus the action (2.2) can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{ab}$ the role of the pullback of a field strength.
+Since we explored the relation between $\Delta _{ab}$ and the Kalb-Ramond field $B_{\mu \nu}$ in Section 4A, this could mean that the Kalb-Ramond 2-form is exact, $B = d A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $d B = d (d A) = 0$.
+Also, we have a direct relation between string tension and scale ...}
+
+to:
+
+\emph{thus the action (2.2) can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{ab}$ the role of the pullback of a field strength.
+Also, we have a direct relation between string tension and scale ...}
 

### 2025-07-02 lqg-strings.tex
feat: T2 - complete sections 3-4 reviewer responses for AOP submission
- Add bimetric ghost limitation acknowledgment in manuscript
- Expand dilaton coupling explanation after eq 4.10
- Remove tangential exactness discussion from Born-Infeld section
- Complete all section 3-4 response document entries
- Ready for section 5 reviewer responses
- Updated memory bank

@@
 
+As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware-Deser ghost in theories of massive gravity.
+However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.
+
 The second possibility is the following.
@@
 thus the action \eqref{eqn:ng-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
-Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
 Also, we have a direct relation between string tension and scale

### 2025-07-05 AoP/response-to-referee.tex
feat: T2 - Complete Section 5 reviewer responses for AOP manuscript
- Add anomaly clarification in main text explaining finite mode truncation
- Add mode truncation physical motivation from LQG discreteness
- Add Table 1 context showing parameter effects on string spectrum
- Complete Section 5(a-c) responses in referee document
- Connect parameter μ to discreteness cutoff controlling modes
- Address reviewer concerns about quantization claims vs standard string theory
- Updated memory bank

@@
 
-\AR
+\AR We have added the following two paragraphs at the end of Section 5, after the sentence ``... and no negative-norm states in physical processes.'':
+
+\emph{It is important to clarify what we mean by ``no anomalies'' in this context.
+This refers specifically to the absence of central charge anomalies in our modified Virasoro-like algebra, which arises due to the finite mode truncation imposed by LQG's discreteness.
+This discreteness is encoded in the paramter $\mu$ in (4.27), which is a cutoff parameter that controls the maximum number of modes we consider in the action.}
+
+\emph{This differs fundamentally from standard string theory, where anomaly cancellation requires critical dimensions ($D = 26$ for bosonic strings) to ensure vanishing of the central charge from an infinite sum over modes.
+Our finite sum naturally avoids this constraint, permitting unconstrained background dimensionality $D$.
+However, this result applies specifically to our truncated model in the regime where $k \ll 1$, where the smooth worldsheet approximation remains valid.
+In the full quantum gravitational regime where $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and a more comprehensive analysis would be required.}
 
@@
 
-\AR
+\AR We have added the following two paragraphs to clarify the issues regarding mode truncation and comparison with other quantum gravity approaches:
+
+\emph{The mode truncation is a key assumption that requires validation.
+While we do not have a rigorous derivation from first principles, the physical motivation comes from LQG's discrete structure: high-frequency modes corresponding to sub-Planckian physics should be suppressed when the spin network discreteness becomes relevant.
+The parameter $\mu$ in (4.27) provides an effective energy cutoff, with modes $|n| > d \approx \mu$ being suppressed.}
+
+\emph{This approach shares similarities with other discrete quantum gravity approaches like causal dynamical triangulation and spin foam models, which also impose natural cutoffs.
+However, a complete justification would require deriving this truncation directly from LQG's canonical quantization procedure, which remains an open question for future work.}
 
@@
 
-\AR
+\AR We have added the following clarifying paragraph right after the table in the text:
+
+\emph{This table shows that $a$ becomes more negative as either the spacetime dimension $D$ or the mass parameter $\mu$ increases. This means:}
+
+\begin{itemize}
+	\item \emph{Higher dimensions lead to more massive ground states}
+	\item \emph{Larger $\mu$ (stronger discreteness effects) also increases ground state masses}
+	\item \emph{The spectrum becomes increasingly separated from the massless limit}
+\end{itemize}
+
+\emph{For example, in $D=2$ with $\mu=1$, $a=-4.24$ gives a relatively light spectrum, while $D=3$ with $\mu=5$ yields $a=-34.27$, producing much heavier states.
+This demonstrates how LQG's discreteness parameter $\mu$ and the background dimensionality jointly control the departure from standard string theory's massless spectrum, with stronger quantum geometric effects pushing all states away from the massless limit expected in conventional string theory.}
 

### 2025-07-05 lqg-strings.tex
feat: T2 - Complete Section 5 reviewer responses for AOP manuscript
- Add anomaly clarification in main text explaining finite mode truncation
- Add mode truncation physical motivation from LQG discreteness
- Add Table 1 context showing parameter effects on string spectrum
- Complete Section 5(a-c) responses in referee document
- Connect parameter μ to discreteness cutoff controlling modes
- Address reviewer concerns about quantization claims vs standard string theory
- Updated memory bank

@@
 
+This table shows that $a$ becomes more negative as either the spacetime dimension $D$ or the mass parameter $\mu$ increases. This means:
+
+\begin{itemize}
+	\item Higher dimensions lead to more massive ground states
+	\item Larger $\mu$ (stronger discreteness effects) also increases ground state masses
+	\item The spectrum becomes increasingly separated from the massless limit
+\end{itemize}
+
+For example, in $D=2$ with $\mu=1$, $a=-4.24$ gives a relatively light spectrum, while $D=3$ with $\mu=5$ yields $a=-34.27$, producing much heavier states.
+This demonstrates how LQG's discreteness parameter $\mu$ and the background dimensionality jointly control the departure from standard string theory's massless spectrum, with stronger quantum geometric effects pushing all states away from the massless limit expected in conventional string theory.
+
 The commutation relations between the constraints are inherited by the Poisson brackets
@@
 
-Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we got similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
+Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we get similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
+
+It is important to clarify what we mean by ``no anomalies'' in this context.
+This refers specifically to the absence of central charge anomalies in our modified Virasoro-like algebra, which arises due to the finite mode truncation imposed by LQG's discreteness.
+This discreteness is encoded in the paramter $\mu$ in \eqref{eqn:mu-constraint-1}, which is a cutoff parameter that controls the maximum number of modes we consider in the action.
+
+This differs fundamentally from standard string theory, where anomaly cancellation requires critical dimensions ($D = 26$ for bosonic strings) to ensure vanishing of the central charge from an infinite sum over modes.
+Our finite sum naturally avoids this constraint, permitting unconstrained background dimensionality $D$.
+However, this result applies specifically to our truncated model in the regime where $k \ll 1$, where the smooth worldsheet approximation remains valid.
+In the full quantum gravitational regime where $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and a more comprehensive analysis would be required.
+
+The mode truncation is a key assumption that requires validation.
+While we do not have a rigorous derivation from first principles, the physical motivation comes from LQG's discrete structure: high-frequency modes corresponding to sub-Planckian physics should be suppressed when the spin network discreteness becomes relevant.
+The parameter $\mu$ in \eqref{eqn:mu-constraint-1} provides an effective energy cutoff, with modes $|n| > d \approx \mu$ being suppressed.
+
+This approach shares similarities with other discrete quantum gravity approaches like causal dynamical triangulation and spin foam models, which also impose natural cutoffs.
+However, a complete justification would require deriving this truncation directly from LQG's canonical quantization procedure, which remains an open question for future work.
 

### 2025-07-05 AoP/response-to-referee.tex
feat(T2): Complete Section 6-7 reviewer responses - Afshordi limitations & holographic clarification
- Acknowledge lack of rigorous LQG derivation for Afshordi constraints, extend caveats to (2+1)D speculation
- Clarify X^r scaling dimension via transformation properties, connect AdS/CFT with appropriate limitations
- Progress: 9/13 steps complete, ready for Discussion improvements
- Updated memory bank

@@
 
-\AR
+\AR We acknowledge the reviewer's concern that the constraints on $m_\mu$ (Eq.
+6.3) appear ad hoc.
+Upon reflection, we must be honest that a rigorous connection between Afshordi's mass parameters and LQG's fundamental discreteness has not yet been established.
+We have added the following two paragraphs to the text right after ``...
+making it possible to predict in which scales the other dimensions should start to open up.''
+
+\emph{Our constraint equation (6.3) represents an attempt to bridge Afshordi's phenomenological emergent dimension model with LQG's general prediction of modified physics at the Planck scale.
+However, the specific form of these constraints and their derivation from first-principles LQG remains an open problem.
+While both frameworks involve discreteness - Afshordi's through hierarchical mass parameters and LQG through quantized geometric operators - establishing a concrete mathematical connection requires significantly more work.}
+
+\emph{This represents an important limitation of our current approach and highlights the need for future research to either derive such constraints from canonical LQG or develop alternative frameworks that more naturally incorporate both emergent dimensions and quantum geometric discreteness.
+Similar caveats also apply to our suggestion that (6.3) should imply that spacetime is $(2 + 1)$-dimensional.}
 
@@
 
-\AR
+\AR We hope that the last sentence of the second paragraph in the previous point address this point.
 
@@
 
-\AR
+\AR We acknowledge that the interpretation of $X^r$ as a "scaling dimension" requires clearer explanation.
+We have added the following clarifying paragraph at the end of section 7B ``Gauging Translations'':
+
+\emph{The interpretation of $X^r$ as a "scaling dimension" follows directly from the transformation properties of the enlarged coordinate system.
+In equations (7.5) and (7.6), we introduce $X^r$ as an auxiliary coordinate needed to close the Poincaré algebra, initially fixing $X^r = 1$.
+However, when $X^r$ is allowed to vary from this reference value, the transformation properties show that the other coordinates $X^\mu$ undergo scale transformations.
+Specifically, in the enlarged coordinate system, physical coordinates can be interpreted as $x^\mu = X^\mu / X^r$, so variations in $X^r$ directly correspond to scaling transformations of the physical coordinates.
+This provides a concrete mathematical justification for interpreting $X^r$ as a scaling dimension - it is precisely the coordinate that controls the scale of the embedding.
+This geometric scaling property is what allows our construction to naturally accommodate the holographic principle, where the extra dimension encodes information about scales in the lower-dimensional theory.}
 
@@
 
-\RC The connection to AdS/CFT (Sec. 7.2) lacks concrete evidence, how does this classical construction relate to the original Maldacena's duality?
+\RC The AdS/CFT connection (Sec. 7.2) lacks concrete evidence, how does this classical construction relate to the original Maldacena's duality?
 
-\AR
+\AR We have clarified this point by adding the following text at the end of Section 7C, right after `` ... for describing the background geometry and its coupling to the string worldsheet.''
+
+\emph{The key observation which enables this is that $X^r$ behaves as a scaling or ``holographic'' dimension as explained at the end of Sec 7B.}
+
+\emph{Our classical construction provides a geometric framework that naturally incorporates key features of the AdS/CFT correspondence.
+The scaling dimension $X^r$ introduced through the mathematical necessity of closing the Poincaré algebra plays a role analogous to the radial coordinate in AdS space.
+Just as in AdS/CFT where the radial direction encodes the energy scale of the boundary theory, variations in our $X^r$ coordinate directly control the scale transformations of the bulk coordinates $X^\mu$.
+This creates a natural holographic setup where information about different energy scales in the ``boundary'' ($X^r = \text{constant}$ surfaces) is encoded in the ``bulk'' (the extended geometry with the extra $X^r$ dimension).}
+
+\emph{However, our construction differs from standard AdS/CFT in several important ways: (1) it emerges at the classical level from gauge theory requirements rather than from quantum/non-perturbative effects, (2) the holographic direction arises from the string action itself rather than being an external bulk geometry, and (3) the correspondence is between worldsheet dynamics and the extended embedding space rather than between a boundary CFT and bulk gravity.
+While this provides a concrete classical realization of holographic principles, establishing a precise correspondence with Maldacena's duality would require demonstrating how our construction reproduces the specific correlation functions and scaling behaviors characteristic of AdS/CFT, which remains an open challenge for future work.}
 

### 2025-07-05 lqg-strings.tex
feat(T2): Complete Section 6-7 reviewer responses - Afshordi limitations & holographic clarification
- Acknowledge lack of rigorous LQG derivation for Afshordi constraints, extend caveats to (2+1)D speculation
- Clarify X^r scaling dimension via transformation properties, connect AdS/CFT with appropriate limitations
- Progress: 9/13 steps complete, ready for Discussion improvements
- Updated memory bank

@@
 
+Our constraint equation (\ref{eqn:X-masses-constraint}) represents an attempt to bridge Afshordi's phenomenological emergent dimension model with LQG's general prediction of modified physics at the Planck scale.
+However, the specific form of these constraints and their derivation from first-principles LQG remains an open problem.
+While both frameworks involve discreteness - Afshordi's through hierarchical mass parameters and LQG through quantized geometric operators - establishing a concrete mathematical connection requires significantly more work.
+
+This represents an important limitation of our current approach and highlights the need for future research to either derive such constraints from canonical LQG or develop alternative frameworks that more naturally incorporate both emergent dimensions and quantum geometric discreteness.
+Similar caveats also apply to our suggestion that \eqref{eqn:X-masses-constraint} should imply that spacetime is $(2 + 1)$-dimensional.
+
 By analysing the equations of motion for the metric $g_{c d}$ from the action \eqref{eqn:emergent-dimensions-action} we get
@@
 Thus we have:
-\begin{equation}
+\begin{equation}\label{eqn:enlarged-Xs-transform}
 	\begin{pmatrix}
@@
 
+Let us note that $X^r$ can be naturally interpreted as a ``scaling dimension'' following directly from the transformation properties of the enlarged coordinate system.
+In equations \eqref{eqn:enlarged-Xs} and \eqref{eqn:enlarged-Xs-transform}, we introduce $X^r$ as an auxiliary coordinate needed to close the Poincaré algebra, initially fixing $X^r = 1$.
+However, when $X^r$ is allowed to vary from this reference value, the transformation properties show that the other coordinates $X^\mu$ undergo scale transformations.
+Specifically, in the enlarged coordinate system, physical coordinates can be interpreted as $x^\mu = X^\mu / X^r$, so variations in $X^r$ directly correspond to scaling transformations of the physical coordinates.
+This provides a concrete mathematical justification for interpreting $X^r$ as a scaling dimension - it is precisely the coordinate that controls the scale of the embedding.
+This geometric scaling property is what allows our construction to naturally accommodate the holographic principle, where the extra dimension encodes information about scales in the lower-dimensional theory.
+
 \subsection{The Einstein-Cartan String}\label{sec:einstein-cartan-string}
@@
 What our discussion in this section shows, however, is that such a classical description is possible if we switch from the metric based approach to the connection based one for describing the background geometry and its coupling to the string worldsheet.
+
+The key observation which enables this is that $X^r$ behaves as a scaling or ``holographic'' dimension as explained at the end of \autoref{sec:translation_gauge}.
+
+Our classical construction provides a geometric framework that naturally incorporates key features of the AdS/CFT correspondence.
+The scaling dimension $X^r$ introduced through the mathematical necessity of closing the Poincaré algebra plays a role analogous to the radial coordinate in AdS space.
+Just as in AdS/CFT where the radial direction encodes the energy scale of the boundary theory, variations in our $X^r$ coordinate directly control the scale transformations of the bulk coordinates $X^\mu$.
+This creates a natural holographic setup where information about different energy scales in the ``boundary'' ($X^r = \text{constant}$ surfaces) is encoded in the ``bulk'' (the extended geometry with the extra $X^r$ dimension).
+
+However, our construction differs from standard AdS/CFT in several important ways: (1) it emerges at the classical level from gauge theory requirements rather than from quantum/non-perturbative effects, (2) the holographic direction arises from the string action itself rather than being an external bulk geometry, and (3) the correspondence is between worldsheet dynamics and the extended embedding space rather than between a boundary CFT and bulk gravity.
+While this provides a concrete classical realization of holographic principles, establishing a precise correspondence with Maldacena's duality would require demonstrating how our construction reproduces the specific correlation functions and scaling behaviors characteristic of AdS/CFT, which remains an open challenge for future work.
 

### 2025-07-05 AoP/response-to-referee.tex
feat: T2 - Complete AOP reviewer responses for Sections 7 and 8.
- Discussion section enhancements with cosmological horizon connection and experimental signatures
- T2 finished, only overall review for typos and grammar required
- Updated memory bank

@@
 
-\AR
+\AR Following the referee's suggestion we have added the following paragraph right after eq (7.12), relating the cosmological constant $\Lambda$ and the deSitter length $l$:
+
+\emph{Given the observed cosmological constant $\Lambda \approx 1.47 \times 10^{-52} \text{m}^{-2}$ \citep{Collaboration2020Planck}, eq (7.12) implies that $l \approx 1.4 \times 10^{26} \text{m}$.
+This happens to coincide with the scale of the cosmological horizon \citep{Peebles2003Cosmological}.
+This would suggest that the scale of the emergent dimension $X^r$ is of the order of the cosmological horizon.
+Of course, this is a very naive ``back of the envelope'' calculation and would require further investigation to place on a firmer footing.}
 
@@
 
-\AR
+\AR We agree with the referee's assessment.
+We have added the following paragraph following the paragraphs discussing the limitations of our ``anomaly free'' claims (which were also added in response to points raised by the referee):
+
+\emph{Additionally, our anomaly-freedom and ghost-freedom analysis is limited to the tree-level constraints; quantum loop corrections and the full quantum effective action may introduce subtleties not captured in this treatment.}
 

### 2025-07-05 lqg-strings.tex
feat: T2 - Complete AOP reviewer responses for Sections 7 and 8.
- Discussion section enhancements with cosmological horizon connection and experimental signatures
- T2 finished, only overall review for typos and grammar required
- Updated memory bank

@@
 
+Additionally, our anomaly-freedom and ghost-freedom analysis is limited to the tree-level constraints; quantum loop corrections and the full quantum effective action may introduce subtleties not captured in this treatment.
+
 The mode truncation is a key assumption that requires validation.
@@
 \begin{equation}\label{eqn:cosmological-constant}
-	\lambda = \frac{3 \ep}{l^2}.
-\end{equation}
+	\Lambda = \frac{3 \ep}{l^2}.
+\end{equation}
+Given the observed cosmological constant $\Lambda \approx 1.47 \times 10^{-52} \text{m}^{-2}$ \cite{Collaboration2020Planck}, eq \eqref{eqn:cosmological-constant} implies that $l \approx 1.4 \times 10^{26} \text{m}$.
+This happens to coincide with the scale of the cosmological horizon \cite{Peebles2003Cosmological}.
+This would suggest that the scale of the emergent dimension $X^r$ is of the order of the cosmological horizon.
+Of course, this is a very naive ``back of the envelope'' calculation and would require further investigation to place on a firmer footing.
+
 One might ask what is the motivation for introducing dS (adS) geometries into the discussion.
@@
 
+\subsection{Open Questions and Future Directions}\label{sec:open-questions}
+
+While our work establishes a promising framework for incorporating LQG insights into string theory, several fundamental questions remain open.
+Building on the pioneering work of Smolin \cite{Smolin1998Strings} and Markopoulou \cite{Markopoulou1997Causal}, a more complete framework is needed to show how smooth worldsheet geometries emerge from the discrete, punctured surfaces of spin networks in Loop Quantum Gravity.
+Our earlier work \cite{Vaid2017Connecting} established that the Nambu-Goto action can be viewed as the expectation value of the LQG area operator, but the detailed emergence mechanism requires further development.
+
+The physical interpretation of the emergent holographic dimension $X^r$ also requires further study.
+Understanding the physical nature of this dimension and its emergence mechanism represents a key theoretical challenge, though the connection to Afshordi's model provides important guidance.
+
+Perhaps most significantly, the relationship between our modified constraint algebra and the fundamental structure of spacetime at the Planck scale requires clarification.
+Do the two-index Virasoro generators correspond to a deeper geometric principle?
+Can they be understood by some suitable deformation of the Virasoro algebra to incorporate the cutoff of the sum over Virasoro modes?
+
 \begin{acknowledgments}

### 2025-07-06 AoP/response-to-referee.tex
T3: Complete AOP manuscript resubmission process with author name change coordination
- Created professional cover letter with optimized single-page formatting
- Coordinated author name change (Luigi → Lin) through Elsevier's inclusive policy
- Successfully resubmitted AOP manuscript 81029 to Annals of Physics
- Documented complete resubmission process in memory bank system
- Updated task registry with T3 completion and session tracking

@@
 \def\papertitle{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
-\def\authors{Deepak Vaid and Luigi Teixeira de Sousa}
+\def\authors{Deepak Vaid and Lin Teixeira de Sousa}
 \def\journal{Annals of Physics}
 \def\doi{AOP 81029}
+\def\date{\today}
 
 \input{AR_to_RC.tex}
+
+\date{}
 
@@
 \AR We must be honest and state that at present the area modified action is not rigorously derived.
-We have added a paragraph right after the action area-modified action (eqn 2.2.
-in the text) to explain this point:
+We have added a paragraph right after the action area-modified action (eqn (2.2) in the text) to explain this point:
 
@@
 
-\AR
-
-\section{Summary of Major Changes}
-
-% This section will be filled once revisions are complete
-\begin{enumerate}
-    \item 
-    \item 
-    \item 
-\end{enumerate}
-
-\section{Submission Requirements}
-
-We confirm that we will submit the following files with our revision:
-\begin{itemize}
-    \item Manuscript source files (LaTeX format)
-    \item Figure source files in acceptable formats (TIFF, EPS)
-    \item Highlights file (3-5 bullet points, maximum 85 characters each)
-\end{itemize}
+\AR Done. Several typos were found and fixed.
 

### 2025-07-06 AoP/resubmit-cover-letter.tex
T3: Complete AOP manuscript resubmission process with author name change coordination
- Created professional cover letter with optimized single-page formatting
- Coordinated author name change (Luigi → Lin) through Elsevier's inclusive policy
- Successfully resubmitted AOP manuscript 81029 to Annals of Physics
- Documented complete resubmission process in memory bank system
- Updated task registry with T3 completion and session tracking

\documentclass[11pt]{article}
\usepackage[margin=1.2in,scale=1.2]{geometry}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{titlesec}

\usepackage{parskip}

\setlength{\parskip}{8pt}
\setlength{\parindent}{0pt}

% Reduce space around sections
\titlespacing*{\section}{0pt}{0.5ex}{0.5ex}
\titlespacing*{\subsection}{0pt}{0.5ex}{0.5ex}

% Reduce list spacing
\setlist{itemsep=0pt, parsep=0pt, topsep=2pt}

\setlength{\baselineskip}{12pt}

\begin{document}

\begin{center}
\textbf{\large Cover Letter for Revised Manuscript Submission}
\end{center}

\vspace{0.2cm}

\noindent
\begin{tabular}{@{}ll}
\textbf{Manuscript Reference Number:} & AOP 81029 \\
\textbf{Journal:} & Annals of Physics \\
\textbf{Date:} & \today \\
\end{tabular}

\vspace{0.3cm}

\noindent
Dear Editor,

We are pleased to submit the revised version of our manuscript entitled ``A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales'' (Reference Number: AOP 81029) for publication in Annals of Physics.

We have carefully addressed all comments and suggestions from the reviewers. A detailed point-by-point response is provided in the accompanying file ``response-to-referee.pdf''.

\textbf{Author Name Change:} One co-author has requested a name change from Luigi Teixeira de Sousa to Lin Teixeira de Sousa. We have contacted namechange@elsevier.com per Elsevier's inclusive author name change policy. This correction does not affect authorship contributions or order.

\textbf{Summary of Revisions:} Major improvements include: (1) Enhanced theoretical foundation with extensive discussions connecting our minimal area approach to existing minimal length proposals in string theory; (2) Clearer physical justification for the expansion parameter $k \ll 1$ and strengthened analogy with T/S-dualities; (3) Clarified anomaly-freedom claims, explaining this refers specifically to absence of central charge anomalies due to finite mode truncation; (4) Added important caveats about approach limitations; (5) Improved interpretation of emergent dimensions and their connection to holographic principles and cosmological horizon scale.

We confirm that: (i) all authors have reviewed and approved the revised manuscript; (ii) the manuscript has not been submitted elsewhere; (iii) all ethical guidelines have been followed; (iv) all necessary permissions have been obtained for copyrighted material.

We thank the reviewers for their constructive feedback and look forward to your favorable consideration.

\vspace{0.3cm}

\noindent
Sincerely,

\vspace{0.4cm}

\noindent
\begin{tabular}{@{}l}
Deepak Vaid \\
502, Broadway Apartments \\
Mangaluru, Karnataka, India \\
Email: dvaid79@gmail.com \\
\textbf{Corresponding Author}
\end{tabular}

\vspace{0.3cm}

\noindent
\textbf{Attachments:} \texttt{response-to-referee.pdf} (detailed response), \texttt{resubmit-cover-letter.pdf} (cover letter), \texttt{lqg-strings.pdf} (revised manuscript), \texttt{lqg-strings-diff.pdf} (diff file), \texttt{lqg-strings.bib} \& \texttt{lqg-strings.bbl} (bibliography files).

\end{document}

### 2025-07-06 lqg-strings-aop-v1.tex
T3: Complete AOP manuscript resubmission process with author name change coordination
- Created professional cover letter with optimized single-page formatting
- Coordinated author name change (Luigi → Lin) through Elsevier's inclusive policy
- Successfully resubmitted AOP manuscript 81029 to Annals of Physics
- Documented complete resubmission process in memory bank system
- Updated task registry with T3 completion and session tracking

--- 2025-07-05 lqg-strings.tex
@@
 
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,final]{hyperref}
+\usepackage[breaklinks,colorlinks=true,citecolor=blue,linkcolor=blue,final]{hyperref}
 %\usepackage{hyperref}
@@
 
-\title{A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
+\title{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
 
@@
 
-Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}
-
-The key insight is to translate this fundamental discreteness of area from spacetime geometry to the worldsheet of the string itself.
-In LQG, the eigenvalues of the area operator are discrete, meaning physical areas can only take values from a quantized spectrum with minimum eigenvalue $\Delta$.
-For a string worldsheet, this suggests that the total worldsheet area $\mathcal{A} = \int d^2\sigma \sqrt{-h}$ cannot be arbitrarily small but must satisfy $\mathcal{A} \geq \Delta$.
-
-Rather than imposing this constraint externally, we incorporate it directly into the action by modifying the area element itself.
-The natural way to ensure the worldsheet area respects LQG's minimal area is to replace the standard area element $\sqrt{-h}$ with $\sqrt{-(h+k\Delta)}$ where $k = l_{pl}/l_s$ is the ratio of Planck to string scales.
-This modification has several appealing features: it reduces to the standard Nambu-Goto action when $k \to 0$, it ensures the worldsheet area can never become arbitrarily small, and it provides a concrete mechanism to incorporate LQG's geometric quantization into string theory.
-
-This approach differs from previous minimal length proposals in string theory \cite{Amati1989Canb,Chang2011Minimal,Gross1987Highenergy,Gross1988String,Yoneya1989Interpretation,Yoneya2000String} in that it specifically targets area rather than length, reflecting LQG's emphasis on area as the fundamental geometric observable.
-
-We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
+Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.} \footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.} We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$.
 We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity.
@@
 Such a theory should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep quantum regime which do not have any sensible description in terms of any Riemannian geometry.
-On the face of it, string theory, at least in its conventional form, does not satisfy this principle \footnote{Recent work has highlighted fundamental challenges to achieving manifest background independence in string theory.
-Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance when higher-derivative corrections are included \cite{Hohm2017Background,Hohm2018Background}.}.
+On the face of it, string theory, at least in its conventional form, does not satisfy this principle.
 The great virtue of LQG on the other hand, is that it respects background independence by construction and proceeds to quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.
@@
 The fixed point of this analysis, remarkably enough, requires one to impose the condition that the background metric obeys Einstein's field equations (more precisely that the background is \emph{Ricci flat}.
-This is explained in greater detail in Appendix \ref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent\footnote{However, developments in string field theory continue to address these foundational issues \cite{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory.
-For an overview of the general concept of background independence in quantum gravity see \cite{Read2023Background}.}.
+This is explained in greater detail in Appendix \ref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is background independent.
 Our reasons are the following:
@@
 \end{equation}
-At present we do not have a rigorous derivation of this expression.
-It is the simplest possible ansatz one can think of to encode the insight from LQG that at the Planck scale there is a minimum quantum of area.
-What makes us more confident in this ansatz is that it is consistent with the Kalb-Ramond field identification and the minimal area interpretation of the scalar density $\Delta$.
-However, this was not known prior to coming up with the ansatz and only discovered after the fact.
-
 Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}.
@@
 \end{equation}
-
-If we take $k$ to be an expansion parameter, then it follows that it should also be small.
-The physical justification for this is the following picture.
-The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams.
-The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures.
-In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network.
-When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - i.e.
-where geometry itself is fully quantum - is required.
-
-The limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
+Presumably the limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$.
 Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(k^2/h^2)$ corrections.
@@
 (or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
-This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.
-
-This duality is reminiscent of, but also distinct from, the T and S dualities in string theory.
-In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$.
-In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$.
-In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$.
-This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small quantum of area ($\Delta$) and large quantum of area ($\Delta'$) and between large string tension $T$ and small string tension $T'$.
 
@@
 
-As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware-Deser ghost in theories of massive gravity.
-However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.
-
 The second possibility is the following.
@@
 thus the action \eqref{eqn:ng-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength.
+Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$.
 Also, we have a direct relation between string tension and scale
@@
 
-This table shows that $a$ becomes more negative as either the spacetime dimension $D$ or the mass parameter $\mu$ increases. This means:
-
-\begin{itemize}
-	\item Higher dimensions lead to more massive ground states
-	\item Larger $\mu$ (stronger discreteness effects) also increases ground state masses
-	\item The spectrum becomes increasingly separated from the massless limit
-\end{itemize}
-
-For example, in $D=2$ with $\mu=1$, $a=-4.24$ gives a relatively light spectrum, while $D=3$ with $\mu=5$ yields $a=-34.27$, producing much heavier states.
-This demonstrates how LQG's discreteness parameter $\mu$ and the background dimensionality jointly control the departure from standard string theory's massless spectrum, with stronger quantum geometric effects pushing all states away from the massless limit expected in conventional string theory.
-
 The commutation relations between the constraints are inherited by the Poisson brackets
@@
 
-Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we get similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
-
-It is important to clarify what we mean by ``no anomalies'' in this context.
-This refers specifically to the absence of central charge anomalies in our modified Virasoro-like algebra, which arises due to the finite mode truncation imposed by LQG's discreteness.
-This discreteness is encoded in the paramter $\mu$ in \eqref{eqn:mu-constraint-1}, which is a cutoff parameter that controls the maximum number of modes we consider in the action.
-
-This differs fundamentally from standard string theory, where anomaly cancellation requires critical dimensions ($D = 26$ for bosonic strings) to ensure vanishing of the central charge from an infinite sum over modes.
-Our finite sum naturally avoids this constraint, permitting unconstrained background dimensionality $D$.
-However, this result applies specifically to our truncated model in the regime where $k \ll 1$, where the smooth worldsheet approximation remains valid.
-In the full quantum gravitational regime where $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and a more comprehensive analysis would be required.
-
-The mode truncation is a key assumption that requires validation.
-While we do not have a rigorous derivation from first principles, the physical motivation comes from LQG's discrete structure: high-frequency modes corresponding to sub-Planckian physics should be suppressed when the spin network discreteness becomes relevant.
-The parameter $\mu$ in \eqref{eqn:mu-constraint-1} provides an effective energy cutoff, with modes $|n| > d \approx \mu$ being suppressed.
-
-This approach shares similarities with other discrete quantum gravity approaches like causal dynamical triangulation and spin foam models, which also impose natural cutoffs.
-However, a complete justification would require deriving this truncation directly from LQG's canonical quantization procedure, which remains an open question for future work.
+Although our method is quite different from the one in \cite{Thiemann2004The-LQG-String:}, we got similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and no negative-norm states in physical processes.
 
@@
 \end{equation}
-from which the pulledback connection is $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$, whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
+from which the pulledback connection $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$ is thus
+\begin{equation} \label{eqn:adS-WS-connection}
+	\mc{A}_{a} = \begin{bmatrix} 0 & 0 & 0 & 0 & \del _{a} X^{0} \\ 0 & 0 & 0 & 0 & \del _{a} X^{1} \\ 0 & 0 & 0 & 0 & \del _{a} X^{2} \\ 0 & 0 & 0 & 0 & \del _{a} X^{3} \\ - \del _{a} X^{0} & \del _{a} X^{1} & \del _{a} X^{2} & \del _{a} X^{3} & 0 \end{bmatrix} ,
+\end{equation}
+whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
 \begin{multline} \label{eqn:Minkowski-sector-EoM}
@@
 \end{equation}
-Thus, the Minkowski sector behaves like regular ST for small perturbations, while the holographic coordinate $X^{r}$ follows a variable-mass Klein-Gordon equation with source.
-Now it should be clear why the choice of $\mu$ for the coupling constant, since in \eqref{eqn:simplified-holographic-EoM} it appears (together with the conformal factor) as a mass term for our perturbation.
-Eq \eqref{eqn:simplified-holographic-EoM} can be solved using the 1d wave equation Green's function to build a perturbation around the homogenous wave equation solution
-\begin{multline} \label{eqn:holo-sol-implicit}
-	X^{r} (x) = X^{r} _{0} (x) - \\ - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) = \\ = X^{r} _{0} (x) + \delta X^{r} (x),
-\end{multline}
-where $X^{r} _{0}$ is a solution for the homogenous wave equation
-\begin{equation} \label{eqn:homo-wave-eqn}
-	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) X^{r} _{0} = 0
-\end{equation}
-and $G (x ; x') = \frac{1}{2} \Theta (\tau - \tau ' - |\sigma - \sigma '|)$ its Green's function
-\begin{equation} \label{eqn:homo-wave-eqn-GF}
-	(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) G (x ; x') = \delta ^{2} (x ; x') .
-\end{equation}
-From \eqref{eqn:holo-sol-implicit}, a recursion can be built, leading to a more explicit form
-\begin{multline}
-	X^{r} (x) = X^{r} _{0} (x) + \\ + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \\ \times (2 + \mu X^{r} _{0} (x^{(k)})) ,
-\end{multline}
-with $x^{(0)} \equiv x$.
+Thus, the Minkowski sector behaves like regular ST for small perturbations, and for the holographic dimension we can solve using a Green's function
+\begin{equation} \label{eqn:Xr-GF}
+	X^{r} (x) = - 4 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} ,
+\end{equation}
+with the Green's function satisfying
+\begin{equation} \label{eqn:Greens-function}
+	(\del _{\sigma} ^2 - \del _{\tau} ^2 + 2 \mu ^2 \e ^{\varphi}) G (x ; x') = \delta ^2 (x , x') .
+\end{equation}
+To find this Green's function, we must fix the conformal factor to be of the form $\e ^{\varphi} = f (\tau) - g (\sigma)$, thus allowing us to separate variables in the homogeneous case of eq \eqref{eqn:Greens-function} into
+\begin{equation} \label{eqn:Green-X}
+	X^{\prime \prime} - 2 \mu ^2 g (\sigma) X = - \lambda X
+\end{equation}
+\begin{equation} \label{eqn:Green-T}
+	\ddot{T} - 2 \mu ^2 f (\tau) T = - \lambda T .
+\end{equation}
+These are Schrodinger's equations for potentials given by $\mu f (\tau)$ and $\mu g (\sigma)$, as such if we assume that $f$ and $g$ are harmonic oscillator potentials $f (\tau) = \omega ^2 \tau ^2 / 2$ and $g (\sigma) = k^2 \sigma ^2 / 2$ we can find known solutions for separation constant $\lambda = 2 \mu E = \mu k (2n + 1) = \mu \omega (2n + 1)$, so by the Spectral Theorem our separated spatial and temporal Green's functions are
+\begin{equation} \label{eqn:X-function}
+	X (\sigma , \sigma ') = \sum _{n \geq 0} - \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
+\end{equation}
+\begin{equation} \label{eqn:T-function}
+	T (\tau , \tau ') = \sum _{m \geq 0} - \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} ,
+\end{equation}
+where $X_{n}$ and $T_{m}$ are harmonic oscillator eigenfunctions. With this, the full Green's function $G = T.X$ and the solution for $X^{r}$ are thus
+\begin{equation} \label{eqn:G-function}
+	G (x ; x') = \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau) T_{m} (\tau ')}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma) X_{n} (\sigma ')}{\mu k (2 n + 1)}
+\end{equation}
+\begin{multline} \label{eqn:Xr-solution}
+	X^{r} (x) = - 4 \mu \sum _{m \geq 0} \sum _{n \geq 0} \frac{T_{m} (\tau)}{\mu \omega (2 m + 1)} \frac{X_{n} (\sigma)}{\mu k (2 n + 1)} \times \\
+	\times \int \diff ^2 x' T_{m} (\tau ') X_{n} (\sigma ') \left( \frac{\omega ^2 \tau ^{\prime 2}}{2} - \frac{k^2 \sigma ^{\prime 2}}{2} \right) .
+\end{multline}
 
@@
 \end{equation}
-Another candidate for what the vector excitations could relate to is the $D = 3 + 1$ Ashtekar electric field $\widetilde{E}^{a} _{i}$,
+Another candidate for what the vector excitations could relate to is the Ashtekar electric field $\widetilde{E}^{\mu} _{I}$,
 \begin{equation} \label{eqn:AEF-string-vector-excitation}
-	\widetilde{E}^{a} _{i} \sim (\Hat{a}^{a} _{i})^{\dagger} \ket{0} .
+	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
 \end{equation}

### 2025-08-25 AoP/response-to-referee-r2.tex
T4: AOP final revisions task - completed Section 2 duality clarification, identified remaining 4 reviewer requirements

\documentclass{article}
\usepackage[square,comma]{natbib}
\def\lettertitle{Author Response to Reviews of}
\def\papertitle{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
\def\authors{Deepak Vaid and Lin Teixeira de Sousa}
\def\journal{Annals of Physics}
\def\doi{AOP 81029}
\def\date{\today}

\input{AR_to_RC.tex}

\date{}

We thank the editor for his patience through the whole process and the referee for taking the time to review the revised manuscript.

\section{Reviewer \#1}

\subsection{Clarifications and Enhancements}

\RC The discussion on the duality between $h_{ab}$ and $h^{ab}$ (Section 2) is now clearer, but a brief mention of how this duality might manifest in observable string dynamics (e.g., through measurable spectra or scattering amplitudes) would provide an wider physical interpretation.

\AR We have added the following paragraph right after ``\emph{and the string tension inversion is reminiscent of S-duality’s strong-weak coupling correspondence.}'' to explain this point:

\emph{Physically, one way in which this duality could manifest in the real world is in the mass spectrum of string excitations which when computed in the strong-coupling regime should exhibit a precise correspondence with spectra in the weak-coupling limit under the transformation rules (2.7a)-(2.7c), while world-sheet correlation functions should satisfy similar duality relations, potentially providing calculable predictions for string phenomenology at both energy scales.}

\RC The connection to the Kalb-Ramond field (Section 3.2) is well-justified, but a brief comment on whether this implies any constraints on the Kalb-Ramond field's dynamics (e.g., torsionless backgrounds) would be insightful.

\AR We have added the following para at the end of Sec 4A, right after ``\emph{since the co- efficient in eq (4.16) is a true scalar and the Levi-Civita symbol is itself a density.}''

\emph{This pullback relationship would suggest a restriction on the allowed bulk configurations. Since the worldsheet area spectrum is discrete due to the underlying LQG quantization, the Kalb-Ramond field strength must be correspondingly quantized. This is analogous to flux quantization in the quantum Hall effect, where the magnetic flux through the 2D electron system is constrained to be integer multiples of $h/e$. In our case, the integrated field strength $\int H_{\mu \nu \rho}$ over appropriate 3-cycles in the bulk should be quantized in units related to the fundamental area quantum $\Delta$, restricting the allowed background field configurations to those compatible with the discrete worldsheet area spectrum.}

\subsection{Open Questions and Future Directions (Section 8.C)}

\RC Open Questions and Future Directions (Section 8.C):
The discussion on emergent dimensions and their cosmological implications (Section 6) is somewhat speculative. A brief acknowledgment of the phenomenological challenges (e.g., observational constraints on extra dimensions) would provide more support.

\AR

\RC The suggestion of a (2+1)-dimensional fundamental spacetime (Section 6) requires more evidence or references to support this claim. You might provide references to recent work on lower-dimensional gravity or holography that could bolster this argument.

\AR

\subsection{Technical Details}

\RC The derivation of the relation between $\Delta_{ab}$ and the Kalb-Ramond field (Eq. 3.21) is now clearer, but a step-by-step derivation in an appendix or supplementary material would provide reproducibility.

\AR

\subsection{Cosmological Implications (Section 7)}

\RC The interpretation of the emergent dimension $X^r$ as a "scaling dimension" is compelling. However, the link to the cosmological horizon scale (Page 30) is tentative. A brief discussion of how this might align or conflict with current cosmological data would be valuable.

\AR

\bibliographystyle{apalike}

\bibliography{../lqg-strings.bib}

\end{document}

### 2025-08-25 lqg-strings.tex
T4: AOP final revisions task - completed Section 2 duality clarification, identified remaining 4 reviewer requirements

@@
 
-% Biblatex setup
-% The default is the 'numerical' style.
-%\usepackage[backend=biber,url=true,eprint=true,doi=true,sorting=none,backref=true,style=phys]{biblatex}
-% We use the following bibliography databases:
-%\usepackage{bibtex}
-%\addbibresource{../bib_library.bib}
-% End biblatex
-
 %%% BEGIN Custom commands %%%
@@
 %text
-\newcommand{\ie}{\textit{i.e.}~}
-\newcommand{\eg}{\textit{e.g.}~}
-\newcommand{\wrt}{\textit{w.r.t.}~}
-\newcommand{\etc}{\textit{etc.}~}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\eg}{\textit{e.g.}}
+\newcommand{\wrt}{\textit{w.r.t.}}
+\newcommand{\etc}{\textit{etc.}}
 
@@
 \email{dvaid79@gmail.com}
-\affiliation{}
-\author{Luigi Teixeira de Sousa}
+\affiliation{502, Broadway Apartments, Mangaluru, Karnataka, India}
+\author{Lin Teixeira de Sousa}
 \email{luigi.tiraque@gmail.com}
@@
 LQG has concrete predictions such as discreteness of physical areas \cite{Rovelli1993Area,Rovelli1994Discreteness}, and also has rigorous mathematical results which reproduce the black hole entropy formulae for Einstein gravity \cite{Rovelli1996Black}.
-Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
+Moreover it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.
 
@@
 The following is the outline of the paper along with a brief summary of what is accomplished in each section.
-For those seeking a rapid review of the principle areas of diffence between the two theories \autoref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.
-
-Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}
+For those seeking a rapid review of the principle areas of difference between the two theories \autoref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.
+
+Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we begin by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}
 
@@
 In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity.
-We find both, the Nambu-Goto and the Polaykov forms of this action.
+We find both, the Nambu-Goto and the Polyakov forms of this action.
 Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.
@@
 In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action.
-Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.
+Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polyakov versions of the modified string action are equivalent to each other.
 
@@
 and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$.
-The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$ , must be annihilated by these constraints:
+The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$, must be annihilated by these constraints:
 \begin{equation}
@@
 While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables.
-This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory of a dualised $\mathfrak{sl} (2 , \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
+This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory of a dualised $\mathfrak{sl} (2, \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
 \begin{equation} \label{eqn:self-dual-spin-connection}
@@
 \begin{equation} \label{eqn:densitized-tetrad}
-	B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K} _{[ \mu} e^{L} _{\nu ]} ,
+	B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K} _{[ \mu} e^{L} _{\nu ]},
 \end{equation}
@@
 \begin{equation} \label{eqn:Ashtekar-E-field-canonical}
-	E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c} ,
+	E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c},
 \end{equation}
@@
 This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity.
-One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.
-
-One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$ \footnote{Here, the index convention followed is that lowercase $i , j , k$ refer to 3-dimensional flat internal ($\mf{su}(2)$) indices and lowercase $a , b , c$ refer to 3-dimensional curved spacetime indices} can no longer be a continuous function of spacetime, rather it becomes a \emph{distribution}, assuming a constant value on one patch of space, then another value at another patch, etc \cite{Bodendorfer-LQG,Rovelli2015Covariant}.
+One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high-energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.
+
+One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$ \footnote{Here, the index convention followed is that lowercase $i, j, k$ refer to 3-dimensional flat internal ($\mf{su}(2)$) indices and lowercase $a, b, c$ refer to 3-dimensional curved spacetime indices} can no longer be a continuous function of spacetime, rather it becomes a \emph{distribution}, assuming a constant value on one patch of space, then another value at another patch, etc \cite{Bodendorfer-LQG,Rovelli2015Covariant}.
 The consequence of this non-continuous distributional nature of the connection is that the triad (or Ashtekar electric field) operator, which formally would be
@@
 \begin{equation} \label{eqn:triad-flux-operator}
-	\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}} ,
+	\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}},
 \end{equation}
@@
 \begin{equation} \label{eqn:area-eigenvalues}
-	\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))} ,
+	\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))},
 \end{equation}
@@
 \end{equation}
-
 If we take $k$ to be an expansion parameter, then it follows that it should also be small.
@@
 In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network.
-When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - i.e.
-where geometry itself is fully quantum - is required.
+When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - \ie~ where geometry itself is fully quantum - is required.
 
@@
 (or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$).
-This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.
+This is a duality between the physics at the Planck scale and the physics at the string scale, \ie~ between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.
 
@@
 This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.
+Physically, one way in which this duality could manifest in the real world is in the mass spectrum of string excitations which when computed in the strong-coupling regime should exhibit a precise correspondence with spectra in the weak-coupling limit under the transformation rules \eqref{eqn:T'}-\eqref{eqn:d2x}, while worldsheet correlation functions should satisfy similar duality relations, potentially providing calculable predictions for string phenomenology at both energy scales.
 
@@
 The expression \eqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$.
-One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polaykov action.
+One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polyakov action.
 
@@
 	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
-	         & + S_{int} [g , h , X].
+	         & + S_{int} [g, h, X].
 \end{align}
@@
 	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
-	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
+	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}},
 \end{multline}
@@
 \begin{equation} \label{eqn:g-expression}
-	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
 \end{equation}
@@
 \begin{equation} \label{eqn:h-expression}
-	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
+	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu},
 \end{equation}
@@
 \begin{equation} \label{eqn:double-ng-action}
-	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
+	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h},
 \end{equation}
@@
 	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
-	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
+	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0,
 \end{multline}
@@
 \end{equation}
-
 If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:
@@
 This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables.
-This action at first glance does not have WS Weyl invariance since the second term has inverse determinant multiplied by inverse metric, however, if one wishes to restore Weyl symmetry one just needs to require that under a Weyl transformation, the $\Delta _{a b}$ field also transforms like the metric \ie
+This action at first glance does not have WS Weyl invariance since the second term has inverse determinant multiplied by inverse metric, however, if one wishes to restore Weyl symmetry one just needs to require that under a Weyl transformation, the $\Delta _{a b}$ field also transforms like the metric \ie~
 \begin{subequations}
@@
 		g_{a b}       & \rightarrow \Lambda (x) g_{a b} \label{eqn:g-Weyl-transform}             \\
-		\Delta _{a b} & \rightarrow \Lambda (x) \Delta _{a b} , \label{eqn:Delta-Weyl-transform}
+		\Delta _{a b} & \rightarrow \Lambda (x) \Delta _{a b}, \label{eqn:Delta-Weyl-transform}
 	\end{align}
@@
 \begin{multline} \label{eqn:inverse-area-em-tensor}
-	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
+	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
 \end{multline}
@@
 \begin{equation} \label{eqn:ws-metric}
-	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
+	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
 \end{equation}
@@
 \begin{multline} \label{eqn:X-eom-inverse-area}
-	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
+	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
 \end{multline}
@@
 \begin{equation} \label{eqn:coupling-X-phi}
-	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0 ,
+	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0,
 \end{equation}
@@
 	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
-	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
+	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big),
 \end{multline}
@@
 	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
-	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
+	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg),
 \end{multline}
@@
 \begin{equation} \label{eqn:f-tilde}
-	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
+	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
 \end{equation}
@@
 \begin{equation} \label{eqn:WS-b-field}
-	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b} ,
+	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
 \end{equation}
@@
 
+This pullback relationship would suggest a restriction on the allowed bulk configurations.
+Since the worldsheet area spectrum is discrete due to the underlying LQG quantization, the Kalb-Ramond field strength must be correspondingly quantized.
+This is analogous to flux quantization in the quantum Hall effect, where the magnetic flux through the 2D electron system is constrained to be integer multiples of $h/e$.
+In our case, the integrated field strength $\int H_{\mu \nu \rho}$ over appropriate 3-cycles in the bulk should be quantized in units related to the fundamental area quantum $\Delta$, restricting the allowed background field configurations to those compatible with the discrete worldsheet area spectrum.
+
 \subsection{Area-Corrected Nambu-Goto Action and Born-Infeld Electrodynamics} \label{sec:area-corrected-BI}
@@
 \begin{equation} \label{eqn:BI-action}
-	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
+	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})},
 \end{equation}
@@
 \begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
-	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
+	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta,
 \end{equation}
@@
 \begin{equation}
-	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
+	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0,
 \end{equation}
@@
 \begin{equation} \label{eqn:derivatives-F-minus}
-	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
+	\partial _{\tau} \ln (F^{-}) = i E, \ \partial _{\sigma} \ln (F^{-}) = i p,
 \end{equation}
@@
 \begin{equation} \label{eqn:ln-F}
-	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
+	\ln (F^{-}) = i (E \tau + p \sigma) + a, \ a \in \mathbb{C}
 \end{equation}
@@
 \begin{equation} \label{eqn:F-minus-exp}
-	F^{-} = A \e ^{i (E \tau + p \sigma)} , \ A \in \C
+	F^{-} = A \e ^{i (E \tau + p \sigma)}, \ A \in \C
 \end{equation}
@@
 \begin{multline} \label{eqn:KG-Polyakov-solution-initial}
-	X^{\mu} (\tau , \sigma) = \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \bigg( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \\
-	+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \bigg) ,
+	X^{\mu} (\tau, \sigma) = \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \bigg( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \\
+	+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \bigg),
 \end{multline}
@@
 \end{equation}
-
 When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
@@
 	\begin{align}
-		L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
-		\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
+		L_{n, p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0, \ \forall \ n, p \in \mathbb{Z}, \label{eqn:"virasoro"-modes-1} \\
+		\widetilde{L}_{n, p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0, \ n \neq p, \label{eqn:"virasoro"-modes-2}                       \\
 		\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
@@
 \end{subequations}
-Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution.
+Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p}, \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0, \ \forall \ |n| > d$, so we have a truncated solution.
 This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.
@@
 \begin{equation} \label{eqn:X-sol-0-term}
-	\sqrt{\frac{\alpha '}{2}} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
+	\sqrt{\frac{\alpha '}{2}} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right),
 \end{equation}
@@
 \begin{multline} \label{eqn:string-rest-mass-classical-1}
-	M^2 = - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
+	M^2 = - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n, n} \right) - \\
 	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) =
@@
 	F^{-} = 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \\
-	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
+	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right),
 \end{multline}
@@
 \begin{equation} \label{eqn:canonical-bracket-relation}
-	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
+	\left\{ X^{\mu} (0, \sigma), \Pi ^{\nu} (0, \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
 \end{equation}
@@
 	\begin{align}
-		\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\}       & = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\} \label{eqn:expansion-modes-bracket-0} \\
-		\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} & = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} , \label{eqn:expansion-modes-bracket-1}
+		\left\{ \alpha ^{\mu} _{n}, \alpha ^{\nu} _{p} \right\}       & = 0 = \left\{ (\alpha ^{\mu} _{n})^{*}, (\alpha ^{\nu} _{p})^{*} \right\} \label{eqn:expansion-modes-bracket-0} \\
+		\left\{ \alpha ^{\mu} _{n}, (\alpha ^{\nu} _{p})^{*} \right\} & = - i E_{n} \delta _{|n|, |p|} \eta ^{\mu \nu}, \label{eqn:expansion-modes-bracket-1}
 	\end{align}
@@
 \begin{equation} \label{eqn:harmonic-bracket-relations}
-	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|n| , |p|} \eta ^{\mu \nu} .
+	\left\{ a^{\mu} _{n}, (a^{\nu} _{p})^{*} \right\} = - i \delta _{|n|, |p|} \eta ^{\mu \nu} .
 \end{equation}
@@
 \begin{align}
-	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
-	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
+	\left\{ x^{\mu}, x^{\nu} \right\} & = 0 = \left\{ p^{\mu}, p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
+	\left\{ x^{\mu}, p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
 \end{align}
@@
 	\begin{equation} \label{eqn:L-brackets-0}
-		\left\{ L_{n , m} , L_{k , p} \right\} = 0
+		\left\{ L_{n, m}, L_{k, p} \right\} = 0
 	\end{equation}
 	\begin{equation} \label{eqn:L-brackets-1}
-		\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( L_{m , k} \delta _{|n| , |p|} + L_{n , k} \delta _{|m| , |p|} \right)
+		\left\{ L_{n, m}, \widetilde{L}_{k, p} \right\} = - i \left( L_{m, k} \delta _{|n|, |p|} + L_{n, k} \delta _{|m|, |p|} \right)
 	\end{equation}
 	\begin{equation} \label{eqn:L-brackets-2}
-		\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( \widetilde{L}_{k , m} \delta _{|n| , |p|} - \widetilde{L}_{n , p} \delta _{|m| , |k|} \right) .
+		\left\{ \widetilde{L}_{n, m}, \widetilde{L}_{k, p} \right\} = - i \left( \widetilde{L}_{k, m} \delta _{|n|, |p|} - \widetilde{L}_{n, p} \delta _{|m|, |k|} \right) .
 	\end{equation}
@@
 We now seek to quantize the Klein-Gordon string by means of covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures,Green2012Superstring}.
-The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ .
-, .
-\}$ being replaced by commutators $\{ .
-, .
-\} \rightarrow - i [ .
-, .
+The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ ., .
+\}$ being replaced by commutators $\{ ., .
+\} \rightarrow - i [ ., .
 ]$:
@@
 	\begin{align}
-		\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
-		\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
-		\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
-		\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
-		\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
-		\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
+		\left[ \Hat{X}^{\mu} (\tau, \sigma), \Hat{\Pi}^{\nu} (\tau, \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
+		\left[ \Hat{X}^{\mu}, \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu}, \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
+		\left[ \Hat{a}^{\mu} _{n}, \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger}, (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
+		\left[ \Hat{a}^{\mu} _{n}, (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n|, |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
+		\left[ \Hat{x}^{\mu}, \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu}, \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
+		\left[ \Hat{x}^{\mu}, \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
 	\end{align}
@@
 \begin{equation} \label{eqn:annihilation-vacuum}
-	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
+	\Hat{a}^{\mu} _{p} \ket{0} = 0, \ \mathrm{for} \ p \neq 0 .
 \end{equation}
@@
 \end{equation}
-
 As usual, the appearance of the Minkowski metric in the non-zero commutator
 \begin{equation} \label{eqn:ghosts}
-	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{|p| , |k|} ,
+	\Big[ \Hat{a}^{\mu} _{p}, (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{|p|, |k|},
 \end{equation}
@@
 	\begin{equation} \label{eqn:L-constraint-quantum-1}
-		\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
+		\bra{\phi} \Hat{L}_{p, k} \ket{\psi} = 0 \, \,
 	\end{equation}
 	\begin{equation} \label{eqn:L-constraint-quantum-2}
-		\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
+		\bra{\phi} \Hat{\widetilde{L}}_{p, k} \ket{\psi} = 0 .
 	\end{equation}
 \end{subequations}
-$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators.
-As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
+$\Hat{L}_{p, k}$ has no ambiguities since it's composed of only annihilation operators.
+As for $\widetilde{L}_{p, k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
 \begin{equation} \label{eqn:L-normal-ordering}
-	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
+	\Hat{\widetilde{L}}_{p, p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
 \end{equation}
@@
 \begin{equation} \label{eqn:shifted-L-constraint}
-	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
+	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n, n} \right) - a \right) \ket{\psi} = 0,
 \end{equation}
@@
 \end{multline}
-This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
+This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d, d)$ is finite, and the result is
 \begin{multline}
 	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
-	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} ,
+	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n},
 \end{multline}
@@
 	\begin{align}
-		\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right]                         & = 0 \label{eqn:L-commutator-0}                                                                                                   \\
-		\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right]             & = \Hat{L}_{m , k} \delta _{|n| , |p|} + \Hat{L}_{n , k} \delta _{|m| , |p|} \label{eqn:L-commutator-1}                           \\
-		\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] & = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} \label{eqn:L-commutator-2} .
+		\left[ \Hat{L}_{n, m}, \Hat{L}_{k, p} \right]                         & = 0 \label{eqn:L-commutator-0}                                                                                                   \\
+		\left[ \Hat{L}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right]             & = \Hat{L}_{m, k} \delta _{|n|, |p|} + \Hat{L}_{n, k} \delta _{|m|, |p|} \label{eqn:L-commutator-1}                           \\
+		\left[ \Hat{\widetilde{L}}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right] & = \Hat{\widetilde{L}}_{k, m} \delta _{|n|, |p|} - \Hat{\widetilde{L}}_{n, p} \delta _{|m|, |k|} \label{eqn:L-commutator-2} .
 	\end{align}
@@
 \begin{multline} \label{eqn:L-commutator-anomalous-initial}
-	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} + \\
-	+ C_{n} \delta _{|n| , |p|} + D_{k} \delta _{|m| , |k|} .
+	\left[ \Hat{\widetilde{L}}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right] = \Hat{\widetilde{L}}_{k, m} \delta _{|n|, |p|} - \Hat{\widetilde{L}}_{n, p} \delta _{|m|, |k|} + \\
+	+ C_{n} \delta _{|n|, |p|} + D_{k} \delta _{|m|, |k|} .
 \end{multline}
@@
 \begin{equation} \label{eqn:F-sequence}
-	F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) ,
+	F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right),
 \end{equation}
@@
 	\begin{align}
-		\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-Hamiltonian}              \\
-		\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-momentum}
+		\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n, n} \label{eqn:WS-Hamiltonian}              \\
+		\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n, n} \label{eqn:WS-momentum}
 	\end{align}
@@
 	\begin{align}
-		\left[ \Hat{H} , \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
-		\left[ \Hat{P} , \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
+		\left[ \Hat{H}, \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
+		\left[ \Hat{P}, \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
 	\end{align}
@@
 	\frac{\alpha '}{8} M^2 = \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
-	- \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Bigg) ,
-\end{multline}
-while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that
+	- \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Bigg),
+\end{multline}
+while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n, 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that
 \begin{equation} \label{eqn:zeta-p-psi}
@@
 \begin{equation} \label{eqn:p-wave-function}
-	\psi (p) = - \frac{\alpha '}{8 \sqrt{2} \mu} p^{\mu} p_{\mu} ,
+	\psi (p) = - \frac{\alpha '}{8 \sqrt{2} \mu} p^{\mu} p_{\mu},
 \end{equation}
@@
 \end{equation}
-The auxiliary $\bra{0 ; p} \xi _{\alpha} \Hat{a}^{\alpha} _{n} \Hat{\widetilde{L}}_{n , 0} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \zeta _{\mu \nu} \ket{0 ; p} = 0$ condition where $\xi _{\alpha}$ is a arbitrary polarization for the auxiliary vector excitation implies that
+The auxiliary $\bra{0 ; p} \xi _{\alpha} \Hat{a}^{\alpha} _{n} \Hat{\widetilde{L}}_{n, 0} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \zeta _{\mu \nu} \ket{0 ; p} = 0$ condition where $\xi _{\alpha}$ is a arbitrary polarization for the auxiliary vector excitation implies that
 \begin{equation} \label{eqn:spin-2-zeta-p=0}
@@
 		B_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} - \zeta _{\nu \mu}) \label{eqn:B-zeta}                                                                          \\
-		\Phi        & = \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \label{eqn:Phi-zeta} ,
+		\Phi        & = \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \label{eqn:Phi-zeta},
 	\end{align}
@@
 $\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-known types of background fields: the spacetime metric $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$, all of those having squared mass given by eq \eqref{eqn:nth-spin-2-mass-shell}.
-We thus see that the symmetric part $S_{\mu \nu} = G_{\mu \nu} + \Phi \eta _{\mu \nu}$ of $\zeta _{\mu \nu}$ is orthogonal to the momentum of the string, $S_{\mu \nu} p^{\mu} = 0$, and since $p^2 < 0$, we can choose a reference frame where $p^{\mu} = (p , 0 , ...
-, 0)$ only has a time component, leaving us with $S_{0 \nu} = 0$, implying that $\zeta _{0 \nu} = - \zeta _{\nu 0}$.
-This condition guarantees that the timelike components of $\zeta _{\mu \nu}$ have a positive contribution to its square $\zeta ^{\mu \nu} \zeta _{\mu \nu} = \zeta ^{i j} \zeta _{i j} + b , \ b = \zeta ^{0 i} \zeta _{0 i} > 0$, and the remaining part is spacelike thus must also have positive square, so we get that $\zeta ^{\mu \nu} \zeta _{\mu \nu} > 0$, so we are free of ghosts in the spin-2 spectrum.
+We thus see that the symmetric part $S_{\mu \nu} = G_{\mu \nu} + \Phi \eta _{\mu \nu}$ of $\zeta _{\mu \nu}$ is orthogonal to the momentum of the string, $S_{\mu \nu} p^{\mu} = 0$, and since $p^2 < 0$, we can choose a reference frame where $p^{\mu} = (p, 0, ..., 0)$ only has a time component, leaving us with $S_{0 \nu} = 0$, implying that $\zeta _{0 \nu} = - \zeta _{\nu 0}$.
+This condition guarantees that the timelike components of $\zeta _{\mu \nu}$ have a positive contribution to its square $\zeta ^{\mu \nu} \zeta _{\mu \nu} = \zeta ^{i j} \zeta _{i j} + b, \ b = \zeta ^{0 i} \zeta _{0 i} > 0$, and the remaining part is spacelike thus must also have positive square, so we get that $\zeta ^{\mu \nu} \zeta _{\mu \nu} > 0$, so we are free of ghosts in the spin-2 spectrum.
 
@@
 \end{equation}
-possible polarizations, which shows that indeed those polarizations fit nicely in a representation of $\mathrm{SO} (D - 1 , 1)$, \ie the traceless symmetric tensor representation, thus all our excited spin-2 states are consistent with Lorentz symmetry at the macroscopic scale even tho near the Planck scale they deviate a bit by having an effective mass.
+possible polarizations, which shows that indeed those polarizations fit nicely in a representation of $\mathrm{SO} (D - 1, 1)$, \ie~ the traceless symmetric tensor representation, thus all our excited spin-2 states are consistent with Lorentz symmetry at the macroscopic scale even tho near the Planck scale they deviate a bit by having an effective mass.
 
@@
 \begin{equation} \label{eqn:LQG-modified-dispersion-relation}
-	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
+	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}},
 \end{equation}
@@
 \begin{equation} \label{eqn:X-masses-constraint}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
-\end{equation}
-where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}},
+\end{equation}
+where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2, (E_{4})^2, ..., (E_{D - 1})^2$, \ie~, the squared WS energy (and momentum) of each field $X^{\mu}$.
 
 Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
-We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
-$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Carlip2003Quantum}).
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0}, m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
+$(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013Zwei-Dreibein},\cite{Blais2013A-new-quantization},\cite{Carlip2003Quantum}).
 We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.
@@
 \begin{equation} \label{eqn:emergent-dimensions-g}
-	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu} ,
+	g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu},
 \end{equation}
@@
 \begin{equation} \label{eqn:emergent-dimensions-f}
-	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} ,
+	\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu},
 \end{equation}
@@
 	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
-	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
+	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big),
 \end{multline}
@@
 \begin{equation} \label{eqn:X-masses-constraint-2}
-	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
+	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n},
 \end{equation}
@@
 \begin{equation} \label{eqn:mu0-phi-relation}
-	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
+	\mu _{0} ^2 \sim \e ^{- \phi (x)},
 \end{equation}
@@
 \begin{equation}\label{eqn:covariant-deriv-v1}
-	D_a X^\mu(\tau , \sigma) = \partial_a X^\mu + \mu \mc{A}_{a}^\mu{}_\nu X^\nu,
+	D_a X^\mu(\tau, \sigma) = \partial_a X^\mu + \mu \mc{A}_{a}^\mu{}_\nu X^\nu,
 \end{equation}
@@
 Therefore, now we will require that the bulk connection $\mc{A}_{\mu} ^{I J}$ and the bulk vielbein $E^{\mu} _{I}$ can be pulled back onto a connection $\mc{A}_{a}^{I J}$ and a dyad $e^a_I$, respectively, living on the string worldsheet $\Sigma$.
-$X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet.
+$X^\mu(\tau, \sigma)$ are the space-time coordinates of a point $(\tau, \sigma)$ on the worldsheet.
 Now if one adopts the ``sigma model'' point of view then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet.
@@
 
-% The end result is that we now have a gauge field $\mc{A}_a^{IJ}(\tau , \sigma)$ living on the worldsheet $\Sigma$.
-Here the lower index $a$ is the worldsheet index and $I , J$ labels the generators of the Lie algebra $\mf{so}(d,1)$.
+% The end result is that we now have a gauge field $\mc{A}_a^{IJ}(\tau, \sigma)$ living on the worldsheet $\Sigma$.
+Here the lower index $a$ is the worldsheet index and $I, J$ labels the generators of the Lie algebra $\mf{so}(d,1)$.
 Remember this is a gauge field which is now living on the worldsheet.
@@
 % \begin{equation}\label{eqn:covariant-deriv-v2}
-% 	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
+% 	\mc{D}_a X^I(\tau, \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
 % \end{equation}
@@
 \begin{equation}\label{eqn:covariant-deriv-v2}
-	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + \mu \mc{A}_{a}^A{}_B X^B.
+	\mc{D}_a X^A(\tau, \sigma) = \partial_a X^A + \mu \mc{A}_{a}^A{}_B X^B.
 \end{equation}
@@
 \begin{equation}\label{eqn:poincare-polyakov-decomp}
-	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r] ,
+	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r],
 \end{equation}
@@
 \begin{multline} \label{eqn:poincare-polyakov-decomp-explicit}
-	S' _{P} [X^{\mu} , X^{r}] = -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \\
+	S' _{P} [X^{\mu}, X^{r}] = -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \\
 	- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r} - \\
-	- \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r} ,
+	- \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r},
 \end{multline}
@@
 \begin{equation} \label{eqn:gauged-f-metric}
-	\frac{1}{f} = g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B} ,
+	\frac{1}{f} = g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B},
 \end{equation}
@@
 	\mc{D}_{a} [\sqrt{- g} g^{a b} \mc{D}_{b} X^{B} G_{B C}] = \\
-	= \sqrt{g} g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} \partial _{C} G_{A B} ,
+	= \sqrt{g} g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} \partial _{C} G_{A B},
 \end{multline}
@@
 \begin{equation} \label{eqn:adS-bulk-connection}
-	\mc{A}_{\mu} = \begin{bmatrix} 0 & 0 & 0 & 0 & \delta ^{0} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{1} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{2} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{3} _{\mu} \\ - \delta ^{0} _{\mu} & \delta ^{1} _{\mu} & \delta ^{2} _{\mu} & \delta ^{3} _{\mu} & 0 \end{bmatrix} ,
+	\mc{A}_{\mu} = \begin{bmatrix} 0 & 0 & 0 & 0 & \delta ^{0} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{1} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{2} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{3} _{\mu} \\ - \delta ^{0} _{\mu} & \delta ^{1} _{\mu} & \delta ^{2} _{\mu} & \delta ^{3} _{\mu} & 0 \end{bmatrix},
 \end{equation}
@@
 \begin{multline}
-	X^{r} (x) = X^{r} _{0} (x) + \\ + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \\ \times (2 + \mu X^{r} _{0} (x^{(k)})) ,
+	X^{r} (x) = X^{r} _{0} (x) + \\ + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \\ \times (2 + \mu X^{r} _{0} (x^{(k)})),
 \end{multline}
@@
 This perspective allows us to construct the Polyakov action for the bimetric string in \eqref{eqn:polyakov-bimetric}.
-Of course, one would expect that the (area-corrected) Polaykov and Nambu-Goto formulations should be physically equivalent.
+Of course, one would expect that the (area-corrected) Polyakov and Nambu-Goto formulations should be physically equivalent.
 Imposing this requirement leads us to the conclusion that the object $\Delta$ in \eqref{eqn:ng-area-corrected} must be worldsheet two-form (antisymmetric tensor) corresponding to the pullback of the \emph{bulk} Kalb-Ramond field.
@@
 Let us make one crucial observation here.
-In the expression \eqref{eqn:ng-area-corrected} we originally took $\Delta$ to a constant representing the smallest quantum of area.
-It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polaykov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form!
+In the expression \eqref{eqn:ng-area-corrected} we originally took $\Delta$ to be a constant representing the smallest quantum of area.
+It is only \emph{later}, by demanding consistency of the area-corrected Nambu-Goto and Polyakov actions that we realise that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form!
 
@@
 This also had the effect of not having distinct left and right moving modes, thus there was no level-matching prohibiting spin-1 states for the closed string, which we postulated to maybe be related to the Ashtekar variables of the background geometry.
-The quantisation of the KG string and the Virasoro-Klein-Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu} , B_{\mu \nu} , \Phi$ fields as part of the spin-2 spectrum.
+The quantisation of the KG string and the Virasoro-Klein-Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu}, B_{\mu \nu}, \Phi$ fields as part of the spin-2 spectrum.
 
@@
 
-\begin{equation}\label{eqn:ws-metric}
+\begin{equation}\label{eqn:induced-metric}
 	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu},
@@
 
-Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x^a$ of the embedding co-ordinates and the vielbein $e_\mu^I$.
+Now, if we compare the two expressions \eqref{eqn:induced-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x^a$ of the embedding co-ordinates and the vielbein $e_\mu^I$.
 This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.
@@
 \begin{equation} \label{eqn:modified-ng-bc}
-	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
+	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0,
 \end{equation}
@@
 \begin{equation} \label{eqn:transverse-'gauge'}
-	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0 ,
+	\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0,
 \end{equation}
@@
 \begin{equation} \label{eqn:string-energy}
-	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
+	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s,
 \end{equation}
@@
 \begin{equation} \label{eqn:corrected-ng-wave-equation}
-	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
+	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0,
 \end{equation}
@@
 \begin{equation} \label{eqn:sigma-parameterization}
-	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2} ,
+	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2},
 \end{equation}
@@
 \begin{equation} \label{eqn:simplified-modified-wave-eqn}
-	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
+	(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0,
 \end{equation}
@@
 
-Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq (\ref{eqn:simplified-modified-wave-eqn}) obtained in section \ref{sec:modified-eom}, renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t , x) \rightarrow (\tau (t , x) , \sigma (t , x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
+Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq (\ref{eqn:simplified-modified-wave-eqn}) obtained in section \ref{sec:modified-eom}, renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t, x) \rightarrow (\tau (t, x), \sigma (t, x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
 \begin{multline} \label{eqn:new-coordinates-constraints-quadratic}
 	\ \ \ \ \ \ \ \ \ \ (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \\
-	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma , \ \ \ \ \ \ \ \ \ \ \ \
+	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma, \ \ \ \ \ \ \ \ \ \ \ \
 \end{multline}
@@
 	\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \partial _{t} \tau = v \partial _{x} \sigma \\
-	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ,
+	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \,
 \end{multline}
@@
 \end{multline}
-Next, we introduce $X^{\mu} = \kappa (\tau , \sigma) W^{\mu} (\tau , \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
+Next, we introduce $X^{\mu} = \kappa (\tau, \sigma) W^{\mu} (\tau, \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
 This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$.
@@
 \begin{equation}
-	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0 ,
+	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0,
 \end{equation}
@@
 \end{equation}
-and $\tau (t , x)$ satisfying constraints (\ref{eqn:new-coordinates-constraints-compact}).
+and $\tau (t, x)$ satisfying constraints (\ref{eqn:new-coordinates-constraints-compact}).
 This shows that our analysis of the action (\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the analysis of the inverse area corrected Nambu-Goto action (\ref{eqn:modified-ng-action}).

### 2025-08-26 AoP/response-to-referee-r2.tex
feat: replying to 2nd of referee comments

@@
 
-\AR
+\AR We have added the following para at the end of Section 6 (Emergent Dimensions and LQG):
+
+\emph{Of course the phenomenological realization of emergent dimensions faces significant observational constraints.
+Current precision tests of general relativity, including lunar laser ranging experiments and binary pulsar observations, constrain deviations from Einstein's theory at scales larger than $\sim 10^{-4}$ m, while accelerator experiments at the LHC probe physics down to $\sim 10^{-19}$ m without detecting signatures of extra dimensions.
+The emergent dimension $X^r$ proposed here would need to manifest in a way that preserves the apparent four-dimensional nature of spacetime at these intermediate scales, possibly through a mechanism analogous to compactification or dimensional reduction, where the emergent dimension becomes effectively decoupled from standard model physics except at very large cosmological scales or very high energies approaching the string scale.}
 
@@
 
-\AR
+\AR We have added the following footnote right after ``\emph{leaves $m_{0}, m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental}}'' in Sec 6:
+
+\emph{Of course, the notion of what is ``fundamental'' is relative.
+After all, this is a phenomenological model and a very crude one at that.
+Moreover if holography is correct then it stands to reason that our $3+1$ dimensional bulk geometry has an equivalent description in terms of a theory living on a $2 + 1$ dimensional  ``boundary''.
+And if one takes the argument to its logical limit then there is no reason \emph{not} to reduce further from $2+1$ $\rightarrow$ $1+1$ $\rightarrow$ $0+1$ dimensions.
+In fact, this is what proponents of matrix models would argue that \emph{is} the ``correct'' picture.}
 
@@
 
-\AR
+\AR In the text we have used the accepted value of the cosmological constant as measured by the Planck collaboration.
+In this sense our argument already relies on current cosmological data.
+Moreover we have already mentioned in the text that this is a speculative idea based on a ``back of the envelope calculation''.
+Doing a deeper analysis of the relation of this idea to current cosmological data would take us too far afield.
 

### 2025-08-26 lqg-strings.tex
feat: replying to 2nd of referee comments

@@
 Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry.
-We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0}, m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
+We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0}, m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental}\footnote{Of course, the notion of what is ``fundamental'' is relative.
+After all, this is a phenomenological model and a very crude one at that.
+Moreover if holography is correct then it stands to reason that our $3+1$ dimensional bulk geometry has an equivalent description in terms of a theory living on a $2 + 1$ dimensional  ``boundary''.
+And if one takes the argument to its logical limit then there is no reason \emph{not} to reduce further from $2+1$ $\rightarrow$ $1+1$ $\rightarrow$ $0+1$ dimensions.
+In fact, this is what proponents of matrix models would argue that \emph{is} the ``correct'' picture.} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}.
 $(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013Zwei-Dreibein},\cite{Blais2013A-new-quantization},\cite{Carlip2003Quantum}).
@@
 where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
+
+Of course the phenomenological realization of emergent dimensions faces significant observational constraints.
+Current precision tests of general relativity, including lunar laser ranging experiments and binary pulsar observations, constrain deviations from Einstein's theory at scales larger than $\sim 10^{-4}$ m, while accelerator experiments at the LHC probe physics down to $\sim 10^{-19}$ m without detecting signatures of extra dimensions.
+The emergent dimension $X^r$ would have to behave in such a way that it either affects the physics at very high energies or at very large scales, perhaps at galactic or cosmological scales where precise observations do not yet exist.
 

### 2025-08-26 lqg-strings.tex
wrote the appendix on the relation between KR field and quantum of area 2-form

@@
 
+\section{Relation between Kalb-Ramond field and Quantum of Area 2-form} \label{sec:KR-QA}
+
+We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$.
+Varying this action \wrt \ $\Delta ^{c d}$ yields
+\begin{multline} \label{eqn:var-act-AC-KR}
+	\frac{\delta S}{\delta \Delta ^{c d}} = - \frac{1}{4 \pi \alpha '} \Bigg( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \bigg( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) - \\
+	- \bigg( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \bigg) \bigg( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \\
+	+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) \Bigg) ,
+\end{multline}
+which when required to vanish can be rearrenged into
+\begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
+	\Delta _{c d} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) - \\
+	- \bigg( g + \frac{k \Delta}{2} \bigg) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
+\end{multline}
+From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Klab-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
+\begin{equation} \label{eqn:QA-pullKR}
+	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
+\end{equation}
+where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb-Ramond field
+\begin{multline} \label{eqn:1/f-KR}
+	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
+	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) .
+\end{multline}
+When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \eqref{eqn:1/f-KR} simplifies to
+\begin{equation} \label{eqn:1/f-KR-simp}
+	\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
+\end{equation}
+or alternatively
+\begin{equation} \label{eqn:f-KR-simp}
+	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
+\end{equation}
+Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb-Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
+\begin{equation} \label{eqn:QA-KR-fin}
+	\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
+\end{equation}
+
 \bibliographystyle{JHEP3}

### 2025-08-26 lqg-strings.tex
fix: spelling correction and clarification about expression for inverse of metric

@@
 \end{multline}
-and completely analogous for the $H_{\mu \nu}$ metric,
+and completely analogously for the $H_{\mu \nu}$ metric,
 \begin{equation} \label{eqn:variation-wrt-h}
@@
 \begin{equation} \label{eqn:h=SgS}
-	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
-\end{equation}
-By writing the inverse metric $g^{a b}$ in terms of Levi-Civita symbols $g^{a b} = \varepsilon ^{a c} \varepsilon ^{b d} g_{c d} / 2 g$, this implies that
+	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d}.
+\end{equation}
+Taking the determinant of both sides of the above equation gives us $h = \Delta ^2 / g$.
+By writing the inverse metric $g^{a b}$ in terms of Levi-Civita symbols $g^{a b} = \varepsilon ^{a c} \varepsilon ^{b d} g_{c d} / 2 g$\footnote{This expression for the inverse of a metric is probably not familiar to many people, but its correctness can be checked by contracting both sides of the expression with $g_{ab}$ and seeing that the resulting expression is the much better known expression for the determinant $g \equiv \det{g_{ab}}$}, this implies that
 \begin{multline} \label{eqn:SgS-implication}
@@
 \end{multline}
-which when required to vanish can be rearrenged into
+which when required to vanish can be rearranged into
 \begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
@@
 \end{multline}
-From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Klab-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
+From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
 \begin{equation} \label{eqn:QA-pullKR}

### 2025-08-27 lqg-strings.tex
corrected the equations in sec 3B missing the f's, clarified the importance of the equation describing the KR pullback and justified the area corrected KR action

@@
 \begin{multline} \label{eqn:SgS-implication}
-	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
+	\left( f^{(H)} \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} f^{(G)} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\
 	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0,
@@
 \begin{equation} \label{eqn:H=1/(2g)G}
-	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .
+	H_{\mu \nu} = \frac{f^{(G)}}{f^{(H)}} \frac{\Delta}{2 g} G_{\mu \nu} .
 \end{equation}
@@
 If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-ng-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish.
-This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field.
-The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
+This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ should be related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but the actions discussed were actions for the free string, not coupled to said field.
+The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}, since this represents the more general and complete diffeomorphism invariant action in $1+1$ dimensions:
 \begin{multline} \label{eqn:area-corrected-K-R-action}
@@
 \end{equation}
-from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
+from which we can find the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ given in terms of the worldsheet metric $g$ and the quantum of area density $\Delta$
 \begin{equation} \label{eqn:WS-b-field}
@@
 
-We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$.
+We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, since this is the most generic and complete 2-dimensional action with worldsheet diffeomorphism invariance and bulk global Lorentz symmetry, with the correction to the worldsheet geometry due to quantum geometry proposed by our central dogma.
+The Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$.
 Varying this action \wrt \ $\Delta ^{c d}$ yields

### 2025-09-07 AoP/resubmit-cover-letter-r2.tex
Complete T4: Submit final AOP manuscript revisions
- Enhanced Kalb-Ramond field derivation with step-by-step exposition
- Fixed equation label references for improved clarity
- Addressed all referee clarifications in response document
- Successfully submitted revised manuscript for final acceptance
- Updated memory bank

--- 2025-07-06 AoP/resubmit-cover-letter.tex
@@
 \begin{center}
-\textbf{\large Cover Letter for Revised Manuscript Submission}
+\textbf{\large Cover Letter for 2nd Manuscript Revision}
 \end{center}
@@
 
-We are pleased to submit the revised version of our manuscript entitled ``A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales'' (Reference Number: AOP 81029) for publication in Annals of Physics.
+We thank you for your provisional acceptance of our paper in your esteemed journal.
 
-We have carefully addressed all comments and suggestions from the reviewers. A detailed point-by-point response is provided in the accompanying file ``response-to-referee.pdf''.
-
-\textbf{Author Name Change:} One co-author has requested a name change from Luigi Teixeira de Sousa to Lin Teixeira de Sousa.
-We have contacted namechange@elsevier.com per Elsevier's inclusive author name change policy.
-This correction does not affect authorship contributions or order.
-
-\textbf{Summary of Revisions:} Major improvements include: (1) Enhanced theoretical foundation with extensive discussions connecting our minimal area approach to existing minimal length proposals in string theory; (2) Clearer physical justification for the expansion parameter $k \ll 1$ and strengthened analogy with T/S-dualities; (3) Clarified anomaly-freedom claims, explaining this refers specifically to absence of central charge anomalies due to finite mode truncation; (4) Added important caveats about approach limitations; (5) Improved interpretation of emergent dimensions and their connection to holographic principles and cosmological horizon scale.
+We have carefully addressed all comments and suggestions from the second round of referee comments.
+A detailed point-by-point response is provided in the accompanying file ``response-to-referee-r2.pdf''.
+We hope that we have satisfactorily addresses any concerns the referee might have had.
 
@@
 
-We thank the reviewers for their constructive feedback and look forward to your favorable consideration.
+We thank the referee and the editor once again for their patient and constructive feedback through this process.
 
@@
 \noindent
-\textbf{Attachments:} \texttt{response-to-referee.pdf} (detailed response), \texttt{resubmit-cover-letter.pdf} (cover letter), \texttt{lqg-strings.pdf} (revised manuscript), \texttt{lqg-strings-diff.pdf} (diff file), \texttt{lqg-strings.bib} \& \texttt{lqg-strings.bbl} (bibliography files).
+\textbf{Attachments:} \texttt{response-to-referee-r2.pdf} (detailed response), \texttt{resubmit-cover-letter-r2.pdf} (cover letter), \texttt{lqg-strings.pdf} (revised manuscript).
 

### 2025-09-07 lqg-strings.tex
Complete T4: Submit final AOP manuscript revisions
- Enhanced Kalb-Ramond field derivation with step-by-step exposition
- Fixed equation label references for improved clarity
- Addressed all referee clarifications in response document
- Successfully submitted revised manuscript for final acceptance
- Updated memory bank

@@
 
-\graphicspath{{figures/}}
+% \graphicspath{{figures/}}
 
@@
 The condition $h = \Delta ^2 / g$ can be achieved by
-\begin{equation} \label{eqn:h=SgS}
+\begin{equation} \label{eqn:h-delta-relation}
 	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d}.
@@
 which can be achieved if the expression in parenthesis vanishes. For this end, the most natural possibility is
-\begin{equation} \label{eqn:S=sigma_y}
+\begin{equation} \label{eqn:delta-epsilon-relation}
 	\Delta _{a c} = \sqrt{\Delta} \varepsilon _{a c}
@@
 since we must have that $\det (\Delta _{a b}) = \Delta$ and $\Delta _{a c} \varepsilon ^{c c'} \sim \delta ^{c'} _{a}$, and also if the background metrics are related by
-\begin{equation} \label{eqn:H=1/(2g)G}
-	H_{\mu \nu} = \frac{f^{(G)}}{f^{(H)}} \frac{\Delta}{2 g} G_{\mu \nu} .
+\begin{equation} \label{eqn:H-G-relation}
+	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .
 \end{equation}
@@
 \end{equation}
-If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:
+If we impose the conditions \eqref{eqn:h-delta-relation}, \eqref{eqn:delta-epsilon-relation} and \eqref{eqn:H-G-relation} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-ng-action}:
 \begin{multline} \label{eqn:inverse-metric-Polyakov}
@@
 
-We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, since this is the most generic and complete 2-dimensional action with worldsheet diffeomorphism invariance and bulk global Lorentz symmetry, with the correction to the worldsheet geometry due to quantum geometry proposed by our central dogma.
-The Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$.
+To see how the area 2-form $\Delta _{ab}$ is related to the Kalb-Ramond field we have to go back to \autoref{sec:ws-kalb-ramond} where we looked at the case of the bimetric string action \eqref{eqn:polyakov-bimetric}.
+We saw that the bimetric Polyakov action can be expressed, quite obviously, as a bimetric Nambu-Goto action \eqref{eqn:double-ng-action}, which we reproduce below for convenience:
+\begin{equation}
+	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h}.
+\end{equation}
+From here if we make the mapping $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-ng-action}
+\begin{equation}
+	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
+\end{equation}
+Now, as noted in the main text, the condition $h = \Delta^2/g$ can be achieved if the following holds true \eqref{eqn:h-delta-relation}:
+\begin{equation*}
+	h_{ab} = \Delta_{ac} \Delta_{bd} g^{cd},
+\end{equation*}
+where $g^{cd}$ is the inverse of $g_{ab}$. Now, let us assume that $\Delta_{ab}$ can be written as \eqref{eqn:delta-epsilon-relation}:
+\begin{equation*}
+	\Delta_{ab} = \sqrt{\Delta} \epsilon_{ab}.
+\end{equation*}
+Now, we recall that the inverse of a $2\times 2$ matrix can be written using the total-antisymmetric symbol as:
+\begin{equation}
+	g^{ab} = \frac{1}{2g} \epsilon^{ac} \epsilon^{bd} g_{cd},
+\end{equation}
+where $g = \det{g_{ab}}$. Inserting this identity into \eqref{eqn:h-delta-relation}, and using the expression for the the determinant of a matrix in terms of product of epsilon symbols:
+\begin{equation*}
+	g = \det{g_{ab}} = \onehalf \epsilon^{ac} \epsilon^{bd} g_{cd},
+\end{equation*}
+we find that $h = \Delta^2/g$, where $\Delta = \det{\Delta_{ab}}$.
+What this tells us is that it is natural to identify $\Delta_{ab}$ with the totally anti-symmetric tensor on the worldsheet.
+Now a two-dimensional manifold can only have one, upto conformal transformations, anti-symmetric tensor and if we require that this tensor be derived from the embedding of the string into the ambient manifold then it makes sense that one should identify $\Delta_{ab}$ with the pullback to the worldsheet of the bulk Kalb-Ramond field $B_{\mu\nu}$.
+
+For a more formal derivation of this fact we start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$.
 Varying this action \wrt \ $\Delta ^{c d}$ yields

### 2025-10-23 AoP/final-proof/aop-format.tex
paper accepted, aop-format.tex file and proofreading in progress

\DocumentMetadata{%
pdfversion=1.7,%
%pdfversion=1.3,%
xmp=false,%
testphase={new-or-1}}%
\documentclass[fleqn,s1,tex]{neptune}
\usepackage[5.5]{neptune-els-dtd}
%% Please do not edit bookindate/proofdate
\bookindate{2025-10-01}
\proofdate{2025-10-09}
\usepackage[casnptn]{neptune-els} %% for CAS

\begin{pkg}
\beginTeX\usepackage{mathrsfs}\endTeX

\beginTeX\usepackage{stm-els-accents}\endTeX
\end{pkg}
\begin{additionalpkgs}

\end{additionalpkgs}

\usepackage{stm-els-tagpdf}
%\tagpdfsetup{paratagging-show=true}

\begin{document}
\newproof{proof}{Proof}

\long\def\stmdocstextcolor#1#2{#2}
\def\stmdocscolor#1{}

%%\def\stmdocsrangecite#1{#1} %% Add missing string in BODY and uncomment the macro

%\beginTeX\let\labelrm\rm\endTeX

%\beginXML\let\labelrm\relax\endXML

\begin{macros}

 \newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\wrt}{\textit{w.r.t.}}

\numberwithin{equation}{section}
\renewcommand{\thesection}{\arabic{section}}

\newcommand{\rarrow}{\rightarrow}

\newcommand{\del}{\partial}
\newcommand{\de}{\mathrm{d}}

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}

\newcommand{\etc}{\textit{etc.}}

\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\ep}{\epsilon}

\newcommand{\bz}{\mathbf{z}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mf}[1]{\mathfrak{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}

\newcommand{\unit}[1]{\hat{\mathbf{#1}}}

\newcommand{\id}{{\numbb{1}}}

\newcommand{\bra}[1]{\llangle #1 \rvert}
\newcommand{\ket}[1]{\lvert #1 \rrangle}

\newcommand{\sltwoc}{\mathfrak{sl}(2,\mathbb{C})}

\newcommand{\onehalf}{\frac{1}{2}}

\newcommand{\Tr}{\mathrm{Tr}}

\newcommand{\Cyl}{\mathrm{Cyl}}

  \newcommand{\diff}{\mathrm{d}}
\newcommand{\inp}{\mathrm{i}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\Lagr}{\mathscr{L}}
\newcommand{\PS}{\mathcal{P}}

\end{macros}
\begin{additionalmacros}

\jshort
\def\xURL{URL\xspace}  %%If prefix URL not required, remove "URL" from the definition\.

\end{additionalmacros}

%%%\endheaderBC

\begin{frontmatter}
%\QUERY[1]

\stmauorcid[Deepak Vaid]{0000-0002-0310-4599}
\stmaucontribution[Deepak Vaid]{Writing -- review \& editing,
Writing -- original draft,
Project administration,
Methodology,
Conceptualization}

\stmaucontribution[Lin Teixeira {de Sousa}]{Writing -- review \& editing,
Writing -- original draft,
Methodology,
Formal analysis}

\title{A loop quantum gravity inspired action for the bosonic string and emergent dimensions at large scales}

%
\addrai[1]{S0003491625003227-c34a61138b2fbb515d7c5be45fd1c03f} 
\addrai[2]{S0003491625003227-20ca3776d8d3b3899ab373e77faa92df}

\begin{authorgroup}

\author[a]{Deepak Vaid}
\email[dvaid79@gmail.com]
%\QUERY[2]
%\QUERY[3]

\shortname{L.T. de Sousa}
\author[b]{Lin Teixeira {de Sousa}} 
\email[luigi.tiraque@gmail.com]
\cormark[1]
\cortext[1]{\COR
% \TFadd[\AffNum].
}

\affiliation[a]{a={Independent Researcher}, ap={}}

\affiliation[b]{o={Universidade Federal de S\~ao Carlos}, cy={Brazil}}

\end{authorgroup}

\begin{abstractgroup}
\begin{abstract}[1]
We propose a modification of the Nambu--Goto action for the bosonic string which is compatible with the existence of a minimum area at the Planck scale. The result is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geometry and are bounded from below. This leads us to a string action which is similar to that of bimetric gravity. We provide formulations of the bimetric string action for both the Nambu--Goto (second order) and Polyakov (first order) formulations. We explore the classical solutions of this action and its quantization and relate it to the conventional string solutions.
\spara
 We further construct a string action in which the effect of the background geometry is described in terms of the pullback of the bulk connection, which encodes the bulk geometry, to the worldsheet. The resulting string action is in the form of a gauged sigma model, where the spacetime co-ordinates are now vectors which transform under the Poincar\'e group $ISO(D,1)$. This requires the introduction of an auxiliary bulk co-ordinate which has a natural interpretation as a holographic or scale direction. We discuss possible cosmological implications of such a large scale emergent dimension.
\end{abstract}

\keywords{Quantum gravity\sep Loop Quantum Gravity\sep String theory\sep Gauge theory\sep Holography\sep Emergent dimensions}

\end{abstractgroup}

\dataavailableat{Data availability}{No data was used for the research described in the article.}

\end{frontmatter}

\section{Introduction}
\xlabel{sec:intro}

``Quantum gravity'' refers to the broad enterprise dedicated to finding a complete, consistent theory in which quantum mechanics coexists peacefully with general relativity. There are two major approaches to quantum gravity which are widely recognized for their success in describing various aspects of physics at the Planck scale.

The first of these is \emph{string theory}~\cite{Polchinski1998String,Polchinski2007String}, the quantum theory of a one dimensional object which is said to contain within it a complete description of all particles, forces
and their interactions, including gravity. However, where precisely in the vast space of effective field theories which can possibly arise as in the low energy limit of a conjectured ``M-Theory'', our Universe with its
collection of particles, forces and coupling constants, exists, is still a matter of vigorous debate.

The second approach is called \emph{loop quantum gravity} or ``LQG'' for short~\cite{Rovelli1998Loop,Rovelli2015Covariant}. LQG is ostensibly meant to be a theory of ``pure quantum gravity'', that is gravity without any
matter. Matter can always be ``added'' in by hand into the framework but is not present to begin with. LQG is also built upon a rigorous mathematical framework which applies the well-established Dirac procedure of
quantization to canonical (ADM) Einstein gravity, and this is crucial, written in terms of Ashtekar variables which is a connection based approach as opposed to the conventional metric formalism. LQG has concrete
predictions such as discreteness of physical areas~\cite{Rovelli1993Area,Rovelli1994Discreteness}, and also has rigorous mathematical results which reproduce the black hole entropy formulae for Einstein
gravity~\cite{Rovelli1996Black}. Moreover it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.

In this paper we present a phenomenological modification of the Nambu--Goto action for the bosonic string which has the property that the worldsheet area can never be less than some fixed constant value $\Delta$ which represents the minimum allowed quantum of area predicted by LQG.

The following is the outline of the paper along with a brief summary of what is accomplished in each section. For those seeking a rapid review of the principle areas of difference between the two theories \xref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.

Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \xref{sec:modified-ng} where we begin by recalling the
Nambu--Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that {there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In
recent work~\cite{Borissova2024From} a very similar expression to ours for the modified Nambu--Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}

The key insight is to translate this fundamental discreteness of area from spacetime geometry to the worldsheet of the string itself. In LQG, the eigenvalues of the area operator are discrete, meaning physical areas can only take values from a quantized spectrum with minimum eigenvalue $\Delta$. For a string worldsheet, this suggests that the total worldsheet area $\mathcal{A} = \int d^2\sigma \sqrt{-h}$ cannot be arbitrarily small but must satisfy $\mathcal{A} \geq \Delta$.

Rather than imposing this constraint externally, we incorporate it directly into the action by modifying the area element itself. The natural way to ensure the worldsheet area respects LQG's minimal area is to replace the standard area element $\sqrt{-h}$ with $\sqrt{-(h+k\Delta)}$ where $k = l_{pl}/l_s$ is the ratio of Planck to string scales. This modification has several appealing features: it reduces to the standard Nambu--Goto action when $k \to 0$, it ensures the worldsheet area can never become arbitrarily small, and it provides a concrete mechanism to incorporate LQG's geometric quantization into string theory.

This approach differs from previous minimal length proposals in string theory~\cite{Amati1989Canb,Chang2011Minimal,Gross1987Highenergy,Gross1988String,Yoneya1989Interpretation,Yoneya2000String} in that it specifically
targets area rather than length, reflecting LQG's emphasis on area as the fundamental geometric observable.

We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length --- the length at which quantum geometric effects become important --- $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$. We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity. In \xref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity. We find both, the Nambu--Goto and the Polyakov forms of this action. Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb--Ramond field $B_{\mu \nu}$ into the worldsheet.

In \xref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion. We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb--Ramond field. Furthermore, we explore an equivalence between our proposed model and the Born--Infeld model in $1 + 1$ dimensions. We conclude this section by solving the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints. In \xref{sec:quantum-kg-string} we follow the route of covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.

In \xref{sec:emergent-dimensions} we complement Afshordi's work~\cite{Afshordi2014Emergent} with insights from LQG, showing that LQG quantum geometry naturally constrains most of the free parameters of said model, leading
to a more concrete theory. We also suggest a possible consequence for the parameters that remain unconstrained and a generalization of the model.

In \xref{sec:holographic-strings} we describe how to construct an action for the bosonic string which encodes the geometry of the bulk spacetime in the language of the connection formulation of general relativity. We find that this can be done by viewing the worldsheet embedding co-ordinates $X$'s as living in the fundamental representation of a suitable gauge group $G$. Consistency between the dual roles played by the $X$'s as both co-ordinates for the background manifold {and} and as objects which can be parallel transported using a connection, requires that the gauge group $G$ be the Poincar\'e group $ISO(D+1,1)$. In other words the string which originally was embedded in a $D+1$ dimensional background, now lives in a $D+2$ dimensional geometry which has one extra ``emergent'' dimension which has the natural interpretation as a {scaling} dimension. We therefore view our construction as providing a natural framework for {classical holography}, where the scale dimension is already built into the theory at the classical level instead of something which arises due to non-perturbative physics.

There are various appendices containing details of calculations and background information. In  \xref{sec:modified-eom} we derive the equations of motion for the modified Nambu--Goto action.  \xref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu--Goto and Polyakov versions of the modified string action are equivalent to each other.

\subsection{Historical Background}
\xlabel{sec:history}

Traditionally, there are two ways in which a classical theory can be quantized. These are the Hamiltonian and Lagrangian approaches. The Lagrangian or path integral approach follows the prescription first suggested by Dirac and then made concrete by Feynman. There one views the classical action associated to a given evolution as corresponding to a {phase angle} which determines the complex weight of the associated evolution. This approach respects spacetime covariance since here the central object is the action which is invariant under spacetime transformations by construction. String theory is an example of such a formalism.

The Hamiltonian approach, on the other hand, involves making a choice of a spacelike surface $\Sigma_t$ and a corresponding timelike vector $t^\mu$, normal to $\Sigma_t$ (here $t$ is a continuous parameter which labels the family of surfaces). This approach, therefore, necessarily does not respect spacetime covariance since it involves making a specific choice of the foliation of the background into spacelike surfaces. Loop quantum gravity is built upon this approach to quantization.

In the decades prior to the advent of string theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches. The Hamiltonian approach involves, as stated earlier, a choice of the foliation of the background geometry into a collection of spacelike surfaces $\Sigma_t$. Central to this approach was the ADM (Arnowitt--Deser--Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein--Hilbert action $S_{EH}$. The resulting phase space is coordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of the extrinsic curvature $k_{ab}$ of the leaves.\footnote{Our notational convention is the following. Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}   The gravity Hamiltonian turns out to be a sum of two constraints known as the diffeomorphism (or ``momentum'') constraint $H_{diff}$ and the Hamiltonian constraint $H_{ham}$:
\begin{equation}
H_{GR} = H_{diff} + H_{ham},
\end{equation}
and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$. The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$, must be annihilated by these constraints:
\begin{equation}
H_{GR} \ket{\Psi_{phys}} \equiv 0
\end{equation}
While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian
constraints on the configuration and momentum variables. This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar~\cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory
of a dualized $\mathfrak{sl} (2, \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
\begin{equation}
 \xlabel{eqn:self-dual-spin-connection}
A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{\beta}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu}
\end{equation}
and its conjugate momenta
\begin{equation}
 \xlabel{eqn:densitized-tetrad}
B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K}_{\text{[} {\mu}} e^{L} _{\nu \text{]}}
,
\end{equation}
which when restricted to a 3-dimensional hypersurface where $* (e \wedge e) = 0$ reduces to
\begin{equation}
 \xlabel{eqn:Ashtekar-connection-canonical}
A^{i} _{a} = \omega ^{i} _{a} + \beta K^{i} _{a}
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:Ashtekar-E-field-canonical}
E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c},
\end{equation}
with $K^{i} _{a}$ being the triad version of the extrinsic curvature $K_{a b} = \frac{1}{2} \mathcal{L}_{n} q_{a b}$ and $q$ the 3-metric. Ashtekar realized that the constraints of general relativity, when expressed in terms of these ``new
variables'', simplified drastically and became polynomial functions of the tetrad and connection variables. It was quickly realized by various researchers that the resulting theory could be quantized using the same methods
used to quantize Yang--Mills gauge theory~\cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network}
states~\cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.

Following this, work by Rovelli and Smolin~\cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct
quantum operators for geometric quantities such as areas of two-dimensional surfaces and volumes of three-dimensional regions. Moreover, these operators could be diagonalized exactly in the spin-network basis and a
discrete spectrum for quantum of area and quantum of volume could be derived. This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression,
in a theory of quantum gravity. One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high-energy theory community, was the calculation of the
entropy of a Schwarzschild black hole~\cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein--Hawking entropy.

One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$\footnote{Here, the index convention followed is that lowercase $i, j, k$ refer to 3-dimensional flat internal
($\mf{su}(2)$) indices and lowercase $a, b, c$ refer to 3-dimensional curved spacetime indices}  can no longer be a continuous function of spacetime, rather it becomes a {distribution}, assuming a constant value on
one patch of space, then another value at another patch, etc~\cite{Bodendorfer-LQG,Rovelli2015Covariant}. The consequence of this non-continuous distributional nature of the connection is that the triad (or Ashtekar
electric field) operator, which formally would be
\begin{equation}
 \xlabel{eqn:triad-operator}
\Hat{\widetilde{E}}\text{}^{a} _{i} = - 8 \pi i \hbar G \frac{\delta}{\delta A^{i} _{a}}
\end{equation}
becomes ill-defined since $A^{i} _{a}$ is non-continuous (in particular, at the edges of a polyhedra it changes abruptly), so the triad needs to be {smeared} over a surface where $A^{i} _{a}$ is constant
\begin{equation}
 \xlabel{eqn:triad-flux-operator}
\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}},
\end{equation}
where $\diff S_{a} = \diff \sigma ^{b} \wedge \diff \sigma ^{c} \varepsilon _{a b c}$. This naturally leads to the {area operator} of said surface
\begin{equation}
 \xlabel{eqn:area-operator}
\Hat{A} (S) = - 8 \pi i l_{pl} ^2 \beta \int _{S} \sqrt{\diff S_{a} \diff S_{b} \frac{\delta}{\delta A^{i} _{a}} \frac{\delta}{\delta A_{b i}}} .
\end{equation}
Notably, since $A^{i} _{a}$ is a $\mf{su}(2)$-valued connection, in the basis which diagonalizes the area operator (the {spin network} basis~\cite{Bodendorfer-LQG}) $\ket{\Tr (h^{(j)} _{c} (A))}$, the eigenvalues of the area operator are
just proportional to {angular momentum} eigenvalues
\begin{equation}
 \xlabel{eqn:area-eigenvalues}
\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))},
\end{equation}
with $j$ being the representation label of $\mf{su}(2)$ along the spin network edge piercing the surface under consideration. Thus, spin network edges carry angular momenta.

One of the primary criticisms of string theory is its apparent lack of ``background independence''. This is more general than the principle of {general covariance} which states that physics should be independent of
the choice of co-ordinates. Background independence is the statement that any {quantum} theory of gravity should provide a description of physics which is independent, not only of the choice of co-ordinates, but also
of the choice of background manifold on which those co-ordinates live. Such a theory should provide a description not only of classical spacetimes, but also of fluctuating, semiclassical geometries and those in the deep
quantum regime which do not have any sensible description in terms of any Riemannian geometry. On the face of it, string theory, at least in its conventional form, does not satisfy this principle.\footnote{Recent work has
highlighted fundamental challenges to achieving manifest background independence in string theory. Hohm has shown that there exists a fundamental conflict between manifest background independence and duality invariance
when higher-derivative corrections are included~\cite{Hohm2017Background,Hohm2018Background}.}   The great virtue of LQG on the other hand, is that it respects background independence by construction and proceeds to
quantize gravity while ensuring that (a notion of) background independence forms the core of the quantum theory.

Some will argue that string theory is, indeed, background independent. The argument for this is as follows. When coupled to the string action, background fields are treated as external ``coupling constants'' and can
therefore be subject to a renormalization group analysis. The fixed point of this analysis, remarkably enough, requires one to impose the condition that the background metric obeys Einstein's field equations (more
precisely that the background is {Ricci flat}. This is explained in greater detail in  \xref{sec:strings-gravity}) In our opinion, however, this result is insufficient evidence for asserting that string theory is
background independent.\footnote{However, developments in string field theory continue to address these foundational issues~\cite{Maccaferri2024String,Sen1994Quantum} primarily in the framework of string field theory. For
an overview of the general concept of background independence in quantum gravity see~\cite{Read2023Background}.}   Our reasons are the following:

\begin{enumerate}[itemsep=0.5em]
 \item While the conformal invariance of the string worldsheet implies that the background is Ricci flat, this, in itself, is not very surprising. After all conformal invariance of worldsheet is equivalent to the statement of diffeomorphism invariance of the worldsheet, and in order for this to be consistent with the bulk geometry, the bulk geometry should also have a description in terms of a diffeomorphism invariant theory, the simplest example of which is Einstein gravity. However, this by itself is not sufficient to characterize string theory as being background independent. Neither do we have an understanding of how to quantize a string for which the bulk is arbitrarily curved to begin with. Nor does this tell us the microscopic mechanism of ``string condensation'' via which an arbitrary curved geometry is supposed to arise.

 \item One can ask what is the quantum mechanical description of the bulk geometry? It is often suggested that the bulk geometry corresponds to a coherent state or a graviton condensate, where the graviton are themselves excitations of the fundamental string. However, there does not appear to be an actual mathematical realization of this statement in terms of non-perturbative physics.
 \item Finally, as mentioned in the introduction, in any {quantum} theory of gravity one would expect to be able to describe the ``atoms of geometry''. There is no sense in which this is realized in this picture of gravity emerging from stringy physics. Even though one can calculate higher order corrections to the graviton beta function and this provides us with the quantum corrected effective action for the bulk geometry, all the physical quantities are still defined in terms of continuous fields such as the metric. For \eg, to the best of our knowledge, there is no clear sense in which one construct a {non-perturbative} state which corresponds to a superposition of geometries using the quantum theory of a bosonic string alone.
\end{enumerate}

Despite all these concerns string theory has emerged as the primary candidate for a theory of quantum gravity. {There are good reasons for this}. AdS/CFT --- in our opinion, the most concrete example of a
{non-perturbative} theory of quantum gravity --- arose out of string theory~\cite{Maldacena1998The-Large,Witten1998Anti,Aharony1999Large,Gubser1998Gauge}. AdS/CFT is a particular realization of quantum gravity rather
than a theory of quantum gravity per se.

Anti-deSitter space describes a universe with a negative cosmological constant ($\Lambda < 0$) whereas the one we inhabit appears to have a small but positive cosmological constant ($\Lambda > 0$). Of course, nowhere in the literature of the AdS/CFT correspondence is it implied that it is the AdS bulk which corresponds to our physical universe. If anything our physical universe will turn out to live on the boundary of an anti-deSitter bulk.

AdS spaces do arise in actual physical phenomena in {our} universe~\cite{Bardeen1999The-Extreme,Guica2009The-Kerr/CFT}. The correspondence itself has passed numerous checks and is now considered part of the
established canon. Moreoever, it has led to numerous theoretical insights. We have gained a deep understanding of the properties of real world systems referred to as ``strange
metals''~\cite{Hartnoll2016Holographic,Sachdev2010Strange,Sachdev2015Bekenstein-Hawking} by studying their dual gravitational theories. The significance of quantum error correction and quantum information for a theory of
quantum gravity was also first most clearly illuminated via AdS/CFT~\cite{Almheiri2014Bulk,Pastawski2015Holographic}. For these, and other reasons too numerous to mention here, many theorists still regard string theory as
the primary (or even the sole) candidate for a theory of quantum gravity.

Thus, we are now at an impasse. We have two theories, both built upon strong mathematical foundations, but which do not appear to be in concordance with each other. There are two possibilities. The first is that one of the two approaches is fundamentally flawed in some way and must be rejected altogether. The second is that we are missing some crucial ingredient which would allow us to find a missing link between the two theories. We feel that it worthwhile to explore the second option in greater detail, if for no other reason then to rule out the possibility of such a link between these two theories.

\section{Modified \?{Nambu Goto} Action}
\xlabel{sec:modified-ng}

Before proceeding let us restate our ``central dogma''. We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators --- such as those that measure the area and volume of a given region of space --- exist and have discrete spectra, thus the transition from no area/volume to some area/volume is a discrete jump rather than a continuous one. We now wish to understand how to construct a worldsheet action which reflects this central dogma.

In a very real sense string theory is a quantum theory of geometry. After all, the Nambu--Goto action:
\begin{equation}
\xlabel{eqn:ng-action}
S_{NG} = -T \int \diff ^2 x \sqrt{- \det h}
\end{equation}
is nothing more than the {area} of the string worldsheet. So when we are constructing the quantum theory of the string we are constructing a theory in which the fundamental excitations are geometric in nature. What we would like to do is to modify the string action in a way which incorporates the insight from LQG that at the Planck scale there is a minimum quantum of area. One simple way in which to do this is to modify the action \neqref{eqn:ng-action} as follows:
\begin{equation}
 \xlabel{eqn:ng-area-corrected}
S_{M N G} = - T \int \diff ^2 x \sqrt{- (h + k \Delta)}.
\end{equation}
At present we do not have a rigorous derivation of this expression. It is the simplest possible ansatz one can think of to encode the insight from LQG that at the Planck scale there is a minimum quantum of area. What makes us more confident in this ansatz is that it is consistent with the Kalb--Ramond field identification and the minimal area interpretation of the scalar density $\Delta$. However, this was not known prior to coming up with the ansatz and only discovered after the fact.

Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale.\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}   In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu--Goto action with small corrections coming from quantum geometry. In this limit we can expand the integrand as follows:
\begin{equation}
 \xlabel{eqn:inverse-metric-correction}
\sqrt{- (h + k \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
\end{equation}
If we take $k$ to be an expansion parameter, then it follows that it should also be small. The physical justification for this is the following picture. The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams. The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures. In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network. When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment --- \ie~ where geometry itself is fully quantum --- is required.

The limit $k \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\Delta$, $h \gg \Delta$. Thus in this limit $ k^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(k^2/h^2)$ corrections. The final area corrected Nambu--Goto action becomes:
\begin{equation}
 \xlabel{eqn:modified-ng-action}
S'_{NG} = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} \frac{k \Delta}{\sqrt{- h}} \right).
\end{equation}
This action has, to the best of our knowledge, not been explored in the string theory literature. However, such an inverse determinant term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections, in the context of the 3D volume of spatial hypersurfaces.

The action Eq. \neqref{eqn:modified-ng-action} has manifest background Poincar\'e invariance since just like the regular Nambu--Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars. At first glance it might seem to not be WS reparameterization invariant because of the second term, however, this is corrected by the fact that $\Delta$ is a scalar {density} of weight 2, thus counteracting the inverse metric determinant. Moreover, if we look at that expression we see that it can be written as:
\begin{equation}
 \xlabel{eqn:modified-ng-action-v2}
S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {k \Delta}{\sqrt{- (h^{-1})}} \right),
\end{equation}
where $h^{-1}$ is now the determinant of the {inverse} metric $h^{ab}$. As such, in the expression \neqref{eqn:modified-ng-action} we can see a duality between the first and second terms. If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \neqref{eqn:modified-ng-action}, but with the difference that the factor of $k \Delta/2$ is mapped to $2 / (k \Delta)$:
\begin{align}
 \xlabel{eqn:modified-ng-action-v3}
S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{k \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {k' \Delta'}\sqrt{- (h')^{-1}} \right),
\end{align}
which has the same form as the original action \neqref{eqn:modified-ng-action}, as long as we make the replacements
\begin{subequations}
\begin{equation}
 \xlabel{eqn:T'}
T \rightarrow T' = - \frac{1}{2} k T
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:k-Delta}
\frac{1}{2} {k \Delta} \rarrow \frac{1}{2} {k' \Delta'} = \frac{2} {k \Delta}
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:d2x}
\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x
\end{equation}
\end{subequations}
(or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$). This is a duality between the physics at the Planck scale and the physics at the string scale, \ie~ between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.

This duality is reminiscent of, but also distinct from, the $T$ and S dualities in string theory. In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$. In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$. In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$. This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence. Physically, one way in which this duality could manifest in the real world is in the mass spectrum of string excitations which when computed in the strong-coupling regime should exhibit a precise correspondence with spectra in the weak-coupling limit under the transformation rules \neqref{eqn:T'}--\neqref{eqn:d2x}, while worldsheet correlation functions should satisfy similar duality relations, potentially providing calculable predictions for string phenomenology at both energy scales.

Now, one might object and say that having an action which is the sum of two Nambu--Goto actions seems strange. However, similar actions have been extensively studied under the heading of ``bimetric gravity'', with the
earliest work dating as far back as 1940 in two papers~\cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER'). In 2010, bimetric gravity gained great popularity
due to the seminal paper~\cite{de-Rham2011Resummation} which showed that by introducing a second {reference} metric into a model for massive gravity one can get rid of the Boulware--Deser
ghost~\cite{Boulware1972Can-Gravitation} which otherwise plagues theories with massive gravitons. The {reference} metric introduced in the work~\cite{de-Rham2011Resummation} was taken to be a flat metric. However
later work~\cite{Hassan2012Bimetric,Hassan2012Ghost-Free} showed that the second metric need not be flat and that an action of the following form:
\begin{eqnarray}
\xlabel{eqn:hassan-bimetric}
\nf&& S = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)} + \nonumber\\\nf&&\xq
+ 2 m^2 M^2_{eff} \int \diff^4 x \sqrt{-g}\sum_{n=0}^{4}\beta_n e_n (\sqrt{g^{-1} f}),
\end{eqnarray}
where $g_{\mu\nu}$ and $f_{\mu\nu}$ are {arbitrary} metrics, $M_g^2, M_f^2$ are the Planck masses for the two sectors respectively. $R^{(g)}, R^{(f)}$ are the respective Ricci scalars for each sector. The third term is an interaction term which is responsible for making one of the gravitons massive while the other remains massless. $M^2_{eff}$ is an {effective} Planck mass given by:
\begin{equation}
\xlabel{eqn:hassan-effective-mpl}
M^2_{eff} = \left( \frac{1}{M^2_g} + \frac{1}{M^2_f} \right)^{-1}
\end{equation}

\section{The Bimetric String}
\xlabel{sec:bimetric-string}

It would be natural to suspect that the action \neqref{eqn:modified-ng-action-v2} might be related to bimetric gravity in the target space of the string. We can see that this is indeed the case as follows.

There are two ways that a string with two metrics might arise. One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$. As a result, the induced metrics on the string worldsheet would also be different for both sets of embedding fields. However, in this case, we would not be talking about {one} string but two {different} strings described by the respective embedding functions. One could then proceed along the lines of \neqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
\begin{equation}
\xlabel{eqn:ws-bimetric-interaction}
S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
\end{equation}
Here $\Phi(g,h)$ is some function of the {induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields. The resulting action would be of the form:
\begin{equation}
\xlabel{eqn:ws-bimetric-action-v1}
S_{BNG} = -T \int \diff^2 x \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
\end{equation}
Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.

As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware--Deser ghost in theories of massive gravity. However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.

The second possibility is the following. Rather than considering two different sets of embedding fields, and consequently two different worldsheets, we can work with one set of embeddings $X^\mu(\tau,\sigma)$ and {two different} bulk metrics $G_{\mu\nu}$ and $H_{\mu\nu}$. As a result, we would now get two different induced metrics on the {same} string worldsheet, given by:
\begin{subequations}
\xlabel{eqn:ws-induced-metrics}
\begin{align}
g_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu}  \\
h_{ab} & = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} H_{\mu\nu}.
\end{align}
\end{subequations}
We can then write down the combined action for the string worldsheet as:
\begin{equation}
\xlabel{eqn:ws-bimetric-action-v2}
S'_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S'_{int},
\end{equation}
where now $S'_{int}[g,h,\mb{X}]$ is a term describing the interaction between the two metrics living on the {same} worldsheet.

\subsection{Bimetric \?Polyakov Action}
\xlabel{sec:bimetric-polyakov}

The expression \neqref{eqn:ws-bimetric-action-v2} is not ideal because it does not retain any memory of the form of the bulk metrics unless these are included in the interaction term $S'_{int}$. One way to manifestly exhibit the dependence of the respective worldsheet actions on the two bulk metrics is to work with the Polyakov action.

Following the general procedure given in~\cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
\begin{equation}
\xlabel{eqn:polyakov-curved}
S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
\begin{eqnarray}
\xlabel{eqn:polyakov-bimetric}
\nf&& S_{PB} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} - \nonumber\\\nf&&\xq
- \frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} +  \nonumber\\\nf&&\xq
+ S_{int} [g, h, X].
\end{eqnarray}

\subsection{(Worldsheet) \?{Kalb Ramond} and Area Quantization}
 \xlabel{sec:ws-kalb-ramond}

In the following, we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified as being the determinant of (a tensor proportional to) the antisymmetric symbol $\varepsilon _{a c}$ living on the worldsheet. The worldsheet antisymmetric symbol can itself be understood as arising from the pullback of a bulk antisymmetric tensor. Now, in string theory, there is already a very important antisymmetric background tensor: the Kalb--Ramond field.

Following the usual procedure such as the one found in~\cite{Tong2009Lectures}, we find two copies of the string energy--momentum tensor:
\begin{equation}
 \xlabel{eqn:variation-wrt-g}
\frac{\delta S_{P B}}{\delta g^{c d}} = 0
\end{equation}
\begin{eqnarray}
 \xlabel{eqn:g-em-tensor}
\nf&& T^{(G)} _{c d} \coloneq  G_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \nonumber\\\nf&&\xq
- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \biggm) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}},
\end{eqnarray}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation}
 \xlabel{eqn:variation-wrt-h}
\frac{\delta S_{P B}}{\delta h^{c d}} = 0
\end{equation}
\begin{eqnarray}
 \xlabel{eqn:h-em-tensor}
\nf&& T^{(H)} _{c d} \coloneq  H_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \nonumber\\\nf&&\xq
- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \biggm) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
\end{eqnarray}
If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
\begin{equation}
 \xlabel{eqn:g-expression}
g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation}
 \xlabel{eqn:g's-f-function}
\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
and for $h_{c d}$
\begin{equation}
 \xlabel{eqn:h-expression}
h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu},
\end{equation}
with $f^{(H)}$ given by
\begin{equation}
 \xlabel{eqn:h's-f-function}
\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
\begin{equation}
 \xlabel{eqn:double-ng-action}
S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h},
\end{equation}
and from here we note that if $T' = - T k/2$ and $h = \Delta ^2/g$, we recover the Nambu--Goto area-corrected action \neqref{eqn:modified-ng-action}
\begin{equation}
 \xlabel{eqn:area-corrected-ng-from-bimetric}
S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
The condition $h = \Delta ^2/g$ can be achieved by
\begin{equation}
 \xlabel{eqn:h-delta-relation}
h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d}.
\end{equation}
Taking the determinant of both sides of the above equation gives us $h = \Delta ^2/g$.
By writing the inverse metric $g^{a b}$ in terms of Levi-Civita symbols $g^{a b} = \varepsilon ^{a c} \varepsilon ^{b d} g_{c d} / 2 g$,\footnote{This expression for the inverse of a metric is probably not familiar to many people, but its correctness can be checked by contracting both sides of the expression with $g_{ab}$ and seeing that the resulting expression is the much better known expression for the determinant $g \equiv \det{g_{ab}}$}  this implies that
\begin{eqnarray}
 \xlabel{eqn:SgS-implication}
\nf&&\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times\nonumber \\\nf&&\xq
\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0,
\end{eqnarray}
which can be achieved if the expression in parenthesis vanishes. For this end, the most natural possibility is
\begin{equation}
 \xlabel{eqn:delta-epsilon-relation}
\Delta _{a c} = \sqrt{\Delta} \varepsilon _{a c}
\end{equation}
since we must have that $\det (\Delta _{a b}) = \Delta$ and $\Delta _{a c} \varepsilon ^{c c'} \sim \delta ^{c'} _{a}$, and also if the background metrics are related by
\begin{equation}
 \xlabel{eqn:H-G-relation}
H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .
\end{equation}
This makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form. Now, since the WS metric $g_{a b}$ is taken as the pullback of the bulk metric $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, which is part of the closed string spin-2 spectrum, then it would make sense for the WS area 2-form $\Delta _{a b}$ to be (at least related to) the pullback of the Kalb--Ramond field, which is the other half of the closed string rank 2 tensor field excitations,
\begin{equation}
 \xlabel{eqn:Delta-B-relation}
\Delta _{a b} \sim \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} .
\end{equation}
If we impose the conditions \neqref{eqn:h-delta-relation}, \neqref{eqn:delta-epsilon-relation,eqn:H-G-relation} plus $T' = - T k/2$ in the interactionless bimetric Polyakov action \neqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \neqref{eqn:modified-ng-action}:
\begin{eqnarray}
 \xlabel{eqn:inverse-metric-Polyakov}
S_{I A P}& =& - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times\nonumber \\\nf&& \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{eqnarray}

\section{Inverse Metric \?Polyakov}
 \xlabel{sec:inverse-metric-Polyakov}

In this section, we explore the action \neqref{eqn:inverse-metric-Polyakov} derived previously. This action is even more manifestly background Poincar\'e invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables. This action at first glance does not have WS Weyl invariance since the second term has inverse determinant multiplied by inverse metric, however, if one wishes to restore Weyl symmetry one just needs to require that under a Weyl transformation, the $\Delta _{a b}$ field also transforms like the metric \ie~
\begin{subequations}
\begin{align}
g_{a b}       & \rightarrow \Lambda (x) g_{a b} \xlabel{eqn:g-Weyl-transform}             \\
\Delta _{a b} & \rightarrow \Lambda (x) \Delta _{a b}, \xlabel{eqn:Delta-Weyl-transform}
\end{align}
\end{subequations}
however, we will not work under this assumption, since we expect that Weyl symmetry is broken near the Planck scale due to the discreteness of space--time.

The equations of motion for the world-sheet metric are completely unchanged by this correction,
\begin{equation}
 \xlabel{eqn:vary-wrt-g}
\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
which leads to the stress--energy tensor for the worldsheet:
\begin{eqnarray}
 \xlabel{eqn:inverse-area-em-tensor}
\nf&& T_{c d} \coloneq  \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \nonumber\\ \nf&&\xq - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
\end{eqnarray}
from which we can extract the metric $g_{c d}$ as
\begin{equation}
 \xlabel{eqn:ws-metric}
g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
\end{equation}
where the function $f$ is given by
\begin{equation}
 \xlabel{eqn:inverse-area-f}
\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
just like the regular ST literature, thus the constraints are unchanged by our correction.

As for variation \wrt \ the embbeding fields $X^{\lambda}$, we have
\begin{equation}
 \xlabel{eqn:vary-wrt-X}
\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}
\begin{eqnarray}
 \xlabel{eqn:X-eom-inverse-area}
\nf&& F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} =\nonumber \\\nf&&\xq = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
\end{eqnarray}
where
\begin{equation}
 \xlabel{eqn:F-minus-def}
F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
\end{equation}
Since all 2-dimensional metrics are conformally flat~\cite{Schottenloher2008A-Mathematical}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify Eq. \neqref{eqn:X-eom-inverse-area} into
\begin{equation}
 \xlabel{eqn:X-eom-simplified}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
\end{equation}
By expanding the definition of $F^{-}$ we get
\begin{equation}
 \xlabel{eqn:coupling-X-phi}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0,
\end{equation}
revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field~\cite{Balthazar-t-backgrounds}. We will come back to
this in \xref{sec:emergent-dimensions}.

\subsection{Worldsheet \?{Kalb--Ramond} field and Quantum of Area}
 \xlabel{sec:WS-Kalb-Ramond-QoA}

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \neqref{eqn:modified-ng-action,eqn:inverse-metric-Polyakov} explored before, one would end up concluding that
either $\Delta _{a b} = 0$ or its determinant $\Delta = 0$ vanish. This happens because, as we explored in  \xref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb--Ramond field $B_{\mu \nu}$, but
those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb--Ramond field~\cite{Tong2009Lectures}
\begin{eqnarray}
 \xlabel{eqn:area-corrected-K-R-action}
S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \nonumber\\\nf&&\xq
\times \Bigl( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigr),
\end{eqnarray}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{eqnarray}
 \xlabel{eqn:area-corrected-K-R-action-v2}
S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times\nonumber \\
&&\times \Bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigm) .
\end{eqnarray}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation}
 \xlabel{eqn:Delta-pullback}
\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{eqnarray}
 \xlabel{eqn:1/f-tilde}
\frac{1}{\widetilde{f}} &=& \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - 
\nonumber\\\nf&&- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm),
\end{eqnarray}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation}
 \xlabel{eqn:f-tilde}
\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
\end{equation}
from which it is easy to see that the pullback of the Kalb--Ramond field $b_{a b} \coloneq  \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation}
 \xlabel{eqn:WS-b-field}
b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation}
 \xlabel{eqn:Delta-b-relation}
\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb--Ramond field is actually a tensor {density} of weight $- 1$, since the coefficient in Eq. \neqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

This pullback relationship would suggest a restriction on the allowed bulk configurations. Since the worldsheet area spectrum is discrete due to the underlying LQG quantization, the Kalb--Ramond field strength must be correspondingly quantized. This is analogous to flux quantization in the quantum Hall effect, where the magnetic flux through the 2D electron system is constrained to be integer multiples of $h/e$. In our case, the integrated field strength $\int H_{\mu \nu \rho}$ over appropriate 3-cycles in the bulk should be quantized in units related to the fundamental area quantum $\Delta$, restricting the allowed background field configurations to those compatible with the discrete worldsheet area spectrum.

\subsection{Area-Corrected \?{Nambu--Goto} Action and \?{Born}--Infeld Electrodynamics}
 \xlabel{sec:area-corrected-BI}

The Nambu--Goto area-corrected action before approximations \neqref{eqn:ng-area-corrected} has a structure strikingly similar to the Born--Infeld
model~\cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
\begin{equation}
 \xlabel{eqn:BI-action}
S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})},
\end{equation}
with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string. Remarkably, if one considers a $(1 + 1)$-dimensional Born--Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
\begin{equation}
 \xlabel{eqn:area-corrected-NG-BI-equivalence}
\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta,
\end{equation}
thus the action \neqref{eqn:ng-area-corrected} can be recast as a Born--Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength. Also, we have a direct relation between string tension and scale
\begin{equation}
 \xlabel{eqn:k-T}
\frac{l_{pl}}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
\end{equation}

\subsection{Simplifying The Equations of Motion}
 \xlabel{sec:solving-eoms-inverse-area}

\eqref{eqn:X-eom-simplified} seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$. By using the ansatz in Eq. \neqref{eqn:X-eom-simplified}, it becomes
\begin{equation}
(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation}
 \xlabel{eqn:derivatives-F-minus}
\partial _{\tau} \ln (F^{-}) = i E, \ \partial _{\sigma} \ln (F^{-}) = i p,
\end{equation}
thus we have
\begin{equation}
 \xlabel{eqn:ln-F}
\ln (F^{-}) = i (E \tau + p \sigma) + a, \ a \in \mathbb{C}
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:F-minus-exp}
F^{-} = A \e ^{i (E \tau + p \sigma)}, \ A \in \C
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:phi}
\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
\end{equation}
It may seem problematic to have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$. With this choice, we thus turned Eq. \neqref{eqn:X-eom-simplified} into a Klein--Gordon equation
\begin{equation}
 \xlabel{eqn:X-Klein-Gordon-eqn}
\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The imposition that
\begin{equation}
 \xlabel{eqn:mu-constraint-1}
i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
\end{equation}
can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as
\begin{eqnarray}
 \xlabel{eqn:mu-constraint-final}
\mu ^2 &=& \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \bigm( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \nonumber\\\nf&&
- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \bigm) .
\end{eqnarray}

\subsection{Solving The String \?Klein--\?{Gordon} Equation}

In the following, we focus on the analysis of the closed string unless otherwise stated.

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein--Gordon Eqs.~\neqref{eqn:X-Klein-Gordon-eqn}, with constraints given by Eq. \neqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they are the same as the ones of regular String Theory. What is new in our analysis is the $\mu ^2$ term, which we take as being constant for a first analysis, making it so the solution is given by Fourier transform
\begin{eqnarray}
 \xlabel{eqn:KG-Polyakov-solution-initial}
X^{\mu} (\tau, \sigma) &=& \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \biggm( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \nonumber\\\nf&&
+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \biggm),
\end{eqnarray}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in~\cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation}
 \xlabel{eqn:reality-consequence}
\beta ^{\mu} _{n} = (\alpha ^{\mu} _{n})^{*} .
\end{equation}
When looking at the constraints, we see that we cannot decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{subequations}
\begin{align}
L_{n, p} \coloneq  \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0, \ \forall \ n, p \in \mathbb{Z}, \xlabel{eqn:"virasoro"-modes-1} \\
\widetilde{L}_{n, p} \coloneq  \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0, \ n \neq p, \xlabel{eqn:"virasoro"-modes-2}                       \\
\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \xlabel{eqn:"virasoro"-modes-sum} .
\end{align}
\end{subequations}
Constraint \neqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p}, \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0, \ \forall \ \svert n\svert  > d$, so we have a truncated solution. This is not surprising, since because space--time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

Before proceeding, we have one remark: the 0-th term of the solution reads
\begin{equation}
 \xlabel{eqn:X-sol-0-term}
\sqrt{\frac{\alpha '}{2}} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right),
\end{equation}
which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$. Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
\begin{equation}
 \xlabel{eqn:a-p-relation}
\alpha ^{\mu} _{0} = \sqrt{\frac{2}{\alpha '}} \mu x^{\mu} + i \frac{1}{2} \sqrt{\frac{\alpha '}{2}} p^{\mu} .
\end{equation}
This in actuality will differ from the normal ST literature by a factor of $1/2$ in the momentum term, but this is needed for the Poisson brackets to give the expected results.

Looking closer at our constraints \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
\begin{eqnarray}
 \xlabel{eqn:string-rest-mass-classical-1}
M^2 &=& - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n, n} \right) - \nonumber\\\nf&&
- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Biggm) =
\end{eqnarray}
\begin{eqnarray}
 \xlabel{eqn:string-rest-mass-classical-2}
\nf&& = \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \nonumber\\\nf&&
- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Biggm) .
\end{eqnarray}

\subsection{The Expansion Modes Algebra}

We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
\begin{eqnarray}
 \xlabel{eqn:canonical-momentum-density}
\Pi ^{\nu} (x) &=& F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \biggm( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \nonumber\\\nf&&
- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \biggm)
\end{eqnarray}
where
\begin{eqnarray}
 \xlabel{eqn:F-minus-full-sum}
F^{-} &=& 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \nonumber\\\nf&&
= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right),
\end{eqnarray}
and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
\begin{equation}
 \xlabel{eqn:canonical-bracket-relation}
\left\{ X^{\mu} (0, \sigma), \Pi ^{\nu} (0, \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$. After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the expected
\begin{subequations}
\begin{align}
\left\{ \alpha ^{\mu} _{n}, \alpha ^{\nu} _{p} \right\}       & = 0 = \left\{ (\alpha ^{\mu} _{n})^{*}, (\alpha ^{\nu} _{p})^{*} \right\} \xlabel{eqn:expansion-modes-bracket-0} \\
\left\{ \alpha ^{\mu} _{n}, (\alpha ^{\nu} _{p})^{*} \right\} & = - i E_{n} \delta _{\svert n\svert , \svert p\svert } \eta ^{\mu \nu}, \xlabel{eqn:expansion-modes-bracket-1}
\end{align}
\end{subequations}
from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
\begin{subequations}
\begin{align}
a^{\mu} _{n}       & \coloneq  \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \xlabel{eqn:normalized-oscillator-modes}         \\
(a^{\mu} _{n})^{*} & \coloneq  \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \xlabel{eqn:normalized-oscillator-modes-*}
\end{align}
\end{subequations}
\begin{equation}
 \xlabel{eqn:harmonic-bracket-relations}
\left\{ a^{\mu} _{n}, (a^{\nu} _{p})^{*} \right\} = - i \delta _{\svert n\svert , \svert p\svert } \eta ^{\mu \nu} .
\end{equation}
The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
\begin{align}
\left\{ x^{\mu}, x^{\nu} \right\} & = 0 = \left\{ p^{\mu}, p^{\nu} \right\} \xlabel{eqn:x-x-p-p-brackets} \\
\left\{ x^{\mu}, p^{\nu} \right\} & = \eta ^{\mu \nu} . \xlabel{eqn:x-p-bracket-relations}
\end{align}

\subsection{The \textquotedblleft \?{Virasoro-Klein}--\?{Gordon}" Algebra}

Having the bracket relations between the vibrational modes of the string, we can now calculate the constraints algebra, which we shall refer to as the Virasoro--Klein--Gordon Algebra. For simplicity, since $E_{n} = \sqrt{n^2 + \mu ^2} > 0$, we shall work with the normalized harmonic oscillator modes $a^{\mu} _{n}$ instead of the expansion modes $\alpha ^{\mu} _{n}$. Then, the algebra in terms of said normalized modes is given by
\begin{subequations}
\begin{equation}
 \xlabel{eqn:L-brackets-0}
\left\{ L_{n, m}, L_{k, p} \right\} = 0
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:L-brackets-1}
\left\{ L_{n, m}, \widetilde{L}_{k, p} \right\} = - i \left( L_{m, k} \delta _{\svert n\svert , \svert p\svert } + L_{n, k} \delta _{\svert m\svert , \svert p\svert } \right)
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:L-brackets-2}
\left\{ \widetilde{L}_{n, m}, \widetilde{L}_{k, p} \right\} = - i \left( \widetilde{L}_{k, m} \delta _{\svert n\svert , \svert p\svert } - \widetilde{L}_{n, p} \delta _{\svert m\svert , \svert k\svert } \right) .
\end{equation}
\end{subequations}

\section{The Quantum \?Klein--\?{Gordon} String}
 \xlabel{sec:quantum-kg-string}

We now seek to quantize the Klein--Gordon string by means of covariant quantization, in a manner much similar to those found in~\cite{Tong2009Lectures,Green2012Superstring}. The string coordinates $X^{\mu}$ and its conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ ., . \}$ being replaced by commutators $\{ ., . \} \rightarrow - i [ ., . ]$:
\begin{subequations}
\begin{align}
\left[ \Hat{X}^{\mu} (\tau, \sigma), \Hat{\Pi}^{\nu} (\tau, \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \xlabel{eqn:X-P-commutator}                                              \\
\left[ \Hat{X}^{\mu}, \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu}, \Hat{\Pi}^{\nu} \right] \xlabel{eqn:X-X-P-P-commutators}                                 \\
\left[ \Hat{a}^{\mu} _{n}, \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger}, (\Hat{a}^{\nu} _{p})^{\dagger} \right] \xlabel{eqn:a-a-a*-a*-commutators} \\
\left[ \Hat{a}^{\mu} _{n}, (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{\svert n\svert , \svert p\svert } \eta ^{\mu \nu} \xlabel{eqn:a-a*-commutator}                                                      \\
\left[ \Hat{x}^{\mu}, \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu}, \Hat{p}^{\nu} \right] \xlabel{eqn:x-x-p-p-commutators}                                     \\
\left[ \Hat{x}^{\mu}, \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \xlabel{eqn:x-p-commutator}
\end{align}
\end{subequations}

As usual, we define the vacuum state of the string to obey
\begin{equation}
 \xlabel{eqn:annihilation-vacuum}
\Hat{a}^{\mu} _{p} \ket{0} = 0, \ \mathrm{for} \ p \neq 0 .
\end{equation}
For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
\begin{subequations}
\begin{align}
\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \xlabel{eqn:x-vacuum-x}                       \\
\Hat{p}_{\mu} \ket{0 ; x} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \xlabel{eqn:p-vacuum-x}
\end{align}
\end{subequations}
in position representation $\ket{0 ; x} \equiv \ket{0} \otimes \psi (x)$ and
\begin{subequations}
\begin{align}
\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \xlabel{eqn:x-vacuum-p} \\
\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \xlabel{eqn:p-vacuum-p}
\end{align}
\end{subequations}
in momentum representation $\ket{0 ; p} \equiv \ket{0} \otimes \psi (p)$.

Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
\begin{equation}
 \xlabel{eqn:general-state}
\ket{\psi} = \prod _{i \neq 0} ((\Hat{a}^{\mu _{i}} _{i})^{\dagger})^{n_{i}} \ket{0} .
\end{equation}
As usual, the appearance of the Minkowski metric in the non-zero commutator
\begin{equation}
 \xlabel{eqn:ghosts}
\Bigl[ \Hat{a}^{\mu} _{p}, (\Hat{a}^{\nu} _{k})^{\dagger} \Bigr] = \eta ^{\mu \nu} \delta _{\svert p\svert , \svert k\svert },
\end{equation}
brings ghosts into the theory which must be dealt with.

When translating the constraints as quantum operators, we impose them strongly, requiring that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$ since said constraints are not self-adjoint:
\begin{subequations}
\begin{equation}
 \xlabel{eqn:L-constraint-quantum-1}
\bra{\phi} \Hat{L}_{p, k} \ket{\psi} = 0 \, \,
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:L-constraint-quantum-2}
\bra{\phi} \Hat{\widetilde{L}}_{p, k} \ket{\psi} = 0 .
\end{equation}
\end{subequations}
$\Hat{L}_{p, k}$ has no ambiguities since it is composed of only annihilation operators. As for $\widetilde{L}_{p, k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
\begin{equation}
 \xlabel{eqn:L-normal-ordering}
\Hat{\widetilde{L}}_{p, p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
\end{equation}
This ambiguity manifests in the imposition of the constraint as
\begin{equation}
 \xlabel{eqn:shifted-L-constraint}
\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n, n} \right) - a \right) \ket{\psi} = 0,
\end{equation}
for some constant $a$. Classically, we had Eq. \neqref{eqn:string-rest-mass-classical-1} for the string rest mass, from which we can now see that the string mass spectrum will get shifted by this constant
\begin{eqnarray}
 \xlabel{eqn:shifted-mass-spectrum}
\Hat{M}^2 &=& \frac{8}{\alpha '} \Biggm( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \nonumber\\\nf&&
- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Biggm) .
\end{eqnarray}
This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d, d)$ is finite, and the result is
\begin{eqnarray}
a &=& - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \nonumber\\\nf&&
= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n},
\end{eqnarray}
which is easily computable given a value for $\mu$. Below we provide a table with the value of $a$ for different spacetime dimensionalities $D$ and mass parameters $\mu$ (see \tabref{TeXFolio:tab1}).
%\QUERY[4]

\begin{table}[width=0.6\textwidth]
\caption{\xlabel{tab:normal-ordering-constant}Values of $a$ for different spacetime dimensionalities and mass parameters. Visibly, the dependence in $D$ is much stronger than the dependence in $\mu$.}
\begin{tabular}{LLLLLL}
\beginthead
 & $\mu = 1$ & $\mu = 2$ & $\mu = 3$ & $\mu = 4$ & $\mu = 5$ \\
\endthead\rowhead 
$D = 2$ & \tmin 4.24 & \tmin 5.37 & \tmin 6.96 & \tmin 8.73 & \tmin 10.59 \\
$D = 3$ & \tmin 18.44 & \tmin 20.78 & \tmin 24.58 & \tmin 29.20 & \tmin 34.27 \\
$D = 4$ & \tmin 48.62 & \tmin 52.11 & \tmin 58.23 & \tmin 66.13 & \tmin 75.19 \\
$D = 5$ & \tmin 100.79 & \tmin 105.39 & \tmin 113.79 & \tmin 125.09 & \tmin 138.49 \\
$D = 6$ & \tmin 180.96 & \tmin 186.63 & \tmin 197.25 & \tmin 211.95 & \tmin 229.84 
\botline
\end{tabular}
\end{table}
This table shows that $a$ becomes more negative as either the spacetime dimension $D$ or the mass parameter $\mu$ increases. This means:

\begin{itemize}
 \item Higher dimensions lead to more massive ground states
 \item Larger $\mu$ (stronger discreteness effects) also increases ground state masses
 \item The spectrum becomes increasingly separated from the massless limit
\end{itemize}

For example, in $D=2$ with $\mu=1$, $a=-4.24$ gives a relatively light spectrum, while $D=3$ with $\mu=5$ yields $a=-34.27$, producing much heavier states. This demonstrates how LQG's discreteness parameter $\mu$ and the background dimensionality jointly control the departure from standard string theory's massless spectrum, with stronger quantum geometric effects pushing all states away from the massless limit expected in conventional string theory.

The commutation relations between the constraints are inherited by the Poisson brackets
\begin{subequations}
\begin{align}
\left[ \Hat{L}_{n, m}, \Hat{L}_{k, p} \right]                         & = 0 \xlabel{eqn:L-commutator-0}                                                                                                   \\
\left[ \Hat{L}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right]             & = \Hat{L}_{m, k} \delta _{\svert n\svert , \svert p\svert } + \Hat{L}_{n, k} \delta _{\svert m\svert , \svert p\svert } \xlabel{eqn:L-commutator-1}                           \\
\left[ \Hat{\widetilde{L}}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right] & = \Hat{\widetilde{L}}_{k, m} \delta _{\svert n\svert , \svert p\svert } - \Hat{\widetilde{L}}_{n, p} \delta _{\svert m\svert , \svert k\svert } \xlabel{eqn:L-commutator-2} .
\end{align}
\end{subequations}
The commutator \neqref{eqn:L-commutator-1} ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator \neqref{eqn:L-commutator-2} have ordering ambiguities for $\svert m\svert  = \svert k\svert $ and/or $\svert n\svert  = \svert p\svert $, so we add the anomalous terms
\begin{eqnarray}
 \xlabel{eqn:L-commutator-anomalous-initial}
\nf&&\left[ \Hat{\widetilde{L}}_{n, m}, \Hat{\widetilde{L}}_{k, p} \right] = \Hat{\widetilde{L}}_{k, m} \delta _{\svert n\svert , \svert p\svert } - \Hat{\widetilde{L}}_{n, p} \delta _{\svert m\svert , \svert k\svert } + \nonumber\\\nf&&
+ C_{n} \delta _{\svert n\svert , \svert p\svert } + D_{k} \delta _{\svert m\svert , \svert k\svert } .
\end{eqnarray}
Clearly, $C_{0} = D_{0} = 0$, since when all indices are $0$ we have only the position and momentum operators, and thus the commutator should vanish identically. Also, because of the symmetry in the indices we have that $C_{- n} = C_{n}$ and $D_{- k} = D_{k}$. Using the Jacobi identity we get the difference equation
\begin{equation}
 \xlabel{eqn:F-difference-eqn}
F_{n + 1} + F_{n} + F_{1} = 0
\end{equation}
for the sum of both sequences $F_{n} = C_{n} + D_{n}$. This difference equation has solution
\begin{equation}
 \xlabel{eqn:F-sequence}
F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right),
\end{equation}
and since both $C_{n}$ and $D_{n}$ need to satisfy the initial value of $0$, each of then is half of $F_{n}$,
\begin{equation}
 \xlabel{eqn:C-D-sequences}
C_{n} = D_{n} = \frac{F_{n}}{2} = \frac{F_{1}}{4} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) .
\end{equation}
Next, by calculating the vacuum expectation value (VEV) of the commutator \neqref{eqn:L-commutator-2} with $\svert m\svert  \neq \svert k\svert $ and $n = p = 1$, we find that $F_{1} = 0$, thus both sequences $C_{n} = D_{n} = 0$ vanish and we conclude that the quantum version of our algebra {has no anomalies}. This is a relevant result, since it could mean our model does not need a specific number of dimensions to work, which will be explored again later in  \xref{sec:emergent-dimensions}.

A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
\begin{subequations}
\begin{align}
\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n, n} \xlabel{eqn:WS-Hamiltonian}              \\
\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n, n} \xlabel{eqn:WS-momentum}
\end{align}
\end{subequations}
since those generate $\tau$ and $\sigma$ translations respectively
\begin{subequations}
\begin{align}
\left[ \Hat{H}, \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \xlabel{eqn:tau-generator}     \\
\left[ \Hat{P}, \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \xlabel{eqn:sigma-generator}
\end{align}
\end{subequations}
Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \neqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string. {Physical states for the KG string have non-conserved WS momentum.} Also, we see that there is no level-matching between left and right-moving modes since those are not distinct in our model.

Let us denote the ground state with momentum $p^{\mu}$ by $\ket{0 ; p}$. Then, the mass-shell condition \neqref{eqn:shifted-mass-spectrum} implies that
\begin{equation}
 \xlabel{eqn:ground-state-mass-shell}
\frac{\alpha '}{8} p^2 = \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert   ^2 + a .
\end{equation}
Next we look at the $n$th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution does not have distinct left and right sectors, thus permitting spin-1 states. We will discuss these closed string single excitation states in  \xref{sec:discussion}. The mass-shell now reads
\begin{eqnarray}
 \xlabel{eqn:nth-state-mass-shell}
\frac{\alpha '}{8} M^2 &=& \Biggm( \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert   ^2 - \nonumber\\\nf&&
- \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Biggm),
\end{eqnarray}
while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n, 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that
\begin{equation}
 \xlabel{eqn:zeta-p-psi}
\zeta _{\mu} p^{\mu} = - \frac{4 \mu}{\alpha '} \zeta _{\mu} \frac{\partial \psi (p)}{\partial p_{\mu}} .
\end{equation}
If the momentum wave-function is taken to be
\begin{equation}
 \xlabel{eqn:p-wave-function}
\psi (p) = - \frac{\alpha '}{8 \sqrt{2} \mu} p^{\mu} p_{\mu},
\end{equation}
eq \neqref{eqn:zeta-p-psi} reduces to $\zeta _{\mu} p^{\mu} = 0$. Putting this back in the mass-shell yields
\begin{equation}
 \xlabel{eqn:ground-state-mass-shell-simplified}
\frac{\alpha '}{16} p^2 = a = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k}
\end{equation}
for the ground state and
\begin{eqnarray}
 \xlabel{eqn:nth-mass-shell-simplified}
\frac{\alpha '}{16} p^2 &=& a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} = \nonumber\\\nf&&
= - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n}
\end{eqnarray}
for the $n$th state. The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, and since by Eq. \neqref{eqn:nth-mass-shell-simplified} we see that $p^2 < 0$, thus $\zeta ^2 > 0$ always holds and we have no ghosts in the closed string spin-1 spectrum. This analysis, however, is for vector states from the closed string. The actual particle we want from the closed string is a symmetric, traceless spin-2 particle, so let us now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor. The mass-shell reads
\begin{equation}
 \xlabel{eqn:nth-spin-2-mass-shell}
\frac{\alpha '}{16} p^2 = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - 4 \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n} .
\end{equation}
The auxiliary $\bra{0 ; p} \xi _{\alpha} \Hat{a}^{\alpha} _{n} \Hat{\widetilde{L}}_{n, 0} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \zeta _{\mu \nu} \ket{0 ; p} = 0$ condition where $\xi _{\alpha}$ is a arbitrary polarization for the auxiliary vector excitation implies that
\begin{equation}
 \xlabel{eqn:spin-2-zeta-p=0}
(\zeta _{\mu \nu} + \zeta _{\nu \mu}) p^{\mu} = 0 .
\end{equation}
We can decompose the polarization into a symmetric traceless part $G_{\mu \nu}$, an anti-symmetric part $B_{\mu \nu}$ and a trace part $\Phi \eta _{\mu \nu}$ given by
\begin{subequations}
\begin{align}
G_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} + \zeta _{\nu \mu}) - \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \eta _{\mu \nu} \xlabel{eqn:G-zeta} \\
B_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} - \zeta _{\nu \mu}) \xlabel{eqn:B-zeta}                                                                          \\
\Phi        & = \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \xlabel{eqn:Phi-zeta},
\end{align}
\end{subequations}
$\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-known types of background fields: the spacetime metric $G_{\mu \nu}$, Kalb--Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$, all of those having squared mass given by Eq. \neqref{eqn:nth-spin-2-mass-shell}. We thus see that the symmetric part $S_{\mu \nu} = G_{\mu \nu} + \Phi \eta _{\mu \nu}$ of $\zeta _{\mu \nu}$ is orthogonal to the momentum of the string, $S_{\mu \nu} p^{\mu} = 0$, and since $p^2 < 0$, we can choose a reference frame where $p^{\mu} = (p, 0, \ldots , 0)$ only has a time component, leaving us with $S_{0 \nu} = 0$, implying that $\zeta _{0 \nu} = - \zeta _{\nu 0}$. This condition guarantees that the timelike components of $\zeta _{\mu \nu}$ have a positive contribution to its square $\zeta ^{\mu \nu} \zeta _{\mu \nu} = \zeta ^{i j} \zeta _{i j} + b, \ b = \zeta ^{0 i} \zeta _{0 i} > 0$, and the remaining part is spacelike thus must also have positive square, so we get that $\zeta ^{\mu \nu} \zeta _{\mu \nu} > 0$, so we are free of ghosts in the spin-2 spectrum.

It seems we are in trouble since Eq. \neqref{eqn:nth-spin-2-mass-shell} tells us we have no massless 2 excitation states, but in fact, this is not a problem and is actually expected since quantum geometric effects are
expected to violate Lorentz invariance near the Planck scale~\cite{Bodendorfer-LQG}, making it so massless particles effectively travel slightly slower than $c$, with corrections on the order of $\sim E_{pl} ^{- 4}$.

The fact that $G_{\mu \nu}$ is symmetric, traceless and satisfies $G_{\mu \nu} p^{\mu} = 0$ leaves it with
\begin{equation}
 \xlabel{eqn:G-polarizations}
\frac{1}{2} D (D - 1) - 1
\end{equation}
possible polarizations, which shows that indeed those polarizations fit nicely in a representation of $\mathrm{SO} (D - 1, 1)$, \ie~ the traceless symmetric tensor representation, thus all our excited spin-2 states are consistent with Lorentz symmetry at the macroscopic scale even tho near the Planck scale they deviate a bit by having an effective mass.

Although our method is quite different from the one in~\cite{Thiemann2004The-LQG-String:}, we get similar results: a quantum Virasoro-like algebra with no anomalies, unconstrained background dimensionality $D$ and
no negative-norm states in physical processes.

It is important to clarify what we mean by ``no anomalies'' in this context. This refers specifically to the absence of central charge anomalies in our modified Virasoro-like algebra, which arises due to the finite mode truncation imposed by LQG's discreteness. This discreteness is encoded in the paramter $\mu$ in \neqref{eqn:mu-constraint-1}, which is a cutoff parameter that controls the maximum number of modes we consider in the action.

This differs fundamentally from standard string theory, where anomaly cancellation requires critical dimensions ($D = 26$ for bosonic strings) to ensure vanishing of the central charge from an infinite sum over modes. Our finite sum naturally avoids this constraint, permitting unconstrained background dimensionality $D$. However, this result applies specifically to our truncated model in the regime where $k \ll 1$, where the smooth worldsheet approximation remains valid. In the full quantum gravitational regime where $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and a more comprehensive analysis would be required.

Additionally, our anomaly-freedom and ghost-freedom analysis is limited to the tree-level constraints; quantum loop corrections and the full quantum effective action may introduce subtleties not captured in this treatment.

The mode truncation is a key assumption that requires validation. While we do not have a rigorous derivation from first principles, the physical motivation comes from LQG's discrete structure: high-frequency modes corresponding to sub-Planckian physics should be suppressed when the spin network discreteness becomes relevant. The parameter $\mu$ in \neqref{eqn:mu-constraint-1} provides an effective energy cutoff, with modes $\svert n\svert  > d \approx \mu$ being suppressed.

This approach shares similarities with other discrete quantum gravity approaches like causal dynamical triangulation and spin foam models, which also impose natural cutoffs. However, a complete justification would require deriving this truncation directly from LQG's canonical quantization procedure, which remains an open question for future work.

\section{Emergent Dimensions and {\?{LQG}}}
 \xlabel{sec:emergent-dimensions}

There is another alternative to incorporate LQG quantum-geometric effects into the string action and get something conceptually similar to what we had in  \xref{sec:inverse-metric-Polyakov}: Afshordi's \textquotedblleft
emergent dimension"~\cite{Afshordi2014Emergent} model, with the action being
\begin{eqnarray}
 \xlabel{eqn:emergent-dimensions-action}
S_{ED} &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \nonumber\\\nf&&
+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \bigm)
\end{eqnarray}
where $T$ is the {temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ... \gg m_{d}$. This is Afshordi's model~\cite{Afshordi2014Emergent}. Where our approach diverges is
that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as~\cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near
the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
\begin{equation}
 \xlabel{eqn:LQG-modified-dispersion-relation}
E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}},
\end{equation}
so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
\begin{equation}
 \xlabel{eqn:X-masses-constraint}
E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}},
\end{equation}
where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2, (E_{4})^2, \ldots , (E_{D - 1})^2$, \ie~, the squared WS energy (and momentum) of each field $X^{\mu}$.

Afshordi's work notes that the action \neqref{eqn:emergent-dimensions-action} only has background Poincar\'e invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the
\textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincar\'e symmetry. We go one step further and note that since eq
\neqref{eqn:X-masses-constraint} leaves $m_{0}, m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being {fundamental}\footnote{Of course, the notion of what is ``fundamental'' is
relative. After all, this is a phenomenological model and a very crude one at that. Moreover if holography is correct then it stands to reason that our $3+1$ dimensional bulk geometry has an equivalent description
in terms of a theory living on a $2 + 1$ dimensional  ``boundary''. And if one takes the argument to its logical limit then there is no reason {not} to reduce further from $2+1$ $\rightarrow$ $1+1$
$\rightarrow$ $0+1$ dimensions. In fact, this is what proponents of matrix models would argue that {is} the ``correct'' picture.}  and thus the true quantum gravitational field should be
$(2 + 1)$-dimensional, in agreement with~\cite{t-Hooft1993Dimensional}. $(2 + 1)$-dimensional gravity has already been successfully quantized
before~\cite{Bergshoeff2013Zwei-Dreibein,Blais2013A-new-quantization,Carlip2003Quantum}. We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \neqref{eqn:X-masses-constraint} should give us a way to
calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.

Our constraint Eq.~\neqref{eqn:X-masses-constraint} represents an attempt to bridge Afshordi's phenomenological emergent dimension model with LQG's general prediction of modified physics at the Planck scale. However, the specific form of these constraints and their derivation from first-principles LQG remains an open problem. While both frameworks involve discreteness --- Afshordi's through hierarchical mass parameters and LQG through quantized geometric operators --- establishing a concrete mathematical connection requires significantly more work.

This represents an important limitation of our current approach and highlights the need for future research to either derive such constraints from canonical LQG or develop alternative frameworks that more naturally incorporate both emergent dimensions and quantum geometric discreteness. Similar caveats also apply to our suggestion that \neqref{eqn:X-masses-constraint} should imply that spacetime is $(2 + 1)$-dimensional.

By analyzing the equations of motion for the metric $g_{c d}$ from the action \neqref{eqn:emergent-dimensions-action} we get
\begin{equation}
 \xlabel{eqn:emergent-dimensions-g}
g_{c d} = 2 f \del _{c} X^{\mu} \del _{d} X^{\nu} \eta _{\mu \nu},
\end{equation}
with $f$ given by
\begin{equation}
 \xlabel{eqn:emergent-dimensions-f}
\frac{1}{f} = g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \mu _{0} ^{2} \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu},
\end{equation}
from which we see that $\e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} = 0$ is actually a constraint and thus the base mass $\mu _{0} ^2$ is a Lagrange multiplier. By dimensional analysis, we see that in SI units $\mu _{0} ^2$ has units of inverse area, so it could be that $\mu _{0} ^2 \sim A_{j} ^{-1}$, where $A_{j}$ is the eigenvalue of the area operator with spin $j$, which depends on where the spin network punctures the WS, thus once more connecting Afshordi's work to LQG quantum geometry.

One could also consider a more general form of action \neqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
\begin{eqnarray}
 \xlabel{eqn:emergent-dimensions-curved}
S' _{E D} &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \nonumber\\\nf&&
+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \bigm),
\end{eqnarray}
where the mass parameters will be constrained as in
\begin{equation}
 \xlabel{eqn:X-masses-constraint-2}
E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n},
\end{equation}
since those are the ones that show up in the $X^{\mu}$ equations of motion
\begin{eqnarray}
\nf&& g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \nonumber\\\nf&&
= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
\end{eqnarray}

In  \xref{sec:inverse-metric-Polyakov} we arrived at Eq. \neqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$. We now explore this claim: since we could be dealing with emergent dimensions with an action \neqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a {worldsheet dilaton}, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
\begin{equation}
 \xlabel{eqn:mu0-phi-relation}
\mu _{0} ^2 \sim \e ^{- \phi (x)},
\end{equation}
where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.

Of course the phenomenological realization of emergent dimensions faces significant observational constraints. Current precision tests of general relativity, including lunar laser ranging experiments and binary pulsar observations, constrain deviations from Einstein's theory at scales larger than $\sim 10^{-4}$ m, while accelerator experiments at the LHC probe physics down to $\sim 10^{-19}$ m without detecting signatures of extra dimensions. The emergent dimension $X^r$ would have to behave in such a way that it either affects the physics at very high energies or at very large scales, perhaps at galactic or cosmological scales where precise observations do not yet exist.

\section{Holography From Classical Strings}
\xlabel{sec:holographic-strings}

Until now we have studied a phenomenological modification of the string action. However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system. Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that geometry to the geometry of the string worldsheet. In this section, we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.  We will explore the natural consequences which follow from considering the symmetries of such an action.

First let us recall the form of the Polyakov action for the bosonic string \neqref{eqn:polyakov-action}:
\begin{equation*}
S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation*}
If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$. The resulting action would now have the form:
\begin{equation}
\xlabel{eqn:polyakov-gauged}
S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} D_a X^\mu D_b X^\nu \eta_{\mu\nu},
\end{equation}
where the covariant derivative $D_a$ is of the form:
\begin{equation}
\xlabel{eqn:covariant-deriv-v1}
D_a X^\mu(\tau, \sigma) = \partial_a X^\mu + \mu \mc{A}_{a}^\mu\text{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu\text{}_\nu$ is the gauge field and $k$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming under the gauge group $\mc G$. But we will see that this is not a problem. In fact, in order to be able to couple the string to an {arbitrarily} curved geometry we will find that we {require} the $X^\mu$ to transform as vectors under the action of some {local} gauge field.

Our goal is to write down the action of a string propagating in a background geometry. One might argue that the expression \neqref{eqn:polyakov-curved-bulk}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry. However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones. An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \neqref{eqn:polyakov-curved-bulk} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates). This, however, leaves open the question of what role the bulk connection should play in this picture.

Further, we can ask what is the physical effect of having a non-trivial connection in the bulk in terms of the local geometry. The bulk connection tells us how the vielbein transforms from point to point and thus effectively measures how much the bulk metric changes from point to point. So, for instance, the connection which describes the geometry around a Kerr black hole also encodes how the local tetrad frame rotates as one moves around the axisymmetric axis of the black hole. All of these considerations lead us to the premise that {if one wishes to describes the bulk geometry in terms of connection variables, then it is only natural to describe the worldsheet geometry in terms of connection variables} and to use the tools that come along with having a gauge connection to understand how the worldsheet geometry can couple to the bulk geometry.

Therefore, now we will require that the bulk connection $\mc{A}_{\mu} ^{I J}$ and the bulk vielbein $E^{\mu} _{I}$ can be pulled back onto a connection $\mc{A}_{a}^{I J}$ and a dyad $e^a_I$, respectively, living on the string worldsheet $\Sigma$. $X^\mu(\tau, \sigma)$ are the space--time coordinates of a point $(\tau, \sigma)$ on the worldsheet. Now if one adopts the ``sigma model'' point of view then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet. But we know that these fields are not a collection of $d+1$ independent scalars. They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space--time. However, the symmetries of a flat background include not only Lorentz transformations bulk also translations. The string action is required to be invariant under both of these:
\begin{subequations}
\xlabel{eqn:poincare-symmetries}
\begin{align}
X^\mu & \rarrow X^\mu + \delta X^\mu; \quad \delta X^\mu \in \mbb{R}^{3,1}            \\
X^\mu & \rarrow \Lambda^\mu\text{}_\nu X^\mu; \quad \Lambda^\mu\text{}_\nu \in \mathrm{SO}(3,1)
\end{align}
\end{subequations}
where $\delta X^\mu$ is some arbitrary vector in Minkowski space. The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $ISO^{3,1}$, the Poincar\'e group in $3+1$ dimensions. Of course, these are good symmetries only if our background is flat. An arbitrarily curved background can have one or more Killing vectors depending on how much symmetry the geometry has, but {in general} even that need not be the case. The best one can hope for is some notion of local flatness is some finite subregion of the background manifold. Moreoever the entire purpose of this work to try and understand how to write down a string action in an {arbitrarily curved} background, assuming that such a thing is even possible.

Even in an arbitrarily curved background, however, symmetry still plays a very important role. Even if we have discarded {global} symmetries, that still leaves us with {local} symmetries in the form of diffeomorphisms under which the action must remain invariant. If, in addition, we have fields such as a gauge connection and an associated vielbein living in the background, then we also have to take local gauge transformations of these objects into account.

However, diffeomorphisms and gauge transformations are not distinct concepts. A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which is a differentiable (and invertible, with inverse also differentiable) map. In more pedestrian language, a diffeomorphism from $\mc{M}$ to itself is an (invertible) change of coordinates on a manifold $\mc{M}$. A gauge transformation is a redefinition of the local fields which live on the underlying manifold. In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' coordinate transformations and gauge representing ``active'' coordinate transformations. From the viewpoint of the formalism of Principal Fiber Bundles, where the gauge symmetry arises from a structure that locally looks like a Cartesian product of the base manifold $\mc{M}$ and the gauge group $G$, $\mc{M} \times G$, gauge transformation arise from local reparameterizations of the group component at each point of the base manifold, so it is a diffeomorphism in the \textquotedblleft enlarged" space $\mc{M} \times G$.

We will assume henceforth that the Poincar\'e group is the gauge group which must be promoted from being a {global} symmetry to being a {local} symmetry of the background spacetime.

\subsection{Gauging \?Lorentz Transformations}
\xlabel{sec:gauging-lt}

Instead of viewing the fields $X^{\mu}$ as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.

This viewpoint on the embedding fields, as elements of the tangent space $T_p(M)$, might appear to be at odds with their prescribed usage as co-ordinate functions on $M$. However, some reflection shows that this is not the case. For instance, one can take the embedding manifold to be a two-dimensional sphere $S^2$. Then the coordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$. The action for this system would be:
\begin{equation}
\xlabel{eqn:s2-string}
S_{S^2} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a \theta^\mu \partial_b \theta^\nu G_{\mu\nu},
\end{equation}
where $\theta^\mu(\sigma,\tau) \in \{\theta, \phi\}$ are the embedding fields, and $G_{\mu\nu}$ is {a} metric living on $S^2$.

There is a difficulty in the above argument. The bulk geometry is $d+1$ dimensional, therefore there are $d+1$ embedding fields. We have taken these fields $X^\mu$ and cast them as components of a $\mf{so}(d,1)$ vector. Let us pick an arbitrary point $P_0$ on the bulk manifold and call it the ``origin''. At $P_0$ the co-ordinates are all zero $\vec X_0 = (0,0,\ldots,0)$. If we start acting with infinitesimal $\mf{iso}(d,1)$ transformations on $\vec X_0$, the resulting surface will correspond to a ``constant energy'' hyperboloid in the bulk. This is because $SO(d,1)$ contains only boosts and rotations. We also need translations to generate the entirety of the bulk starting from a single base point.

\subsection{Gauging Translations}
\xlabel{sec:translation_gauge}

This is where we run into a problem. There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix-valued group on a point living in $\mbb{R}^{d+1}$. In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold. Now we have $d+2$ embedding fields which we can write as:
\begin{equation}
\xlabel{eqn:enlarged-Xs}
X^A \coloneq  \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
\end{equation}
where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate. As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein--Cartan geometry.

If one wants to treat the $X$'s as elements of a vector which transforms under both translations and rotations as in \neqref{eqn:poincare-symmetries}, we must extend the number of spacetime dimensions by one, introducing an ``auxiliary'' dimension whose value is initially set to be $X^r = 1$. Thus we have:
\begin{equation}
\xlabel{eqn:enlarged-Xs-transform}
\begin{pmatrix}
X^\mu \\
1
\end{pmatrix}
 \rarrow 
\begin{pmatrix}
X'^\mu \\
1
\end{pmatrix}
 = 
\begin{pmatrix}
\Lambda^\mu\text{}_\mu & \delta X^\mu \\
0                 & 1
\end{pmatrix} 
\begin{pmatrix}
X^\mu \\
1
\end{pmatrix}
\end{equation}
Now, one might be inclined to treat the new co-ordinate $X^r$ as purely an auxiliary variable which will not affect the physics. However, if we stare at the expression $X^r = 1$ for a moment, we will realize that
this expression is the same form as the Dirichlet boundary condition for the end-points of a string. And, from what we know about strings with Dirichlet boundary conditions is that the constraint surface on which the
end-points live will end up behaving like a dynamical object or ``D-brane''~\cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background}. In our case we now have a new enlarged bulk $\mb{M}$ with
$d+1$ space dimensions --- treating the auxiliary variable as a co-ordinate which can vary --- and one time dimensions, or $d+2$ dimensions in total. If we fix $X^r = 1$, that leaves us with a $d+1$
submanifold $\mb{\Gamma} \in \mb{M}$ on which the string end-point is free to move.

However, in our case, the condition $X^r = 1$ is much stronger than the Dirichlet boundary condition, because it applies not only to the end-points of the string, but to every point of the worldsheet. In other words, the {entire} string worldsheet is confined to move only along the $d+1$ dimensional submanifold $\mb{\Gamma}$. Now, one can ask what should the form of the action for a string moving in this enlarged bulk look like? Well, it will be of the same form \neqref{eqn:polyakov-gauged}, only now the worldsheet connection is an $\mf{iso}(d,1)$ valued one-form, with the embedding fields living in the enlarged $d+2$ dimensional set.

Let us note that $X^r$ can be naturally interpreted as a ``scaling dimension'' following directly from the transformation properties of the enlarged coordinate system. In Eqs.~\neqref{eqn:enlarged-Xs,eqn:enlarged-Xs-transform}, we introduce $X^r$ as an auxiliary coordinate needed to close the Poincar\'e algebra, initially fixing $X^r = 1$. However, when $X^r$ is allowed to vary from this reference value, the transformation properties show that the other coordinates $X^\mu$ undergo scale transformations. Specifically, in the enlarged coordinate system, physical coordinates can be interpreted as $x^\mu = X^\mu/X^r$, so variations in $X^r$ directly correspond to scaling transformations of the physical coordinates. This provides a concrete mathematical justification for interpreting $X^r$ as a scaling dimension --- it is precisely the coordinate that controls the scale of the embedding. This geometric scaling property is what allows our construction to naturally accommodate the holographic principle, where the extra dimension encodes information about scales in the lower-dimensional theory.

\subsection{The \?{Einstein}--\?Cartan String}
\xlabel{sec:einstein-cartan-string}

It is useful to see the explicit form of a $\mf{iso}(3,1)$ gauge connection. The elements of the Lie algeba of $\mf{iso}(3,1)$ have the following form~\cite{Wise2010MacDowell-Mansouri}
\begin{align}
\xlabel{eqn:poincare-lie-algeba}
T^A\text{}_B & \coloneq  
\begin{pmatrix}
             0          & b^1        & b^2        & b^3        & p^0/l \\
             b^1        & 0          & j^3        & -j^2       & p^1/l \\
             b^2        & -j^3       & 0          & j^1        & p^2/l \\
             b^3        & j^2        & -j^1       & 0          & p^3/l \\
             \ep p^0/l & -\ep p^1/l & -\ep p^2/l & -\ep p^3/l & 0
\end{pmatrix}
 \nonumber \\
        & = j^i J_i + b^i B_i + \frac{1}{l}p^a P_a,
\end{align}
where $J_i, B_i$ are the generators of rotations and boosts respectively. $P_a \coloneq  (P_0, P_i)$ are the generators of translations. The parameter $\ep$ takes values in $\{-1,0,1\}$. Strictly speaking the above expression corresponds to an $\mf{iso}(3,1)$ Lie algebra generator only when $\ep = 0$. $l$ is a length scale which must be introduced so that the components of the ``vector'' $(p^0, p^i)$ can be viewed as components of a translation vector along the $3+1$ dimensional geometry $\mb{\Gamma}$. Similarly the boosts and rotations describe
where $J_i, B_i$ are the generators of rotations and boosts respectively. $P_a \coloneq  (P_0, P_i)$ are the generators of translations. The parameter $\ep$ takes values in $\{-1,0,1\}$.

Strictly speaking the above expression corresponds to an $\mf{iso}(3,1)$ Lie algebra generator only when $\ep = 0$. The case when $\ep = \pm 1$ will be motivated and discussed later. $l$ is a length scale which must be introduced so that the components $(p^0, p^i)$ can be viewed as components of a ``translation vector'' living in the tangent space of the $3+1$ dimensional geometry $\mb{\Gamma}$. Similarly the boosts and rotations generators are for objects living in $\mb{\Gamma}$.

Let us write down the gauged Polyakov action for the Poincar\'e lie algebra valued connection $\mc{A}_a$ whose components are given in \neqref{eqn:poincare-lie-algeba}:
\begin{equation}
\xlabel{eqn:poincare-polyakov}
S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B G_{AB},
\end{equation}
where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \neqref{eqn:enlarged-Xs}) and $G_{AB}$ is the expanded metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \neqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
\begin{equation}
\xlabel{eqn:covariant-deriv-v2}
\mc{D}_a X^A(\tau, \sigma) = \partial_a X^A + \mu \mc{A}_{a}^A\text{}_B X^B.
\end{equation}
Now, we will expand out the action \neqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately. It is clear that the resulting expression will be sum of three terms, with the first term being the (gauged) Polyakov action for the string on $\mb{\Gamma}$, terms describing the coupling of the string on $\mb{\Gamma}$ with fluctuations along the extra dimensions $X^r$ and finally a Polyakov like term for the lone extra dimension. We can write this schematically as:
\begin{equation}
\xlabel{eqn:poincare-polyakov-decomp}
S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r],
\end{equation}
or more explicitly as
\begin{eqnarray}
 \xlabel{eqn:poincare-polyakov-decomp-explicit}
S' _{P} [X^{\mu}, X^{r}] &=& -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \nonumber\\\nf&&
- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r} - \nonumber\\\nf&&
- \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r},
\end{eqnarray}
where we can see a natural decomposition of the expanded bulk metric $G_{A B}$ as a $(d+1)$-dimensional tensor $\eta _{\mu \nu}$, a $(d+1)$-dimensional vector $V_{\mu} = G_{\mu r}$ and a scalar $V = G_{r r}$, akin to the ADM decomposition of the metric in standard GR literature.

One can now argue along the same lines as the original arguments which led to the discovery of D-branes~\cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background} to say that the extra dimension
$X^r$ will become dynamical in the full theory even though it began life only as a classical constraint on the string worldsheet's location. This will imply that while most of the time the string will remain
confined to $\mb{\Gamma}$, fluctuations along $X^r$ can cause the string to leave the ``brane'' and venture out into the bulk $\mb{M}$. If this is truly the case then the geometry of the enlarged bulk
$\mb{M}$ will be essential for a description of the full string dynamics.

This is where the non-zero value of $\ep$ mentioned in \neqref{eqn:poincare-lie-algeba} come into play. It turns out that for $\ep = +1$ ($\ep = -1$) the connection in \neqref{eqn:poincare-lie-algeba} describes a $\mf{so}(4,1)$ ($\mf{so}(3,2)$) connection respectively. These describe the symmetries of (asymptotically) deSitter and anti-deSitter spacetimes respectively. The length scale $l$ determines the value of the effective cosmological constant in the dS (adS) geometries:
\begin{equation}
\xlabel{eqn:cosmological-constant}
\Lambda = \frac{3 \ep}{l^2}.
\end{equation}
Given the observed cosmological constant $\Lambda \approx 1.47 \times 10^{-52} \text{m}^{-2}$~\cite{Collaboration2020Planck}, Eq. \neqref{eqn:cosmological-constant} implies that $l \approx 1.4 \times 10^{26} \text{m}$. This happens to coincide with the scale of the cosmological
horizon~\cite{Peebles2003Cosmological}. This would suggest that the scale of the emergent dimension $X^r$ is of the order of the cosmological horizon. Of course, this is a very naive ``back of the envelope''
calculation and would require further investigation to place on a firmer footing.

One might ask what is the motivation for introducing dS (adS) geometries into the discussion. The main motivation of course is the Maldacena or adS/CFT correspondence. The adS spacetime is usually understood to arise as a consequence of non-perturbative effects which nobody really has a proper understanding of as yet. One might hope that for a correspondence which has passed all possible checks uptil now, there should be some way to realize it in the classical theory also.

What our discussion in this section shows, however, is that such a classical description is possible if we switch from the metric based approach to the connection based one for describing the background geometry and its coupling to the string worldsheet.

The key observation which enables this is that $X^r$ behaves as a scaling or ``holographic'' dimension as explained at the end of \xref{sec:translation_gauge}.

Our classical construction provides a geometric framework that naturally incorporates key features of the AdS/CFT correspondence. The scaling dimension $X^r$ introduced through the mathematical necessity of closing the Poincar\'e algebra plays a role analogous to the radial coordinate in AdS space. Just as in AdS/CFT where the radial direction encodes the energy scale of the boundary theory, variations in our $X^r$ coordinate directly control the scale transformations of the bulk coordinates $X^\mu$. This creates a natural holographic setup where information about different energy scales in the ``boundary'' ($X^r = \text{constant}$ surfaces) is encoded in the ``bulk'' (the extended geometry with the extra $X^r$ dimension).

However, our construction differs from standard AdS/CFT in several important ways: (1) it emerges at the classical level from gauge theory requirements rather than from quantum/non-perturbative effects, (2) the holographic direction arises from the string action itself rather than being an external bulk geometry, and (3) the correspondence is between worldsheet dynamics and the extended embedding space rather than between a boundary CFT and bulk gravity. While this provides a concrete classical realization of holographic principles, establishing a precise correspondence with Maldacena's duality would require demonstrating how our construction reproduces the specific correlation functions and scaling behaviors characteristic of AdS/CFT, which remains an open challenge for future work.

\subsection{Gauged \?Polyakov Equations of Motion}

By varying the action \neqref{eqn:poincare-polyakov}, we get two sets of constraints from the variation of $g_{a b}$ and $A_{a} ^{A B}$, namely the vanishing of the worldsheet energy--momentum and spin-linear-momentum tensors $T_{a b}$ and $\sigma _{a} ^{A B}$
\begin{eqnarray}
 \xlabel{eqn:gauged-WS-EM-tensor}
T_{a b} : &=& \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B} - \nonumber\\\nf&&
- g_{a b} g^{c d} \mc{D}_{c} X^{A} \mc{D}_{d} X^{B} G_{A B} = 0
\end{eqnarray}
\xpar\cvskip[-1pc] 
\begin{equation}
\sigma ^{A B} _{a} : = \mc{D}_{a} X^{\mbox{[}A} X^{B\mbox{]}} = 0 .
\end{equation}
The former allows us to solve for the worldsheet \textquotedblleft covariant metric" $g_{a b}$ as
\begin{equation}
 \xlabel{eqn:gauged-WS-metric}
g_{a b} = 2 f \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B}
\end{equation}
where
\begin{equation}
 \xlabel{eqn:gauged-f-metric}
\frac{1}{f} = g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B},
\end{equation}
while the latter should allow one to solve for $\mc{A}_{a}$ in terms of $X^{A}$.

The variation of the action \wrt $X^{A}$ results in the equation of motion of the embbeding fields
\begin{eqnarray}
 \xlabel{eqn:gauged-X-EoM}
\nf&& \mc{D}_{a} [\sqrt{- g} g^{a b} \mc{D}_{b} X^{B} G_{B C}] = \nonumber\\\nf&&
= \sqrt{g} g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} \partial _{C} G_{A B},
\end{eqnarray}
which in worldsheet \textquotedblleft covariant conformal gauge" $g^{a b} = \e ^{- \phi} \eta ^{a b}$ and for flat background geometry $G_{A B} = \eta ' _{A B}$ with
\begin{equation}
 \xlabel{eqn:flat-bulk-metric}
[\eta ' _{A B}] = 
\begin{bmatrix}
 [\eta _{\mu \nu}] & 0 \\ 0 & \epsilon 
\end{bmatrix}
\end{equation}
simplifies to
\begin{equation}
\eta ^{a b} \mc{D}_{a} \mc{D}_{b} X^{A} \eta ' _{A B} = 0 .
\end{equation}
From here on, we will work on the case of $\ep = - 1$ (adS background), for which the above equation can be expanded as
\begin{eqnarray}
 \xlabel{eqn:expanded-gauged-X-EoM}
\nf&& \eta ^{a b} \bigm( \del _{a} \del _{b} X^{A} + 2 \mu A^{A} _{a B} \del _{b} X^{B} + \nonumber\\\nf&&
+ \mu \del _{a} A^{A} _{b B} X^{B} + \mu ^2 A^{A} _{a B} A^{B} _{b C} X^{C} \bigm) = 0 .
\end{eqnarray}
To produce the desired bulk geometry, the background connection can be taken as
\begin{equation}
 \xlabel{eqn:adS-bulk-connection}
\mc{A}_{\mu} = 
\begin{bmatrix}
 0 & 0 & 0 & 0 & \delta ^{0} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{1} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{2} _{\mu} \\ 0 & 0 & 0 & 0 & \delta ^{3} _{\mu} \\ - \delta ^{0} _{\mu} & \delta ^{1} _{\mu} & \delta ^{2} _{\mu} & \delta ^{3} _{\mu} & 0 
\end{bmatrix}
,
\end{equation}
from which the pulledback connection is $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$, whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
\begin{eqnarray}
 \xlabel{eqn:Minkowski-sector-EoM}
\nf&& \eta ^{a b} \del _{a} \del _{b} X^{\mu} + \nonumber\\\nf&&
+ \frac{\mu \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + k \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} = 0
\end{eqnarray}
\begin{eqnarray}
 \xlabel{eqn:holographic-dim-EoM}
\nf&& \eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} + 4 \mu \e ^{\varphi} - \nonumber\\\nf&&
- \frac{\mu ^2 \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + \mu \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} X_{\mu} = 0 .
\end{eqnarray}
Assuming the perturbations on the string are small $\svert X^{A}\svert  \ll 1$, we get a massive simplification
\begin{equation}
 \xlabel{eqn:simplified-Minkowski-EoM}
\eta ^{a b} \del _{a} \del _{b} X^{\mu} = 0
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:simplified-holographic-EoM}
\eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} = - 4 \mu \e ^{\varphi} .
\end{equation}
Thus, the Minkowski sector behaves like regular ST for small perturbations, while the holographic coordinate $X^{r}$ follows a variable-mass Klein--Gordon equation with source. Now it should be clear why the choice of $\mu$ for the coupling constant, since in \neqref{eqn:simplified-holographic-EoM} it appears (together with the conformal factor) as a mass term for our perturbation. Eq.~\neqref{eqn:simplified-holographic-EoM} can be solved using the 1d wave equation Green's function to build a perturbation around the homogenous wave equation solution
\begin{eqnarray}
 \xlabel{eqn:holo-sol-implicit}
\nf&& X^{r} (x) = X^{r} _{0} (x) - \nonumber\\\nf&& \xq - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) = \nonumber\\\nf&&\xq\xq = X^{r} _{0} (x) + \delta X^{r} (x),
\end{eqnarray}
where $X^{r} _{0}$ is a solution for the homogenous wave equation
\begin{equation}
 \xlabel{eqn:homo-wave-eqn}
(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) X^{r} _{0} = 0
\end{equation}
and $G (x ; x') = \frac{1}{2} \Theta (\tau - \tau ' - \svert \sigma - \sigma '\svert )$ its Green's function
\begin{equation}
 \xlabel{eqn:homo-wave-eqn-GF}
(\partial _{\sigma} ^{2} - \del _{\tau} ^{2}) G (x ; x') = \delta ^{2} (x ; x') .
\end{equation}
From \neqref{eqn:holo-sol-implicit}, a recursion can be built, leading to a more explicit form
\begin{eqnarray}
X^{r} (x) &=& X^{r} _{0} (x) + \nonumber\\\nf&& + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \nonumber\\\nf&& \times (2 + \mu X^{r} _{0} (x^{(k)})),
\end{eqnarray}
with $x^{(0)} \equiv x$.

\section{Discussion}
 \xlabel{sec:discussion}

In this article we have presented a phenomenological modification of the Nambu--Goto action {inspired by the central result of loop quantum gravity, according to which area and other geometric observables are quantized at the Planck scale}. In particular the spectrum of the area operator is discrete and the smallest eigenvalue is non-zero (of the order $l_{pl}^2 \sim 10^{-68}\,\text{m}^2$). On the other hand we also took as a working hypothesis the statement that string theory, or some suitable version of it, provides the correct description of the low energy physics of the world around us. We then searched for the way in which both of these paradigms can be incorporated into a single theoretical model. The form of the action shown in \neqref{eqn:ng-area-corrected} appears, at least superficially, as the simplest possible modification of the Nambu--Goto action which incorporates a minimum eigenvalue for the area. This value is encoded in the modulus of the $\Delta(x)$ field. In the process we introduced a new coupling parameter $ k = l_{pl}/l_s$ which is the ratio of the string scale to the Planck scale.

Assuming that $l_{pl} \ll l_s$, we have $k \ll 1$ and consequently \neqref{eqn:ng-area-corrected} can be expanded as a power series in $k$. Keeping only the term linear in $k$, we obtain an action which is
the sum of two copies of the Nambu--Goto action, one for the original metric $h_{ab}$ and the second for the inverse metric $h^{ab}$. We then pointed out the similarity between this expression and previous studies
of {bimetric gravity}~\cite{Hassan2012Bimetric}. We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before
by~\cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the {bulk} geometry rather than a bimetric action for the worldsheet, itself, of the type given in
\neqref{eqn:modified-ng-action-v2}.

The bimetric viewpoint for the area-corrected Nambu--Goto action is more than just an interesting curiosity. This perspective allows us to construct the Polyakov action for the bimetric string in \neqref{eqn:polyakov-bimetric}. Of course, one would expect that the (area-corrected) Polyakov and Nambu--Goto formulations should be physically equivalent. Imposing this requirement leads us to the conclusion that the object $\Delta$ in \neqref{eqn:ng-area-corrected} must be worldsheet two-form (antisymmetric tensor) corresponding to the pullback of the {bulk} Kalb--Ramond field. All of this eventually leads us to recognize the relation of our proposed action \neqref{eqn:ng-area-corrected} to the Born--Infeld action \neqref{eqn:BI-action} which arises when one studies the dynamics of D-branes in string theory.

Let us make one crucial observation here. In the expression \neqref{eqn:ng-area-corrected} we originally took $\Delta$ to be a constant representing the smallest quantum of area. It is only {later}, by demanding consistency of the area-corrected Nambu--Goto and Polyakov actions that we realize that $\Delta \equiv \Delta_{ab}(x) $ is in fact an antisymmetric worldsheet two-form!

After exploring the equations of motion of the area corrected string, we found that said equations can be recast as a set of Klein--Gordon equations, which for a first analysis we assumed to have constant coefficient $\mu$, however that need not be the case. The solution of these equations and their consequences for the constraints lead us to a modified \textquotedblleft Virasoro-Klein--Gordon" algebra, where the algebra modes have two indices, which in turn resulted in a truncated solution. This also had the effect of not having distinct left and right moving modes, thus there was no level-matching prohibiting spin-1 states for the closed string, which we postulated to maybe be related to the Ashtekar variables of the background geometry. The quantization of the KG string and the Virasoro--Klein--Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu}, B_{\mu \nu}, \Phi$ fields as part of the spin-2 spectrum.

We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into String Theory by considering Afshordi's model~\cite{Afshordi2014Emergent} with some key insights from LQG complementing
said model, creating a more concrete picture of the mechanism behind the emerging dimensions and how ultimately spacetime (and thus the true quantum gravitational field) might be actually $(2+1)$-dimensional at the
Planck scale.

Ultimately one cannot be satisfied with the heuristic action of the form \neqref{eqn:ng-area-corrected}. Therefore in \xref{sec:holographic-strings} we attempt to build, from the ground up, a modified string action which incorporates the following chain of thought. We seek to describe the behavior of a string in an arbitrarily curved background geometry at a {classical} level. For this an action of the form \neqref{eqn:polyakov-curved} is unsuitable because that action treats the bulk metric as non-dynamical variables. Connection variables are used in LQG to describe the geometry of a manifold. The coupling of the string worldsheet to the bulk geometry should reflect this fact. This leads us to an action of the form \neqref{eqn:poincare-polyakov}. This action no longer possess the global Poincar\'e symmetry of the original Polyakov action. However it is invariant under {local} Poincar\'e gauge transformations.

For an arbitrarily (or even a minor deviation from flat space) curved bulk geometry, global Poincar\'e symmetry of embedding fields is not meaningful. Local Poincar\'e symmetry, on the other hand, provides a perfectly
adequate framework~\cite{Hehl2023Four} for constructing a theory of gravity on an arbitrary bulk. Thus we conjecture that the bulk theory is that of gauged Poincar\'e gravity.

Finally, the interpretation of embedding fields as co-ordinate fields on the bulk and {also} as vectors living in the fundamental representation of the Poincar\'e group necessitates the introduction of an ``auxiliary'' co-ordinate which has the natural interpretation as a holographic or scale direction.

\subsection{Poincar\'e Spin Networks}
\xlabel{sec:poincare-networks}

The above considerations feed back into our understanding of the bulk gravity theory. Recall, that we started with LQG in which the gauge group for the $3+1$ dimensional bulk is $\sltwoc$. However, our
considerations regarding viewing the embedding fields as representations of the Poincar\'e group imply that the bulk is $4+1$ dimensional, when one includes the emergent (spacelike) holographic direction, and
therefore the gravitational theory for the full bulk should be gauge theory of the Poincar\'e group. Now, if we wish to construct the resulting spin-network and spin-foam states for the bulk by following the LQG
quantization procedure, what we end up with will not be the usual $ \mf{su}(2) $ ($ \mf{sl}(2,\C)$) spin-networks (spin-foams), but {Poincar\'e spin-foams} of the kind recently discussed in a work by
Altaisky~\cite{Altaisky2024Poincare}.

This suggests that it might make greater sense to use Poincar\'e spin foams rather than Lorentzian spin foams to describe the behavior of quantum geometry at the Planck scale. Though even with such a change, the fundamental result of LQG --- quantization of areas --- which underpins this work, will likely not be affected.

\subsection{Closed String Spin-1 States}
 \xlabel{sec:spin-1-states}

In  \xref{sec:quantum-kg-string} we saw that our area-corrected model allows closed string spin-1 excitations, which is due to our solution not having distinct left and right sectors and the physical states not being
invariant under rigid rotations of the string. Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the vector states of the closed string relate to? Well,
in  \xref{sec:gauging-lt} we discussed a possible formulation of ST in terms of a Poincar\'e connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in tetrad-connection~\cite{Bodendorfer-LQG}
formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
\begin{equation}
 \xlabel{eqn:connection-string-vector-excitation}
\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
\end{equation}
Another candidate for what the vector excitations could relate to is the $D = 3 + 1$ Ashtekar electric field $\widetilde{E}^{a} _{i}$,
\begin{equation}
 \xlabel{eqn:AEF-string-vector-excitation}
\widetilde{E}^{a} _{i} \sim (\Hat{a}^{a} _{i})^{\dagger} \ket{0} .
\end{equation}

\subsection{Open Questions and Future Directions}
\xlabel{sec:open-questions}

While our work establishes a promising framework for incorporating LQG insights into string theory, several fundamental questions remain open. Building on the pioneering work of Smolin~\cite{Smolin1998Strings} and
Markopoulou~\cite{Markopoulou1997Causal}, a more complete framework is needed to show how smooth worldsheet geometries emerge from the discrete, punctured surfaces of spin networks in Loop Quantum Gravity. Our earlier
work~\cite{Vaid2017Connecting} established that the Nambu--Goto action can be viewed as the expectation value of the LQG area operator, but the detailed emergence mechanism requires further development.

The physical interpretation of the emergent holographic dimension $X^r$ also requires further study. Understanding the physical nature of this dimension and its emergence mechanism represents a key theoretical challenge, though the connection to Afshordi's model provides important guidance.

Perhaps most significantly, the relationship between our modified constraint algebra and the fundamental structure of spacetime at the Planck scale requires clarification. Do the two-index Virasoro generators correspond to a deeper geometric principle? Can they be understood by some suitable deformation of the Virasoro algebra to incorporate the cutoff of the sum over Virasoro modes?

\printauthorcredits
\conflictofinterest

\DoCIno
\ackheads 
 DV would like to thank Thomas van Riet for going over an early draft of this work and for his valuable comments. DV and LdS would both like to thank David Schmidtt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb--Ramond field, and also the equivalence of the area corrected action with a Born--Infeld model in the worldsheet. Finally, we would like to humbly dedicate this work to the memory of the victims of the genocide in Gaza.
%\QUERY[5]

\appendix{}
\section[pfx={Appendix\space}]{Strings in Background Fields and Emergent Gravity}
\xlabel{sec:strings-gravity}

Let us begin by recalling the Polyakov action for the bosonic string.
\numberwithin{equation}{section}\setcounter{equation}{0}
\begin{equation}
\xlabel{eqn:polyakov-action}
S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

Now, one proceeds in the usual way by determining the symmetries of the action \neqref{eqn:polyakov-bimetric}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion. Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to the description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.

The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$. Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background. It would not make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds. The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
\begin{equation}
\xlabel{eqn:polyakov-curved-bulk}
S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}
where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$. Now this metric is still non-dynamical because the action \neqref{eqn:polyakov-curved-bulk} does not contain any terms with time derivatives of $G_{\mu\nu}$. However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of {coupling constants}, rather than a dynamical entity which exists independent of the string. One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.

Then, as shown long ago by Friedan~\cite{Friedan1985Nonlinear} (see also~\cite{Callan1989Sigma,Callan1985Strings} or~\cite[Sec 3.7]{Polchinski1998aString},~\cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical
explanation), the graviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry. The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
\begin{equation}
\xlabel{eqn:ricci-flat}
\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
\end{equation}
Therefore we find that conformal invariance of the string worldsheet {implies} that the background geometry in which the string propagates satisfies the {vacuum} Einstein equations. It is this result which is often cited as evidence for the claim that string theory is a {background independent} theory of quantum gravity.

\section[pfx={Appendix\space}]{Two Expressions for Area}

\xlabel{eqn:area-formulae}

There is another explanation for why it makes sense to promote the $X$'s to local fields. This can be found in terms of the expression for the area of a 2-surface. We have a manifold $\mc M$, within which is embedded a two dimensional submanifold $\mc N$. Let $(\tau,\sigma)$ be the location of a point on the worldsheet and $X^\mu(\tau, \sigma)$ be the location of that same point in terms of co-ordinates on $\mc M$. Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of derivatives of the embedding fields (the pullback):
\numberwithin{equation}{section}\setcounter{equation}{0}
\begin{equation}
\xlabel{eqn:induced-metric}
h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is the metric in the ambient space $\mc M$. Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{- \det(h)}$ and integrating over that patch:
\begin{equation}
\xlabel{eqn:patch-area-v1}
A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{- \det(h)}.
\end{equation}
This is, of course, the expression for the Nambu--Goto action --- modulo some constants --- which we all know and love. In LQG we do not have a notion of embedding fields. Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding coordinates of the curves and surface turn to not be needed. When promoting classical observables into quantum operators acting on lines and surfaces the embedding coordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.

How then does one define the area of a surface in LQG? It is defined as the magnitude of the area two form. Recall that given a tetradic basis $e_\mu^I$ for a local Lorentz frame whose metric is given by $g_{\mu\nu}$, we can write the metric in terms of the tetrad in the usual manner:
\begin{equation}
\xlabel{eqn:metric-from-tetrad}
g_{\mu\nu} = e_\mu^I e_\nu^J \eta_{IJ},
\end{equation}
where $\eta_{IJ}$ is the flat Minkowski metric on the ``internal'' flat space. If we consider any two dimensional surface in the local Lorentz frame, then its area can be written in terms of the vielbein as:
\begin{equation}
A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e \wedge e),
\end{equation}
where $e = e_{\mu} \diff x^{\mu}$ and the trace is taken over the ``internal'' Lorentz indices.

Now, if we compare the two expressions \neqref{eqn:induced-metric,eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x^a$ of the embedding co-ordinates and the vielbein $e_\mu^I$. This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \neqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.

\textbf{From Embedding Fields:}

We take the bulk metric $g_{\mu\nu}$ to be flat. Let $\{\tau,\sigma\} \coloneq  \{x^0, x^1\}$ be the spacetime co-ordinates on the worldsheet. Derivatives of the $X$'s in terms of these co-ordinates can be written as:
\begin{equation}
\dot X \coloneq  \left\{\frac{\partial X^\mu}{\partial \tau}\right\}; \quad X' \coloneq  \left\{\frac{\partial X^\mu}{\partial \sigma}\right\}
\end{equation}
we obtain the following form for the determinant of the worldsheet metric (\neqref{eqn:patch-area-v1}) in terms of the embedding fields:
\begin{align}
\xlabel{eqn:area-embedding}
\det h & = 
\begin{vmatrix}
           h_{00} &  & h_{01} \\
           h_{10} &  & h_{11}
\end{vmatrix}
 = 
\begin{vmatrix}
                           \dot X^2        &  & \dot X \cdot X' \\
                           \dot X \cdot X' &  & X^{\prime 2}
\end{vmatrix}
 \nonumber \\
       & = \dot X^2 X^{\prime 2} - (\dot X \cdot X')^2
\end{align}

\cvp\textbf{From Vielbein:}

We can proceed to obtain the area of a 2-surface from the bulk vielbein as follows. Starting with the bulk vielbein $e_\mu^I$, we perform a local Lorentz transformation such that two ``legs'' of the vielbein are tangent to the worldsheet surface. We then project down the vielbein $e_\mu^I$ to a dyad $e_a^I$ living in the tangent space of the worldsheet, in terms of which the worldsheet metric can be written as:
\begin{equation}
h_{ab} = e_a^I e_b^J \eta_{I J},
\end{equation}
where $\eta_{I J}$ is the flat Minkowski metric in group space. The determinant then becomes:
\begin{align}
\xlabel{eqn:area-vielbein}
\det h & = 
\begin{vmatrix}
           h_{00} &  & h_{01} \\
           h_{10} &  & h_{11}
\end{vmatrix}
 = 
\begin{vmatrix}
                           e_t^I e_t^J & e_t^I e_x^J \\
                           e_x^I e_t^J & e_x^I e_x^J
\end{vmatrix}
 \eta_{I J} \nonumber       \\
       & = \vec e_t\text{}^2 \vec e_x\text{}^2 - (\vec e_t \cdot \vec e_x)^2,
\end{align}
where $\vec e_t \cdot \vec e_x = e_t^I e_x^J \eta_{I J}$. It is clear by comparing the two expressions \neqref{eqn:area-embedding,eqn:area-vielbein} that we have the following correspondence between the vielbein and the $X$ derivatives:
\begin{equation}
\vec e_\tau \equiv \frac{\partial \vec X}{\partial \tau}; \quad \vec e_\sigma \equiv \frac{\partial \vec X}{\partial \sigma}.
\end{equation}
In other words, we can directly identify the zweibein with the derivatives of the embedding fields. Of course, this is not altogether surprising. If we consider any manifold on which we have some set of fields $\{X^I(x^\mu)\}$, where $I$ is valued in the Lie algebra $\mf{g}$ of some group $\mc G$, as a function of some  ``fiducial'' co-ordinates $\{x^\mu\}$, then we can always define a set of $\mf{g}$-valued vector fields:
\begin{equation*}
e^I_\mu \coloneq  \frac{\partial X^I}{\partial x^\mu}.
\end{equation*}
In the usual formulation of the string action, the embedding fields are {not} Lie-algebra valued but are c-ordinate fields on what is generally taken to be a flat background. For this correspondence between vielbein and pullback Jacobian to work we have to view the $X$ fields as taking values in a Lie algebra. But these same $X$ fields {also} serve as local coordinates for the bulk. If we want the coordinates to change from point to point in the bulk geometry, we must therefore require that the connection $\mc A$ in \neqref{eqn:covariant-deriv-v2} can never vanish completely! If $\mc A$ vanishes then that will imply that the fields $X$ do not change from one point to the next and cannot therefore be viewed as co-ordinate functions. Thus the amplitude $\svert \mc A\svert $ can be arbitrarily small but it can never be zero.

\section[pfx={Appendix\space}]{Modified \?{Nambu Goto} Equations of Motion}

\xlabel{sec:modified-eom}

Following the procedure done in~\cite{Zwiebach2009A-First}, the correction \neqref{eqn:modified-ng-action} does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still
given by
\numberwithin{equation}{section}\setcounter{equation}{0}
\begin{equation}
 \xlabel{eqn:modified-ng-eom}
\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
\end{equation}
and
\begin{equation}
 \xlabel{eqn:modified-ng-bc}
\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} {\mbigvert} _{\sigma = 0} ^{\sigma = \sigma _1} = 0,
\end{equation}
where
\begin{align}
 \xlabel{eqn:modified-ng-tau-currents}
\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
\xpar\cvskip[-1pc] 
\begin{align}
 \xlabel{eqn:modified-ng-sigma-currents}
\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu--Goto world-sheet currents.

In the following, we parametrize the string WS using the static gauge $\tau = t$ and transverse gauge
\begin{equation}
 \xlabel{eqn:transverse-'gauge'}
\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0,
\end{equation}
where $s$ is the length along the string parameter since this gives the motion of the string in terms of transverse velocity, which is a natural dynamical variable of the string. We find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu--Goto string times the correction factor
\begin{equation}
 \xlabel{eqn:string-energy}
E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s,
\end{equation}
and the form of the wave equation maintains its shape as in
\begin{equation}
 \xlabel{eqn:corrected-ng-wave-equation}
\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \xlabel{eqn:effective-mass}            \\
T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \xlabel{eqn:effective-tension}
\end{align}

Rewriting eq\neqref{eqn:corrected-ng-wave-equation} in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F^+ = 1 + g \Delta/2 (- h)$)
\begin{equation}
 \xlabel{eqn:sigma-parameterization}
\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{(F^+)^2},
\end{equation}
we find the variable-speed wave equation
\begin{equation}
 \xlabel{eqn:simplified-modified-wave-eqn}
(F^+)^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0,
\end{equation}
from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
\begin{equation}
 \xlabel{eqn:wave-speed-corrected}
v = \frac{c}{F^+}.
\end{equation}

\section[pfx={Appendix\space}]{Relating \?{Nambu--Goto} and \?{Polyakov} analysis}

 \xlabel{sec:polyakov-ng-relation}

At first glance, our analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu--Goto string. However, as pointed out
in~\cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu--Goto analysis) can be turned into Klein--Gordon equations (what we found in  \xref{sec:inverse-metric-Polyakov}). While
their work deals only with space-varying wave speed, it is straightforward to generalize the procedure to also include time dependence.

Following the procedure found in~\cite{Grimshaw2010Homogenization}, we start with Eq. \neqref{eqn:simplified-modified-wave-eqn} obtained in  \xref{sec:modified-eom}, renaming $\sigma$ as $x$ and dividing by
$(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t, x) \rightarrow (\tau (t, x), \sigma (t, x))$, where without loss of generality (one needs just to rescale and/or rotate the
coordinates) we set
\numberwithin{equation}{section}\setcounter{equation}{0}
\begin{eqnarray}
 \xlabel{eqn:new-coordinates-constraints-quadratic}
\nf&& (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \nonumber\\\nf&&
\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma,  
\end{eqnarray}
or more compactly,
\begin{eqnarray}
 \xlabel{eqn:new-coordinates-constraints-compact}
\nf&& \partial _{t} \tau = v \partial _{x} \sigma \nonumber\\\nf&&
\partial _{t} \sigma = v \partial _{x} \tau 
\end{eqnarray}
which is equivalent to
\begin{eqnarray}
 \xlabel{eqn:new-coordinates-constraints-second-order}
 \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau &=& \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \nonumber\\\nf&&
\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . 
\end{eqnarray}
This turns Eq. \neqref{eqn:simplified-modified-wave-eqn} into
\begin{eqnarray}
 \xlabel{eqn:modified-wave-eqn-new}
\nf&& \partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \nonumber\\\nf&&\xq
+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \nonumber\\\nf&&\xq
+ \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
\end{eqnarray}
Next, we introduce $X^{\mu} = \kappa (\tau, \sigma) W^{\mu} (\tau, \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out. This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$. With this, Eq. \neqref{eqn:modified-wave-eqn-new} turns into a Klein--Gordon equation
\begin{equation}
\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0,
\end{equation}
with \textquotedblleft mass" squared given by
\begin{equation}
\mu ^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
\end{equation}
and $\tau (t, x)$ satisfying constraints \neqref{eqn:new-coordinates-constraints-compact}. This shows that our analysis of the action \neqref{eqn:inverse-metric-Polyakov} is indeed in agreement with the analysis of the inverse area corrected Nambu--Goto action \neqref{eqn:modified-ng-action}.

\section[pfx={Appendix\space}]{Relation between \?{Kalb--Ramond} field and Quantum of Area 2-form}

 \xlabel{sec:KR-QA}

To see how the area 2-form $\Delta _{ab}$ is related to the Kalb--Ramond field we have to go back to \xref{sec:ws-kalb-ramond} where we looked at the case of the bimetric string action \neqref{eqn:polyakov-bimetric}. We saw that the bimetric Polyakov action can be expressed, quite obviously, as a bimetric Nambu--Goto action \neqref{eqn:double-ng-action}, which we reproduce below for convenience:
\numberwithin{equation}{section}\setcounter{equation}{0}
\begin{equation}
S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h}.
\end{equation}
From here if we make the mapping $T' = - T k/2$ and $h = \Delta ^2/g$, we recover the Nambu--Goto area-corrected action \neqref{eqn:modified-ng-action}
\begin{equation}
S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
Now, as noted in the main text, the condition $h = \Delta^2/g$ can be achieved if the following holds true \neqref{eqn:h-delta-relation}:
\begin{equation*}
h_{ab} = \Delta_{ac} \Delta_{bd} g^{cd},
\end{equation*}
where $g^{cd}$ is the inverse of $g_{ab}$. Now, let us assume that $\Delta_{ab}$ can be written as \neqref{eqn:delta-epsilon-relation}:
\begin{equation*}
\Delta_{ab} = \sqrt{\Delta} \epsilon_{ab}.
\end{equation*}
Now, we recall that the inverse of a {2~\ttimes~2} matrix can be written using the total-antisymmetric symbol as:
\begin{equation}
g^{ab} = \frac{1}{2g} \epsilon^{ac} \epsilon^{bd} g_{cd},
\end{equation}
where $g = \det{g_{ab}}$. Inserting this identity into \neqref{eqn:h-delta-relation}, and using the expression for the determinant of a matrix in terms of product of epsilon symbols:
\begin{equation*}
g = \det{g_{ab}} = \onehalf \epsilon^{ac} \epsilon^{bd} g_{cd},
\end{equation*}
we find that $h = \Delta^2/g$, where $\Delta = \det{\Delta_{ab}}$. What this tells us is that it is natural to identify $\Delta_{ab}$ with the totally anti-symmetric tensor on the worldsheet. Now a two-dimensional manifold can only have one, upto conformal transformations, anti-symmetric tensor and if we require that this tensor be derived from the embedding of the string into the ambient manifold then it makes sense that one should identify $\Delta_{ab}$ with the pullback to the worldsheet of the bulk Kalb--Ramond field $B_{\mu\nu}$.

For a more formal derivation of this fact we start from the action in \neqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb--Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$. Varying this action \wrt \ $\Delta ^{c d}$ yields
\begin{eqnarray}
 \xlabel{eqn:var-act-AC-KR}
\frac{\delta S}{\delta \Delta ^{c d}} &=& - \frac{1}{4 \pi \alpha '} \Biggm( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \biggm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \biggm) - \nonumber\\\nf&&
- \biggl( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \biggr) \biggm( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \nonumber\\\nf&&
+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \biggm) \Biggm) ,
\end{eqnarray}
which when required to vanish can be rearranged into
\begin{eqnarray}
 \xlabel{eqn:eqn:var-act-AC-KR-rear}
\nf&& \Delta _{c d} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&\xq
- \biggl( g + \frac{3 k \Delta}{4} \biggr) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm) - \nonumber\\\nf&&\xq
- \biggl( g + \frac{k \Delta}{2} \biggr) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
\end{eqnarray}
From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb--Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
\begin{equation}
 \xlabel{eqn:QA-pullKR}
\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
\end{equation}
where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb--Ramond field
\begin{eqnarray}
 \xlabel{eqn:1/f-KR}
\frac{1}{\widetilde{f}} &=& \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
- \biggl( g + \frac{3 k \Delta}{4} \biggr) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm) .
\end{eqnarray}
When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \neqref{eqn:1/f-KR} simplifies to
\begin{equation}
 \xlabel{eqn:1/f-KR-simp}
\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
\end{equation}
or alternatively
\begin{equation}
 \xlabel{eqn:f-KR-simp}
\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
\end{equation}
Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb--Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
\begin{equation}
 \xlabel{eqn:QA-KR-fin}
\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}

\back{}

\let\stmbibsectioncase\stmsectioncase

\bibliographystyle{stm-xml-sort-num-fnm-abre}

\nocite{*}

\bibliography{\jobname.bib}

\begin{bibwrite}{\jobname.bib}

@preamble{"\tfbibfldoff[issn,isbn]"}
%\QUERY[6]
@inbook{Polchinski1998String,

SerialNo={1},
author={Polchinski, Joseph},
 year={1998},
booktitle={String {{Theory}}: {{Volume}} {\?{1}}: {{An Introduction}} to the {{Bosonic
  String}}},
 series={Cambridge {{Monographs}} on {{Mathematical Physics}}},
 volume={vol. 1},
 orgname={{Cambridge University Press}},
 city = {{Cambridge}},
doi={10.1017/cbo9780511816079},
 isbn={978-0-521-63303-1},
}

@inbook{Polchinski2007String,
SerialNo={2},
author={Polchinski, J.},
 year={2007},
booktitle={String {{Theory}}: {{Volume}} {\?{2}}: {{Superstring}} Theory and Beyond},
 series={Cambridge {{Monographs}} on {{Mathematical Physics}}},
 orgname={{Cambridge University Press}},
doi={10.1017/cbo9780511618123},
 isbn={978-0-511-25228-0 978-0-521-63304-8 978-0-521-67228-3},
 keywords={bibliography,book,compactification},
xorgname={Calabi-Yau,membrane model:
  D-brane,orbifold,string model,supersymmetry}
}

@article{Rovelli1998Loop,
SerialNo={3},
author={Rovelli, Carlo},
 year={1998},
title={Loop {{Quantum Gravity}}},
journal={Living {\rvtissnReview} {\rvtissnRelativi}},
 volume={1},
 number={1},
post={\myehost{http://arxiv.org/abs/gr-qc/9710008}[arXiv:gr-qc/9710008]},
doi={10.12942/lrr-1998-1},
 issn={2367-3613, 1433-8351},
 keywords={_tablet,General Relativity and Quantum Cosmology,High Energy Physics
  - Theory},
}

@book{Rovelli2015Covariant,
SerialNo={4},
author={Rovelli, Carlo and Vidotto, Francesca},
 year={2015},
booktitle={Covariant Loop Quantum Gravity: {{An}} Elementary Introduction to
  Quantum Gravity and Spinfoam Theory},
xjournal={Covariant Loop Quantum Gravity: An Elementary {\rvtissnIntroduc} To Quantum
  Gravity Spinfoam Theory},
 orgname={Cambridge University Press},
 city = {Cambridge},
doi={10.1017/cbo9781107706910},
 isbn={978-1-107-70691-0},
 keywords={area operator,arrow of time,ashtekar_variables,black
  holes,black-hole-entropy,book,cosmology,introductionl,loop_quantum_gravity,pedagogical,quantum
  gravity,rovelli_carlo,tetrad formalism,vidotto_francesca,volume operator},
}

@CUSTOMBIB{Rovelli1993Area,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={5},
author={Rovelli, Carlo},
 year={1993},
title={Area is the length of {Ashtekar}'s triad field},
 volume={47},
  pages={1703--1705},
doi={10.1103/PhysRevD.47.1703},
 xpost={\xURL \myehost{http://dx.doi.org/10.1103/PhysRevD.47.1703}},
}

@CUSTOMBIB{Rovelli1994Discreteness,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={6},
author={Rovelli, Carlo and Smolin, Lee},
 year={1994},
title={Discreteness of area and volume in quantum gravity},
post={\myehost{http://arxiv.org/abs/gr-qc/9411005}[arXiv:gr-qc/9411005]},
 xpost={\xURL \myehost{http://arxiv.org/abs/gr-qc/9411005}},
}

@article{Rovelli1996Black,
SerialNo={7},
author={Rovelli, C.},
 year={1996},
title={Black {{Hole Entropy}} from {{Loop Quantum Gravity}}},
journal={\rvtsclPhysRevLett},
 volume={77},
 number={16},
  pages={3288--3291},
post={\myehost{http://arxiv.org/abs/gr-qc/9603063}[arXiv:gr-qc/9603063]},
doi={10.1103/PhysRevLett.77.3288},
 issn={1079-7114},
 keywords={bekenstein_bound,black-hole-entropy,nosource,quantum_geometry,quantum_gravity,schwarzschild,statistical_mechanics},
}

@CUSTOMBIB{Borissova2024From,
 mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={8},
author={Borissova, Johanna and Ho, Pei-Ming},
 year={2024},
title={From Area Metric Backgrounds to Cosmological Constant and Corrections
  to the \?{{Polyakov}} Action},
 xnumber={arXiv:2404.14478},
 xorgname={arXiv},
post={\myehost{http://arxiv.org/abs/2404.14478}[arXiv:2404.14478]},
 primaryClass={gr-qc, physics:hep-th},
doi={10.48550/arXiv.2404.14478},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@article{Amati1989Canb,
SerialNo={9},
author={Amati, D. and Ciafaloni, M. and Veneziano, G.},
 year={1989},
title={Can Spacetime Be Probed below the String Size?},
chsep={\chsep[atitle]{~}},
journal={\rvtsclPhysLettB},
 volume={216},
 number={1},
  pages={41--47},
doi={10.1016/0370-2693(89)91366-x},
 issn={0370-2693},
}

@article{Chang2011Minimal,
SerialNo={10},
author={Chang, Lay Nam and Lewis, Zachary and Minic, Djordje and Takeuchi,
  Tatsu},
 year={2011},
title={On the {{Minimal Length Uncertainty Relation}} and the {{Foundations}}
  of {{String Theory}}},
journal={\rvtsclAdvHighEnergyPhys},
 volume={2011},
  pages={1--30},
post={\myehost{http://arxiv.org/abs/1106.0068}[arXiv:1106.0068]},
 primaryClass={hep-th},
doi={10.1155/2011/493514},
 issn={1687-7357, 1687-7365},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@article{Gross1987Highenergy,
SerialNo={11},
author={Gross, David J. and Mende, Paul F.},
 year={1987},
title={The High-Energy Behavior of String Scattering Amplitudes},
journal={\rvtsclPhysLettB},
 volume={197},
 number={1},
  pages={129--134},
doi={10.1016/0370-2693(87)90355-8},
 issn={0370-2693},
}

@article{Gross1988String,
SerialNo={12},
author={Gross, David J. and Mende, Paul F.},
 year={1988},
title={String {{Theory Beyond}} the {{\?{Planck} Scale}}},
journal={\rvtsclNuclearPhysB},
 volume={303},
  pages={407--454},
doi={10.1016/0550-3213(88)90390-2},
 keywords={ASYMPTOTIC BEHAVIOR: SCATTERING AMPLITUDE,BETA,FIELD THEORY:
  CONFORMAL,MATHEMATICAL METHODS: Riemann surface,MODEL: STRING,PERTURBATION
  THEORY: HIGHER-ORDER,SCATTERING AMPLITUDE: ASYMPTOTIC BEHAVIOR},
}

@article{Yoneya1989Interpretation,
SerialNo={13},
author={Yoneya, Tamiaki},
 year={1989},
title={On the {{Interpretation}} of {{Minimal Length}} in {{String
  Theories}}},
journal={\rvtsclModernPhysLettA},
 volume={4},
  pages={1587},
doi={10.1142/s0217732389001817},
 keywords={BETA,FUNDAMENTAL CONSTANT: LENGTH,HIGHER-ORDER: SCATTERING
  AMPLITUDE,INVARIANCE: REPARAMETRIZATION,MATHEMATICAL METHODS: Riemann
  surface,MODEL: STRING,SCATTERING AMPLITUDE: HIGHER-ORDER},
}

@article{Yoneya2000String,
SerialNo={14},
author={Yoneya, Tamiaki},
 year={2000},
title={String {{Theory}} and the {{Space-Time Uncertainty Principle}}},
journal={\rvtsclProgrTheoretPhys},
 volume={103},
 number={6},
  pages={1081--1125},
post={\myehost{http://arxiv.org/abs/hep-th/0004074}[arXiv:hep-th/0004074]},
doi={10.1143/ptp.103.1081},
 issn={0033-068x, 1347-4081},
 keywords={High Energy Physics - Theory},
}

@article{Afshordi2014Emergent,
SerialNo={15},
author={Afshordi, Niayesh and Stojkovic, Dejan},
 year={2014},
title={Emergent Spacetime in Stochastically Evolving Dimensions},
journal={{\rvtissnPhysics} {\rvtissnLetter} {\rvtissnSecti} B: {\rvtissnNuclear} Elementary {\rvtissnParticle}   High-Energy {\rvtissnPhysics}},
 volume={739},
  pages={117--124},
post={\myehost{http://arxiv.org/abs/1405.3297}[arXiv:1405.3297]},
doi={10.1016/j.physletb.2014.10.048},
 issn={03702693},
 keywords={afshordi_niayesh,cosmology,dimensional_transmutaion,dimensionality,evolutionary,high_energy,quantum_gravity,stojkovic_dejan,string_theory},
}

@article{Ashketar1986New,
SerialNo={16},
author={Ashtekar, Abhay},
 year={1986},
title={New Variables for Classical and Quantum Gravity},
journal={\rvtsclPhysRevLett},
 volume={57},
 number={18},
  pages={2244--2247},
 orgname={American Physical Society},
doi={10.1103/PhysRevLett.57.2244},
 issn={00319007},
 keywords={nosource},
}

@article{Ashtekar1987New,
SerialNo={17},
author={Ashtekar, Abhay},
 year={1987},
title={New {{\?{Hamiltonian}}} Formulation of General Relativity},
journal={\rvtsclPhysRevD},
 volume={36},
 number={6},
  pages={1587--1602},
 orgname={American Physical Society},
doi={10.1103/PhysRevD.36.1587},
 issn={05562821},
 keywords={nosource},
}

@CUSTOMBIB{Ashtekar1992Weaving,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={18},
author={Ashtekar, Abhay and Rovelli, Carlo and Smolin, Lee},
 year={1992},
title={Weaving a classical metric with quantum threads},
 volume={69},
 number={2},
  pages={237--240},
doi={10.1103/PhysRevLett.69.237},
 xpost={\xURL \myehost{http://dx.doi.org/10.1103/PhysRevLett.69.237}},
}

@CUSTOMBIB{Ashtekar2004Background,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={19},
author={Ashtekar, Abhay and Lewandowski, Jerzy},
 year={2004},
title={Background independent quantum gravity: a status report},
 volume={21},
 number={15},
  pages={R53--r152},
doi={10.1088/0264-9381/21/15/r01},
 xpost={\xURL \myehost{http://dx.doi.org/10.1088/0264-9381/21/15/R01}},
}

@article{Rovelli1988Knot,
SerialNo={20},
author={Rovelli, Carlo and Smolin, Lee},
 year={1988},
title={Knot Theory and Quantum Gravity},
journal={\rvtsclPhysRevLett},
 volume={61},
 number={10},
  pages={1155--1158},
 orgname={American Physical Society},
doi={10.1103/PhysRevLett.61.1155},
 issn={00319007},
 keywords={bibliography,classic,constraints,knot_theory,lqg,quantum_gravity},
}

@article{Rovelli1990Loop,
SerialNo={21},
author={Rovelli, Carlo and Smolin, Lee},
 year={1990},
title={Loop Space Representation of Quantum General Relativity},
journal={{\rvtissnNuclear} {\rvtissnPhysics} {\rvtissnSecti} B},
 volume={331},
 number={1},
  pages={80--152},
doi={10.1016/0550-3213(90)90019-a},
 issn={05503213},
 keywords={ashtekar_variables,classic,constraint,diffeomorphism,knot_theory,lee_smolin,nosource,quantum_gravity,rovelli,self_dual,yang_mills},
}

@article{Ashtekar1992Gravitons,
SerialNo={22},
author={Ashtekar, Abhay and Rovelli, Carlo and Smolin, Lee},
 year={1992},
title={Gravitons and {{Loops}}},
journal={\rvtsclPhysRevD},
 volume={44},
 number={6},
  pages={1740--1755},
doi={10.1103/PhysRevD.44.1740},
}

@CUSTOMBIB{Bodendorfer-LQG,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={23},
author={N. Bodendorfer},
 year={2016},
title={An elementary introduction to loop quantum gravity},
doi={10.48550/arXiv.1607.05129},
}

@article{Hohm2017Background,
SerialNo={24},
author={Hohm, Olaf},
 year={2017},
title={On {{Background Independence}} and {{Duality Invariance}} in {{String
  Theory}}},
journal={\rvtsclPhysRevLett},
 volume={118},
 number={13},
  artnum={131601},
post={\myehost{http://arxiv.org/abs/1612.03966}[arXiv:1612.03966]},
 primaryClass={hep-th},
doi={10.1103/PhysRevLett.118.131601},
 issn={0031-9007, 1079-7114},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@article{Hohm2018Background,
SerialNo={25},
author={Hohm, Olaf},
 year={2018},
title={On {{Background Independence}} in {{String Theory}}},
journal={\rvtsclInternatJModernPhysD},
 volume={27},
 number={14},
  artnum={1847026},
post={\myehost{http://arxiv.org/abs/1806.08704}[arXiv:1806.08704]},
 primaryClass={hep-th},
doi={10.1142/s0218271818470260},
 issn={0218-2718, 1793-6594},
 keywords={High Energy Physics - Theory},
}

@CUSTOMBIB{Maccaferri2024String,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={26},
author={Maccaferri, Carlo},
 year={2024},
title={String {{Field Theory}}},
post={\myehost{http://arxiv.org/abs/2308.00875}[arXiv:2308.00875]},
 primaryClass={hep-th},
doi={10.1093/acrefore/9780190871994.013.66},
 keywords={High Energy Physics - Theory},
}

@article{Sen1994Quantum,
SerialNo={27},
author={Sen, Ashoke and Zwiebach, Barton},
 year={1994},
title={Quantum {{Background Independence}} of {{Closed String Field Theory}}},
journal={\rvtsclNuclearPhysB},
 volume={423},
 number={2--3},
  pages={580--630},
post={\myehost{http://arxiv.org/abs/hep-th/9311009}[arXiv:hep-th/9311009]},
doi={10.1016/0550-3213(94)90145-7},
 issn={05503213},
 keywords={High Energy Physics - Theory},
}

@book{Read2023Background,
SerialNo={28},
author={Read, James and Read, James},
 year={2023},
booktitle={Background {{Independence}} in {{Classical}} and {{Quantum Gravity}}},
 orgname={Oxford University Press},
 city = {Oxford, New York},
 isbn={978-0-19-288911-9},
}

@article{Maldacena1998The-Large,
SerialNo={29},
author={Maldacena, Juan},
 year={1998},
title={The Large {\?{N Limit}} of Superconformal Field Theories and
  Supergravity},
journal={\rvtsclAdvTheorMathPhys},
 volume={2},
 number={2},
  pages={231--252},
post={\myehost{http://arxiv.org/abs/hep-th/9711200}[arXiv:hep-th/9711200]},
doi={10.1023/a:1026654312961},
 issn={10950761},
 isbn={00207748},
 keywords={antidesitter,cft,holography,large\_n\_theories,m\_theory,maldacena\_conjecture,susy},
}

@article{Witten1998Anti,
SerialNo={30},
author={Witten, Edward},
 year={1998},
title={Anti de Sitter Space and Holography},
journal={\rvtsclAdvTheorMathPhys},
 volume={2},
 number={2},
  pages={253--290},
post={\myehost{http://arxiv.org/abs/hep-th/9802150}[arXiv:hep-th/9802150]},
doi={10.4310/ATMP.1998.v2.n2.a2},
 issn={10950761},
 isbn={1753-6561 (Electronic)},
 keywords={adscft,antidesitter,classic,conformal_field_theory,holography,maldacena_conjecture,supergravity,thermodynamics,witten},
}

@article{Aharony1999Large,
SerialNo={31},
author={Aharony, Ofer and Gubser, S.S. S. and Maldacena, Juan and Ooguri,
  Hirosi and Oz, Yaron},
 year={1999},
title={Large {{\?N Field Theories}}, {{String Theory}} and {{Gravity}}},
journal={\rvtsclPhysRep},
 volume={323},
 number={3--4},
  pages={261},
post={\myehost{http://arxiv.org/abs/hep-th/9905111}[arXiv:hep-th/9905111]},
doi={10.1016/s0370-1573(99)00083-6},
 issn={03701573},
 isbn={9780511618482},
 keywords={adscft,General Relativity and Quantum Cosmology,High Energy Physics
  - Lattice,High Energy Physics - Phenomenology,High Energy Physics -
  Theory,largen-theories,qcd,qft,quantum-gravity,string-theory},
}

@article{Gubser1998Gauge,
SerialNo={32},
author={Gubser, S. S. and Klebanov, Igor R. and Polyakov, Alexander M.},
 year={1998},
title={Gauge {{Theory Correlators}} from {{Non-Critical String Theory}}},
journal={{\rvtissnPhysica} {\rvtissnLetter}},
 volume={B428},
  pages={105--114},
post={\myehost{http://arxiv.org/abs/hep-th/9802109v2}[arXiv:hep-th/9802109v2]},
doi={10.1016/s0370-2693(98)00377-3},
 keywords={adscft,classic,correlation_functions,gauge_theory,greens_functions,holography,large_n_theories,nosource,string_theory,strong_coupling,susy,yang_mills},
}

@article{Bardeen1999The-Extreme,
SerialNo={33},
author={Bardeen, James and Horowitz, Gary T.},
 year={1999},
title={The {{Extreme \?{Kerr} Throat Geometry}}: {{\?A Vacuum Analog}} of {\?{AdS}}\_2
  x {\?S}{\textasciicircum}2},
journal={{\rvtissnPhysica} {\rvtissnReview} D - {\rvtissnParticle} Fields, {\rvtissnGravitation} {\rvtissnCosmolog}},
 volume={60},
 number={10},
  artnum={104030},
post={\myehost{http://arxiv.org/abs/hep-th/9905099}[arXiv:hep-th/9905099]},
doi={10.1103/PhysRevD.60.104030},
 issn={15502368},
}

@article{Guica2009The-Kerr/CFT,
SerialNo={34},
author={Guica, Monica and Hartman, Thomas and Song, Wei and Strominger,
  Andrew},
 year={2009},
title={The {{\?{Kerr}}}/{{\?{CFT} Correspondence}}},
journal={\rvtsclPhysRevD},
 volume={80},
 number={12},
  artnum={124008},
post={\myehost{http://arxiv.org/abs/0809.4266}[arXiv:0809.4266]},
doi={10.1103/PhysRevD.80.124008},
 issn={1550-7998, 1550-2368},
 keywords={_tablet,Astrophysics,General Relativity and Quantum Cosmology,High
  Energy Physics - Theory},
}

@CUSTOMBIB{Hartnoll2016Holographic,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={35},
author={Hartnoll, Sean A. and Lucas, Andrew and Sachdev, Subir},
 year={2016},
title={Holographic Quantum Matter},
post={\myehost{http://arxiv.org/abs/1612.07324}[arXiv:1612.07324]},
 primaryClass={hep-th},
 isbn={978-0-262-03843-0},
}

@CUSTOMBIB{Sachdev2010Strange,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={36},
author={Sachdev, Subir},
 year={2010},
title={Strange Metals and the {{AdS}}/{{\?{CFT}}} Correspondence},
post={\myehost{http://arxiv.org/abs/1010.0682}[arXiv:1010.0682]},
doi={10.1088/1742-5468/2010/11/p11022},
 issn={1742-5468},
 keywords={adscft,condensed_matter,fermi-liquid,fractionalization,impurities,lattice_models,review,sachdev},
}

@article{Sachdev2015Bekenstein-Hawking,
SerialNo={37},
author={Sachdev, Subir},
 year={2015},
title={Bekenstein-Hawking Entropy and Strange Metals},
journal={{\rvtissnPhysica} {\rvtissnReview} X},
 volume={5},
 number={4},
post={\myehost{http://arxiv.org/abs/1506.05111}[arXiv:1506.05111]},
doi={10.1103/PhysRevX.5.041025},
 issn={21603308},
 keywords={Condensed matter physics,Particles and fields},
}

@article{Almheiri2014Bulk,
SerialNo={38},
author={Almheiri, Ahmed and Dong, Xi and Harlow, Daniel},
 year={2014},
title={Bulk {{Locality}} and {{Quantum Error Correction}} in {\?{AdS}} /
  {{\?{CFT}}}},
journal={\rvtsclJHighEnergyPhys},
 volume={2015},
 number={4},
post={\myehost{http://arxiv.org/abs/1411.7041v2}[arXiv:1411.7041v2]},
doi={10.1007/jhep04(2015)163},
 issn={10298479},
}

@article{Pastawski2015Holographic,
SerialNo={39},
author={Pastawski, Fernando and Yoshida, Beni and Harlow, Daniel and Preskill,
  John},
 year={2015},
title={Holographic Quantum Error-Correcting Codes: \?{T}oy Models for the
  Bulk/Boundary Correspondence},
journal={\rvtsclJHighEnergyPhys},
 volume={2015},
 number={6},
  pages={149},
post={\myehost{http://arxiv.org/abs/1503.06237}[arXiv:1503.06237]},
doi={10.1007/jhep06(2015)149},
 issn={1029-8479},
 keywords={nosource},
}

@article{Rosen1940General,
SerialNo={40},
author={Rosen, N.},
 year={1940},
title={General {{Relativity}} and {{Flat Space}}. \?{I}},
journal={\rvtiopPhysRev},
 volume={57},
 number={2},
  pages={147--150},
 orgname={{American Physical Society}},
doi={10.1103/PhysRev.57.147},
}

@article{Rosen1940aGeneral,
SerialNo={41},
author={Rosen, N.},
 year={1940},
title={General {{Relativity}} and {{Flat Space}}. {{\?{II}}}},
journal={\rvtiopPhysRev},
 volume={57},
 number={2},
  pages={150--153},
 orgname={{American Physical Society}},
doi={10.1103/PhysRev.57.150},
}

@article{de-Rham2011Resummation,
SerialNo={42},
author={{{de Rham}}, Claudia and Gabadadze, Gregory and Tolley, Andrew J.},
 year={2011},
title={Resummation of {{Massive Gravity}}},
journal={\rvtsclPhysRevLett},
 volume={106},
 number={23},
  artnum={231101},
post={\myehost{http://arxiv.org/abs/1011.1232}[arXiv:1011.1232]},
 primaryClass={gr-qc, physics:hep-th},
doi={10.1103/PhysRevLett.106.231101},
 issn={0031-9007, 1079-7114},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@article{Boulware1972Can-Gravitation,
SerialNo={43},
author={Boulware, David G. and Deser, S.},
 year={1972},
title={Can {{Gravitation Have}} a {{Finite Range}}?},
chsep={\chsep[atitle]{~}},
journal={\rvtsclPhysRevD},
 volume={6},
  pages={3368--3382},
doi={10.1103/PhysRevD.6.3368},
 issn={1550-79980556-2821},
}

@article{Hassan2012Bimetric,
SerialNo={44},
author={Hassan, S. F. and Rosen, Rachel A.},
 year={2012},
title={Bimetric {{Gravity}} from {{Ghost-free Massive Gravity}}},
journal={\rvtsclJHighEnergyPhys},
 volume={2012},
 number={2},
  pages={126},
post={\myehost{http://arxiv.org/abs/1109.3515}[arXiv:1109.3515]},
 primaryClass={hep-th},
doi={10.1007/jhep02(2012)126},
 issn={1029-8479},
 keywords={High Energy Physics - Theory},
}

@article{Hassan2012Ghost-Free,
SerialNo={45},
author={Hassan, S. F. and Rosen, Rachel A. and {Schmidt-May}, Angnis},
 year={2012},
title={Ghost-Free {{Massive Gravity}} with a {{General Reference Metric}}},
journal={\rvtsclJHighEnergyPhys},
 volume={2012},
 number={2},
  pages={26},
post={\myehost{http://arxiv.org/abs/1109.3230}[arXiv:1109.3230]},
 primaryClass={hep-th},
doi={10.1007/jhep02(2012)026},
 issn={1029-8479},
 keywords={High Energy Physics - Theory},
}

@article{Callan1985Strings,
SerialNo={46},
author={Callan, C. G. and Friedan, D. and Martinec, E. J. and Perry, M. J.},
 year={1985},
title={Strings in Background Fields},
journal={{\rvtissnNuclear} {\rvtissnPhysics} {\rvtissnSecti} B},
 volume={262},
 number={4},
  pages={593--609},
doi={10.1016/0550-3213(85)90506-1},
 issn={05503213},
 keywords={antisymmetric tensor,background,bosonic
  string,callan\_curtis,classic,conformal
  invariance,dilaton,fermions,friedan\_daniel,heterotic
  string,martinec\_e\_j,metric,perry\_m\_j,quantum
  gravity,string-theory,supersymmetry},
}

@CUSTOMBIB{Tong2009Lectures,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={47},
author={Tong, David},
 year={2009},
title={Lectures on {{String Theory}}},
post={\myehost{http://arxiv.org/abs/0908.0333}[arXiv:0908.0333]},
 keywords={beginner,introductory,lecture\_notes,lectures,pedagogical,semester\_course,string
  theory,string\_theory,tong\_david},
}

@book{Schottenloher2008A-Mathematical,
SerialNo={48},
author={M. Schottenloher},
 year={2008},
booktitle={A Mathematical Introduction to Conformal Field Theory},
 edition={second ed.},
 orgname={{Springer Berlin, Heidelberg}},
 city = {{Berlin}},
doi={10.1007/978-3-540-68628-6},
}

@CUSTOMBIB{Balthazar-t-backgrounds,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={49},
author={Bruno Balthazar, Jinwei Chu, David Kutasov},
 year={2023},
title={On Time-Dependent Backgrounds In {\?{1}}+1 Dimensional String Theory},
doi={10.48550/arXiv.2311.17992},
}

@article{Bergshoeff1987BornInfeld,
SerialNo={50},
author={Bergshoeff, E. and Sezgin, E. and Pope, C. N. and Townsend, P. K.},
 year={1987},
title={The {{\?{Born}-\?{Infeld}}} Action from Conformal Invariance of the Open
  Superstring},
journal={\rvtsclPhysLettB},
 volume={188},
 number={1},
  pages={70--74},
doi={10.1016/0370-2693(87)90707-6},
 issn={0370-2693},
}

@article{Leigh1989Dirac-Born-Infeld,
SerialNo={51},
author={Leigh, R. G.},
 year={1989},
title={{Dirac}-{{\?{Born}-Infeld Action}} from {{\?{Dirichlet} Sigma Model}}},
journal={\rvtsclModernPhysLettA},
 volume={04},
 number={28},
  pages={2767--2772},
 orgname={{World Scientific Publishing Co.}},
doi={10.1142/s0217732389003099},
 issn={0217-7323},
}

@article{Metsaev1987Borninfeld,
SerialNo={52},
author={Metsaev, R. R. and Rahmanov, M. A. and Tseytlin, A. A.},
 year={1987},
title={The \?{Born}-Infeld Action as the Effective Action in the Open Superstring
  Theory},
journal={\rvtsclPhysLettB},
 volume={193},
 number={2},
  pages={207--212},
doi={10.1016/0370-2693(87)91223-8},
 issn={0370-2693},
}

@article{Tseytlin1996Self-Duality,
SerialNo={53},
author={Tseytlin, A. A.},
 year={1996},
title={Self-Duality of {{\?{Born}-\?{Infeld}}} Action and {{\?{Dirichlet}}} {\?{3}}-Brane of
  Type {{\?{IIB}}} Superstring Theory},
journal={\rvtsclNuclearPhysB},
 volume={469},
 number={1--2},
  pages={51--67},
post={\myehost{http://arxiv.org/abs/hep-th/9602064}[arXiv:hep-th/9602064]},
doi={10.1016/0550-3213(96)00173-3},
 issn={05503213},
 keywords={High Energy Physics - Theory},
}

@inbook{Green2012Superstring,
SerialNo={54},
author={Green, Michael B. and Schwarz, John H. and Witten, Edward},
 year={2012},
booktitle={Superstring Theory: 25th Anniversary Edition},
 series={Cambridge Monographs on Mathematical Physics},
 orgname={Cambridge University Press},
doi={10.1017/cbo9781139248563},
}

@CUSTOMBIB{Thiemann2004The-LQG-String:,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={55},
author={Thiemann, Thomas},
 year={2004},
title={The {\?{LQG}}-String: \?{L}oop Quantum Gravity Quantization of String Theory I.
  Flat Target Space},
post={\myehost{http://arxiv.org/abs/hep-th/0401172}[arXiv:hep-th/0401172]},
 xpost={\xURL \myehost{http://arxiv.org/abs/hep-th/0401172}},
}

@CUSTOMBIB{t-Hooft1993Dimensional,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={56},
author={{'t Hooft}, G.},
 year={1993},
title={Dimensional {{Reduction}} in {{Quantum Gravity}}},
post={\myehost{http://arxiv.org/abs/gr-qc/9310026}[arXiv:gr-qc/9310026]},
doi={10.1088/0305-4470/27/6/041},
 issn={0305-4470},
 keywords={algebra,boolean,cellular\_automata,classic,dimensional\_reduction,holography,two\_dimensional},
}

@article{Bergshoeff2013Zwei-Dreibein,
SerialNo={57},
author={Bergshoeff, Eric A. and {{de Haan}}, Sjoerd and Hohm, Olaf and Merbis,
  Wout and Townsend, Paul K.},
 year={2013},
title={Zwei-{{Dreibein Gravity}}},
journal={\rvtsclPhysRevLett},
 volume={111},
 number={11},
  artnum={111102},
post={\myehost{http://arxiv.org/abs/1307.2774}[arXiv:1307.2774]},
 primaryClass={hep-th},
doi={10.1103/PhysRevLett.111.111102},
 issn={0031-9007, 1079-7114},
 keywords={High Energy Physics - Theory},
}

@book{Blais2013A-new-quantization,
SerialNo={58},
author={Blais, Timothy},
 year={2013},
booktitle={A New Quantization Condition for Parity-Violating Three-Dimensional
  Gravity},
 orgname={McGill U.},
}

@inbook{Carlip2003Quantum,
SerialNo={59},
author={Carlip, Steven},
 year={2003},
booktitle={Quantum Gravity in {\?{2}}+1 Dimensions},
 series={Cambridge Monographs on Mathematical Physics},
 orgname={Cambridge University Press},
doi={10.1017/cbo9780511564192},
 isbn={978-0-521-54588-4, 978-0-511-82229-2},
}

@article{Dai1989New-Connections,
SerialNo={60},
author={{Jin Dai}, {} and Leigh, R.G. and {Joseph Polchinski}, {}},
 year={1989},
title={New {{Connections Between String Theories}}},
journal={\rvtsclModernPhysLettA},
 volume={04},
 number={21},
  pages={2073--2083},
doi={10.1142/s0217732389002331},
 issn={0217-7323},
 keywords={nosource},
}

@article{Polchinski1995Dirichlet-Branes,
SerialNo={61},
author={Polchinski, Joseph},
 year={1995},
title={{Dirichlet} Branes and {{Ramond-Ramond}} Charges},
journal={\rvtsclPhysRevLett},
 volume={75},
 number={26},
  pages={4724--4727},
 orgname={American Physical Society},
post={\myehost{http://arxiv.org/abs/hep-th/9510017}[arXiv:hep-th/9510017]},
doi={10.1103/PhysRevLett.75.4724},
 issn={00319007},
 keywords={classic,cosmological_constant,d-branes,polchinski,string_theory,superstrings,supersymmetry},
}

@article{Horava1989Background,
SerialNo={62},
author={Ho{\v r}ava, Petr},
 year={1989},
title={Background Duality of Open-String Models},
journal={\rvtsclPhysLettB},
 volume={231},
 number={3},
  pages={251--257},
doi={10.1016/0370-2693(89)90209-8},
 issn={0370-2693},
}

@article{Wise2010MacDowell-Mansouri,
SerialNo={63},
author={Wise, Derek Keith},
 year={2010},
title={{{\?{MacDowell}}}-{{Mansouri Gravity}} and {{Cartan Geometry}}},
journal={\rvtsclClassicalQuantumGravity},
 volume={27},
 number={15},
  artnum={155010},
post={\myehost{http://arxiv.org/abs/gr-qc/0611154}[arXiv:gr-qc/0611154]},
doi={10.1088/0264-9381/27/15/155010},
 issn={0264-9381},
 keywords={cartan-geometry,macdowell-mansouri},
}

@article{Collaboration2020Planck,
SerialNo={64},
author={Collaboration, Planck and Aghanim, N. and Akrami, Y. and Ashdown, M.
  and Aumont, J. and Baccigalupi, C. and others},
 year={2020},
title={{Planck} 2018 Results. {{\?{VI}}}. {\?{Cosmological}} Parameters},
journal={\rvtiopAstronAstrophys},
 volume={641},
  pages={A6},
post={\myehost{http://arxiv.org/abs/1807.06209}[arXiv:1807.06209]},
 primaryClass={astro-ph},
doi={10.1051/0004-6361/201833910},
 issn={0004-6361, 1432-0746},
 keywords={Astrophysics - Cosmology and Nongalactic Astrophysics},
}

@article{Peebles2003Cosmological,
SerialNo={65},
author={Peebles, P. J. E. and Ratra, Bharat},
 year={2003},
title={The {{Cosmological Constant}} and {{Dark Energy}}},
journal={\rvtsclRevModernPhys},
 volume={75},
 number={2},
  pages={559--606},
post={\myehost{http://arxiv.org/abs/astro-ph/0207347}[arXiv:astro-ph/0207347]},
doi={10.1103/RevModPhys.75.559},
 issn={0034-6861, 1539-0756},
 keywords={Astrophysics,General Relativity and Quantum Cosmology,High Energy
  Physics - Phenomenology,High Energy Physics - Theory},
}

@article{Lust2021Extracting,
SerialNo={66},
author={Lust, Dieter and Markou, Chrysoula and Mazloumi, Pouria and
  Stieberger, Stephan},
 year={2021},
title={Extracting {{Bigravity}} from {{String Theory}}},
journal={\rvtsclJHighEnergyPhys},
 volume={2021},
 number={12},
  pages={220},
post={\myehost{http://arxiv.org/abs/2106.04614}[arXiv:2106.04614]},
 primaryClass={gr-qc, physics:hep-ph, physics:hep-th},
doi={10.1007/jhep12(2021)220},
 issn={1029-8479},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Phenomenology,High Energy Physics - Theory},
}

@article{Yan2021Strings,
SerialNo={67},
author={Yan, Ziqi},
 year={2021},
title={Strings in {{Bimetric Spacetimes}}},
journal={\rvtsclJHighEnergyPhys},
 volume={2021},
 number={9},
  pages={164},
post={\myehost{http://arxiv.org/abs/2105.00011}[arXiv:2105.00011]},
 primaryClass={gr-qc, physics:hep-th},
doi={10.1007/jhep09(2021)164},
 issn={1029-8479},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@CUSTOMBIB{Hehl2023Four,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={68},
author={Hehl, Friedrich W.},
 year={2023},
title={Four {{Lectures}} on {\?{Poincar\'e}} {{Gauge Field Theory}}},
 xnumber={arXiv:2303.05366},
 xorgname={arXiv},
post={\myehost{http://arxiv.org/abs/2303.05366}[arXiv:2303.05366]},
 primaryClass={gr-qc, physics:hep-th},
doi={10.48550/arXiv.2303.05366},
 keywords={General Relativity and Quantum Cosmology,High Energy Physics -
  Theory},
}

@article{Altaisky2024Poincare,
SerialNo={69},
author={Altaisky, M. V.},
 year={2024},
title={Poincar\'e Group Spin Networks},
journal={\rvtsclInternatJTheoretPhys},
 volume={63},
 number={6},
  pages={145},
post={\myehost{http://arxiv.org/abs/2311.06328}[arXiv:2311.06328]},
 primaryClass={gr-qc},
doi={10.1007/s10773-024-05688-7},
 issn={1572-9575},
 keywords={General Relativity and Quantum Cosmology},
}

@CUSTOMBIB{Smolin1998Strings,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={70},
author={Smolin, Lee},
 year={1998},
title={Strings as perturbations of evolving spin-networks},
post={\myehost{http://arxiv.org/abs/hep-th/9801022}[arXiv:hep-th/9801022]},
doi={10.1016/s0920-5632(00)00758-1},
 xpost={\xURL \myehost{http://dx.doi.org/10.1016/S0920-5632(00)00758-1}},
}

@article{Markopoulou1997Causal,
SerialNo={71},
author={Markopoulou, Fotini and Smolin, Lee},
 year={1997},
title={Causal Evolution of Spin Networks},
journal={\rvtsclNuclearPhysB},
 volume={508},
 number={1--2},
  pages={32},
post={\myehost{http://arxiv.org/abs/gr-qc/9702025}[arXiv:gr-qc/9702025]},
doi={10.1016/s0550-3213(97)00488-4},
 issn={05503213},
 keywords={causality,classical limit,critical behavior,evolution,lattice
  models,lqg,many body,markopoulou_f,percolation,potts model,smolin_lee,spin
  networks},
}

@CUSTOMBIB{Vaid2017Connecting,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={72},
author={Vaid, Deepak},
 year={2017},
title={Connecting {{Loop Quantum Gravity}} and {{String Theory}} via {{Quantum
  Geometry}}},
post={\myehost{http://arxiv.org/abs/1711.05693}[arXiv:1711.05693]},
 keywords={area operator,conformal invariance,emergent gravity,loop quantum
  gravity,nambu-goto action,quantum gravity,string
  theory,unification,vaid\_deepak},
}

@article{Friedan1985Nonlinear,
SerialNo={73},
author={Friedan, Daniel Harry},
 year={1985},
title={Nonlinear {{Models}} in {{Two}} + {{Epsilon Dimensions}}},
journal={{\rvtissnAnnal} {\rvtissnPhysica}},
 volume={163},
  pages={318},
doi={10.1016/0003-4916(85)90384-7},
 keywords={Approximation: Epsilon Expansion,field Theory: Nonlinear,field
  Theory: Scalar,field Theory: Space-time,field Theory:
  Two-dimensional,perturbation Theory: Higher-order,renormalization
  Group,renormalization: Regularization,temperature: Low,thesis},
}

@INPROCEEDINGS{Callan1989Sigma,
SerialNo={74},
author={Callan, Jr., Curtis G. and Thorlacius, Larus},
 year={1989},
title={Sigma {{Models}} and {{String Theory}}},
booktitle={Theoretical {{Advanced Study Institute}} in {{Elementary Particle
  Physics}}: {{Particles}}, {{Strings}} and {{Supernovae}}},
ctitle={TASI 88},
 keywords={algebra: Virasoro,background field,dimension: 2,field theory:
  conformal,field theory: dilaton,invariance:
  reparametrization,lectures,operator product expansion,sigma model:
  nonlinear,string model},
}

@inbook{Polchinski1998aString,
SerialNo={75},
author={Polchinski, Joseph},
 year={1998},
series={String Theory (Cambridge Monographs on Mathematical Physics)},
volume={vol. 1},
 edition={first ed.},
 orgname={Cambridge University Press},
 isbn={9780521633031},
 post={\xURL \myehost{http://www.amazon.com/exec/obidos/redirect?tag=citeulike07-20\&path=ASIN/0521633036}},
}

@CUSTOMBIB{Tong2010Lectures,
mypattern={[authors,atitle,midc][booktag,bktitle,yr,endbooktag,bibpages,bibdoi][post,myehost]},
SerialNo={76},
author={Tong, David},
 year={2010},
title={{Lectures on String Theory}},
post={\myehost{http://arxiv.org/abs/0908.0333}[arXiv:0908.0333]},
 xpost={\xURL \myehost{http://arxiv.org/abs/0908.0333}},
}

@book{Zwiebach2009A-First,
SerialNo={77},
author={Barton Zwiebach},
 year={2009},
booktitle={A First Course in String Theory},
 edition={second ed.},
 orgname={Cambridge University Press},
 isbn={9780521880329,0521880327},
 post={\xURL \myehost{http://gen.lib.rus.ec/book/index.php?md5=B4D347FF21638FD4593C0C2BAFBEC160}},
}

@article{Grimshaw2010Homogenization,
SerialNo={78},
author={Grimshaw, Roger and Pelinovsky, Dmitry and Pelinovsky, Efim},
 year={2010},
title={Homogenization of the Variable-Speed Wave Equation},
journal={\rvtsclWaveMotion},
 volume={47},
 number={8},
  pages={496--507},
doi={10.1016/j.wavemoti.2010.03.001},
 issn={0165-2125},
 keywords={Exact solutions,Point symmetries,Variable media,Wave equation},
}

\end{bibwrite}

\end{document}

### 2025-10-23 AoP/final-proof/aop-format.tex
Final version of published article

@@
 later work~\cite{Hassan2012Bimetric,Hassan2012Ghost-Free} showed that the second metric need not be flat and that an action of the following form:
-\begin{eqnarray}
+\begin{equation}
 \xlabel{eqn:hassan-bimetric}
-\nf&& S = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)} + \nonumber\\\nf&&\xq
+S = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)}
 + 2 m^2 M^2_{eff} \int \diff^4 x \sqrt{-g}\sum_{n=0}^{4}\beta_n e_n (\sqrt{g^{-1} f}),
-\end{eqnarray}
+\end{equation}
 where $g_{\mu\nu}$ and $f_{\mu\nu}$ are {arbitrary} metrics, $M_g^2, M_f^2$ are the Planck masses for the two sectors respectively.
@@
 where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
-\begin{eqnarray}
+\begin{equation}
 \xlabel{eqn:polyakov-bimetric}
-\nf&& S_{PB} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} - \nonumber\\\nf&&\xq
-- \frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} +  \nonumber\\\nf&&\xq
+S_{PB} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}
+- \frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}
 + S_{int} [g, h, X].
-\end{eqnarray}
+\end{equation}
 
@@
 \end{equation}
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:g-em-tensor}
-\nf&& T^{(G)} _{c d} \coloneq  G_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \nonumber\\\nf&&\xq
+T^{(G)} _{c d} \coloneq  G_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\nu}
 - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \biggm) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}},
-\end{eqnarray}
+\end{equation}
 and completely analogously for the $H_{\mu \nu}$ metric,
@@
 \end{equation}
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:h-em-tensor}
-\nf&& T^{(H)} _{c d} \coloneq  H_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \nonumber\\\nf&&\xq
+T^{(H)} _{c d} \coloneq  H_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\mu}
 - \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \biggm) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
-\end{eqnarray}
+\end{equation}
 If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
@@
 By writing the inverse metric $g^{a b}$ in terms of Levi-Civita symbols $g^{a b} = \varepsilon ^{a c} \varepsilon ^{b d} g_{c d} / 2 g$,\footnote{This expression for the inverse of a metric is probably not familiar to many people, but its correctness can be checked by contracting both sides of the expression with $g_{ab}$ and seeing that the resulting expression is the much better known expression for the determinant $g \equiv \det{g_{ab}}$}  this implies that
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:SgS-implication}
-\nf&&\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times\nonumber \\\nf&&\xq
+\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right)
 \times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0,
-\end{eqnarray}
+\end{equation}
 which can be achieved if the expression in parenthesis vanishes. For this end, the most natural possibility is
@@
 If we impose the conditions \neqref{eqn:h-delta-relation}, \neqref{eqn:delta-epsilon-relation,eqn:H-G-relation} plus $T' = - T k/2$ in the interactionless bimetric Polyakov action \neqref{eqn:polyakov-bimetric}, we obtain the Polyakov version of the area-corrected action \neqref{eqn:modified-ng-action}:
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:inverse-metric-Polyakov}
-S_{I A P}& =& - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times\nonumber \\\nf&& \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
-\end{eqnarray}
+S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
+\end{equation}
 
@@
 which leads to the stress--energy tensor for the worldsheet:
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:inverse-area-em-tensor}
-\nf&& T_{c d} \coloneq  \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \nonumber\\ \nf&&\xq - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
-\end{eqnarray}
+T_{c d} \coloneq  \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
+\end{equation}
 from which we can extract the metric $g_{c d}$ as
@@
 \end{equation}
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:X-eom-inverse-area}
-\nf&& F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} =\nonumber \\\nf&&\xq = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
-\end{eqnarray}
+F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
+\end{equation}
 where
@@
 The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb--Ramond field~\cite{Tong2009Lectures}
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:area-corrected-K-R-action}
-S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \nonumber\\\nf&&\xq
+S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right)
 \times \Bigl( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigr),
-\end{eqnarray}
+\end{equation}
 where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:area-corrected-K-R-action-v2}
-S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times\nonumber \\
-&&\times \Bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
+S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \Bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
 - \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigm) .
-\end{eqnarray}
+\end{equation}
 By varying this action \wrt $\Delta ^{c d}$ we get
@@
 with $\widetilde{f}$ given by
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:1/f-tilde}
-\frac{1}{\widetilde{f}} &=& \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - 
-\nonumber\\\nf&&- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm),
-\end{eqnarray}
+\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm),
+\end{equation}
 where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
@@
 can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:mu-constraint-final}
-\mu ^2 &=& \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \bigm( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \nonumber\\\nf&&
+\mu ^2 = \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \bigm( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right)
 - E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \bigm) .
-\end{eqnarray}
+\end{equation}
 
@@
 What is new in our analysis is the $\mu ^2$ term, which we take as being constant for a first analysis, making it so the solution is given by Fourier transform
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:KG-Polyakov-solution-initial}
-X^{\mu} (\tau, \sigma) &=& \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \biggm( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \nonumber\\\nf&&
+X^{\mu} (\tau, \sigma) = \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \biggm( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)}
 + \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \biggm),
-\end{eqnarray}
+\end{equation}
 with $E_{p} = \sqrt{p^2 + \mu ^2}$.
@@
 Looking closer at our constraints \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:string-rest-mass-classical-1}
-M^2 &=& - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n, n} \right) - \nonumber\\\nf&&
-- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Biggm) =
-\end{eqnarray}
-\begin{eqnarray}
+M^2 = - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n, n} \right)
+- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Biggm)
+\end{equation}
+\begin{equation}
  \xlabel{eqn:string-rest-mass-classical-2}
-\nf&& = \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \nonumber\\\nf&&
+= \frac{4}{\alpha '} \Biggm( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) 
 - \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Biggm) .
-\end{eqnarray}
+\end{equation}
 
@@
 We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:canonical-momentum-density}
-\Pi ^{\nu} (x) &=& F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \biggm( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \nonumber\\\nf&&
+\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \biggm( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)}
 - (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \biggm)
-\end{eqnarray}
+\end{equation}
 where
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:F-minus-full-sum}
-F^{-} &=& 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \nonumber\\\nf&&
+F^{-} = 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}}
 = \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right),
-\end{eqnarray}
+\end{equation}
 and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
@@
 \neqref{eqn:string-rest-mass-classical-1} for the string rest mass, from which we can now see that the string mass spectrum will get shifted by this constant
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:shifted-mass-spectrum}
-\Hat{M}^2 &=& \frac{8}{\alpha '} \Biggm( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \nonumber\\\nf&&
+\Hat{M}^2 = \frac{8}{\alpha '} \Biggm( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu}
 - \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Biggm) .
-\end{eqnarray}
+\end{equation}
 This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d, d)$ is finite, and the result is
-\begin{eqnarray}
-a &=& - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \nonumber\\\nf&&
+\begin{equation}
+a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n}
 = - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n},
-\end{eqnarray}
+\end{equation}
 which is easily computable given a value for $\mu$. Below we provide a table with the value of $a$ for different spacetime dimensionalities $D$ and mass parameters $\mu$ (see \tabref{TeXFolio:tab1}).
@@
 The mass-shell now reads
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:nth-state-mass-shell}
-\frac{\alpha '}{8} M^2 &=& \Biggm( \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert   ^2 - \nonumber\\\nf&&
+\frac{\alpha '}{8} M^2 = \Biggm( \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert^2 
 - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Biggm),
-\end{eqnarray}
+\end{equation}
 while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n, 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that
@@
 for the ground state and
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:nth-mass-shell-simplified}
-\frac{\alpha '}{16} p^2 &=& a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} = \nonumber\\\nf&&
+\frac{\alpha '}{16} p^2 a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} 
 = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n}
-\end{eqnarray}
+\end{equation}
 for the $n$th state.
@@
 emergent dimension"~\cite{Afshordi2014Emergent} model, with the action being
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:emergent-dimensions-action}
-S_{ED} &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \nonumber\\\nf&&
+S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu}
 + \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \bigm)
-\end{eqnarray}
+\end{equation}
 where $T$ is the {temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ...
@@
 One could also consider a more general form of action \neqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:emergent-dimensions-curved}
-S' _{E D} &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \nonumber\\\nf&&
+S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
 + \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \bigm),
-\end{eqnarray}
+\end{equation}
 where the mass parameters will be constrained as in
@@
 since those are the ones that show up in the $X^{\mu}$ equations of motion
-\begin{eqnarray}
-\nf&& g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \nonumber\\\nf&&
+\begin{equation}
+g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda}
 = \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
-\end{eqnarray}
+\end{equation}
 
@@
 or more explicitly as
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:poincare-polyakov-decomp-explicit}
-S' _{P} [X^{\mu}, X^{r}] &=& -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \nonumber\\\nf&&
-- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r} - \nonumber\\\nf&&
+S' _{P} [X^{\mu}, X^{r}] = -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} 
+- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r}
 - \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r},
-\end{eqnarray}
+\end{equation}
 where we can see a natural decomposition of the expanded bulk metric $G_{A B}$ as a $(d+1)$-dimensional tensor $\eta _{\mu \nu}$, a $(d+1)$-dimensional vector $V_{\mu} = G_{\mu r}$ and a scalar $V = G_{r r}$, akin to the ADM decomposition of the metric in standard GR literature.
@@
 By varying the action \neqref{eqn:poincare-polyakov}, we get two sets of constraints from the variation of $g_{a b}$ and $A_{a} ^{A B}$, namely the vanishing of the worldsheet energy--momentum and spin-linear-momentum tensors $T_{a b}$ and $\sigma _{a} ^{A B}$
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:gauged-WS-EM-tensor}
-T_{a b} : &=& \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B} - \nonumber\\\nf&&
+T_{a b} : = \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} G_{A B}
 - g_{a b} g^{c d} \mc{D}_{c} X^{A} \mc{D}_{d} X^{B} G_{A B} = 0
-\end{eqnarray}
+\end{equation}
 \xpar\cvskip[-1pc] 
@@
 The variation of the action \wrt $X^{A}$ results in the equation of motion of the embbeding fields
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:gauged-X-EoM}
-\nf&& \mc{D}_{a} [\sqrt{- g} g^{a b} \mc{D}_{b} X^{B} G_{B C}] = \nonumber\\\nf&&
+\mc{D}_{a} [\sqrt{- g} g^{a b} \mc{D}_{b} X^{B} G_{B C}] 
 = \sqrt{g} g^{a b} \mc{D}_{a} X^{A} \mc{D}_{b} X^{B} \partial _{C} G_{A B},
-\end{eqnarray}
+\end{equation}
 which in worldsheet \textquotedblleft covariant conformal gauge" $g^{a b} = \e ^{- \phi} \eta ^{a b}$ and for flat background geometry $G_{A B} = \eta ' _{A B}$ with
@@
 From here on, we will work on the case of $\ep = - 1$ (adS background), for which the above equation can be expanded as
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:expanded-gauged-X-EoM}
-\nf&& \eta ^{a b} \bigm( \del _{a} \del _{b} X^{A} + 2 \mu A^{A} _{a B} \del _{b} X^{B} + \nonumber\\\nf&&
+\eta ^{a b} \bigm( \del _{a} \del _{b} X^{A} + 2 \mu A^{A} _{a B} \del _{b} X^{B}
 + \mu \del _{a} A^{A} _{b B} X^{B} + \mu ^2 A^{A} _{a B} A^{B} _{b C} X^{C} \bigm) = 0 .
-\end{eqnarray}
+\end{equation}
 To produce the desired bulk geometry, the background connection can be taken as
@@
 from which the pulledback connection is $\mc{A}_{a} = \del _{a} X^{\mu} \mc{A}_{\mu}$, whereby imposing conformal gauge on the induced metric $\gamma _{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} = \e ^{\varphi} \eta _{a b}$ we can separate equations for the Minkowski sector $X^{\mu}$ and for the holographic dimension $X^{r}$:
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:Minkowski-sector-EoM}
-\nf&& \eta ^{a b} \del _{a} \del _{b} X^{\mu} + \nonumber\\\nf&&
+\eta ^{a b} \del _{a} \del _{b} X^{\mu}
 + \frac{\mu \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + k \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} = 0
-\end{eqnarray}
-\begin{eqnarray}
+\end{equation}
+\begin{equation}
  \xlabel{eqn:holographic-dim-EoM}
-\nf&& \eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} + 4 \mu \e ^{\varphi} - \nonumber\\\nf&&
+\eta ^{a b} \del _{a} \del _{b} X^{r} + 2 \mu ^2 \e ^{\varphi} X^{r} + 4 \mu \e ^{\varphi}
 - \frac{\mu ^2 \eta ^{a b}}{1 + \mu X^{r}} \left( 2 \del _{a} X^{r} + \mu \del _{a} X^{\nu} X_{\nu} \right) \del _{b} X^{\mu} X_{\mu} = 0 .
-\end{eqnarray}
+\end{equation}
 Assuming the perturbations on the string are small $\svert X^{A}\svert  \ll 1$, we get a massive simplification
@@
  \xlabel{eqn:holo-sol-implicit}
-\nf&& X^{r} (x) = X^{r} _{0} (x) - \nonumber\\\nf&& \xq - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) = \nonumber\\\nf&&\xq\xq = X^{r} _{0} (x) + \delta X^{r} (x),
+\nf&& X^{r} (x) = X^{r} _{0} (x) - 2 \mu \int \diff ^2 x' G (x ; x') \e ^{\varphi (x')} (2 + \mu X^{r} (x')) \nonumber\\\nf&&\xq\xq = X^{r} _{0} (x) + \delta X^{r} (x),
 \end{eqnarray}
@@
 From \neqref{eqn:holo-sol-implicit}, a recursion can be built, leading to a more explicit form
-\begin{eqnarray}
-X^{r} (x) &=& X^{r} _{0} (x) + \nonumber\\\nf&& + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times \nonumber\\\nf&& \times (2 + \mu X^{r} _{0} (x^{(k)})),
-\end{eqnarray}
+\begin{equation}
+X^{r} (x) = X^{r} _{0} (x) + \sum _{k \geq 1} (- 2)^{k} (\mu)^{2 k -1} \int \prod _{n = 1} ^{k} \diff ^{2} x^{(n)} G (x^{(n - 1)} ; x^{(n)}) \e ^{\varphi (x^{(n)})} \times (2 + \mu X^{r} _{0} (x^{(k)})),
+\end{equation}
 with $x^{(0)} \equiv x$.
@@
  \xlabel{eqn:new-coordinates-constraints-second-order}
- \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau &=& \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \nonumber\\\nf&&
-\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . 
+ \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau &=& \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \nonumber\\\nf
+\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma &=& \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . 
 \end{eqnarray}
 This turns Eq. \neqref{eqn:simplified-modified-wave-eqn} into
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:modified-wave-eqn-new}
-\nf&& \partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \nonumber\\\nf&&\xq
-+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \nonumber\\\nf&&\xq
+\partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu}
++ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu}
 + \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
-\end{eqnarray}
+\end{equation}
 Next, we introduce $X^{\mu} = \kappa (\tau, \sigma) W^{\mu} (\tau, \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out.
@@
  \xlabel{eqn:var-act-AC-KR}
-\frac{\delta S}{\delta \Delta ^{c d}} &=& - \frac{1}{4 \pi \alpha '} \Biggm( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \biggm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
+\frac{\delta S}{\delta \Delta ^{c d}} &=& - \frac{1}{4 \pi \alpha '} \Biggm( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \biggm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
 - \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \biggm) - \nonumber\\\nf&&
-- \biggl( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \biggr) \biggm( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \nonumber\\\nf&&
+- \biggl( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \biggr) \biggm( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}
 + \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \biggm) \Biggm) ,
@@
 which when required to vanish can be rearranged into
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:eqn:var-act-AC-KR-rear}
-\nf&& \Delta _{c d} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&\xq
-- \biggl( g + \frac{3 k \Delta}{4} \biggr) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm) - \nonumber\\\nf&&\xq
+\Delta _{c d} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
+- \biggl( g + \frac{3 k \Delta}{4} \biggr) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm)
 - \biggl( g + \frac{k \Delta}{2} \biggr) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
-\end{eqnarray}
+\end{equation}
 From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb--Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
@@
 where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb--Ramond field
-\begin{eqnarray}
+\begin{equation}
  \xlabel{eqn:1/f-KR}
-\frac{1}{\widetilde{f}} &=& \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
+\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
 - \biggl( g + \frac{3 k \Delta}{4} \biggr) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm) .
-\end{eqnarray}
+\end{equation}
 When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \neqref{eqn:1/f-KR} simplifies to
